### 2019-03-25 emsoft-2019/emsoft2019.tex
Init emsoft-2019 repository

%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}
\usepackage{listings}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{amsmath}

%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand{\statevar}{x_{k}}
\newcommand{\statevarmath}{$x_{k}\,$}
\newcommand{\qstatevar}{\hat{x}_{k}}
\newcommand{\qstatevarmath}{$\hat{x}_{k}\,$}
\newcommand{\statespace}{X}
\newcommand{\regioni}[1]{$X_{{#1}}$}
\newcommand{\regionimath}[1]{X_{{#1}}}
% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%
% end of the preamble, start of the body of the document source.
\begin{document}

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title is Hope}

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}

\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}
%\keywords{datasets, neural networks, gaze detection, text tagging}

%
% A "teaser" image appears between the author and affiliation information and the body 
% of the document, and typically spans the page. 
%\begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}

%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle

\section{Introduction}
\section{Background}
\section{Problem Description}
In this work we present an innovative method for the off-line design of robust MPC controllers (explicit), for linear time invariant systems.

To guarantee stability of the system at runtime, at design time the designer specifies the maximal disturbance value the system can tolerate: we call this numeric value \texttt{delta}. This delta has to be an upper bound for both errors generated by the system itself (e.g. noise from sensors) and disturbance coming from sources external to the system (e.g. friction).

The system is then designed to be robust against a maximal disturbance of value \texttt{delta}.

Among the sources of disturbance targeting the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design value \texttt{delta}.

In particular, (i) first we want to guarantee that the finite precision implementation of the controller produces an approximation error that is at most equal to delta.

(ii) Second, we want to take advantage of this disturbance delta, and reduce the arithmetic precision used for computations and storage, while still guarantee that the approximation error generated is bounded by delta. Our intuition is that a greater value for delta allows for a reduced precision for computations (e.g. with respect to 32bits).

Given an initial delta, we design the controller by solving an off-line optimization problem. We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. 
The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in this partitioning is called a region.
A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities $H_{i}\statevar<=K_{i}$.

We call \statespace\space the union of all regions $i$ is the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}

Each region $i$ is associated with an activation function $u_{i,k}=F_{i}x_{k}+G_{i}$.

%https://en.wikipedia.org/wiki/Polyhedron
%https://en.wikipedia.org/wiki/Polytope

A drawback in the design of explicit MPC is that both regions boundaries (H and K) and activation functions (F and G), have to be stored on the micro-controller. Usually these devices have limited memory in the order of KBs.

At runtime, the value of state variable \statevarmath  is compared against the polytopes bounds stored on the device: depending on the region containing \statevarmath, the corresponding activation function is computed.

This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.

\begin{lstlisting}[escapeinside={(*}{*)},label={lst:caseof}, caption=switch for region selection]
switch((*\statevarmath*)):
  case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{1}$*)
  case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}$*)
  case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}$*)
  ...
  case (*$ H_{n}\statevar<=K_{n}$*) then (*$u_{n}$*)
\end{lstlisting}

\section{Error Analysis}
Since (i) any measurement of the plant comes with some uncertainty (e.g. uncertainty from sensors) but also (ii) due to analog-digital conversion, the value of state variable \statevarmath comes with some numerical errors. The equation for \statevarmath is than defined as:
\begin{equation}
\qstatevar=\statevar + \texttt{err}
\end{equation}
where \statevarmath is the true (unknown) measure of the plant, while \qstatevarmath is the actual value.

\texttt{err} generates instability when it is time to verify which region \qstatevarmath belongs to: given the value of \statevarmath the region should be $i$, but because of \texttt{err}, actually region $j$ is selected. This scenario becomes more intuitive when \qstatevarmath falls \texttt{close} to the border between two generic regions $i$ and $j$, but in general it depends on the magnitude of \texttt{err}.

Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.

Our goal is to build a feasible geometrical space around the border between regions $i$ and $j$, where actually it is feasible that \statevarmath belongs to region $i$ but \qstatevarmath follows in region $j$.

We call this geometrical space the \texttt{tube}.

There are two main sources of error affecting the size of the \texttt{tube}: (i) the first one is caused by analog-digital conversion, happening just before the controller receives an estimation of the plant from the sensors. We call this error $\varepsilon_{A/D}$:

\begin{equation}\nonumber
\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
\end{equation}

Where $V_{cc}$ is the reference voltage of the converter (e.g. typical 5V) and $p$ represents the number of bit of the processor.

The second error affecting the size of the \texttt{tube} is caused by (ii) the quantization of region bounds in the memory of the micro-controller. We call this error $\varepsilon_{Q}$ for error quantization.

While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries. This second error can be regulated based on a trade-off among accuracy of the storage and memory save.

The total size of the \texttt{tube} is then:
\begin{equation}\label{eq:epsilontot}
\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
\end{equation}
\section{Finite Precision Implementation}
The output of the controller can be affected by two main errors: (i) the first one happens when the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), while the second one (ii) is the approximation error deriving from the finite precision arithmetic used to compute the activation function itself.

The effect of selecting the wrong activation function are the same as instability in the conditional switch reported in Listing \ref{lst:caseof}: suppose an hypothetic scenario where all the measurements were done in infinite precision and without any uncertainty, the controller $i$ would be activated, but because of these limitations actually $j$ is selected. The resulting error is then the difference between the two branches $i$ and $j$ in Listing \ref{lst:caseof}.

The system has to be robust against a mistake in choosing controller $i$ instead of $j$ only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.

In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:

%\begin{equation}
\begin{flalign}
\label{eq:maximization}
&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
\end{flalign}
%\end{equation}

Because of the linearity of the function $U_{i}-U_{j}$, and because of the convexity of regions $i$, $j$ it is enough to evaluate function (\ref{eq:maximization}) at the corners of the \texttt{tube}.

%The geometrical space where $\hat{X}$ activates $U_{i}$, while X would activate $U_{j}$ can be bounded thanks to a preliminary knowledge of the error $\varepsilon$: the distance between region $i$ and $j$ such that:
%\begin{equation}
%\hat{X}-X <= \varepsilon
%\end{equation}
%and $\hat{X}$ belongs to region $i$ but $X$ to $j$ (or vice-versa).

We compute (\ref{eq:maximization}) for all pairs of neighbor regions $i$ and $j$. Two regions are neighbors when they share at least a border.

In formula $\exists\; m,n \;$such that:
\begin{equation}
(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
\end{equation}
where $m$ and $n$ are the index of the two matching borders. We label $border_{i,j}$ the matching border shared among the two regions.

Starting from the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute (\ref{eq:maximization}) with: 
\begin{equation}
\begin{aligned}
border_{i,j} >= -\varepsilon\\
border_{i,j} <= \varepsilon
\end{aligned} 
\end{equation}
We call such geometrical space the \texttt{tube} between $i$ and $j$.

When \qstatevarmath belongs to the \texttt{tube}, it might be that $u_{i}$ is activated instead of $u_{j}$ (or vice-versa). Otherwise, when \qstatevarmath does not belong to the tube, no matter the error \texttt{err}, the right activation function is activated, and we consider only the error deriving from the computation itself.

Since computing $u_{i}$ introduces approximation error because of finite precision arithmetic, the system has to be robust against an error that is:

\begin{equation}\label{eq:fperror}
err(u_{i})_{p}=|(\hat{F}_{p}-F)\qstatevar+(\hat{G}_{p}-G)|
\end{equation}

where $\hat{F}$ and $\hat{G}$ represent the rounded values (in p bits) for the infinite precision values $F$ and $G$.

In (7) the domain of \qstatevarmath are all the points in region $i$, but also all the values in the \texttt{tube} between region $i$ and any of the neighbors of $i$. Even for values that do not belong to region $i$ it might be the case that $u_{i}$ is (erroneously) activated. In particular, this is true for values in the \texttt{tube}.

We compute (\ref{eq:fperror}) for all regions in \statespace\space and we take the maximum value:

\begin{equation}\label{eq:maxfperror}
\max_{\forall \regionimath{i}\;in\;\statespace} err(u_{i})_{p}
\end{equation}

The disturbance \texttt{delta} then has to be an upper bound to the summation of (\ref{eq:maximization}) and (\ref{eq:fperror}).

In formula:
\begin{flalign}
\label{eq:delta}
&delta >= \\
&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| + \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}

\section{Precision Tuning}
In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ generated by the quantization of hyperplanes H and K in a finite number of bits.
This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
The rule for $\varepsilon_{Q}$ is the following:
\begin{equation}\label{eq:quantizationlines}
\varepsilon_{Q} > (H-(\hat{H})_{p})\qstatevar+(K-(\hat{K})_{p})
\end{equation}
This inequality assures that the distance between any hyperplane represented in infinite precision, and the counter-part quantized in p bits, is bounded by $\varepsilon_{Q}$.

Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: find the minimal-precision for all the coefficients such that the inequality holds.

The main advantage in doing this (compared to fixing the precision a priori), is that the value of p can be tuned based on the memory available in the micro-controller.

To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for both floating-point and fixed-point expressions, able to provide a sound upper-bound to the maximal approximation error of an expression with respect to its real (infinite precision) counterpart. Because the magnitude of the round-off error depends on the range of input variable, all variables encoded in Daisy have to be bounded. 
Since the state variable \statevarmath is bounded, and F,G,H,K are vectors of constants, we can rely on Daisy for this verification step.

In a similar way, we use Daisy to solve the inequality in (\ref{eq:delta}) with respect to p.

\begin{flalign}
\label{eq:deltaminusmax}
&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}
We want to point out that the left side of the inequality is not parametrized in p. Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p. Again, we encode (\ref{eq:deltaminusmax}) in Daisy to detect what is the minimal precision that still satisfy the inequality.

\section{Algorithm}

\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},caption=design of robust MPC with verification and precision tuning,label={lst:alg}]
 delta=input()
 (*$\varepsilon_{Q}$*)=input()
 assert (delta>=0 and (*$\varepsilon_{Q}$*)>0)
 epsilon=(*$\varepsilon_{A/D}$*)+(*$\varepsilon_{Q}$*) #size of the tubes

 while True:
   design_robust_MPC(delta)
   maxUij = compute (*(\ref{eq:maximization})*) with size(tube)=(*$\varepsilon$*)
   if delta > maxUij:
     max_err=delta-maxUij
     UNI_MIX_precision(F,G,max_err)
     UNI_MIX_precision(H,K,(*$\varepsilon_{Q}$*))
     break
   else:
     delta=maxUij+(*$\varepsilon_{SAFE}$*)

\end{lstlisting}
In Listing \ref{lst:alg} we describe the procedure used to design an MPC controller robust to both (\ref{eq:maximization}) and (\ref{eq:maxfperror}).

First, the designer fixes the initial values for delta and $\varepsilon_{Q}$.

Even if it possible to assign value zero to delta\cite{imperial}, we do not encourage such initialization: it is going to fail the analysis at least once, because the error in (\ref{eq:maxfperror}) is going to be greater than zero (even in case (\ref{eq:maximization}) is zero). A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.

On the other hand, the value for $\varepsilon_{Q}$ has to be strictly greater than zero, otherwise we could rely on infinite precision for p in (\ref{eq:quantizationlines}).

Once input parameters are verified, we use MATLAB toolbox to design a controller with robustness value equal to delta.

Then, we compute (\ref{eq:maximization}) and we compare the result with delta: we are aware that the computation of (\ref{eq:maximization}) is not exact (even if it is done in 64bits precision), but usually the computation of (\ref{eq:maximization}) results in a value that is several orders of magnitude greater than the error of the computation itself. For this reason we consider this approximation error negligible from the point of view of our analysis.

Again, in the conditional inside the loop, delta has to be strictly greater than \texttt{maxUij} otherwise we do not have space for computing the precision for (\ref{eq:deltaminusmax}).

In case the conditional is verified,
the precision tuning phase starts.
For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is because we still need to satisfy (\ref{eq:delta}).
On the other hand, the quantization of polytopes borders (the region bounds in \statespace) can produce an error that is at most $\varepsilon_{Q}$, in this way we satisfy 
(\ref{eq:quantizationlines}).

In case the conditional fails and \texttt{maxUij} is greater than delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}. The same consideration done for the initialization values holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value delta for the controller, to a slight greater value than \texttt{maxUij}. In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop. Otherwise, in case of $\varepsilon_{SAFE}$ equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision values p, usually greater than 32 bits. 
We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions.
In case the analysis outputs a precision greater than 32bits, we fail in our goal.
Then, with a minimal alteration to the upper bound of delta, we sensibly reduced the precision needed for $F$ and $G$, with respect to the standard 32 bits.

\section{Experimental Results}

\subsection{Case of study: Inverted Pendulum}
%\begin{landscape}
%\begin{table*}[t]
%	\centering
%	\caption{Inverted Pendolum: delta}
%	\label{tab:ipd}
%	\begin{tabular}{r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
%		\multicolumn{4}{c}{} &
%		\multicolumn{2}{c}{Xbounds} &
%		\multicolumn{2}{c}{} &
%		\multicolumn{4}{c}{F and G} &
%		\multicolumn{4}{c}{H and K} 
%		\\
%		\multicolumn{1}{c}{delta}&
%		\multicolumn{1}{c}{eps} &
%		\multicolumn{1}{c}{regs} &
%		\multicolumn{1}{c}{hyps} &
%		\multicolumn{1}{c}{X0}&
%		\multicolumn{1}{c}{X1}&
%		\multicolumn{1}{c}{max\_Uij} &
%		\multicolumn{1}{c}{err} &
%		\multicolumn{1}{c}{tot.uni32}&
%		\multicolumn{1}{c}{tot.uni}&
%		\multicolumn{1}{c}{tot.mix}&
%		\multicolumn{1}{c}{\% saved}&
%		\multicolumn{1}{c}{tot.uni32}&
%		\multicolumn{1}{c}{tot.uni}&
%		\multicolumn{1}{c}{tot.mix}&
%		\multicolumn{1}{c}{\% saved}
%		%\multicolumn{1}{c}{\multirow{2}{*}{max|Ui-Uj|}} &
%		%\multicolumn{1}{c}{\multirow{2}{*}{FP\_err}} &
%		%\multicolumn{4}{c}{F and G} &
%		%\multicolumn{4}{c}{H and K} \\
%		%\cline{5-6}\cline{9-12}\cline{13-16} &
%		%\multicolumn{1}{c}{X0}
%		%\multicolumn{1}{c}{X1} &
%		
%	\end{tabular}
%\end{table*}
%\end{landscape}

\subsection{Case of study: 4d example}
\section{Related Work}
\section{Conclusions}

%\begin{table*}
%  \caption{Some Typical Commands}
%  \label{tab:commands}
%  \begin{tabular}{ccl}
%    \toprule
%    Command &A Number & Comments\\
%    \midrule
%    \texttt{{\char'134}author} & 100& Author \\
%    \texttt{{\char'134}table}& 300 & For tables\\
%    \texttt{{\char'134}table*}& 400& For wider tables\\
%    \bottomrule
%  \end{tabular}
%\end{table*}

%\begin{figure}[h]
%  \centering
%  \includegraphics[width=\linewidth]{sample-franklin}
%  \caption{1907 Franklin Model D roadster. Photograph by Harris \& Ewing, Inc. [Public domain], via Wikimedia Commons. (\url{https://goo.gl/VLCRBB}).}
%  \Description{The 1907 Franklin Model D roadster.}
%\end{figure}

%Some examples.  A paginated journal article \cite{Abril07}, an enumerated journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series (see 2a in spec. document)

\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

\end{document}

### 2019-03-26 emsoft-2019/main.tex
"Main file" now called main.tex

--- 2019-03-25 emsoft-2019/emsoft2019.tex
@@
 While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries.
-This second error can be regulated based on a trade-off among accuracy of the storage and memory save.
+This second error can be regulated based on a trade-off among accuracy of the storage and memory save~\cite{memoryMPC}.
 
@@
 \section{Finite Precision Implementation}
-The output of the controller can be affected by two main errors: (i) the first one happens when the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), while the second one (ii) is the approximation error deriving from the finite precision arithmetic used to compute the activation function itself.
+The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), while (ii) is the approximation error deriving from the finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.
 
-The effect of selecting the wrong activation function are the same as instability in the conditional switch reported in Listing \ref{lst:caseof}: suppose an hypothetic scenario where all the measurements were done in infinite precision and without any uncertainty, the controller $i$ would be activated, but because of these limitations actually $j$ is selected.
-The resulting error is then the difference between the two branches $i$ and $j$ in Listing \ref{lst:caseof}.
+The effect of selecting the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}.
+Suppose an hypothetic scenario where all the measurements were done in infinite precision and without any uncertainty: the controller $i$ would be activated.
 
-The system has to be robust against a mistake in choosing controller $i$ instead of $j$ only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
+Instead, because of these limitations controller $j$ is selected. The resulting error is then the difference between the output of the two branches $i$ and $j$.
+
+The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa) only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
 
 In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:
-
-%\begin{equation}
 \begin{flalign}
@@
 &\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
-&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
+&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
 \end{flalign}
-%\end{equation}
 
-Because of the linearity of the function $U_{i}-U_{j}$, and because of the convexity of regions $i$, $j$ it is enough to evaluate function (\ref{eq:maximization}) at the corners of the \texttt{tube}.
+Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$, $j$ it is enough to evaluate function (\ref{eq:maximization}) at the corners of the \texttt{tube}.
 
@@
 \end{equation}
-where $m$ and $n$ are the index of the two matching borders. We label $border_{i,j}$ the matching border shared among the two regions.
+where $m$ and $n$ are the index of the two matching borders. We label with $border_{i,j}$ the matching border shared among the two regions.
 
@@
 \end{equation}
+where $\varepsilon$ is defined in (\ref{eq:epsilontot}).
+
 We call such geometrical space the \texttt{tube} between $i$ and $j$.
@@
 \section{Precision Tuning}
-In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ generated by the quantization of hyperplanes H and K in a finite number of bits.
+In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is generated by the quantization of hyperplanes $H\statevar<=K$ in a finite number of bits.
 This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
@@
 \end{equation}
-This inequality assures that the distance between any hyperplane represented in infinite precision, and the counter-part quantized in p bits, is bounded by $\varepsilon_{Q}$.
+This inequality assures that the distance between any hyperplane represented in infinite precision, and its counter-part quantized in p bits, is bounded by $\varepsilon_{Q}$.
 
-Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: find the minimal-precision for all the coefficients such that the inequality holds.
+Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: find the minimal-precision p such that the inequality holds.
 
@@
 
-To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for both floating-point and fixed-point expressions, able to provide a sound upper-bound to the maximal approximation error of an expression with respect to its real (infinite precision) counterpart.
-Because the magnitude of the round-off error depends on the range of input variable, all variables encoded in Daisy have to be bounded.
-Since the state variable \statevarmath is bounded, and F,G,H,K are vectors of constants, we can rely on Daisy for this verification step.
+To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, able to provide a sound upper-bound to the maximal approximation error of an expression with respect to its real (infinite precision) counterpart.
+Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.
+
+Since the state variable \statevarmath is bounded, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.
 
@@
 Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p.
-Again, we encode (\ref{eq:deltaminusmax}) in Daisy to detect what is the minimal precision that still satisfy the inequality.
+We encode the inequality (\ref{eq:deltaminusmax}) in Daisy, to detect what is the minimal precision that satisfy the inequality.
 
@@
 
-Even if it possible to assign value zero to delta\cite{imperial}, we do not encourage such initialization: it is going to fail the analysis at least once, because the error in (\ref{eq:maxfperror}) is going to be greater than zero (even in case (\ref{eq:maximization}) is zero).
+Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization: it is going to fail the analysis at least once because the error in (\ref{eq:maxfperror}) is going to be greater than zero (even in case (\ref{eq:maximization}) is zero).
 A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.
@@
 
-In case the conditional is verified,
+In case the conditional statement is verified,
 the precision tuning phase starts.
@@
 In case the conditional fails and \texttt{maxUij} is greater than delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}.
-The same consideration done for the initialization values holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value delta for the controller, to a slight greater value than \texttt{maxUij}.
+The same consideration done for the initialization of input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value delta for the controller, to a value slightly greater than \texttt{maxUij}.
 In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop.
 Otherwise, in case of $\varepsilon_{SAFE}$ equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision values p, usually greater than 32 bits.
-We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions.
-In case the analysis outputs a precision greater than 32bits, we fail in our goal.
-Then, with a minimal alteration to the upper bound of delta, we sensibly reduced the precision needed for $F$ and $G$, with respect to the standard 32 bits.
+We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions: in case the analysis outputs a precision greater than 32bits, we fail in our goal.
+Then, with a minimal alteration to the upper bound of delta, we sensibly reduce the precision needed for $F$ and $G$, with respect to the standard 32 bits precision.
 

### 2019-03-26 emsoft-2019/main.tex
background subsections, and other fix to several formulas

@@
 \section{Background}
+\subsection{Robust MPC}
+\subsection{Finite Precision Arithmetic}
+\subsection{Daisy}
 \section{Problem Description}
@@
 To guarantee stability of the system at runtime, at design time the designer specifies the maximal disturbance value the system can tolerate: we call this numeric value \texttt{delta}.
-This delta has to be an upper bound for both errors generated by the system itself (e.g.
-noise from sensors) and disturbance coming from sources external to the system (e.g.
-friction).
 
-The system is then designed to be robust against a maximal disturbance of value \texttt{delta}.
+\texttt{delta} has to be an upper bound for both errors generated by the system itself (e.g. noise from sensors) and disturbance coming from sources external to the system (e.g. friction).
 
-Among the sources of disturbance targeting the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design value \texttt{delta}.
+The system is then designed to be robust against any kind of disturbance up to a maximal value \texttt{delta}.
+
+Among the sources of disturbance targeting the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design property.
 
@@
 
-(ii) Second, we want to take advantage of this disturbance delta, and reduce the arithmetic precision used for computations and storage, while still guarantee that the approximation error generated is bounded by delta.
+(ii) Second, we want to take advantage of this disturbance delta, and reduce the arithmetic precision used for computations and storage, while still guarantee that the approximation error is bounded by delta.
 Our intuition is that a greater value for delta allows for a reduced precision for computations (e.g.
-with respect to 32bits).
+with respect to 32bits precision).
 
-Given an initial delta, we design the controller by solving an off-line optimization problem.
+Given an initial delta, we find the right controller for a system by solving an off-line optimization problem.
 We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}.
-The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in this partitioning is called a region.
-A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities $H_{i}\statevar<=K_{i}$.
+The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called a region.
+A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar<=K_{i}$.
 
@@
 
-Each region $i$ is associated with an activation function $u_{i,k}=F_{i}x_{k}+G_{i}$.
-
 %https://en.wikipedia.org/wiki/Polyhedron
@@
 
+Each region $i$ is associated with an activation function $u_{i,k}=F_{i}x_{k}+G_{i}$.
+At runtime, the value of state variable \statevarmath  is compared against the polytopes bounds: depending on the region $i$ containing \statevarmath, the corresponding activation function $u_{i}$ is computed.
+
 A drawback in the design of explicit MPC is that both regions boundaries (H and K) and activation functions (F and G), have to be stored on the micro-controller.
-Usually these devices have limited memory in the order of KBs.
-
-At runtime, the value of state variable \statevarmath  is compared against the polytopes bounds stored on the device: depending on the region containing \statevarmath, the corresponding activation function is computed.
+Usually these devices have limited memory, in the order of KBs.
 
@@
 
-\texttt{err} generates instability when it is time to verify which region \qstatevarmath belongs to: given the value of \statevarmath the region should be $i$, but because of \texttt{err}, actually region $j$ is selected.
-This scenario becomes more intuitive when \qstatevarmath falls \texttt{close} to the border between two generic regions $i$ and $j$, but in general it depends on the magnitude of \texttt{err}.
+\texttt{err} generates instability when it is time to verify which region \qstatevarmath belongs to: it can happen that \statevarmath satisfies the bounds of region $i$, but because of \texttt{err}, \qstatevarmath belongs to region $j$.
+This scenario becomes more intuitive when \qstatevarmath falls \texttt{close} to the border between two neighbor regions $i$ and $j$, but in general this instability depends on the magnitude of error \texttt{err}.
 
@@
 
-Our goal is to build a feasible geometrical space around the border between regions $i$ and $j$, where actually it is feasible that \statevarmath belongs to region $i$ but \qstatevarmath follows in region $j$.
-
+Our goal is to build a feasible geometrical space around the border between two neighbor regions $i$ and $j$, where actually it is feasible that \statevarmath belongs to region $i$ but \qstatevarmath follows in region $j$ (or vice-versa).
 We call this geometrical space the \texttt{tube}.
@@
 \section{Finite Precision Implementation}
-The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), while (ii) is the approximation error deriving from the finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.
+The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), and (ii) the approximation error deriving from finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.
 
-The effect of selecting the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}.
-Suppose an hypothetic scenario where all the measurements were done in infinite precision and without any uncertainty: the controller $i$ would be activated.
+The effect of picking the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}.
 
-Instead, because of these limitations controller $j$ is selected. The resulting error is then the difference between the output of the two branches $i$ and $j$.
+In an hypothetic scenario where all the measurements were done in infinite precision arithmetic and without any uncertainty, we assume the controller $i$ would be activated.
+Instead, because we cannot rely on infinite precision, controller $j$ is selected.
 
-The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa) only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
+The error committed is the difference between the output of the two branches $i$ and $j$.
+
+The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa), only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
+Moveover, we are interested in the worst case scenario where is maximized the difference between the activation functions of any two neighbor regions.
 
@@
 \end{flalign}
-
-Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$, $j$ it is enough to evaluate function (\ref{eq:maximization}) at the corners of the \texttt{tube}.
+where \statevarmath belongs to the \texttt{tube} between region $i$ and $j$.
+Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$ and $j$, it is enough to evaluate function (\ref{eq:maximization}) at the corner points of the \texttt{tube}, instead of solving a maximization problem.
 
@@
 \begin{aligned}
-border_{i,j} >= -\varepsilon\\
-border_{i,j} <= \varepsilon
+(border_{i,j} >= -\varepsilon) \land
+(border_{i,j} <= \varepsilon)
 \end{aligned} 
 \end{equation}
-where $\varepsilon$ is defined in (\ref{eq:epsilontot}).
-
-We call such geometrical space the \texttt{tube} between $i$ and $j$.
+where $\varepsilon$ is defined in (\ref{eq:epsilontot}). We call such geometrical space the \texttt{tube} between $i$ and $j$.
 
 When \qstatevarmath belongs to the \texttt{tube}, it might be that $u_{i}$ is activated instead of $u_{j}$ (or vice-versa).
-Otherwise, when \qstatevarmath does not belong to the tube, no matter the error \texttt{err}, the right activation function is activated, and we consider only the error deriving from the computation itself.
+Otherwise, when \qstatevarmath does not belong to the tube, no matter the error $\varepsilon$, the right activation function is activated, and we consider only the error deriving from the computation itself.
 
@@
 In (7) the domain of \qstatevarmath are all the points in region $i$, but also all the values in the \texttt{tube} between region $i$ and any of the neighbors of $i$.
-Even for values that do not belong to region $i$ it might be the case that $u_{i}$ is (erroneously) activated.
-In particular, this is true for values in the \texttt{tube}.
+Even if some points in the tube do not belong to region $i$, it might that $u_{i}$ is (erroneously) activated.
 
-We compute (\ref{eq:fperror}) for all regions in \statespace\space and we take the maximum value:
+We compute (\ref{eq:fperror}) for all regions in \statespace\space and we take the maximum value of the error (worst case):
 
@@
 
-The disturbance \texttt{delta} then has to be an upper bound to the summation of (\ref{eq:maximization}) and (\ref{eq:fperror}).
+The disturbance \texttt{delta}  has to be an upper bound to the summation of (\ref{eq:maximization}) and (\ref{eq:maxfperror}).
 
@@
 \begin{equation}\label{eq:quantizationlines}
-\varepsilon_{Q} > (H-(\hat{H})_{p})\qstatevar+(K-(\hat{K})_{p})
+\varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
 \end{equation}
-This inequality assures that the distance between any hyperplane represented in infinite precision, and its counter-part quantized in p bits, is bounded by $\varepsilon_{Q}$.
+This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$.
 
-Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: find the minimal-precision p such that the inequality holds.
+Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: assign an arbitrary value to $\varepsilon_{Q}$ and find the minimal-precision p such that the inequality holds.
 
-The main advantage in doing this (compared to fixing the precision a priori), is that the value of p can be tuned based on the memory available in the micro-controller.
+The main advantage in this approach (compared to fixing the precision p a priori), is that the value of p can be tuned based on the memory availability in the micro-controller.
 
-To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, able to provide a sound upper-bound to the maximal approximation error of an expression with respect to its real (infinite precision) counterpart.
+To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, ables to provide a sound upper-bound to the maximal approximation error of a formula with respect to its real (infinite precision) counterpart.
 Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.
 
-Since the state variable \statevarmath is bounded, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.
+Since the state variable \statevarmath is bounded by \statespace, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.
 
-In a similar way, we use Daisy to solve the inequality in (\ref{eq:delta}) with respect to p.
-
+In a similar way, we use Daisy to solve the inequality in (\ref{eq:delta}) with respect to p:
 \begin{flalign}
@@
 \end{flalign}
-We want to point out that the left side of the inequality is not parametrized in p.
+
+Be aware that the left side of the inequality is not parametrized in p.
 Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p.
-We encode the inequality (\ref{eq:deltaminusmax}) in Daisy, to detect what is the minimal precision that satisfy the inequality.
+After we come up with a numerical value for the left side of the inequality, we encode (\ref{eq:deltaminusmax}) in Daisy in the same way done for (\ref{eq:quantizationlines}).
 
@@
  assert (delta>=0 and (*$\varepsilon_{Q}$*)>0)
- epsilon=(*$\varepsilon_{A/D}$*)+(*$\varepsilon_{Q}$*) #size of the tubes
+ (*$\varepsilon$*)=(*$\varepsilon_{A/D}$*)+(*$\varepsilon_{Q}$*)
 
@@
      delta=maxUij+(*$\varepsilon_{SAFE}$*)
-
 \end{lstlisting}
-In Listing \ref{lst:alg} we describe the procedure used to design an MPC controller robust to both (\ref{eq:maximization}) and (\ref{eq:maxfperror}).
+In Listing \ref{lst:alg} we describe the procedure used to design a robust MPC controller such that (\ref{eq:delta}) is respected.
 
@@
 
-Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization: it is going to fail the analysis at least once because the error in (\ref{eq:maxfperror}) is going to be greater than zero (even in case (\ref{eq:maximization}) is zero).
+Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization value: it is going to fail the analysis (at least) for the first iteration because the error in (\ref{eq:maxfperror}) is going to be greater than zero (in the remote scenario where  (\ref{eq:maximization}) is equal to zero).
 A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.
@@
 the precision tuning phase starts.
-For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is because we still need to satisfy (\ref{eq:delta}).
+For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is exactly what is described in (\ref{eq:deltaminusmax}).
+
 On the other hand, the quantization of polytopes borders (the region bounds in \statespace) can produce an error that is at most $\varepsilon_{Q}$, in this way we satisfy 
@@
 
-In case the conditional fails and \texttt{maxUij} is greater than delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}.
-The same consideration done for the initialization of input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value delta for the controller, to a value slightly greater than \texttt{maxUij}.
+In case the conditional fails and \texttt{maxUij} is greater than (or equal to) delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}.
+The same consideration done for the initialization of input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value for delta, to a value slightly greater than \texttt{maxUij}.
 In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop.
-Otherwise, in case of $\varepsilon_{SAFE}$ equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision values p, usually greater than 32 bits.
+Otherwise, in case $\varepsilon_{SAFE}$ is equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision value for p, usually greater than 32 bits.
 We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions: in case the analysis outputs a precision greater than 32bits, we fail in our goal.

### 2019-03-26 emsoft-2019/main.tex
fix problem description

@@
 \section{Problem Description}
-In this work we present an innovative method for the off-line design of robust MPC controllers (explicit), for linear time invariant systems.
+In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.
 
-To guarantee stability of the system at runtime, at design time the designer specifies the maximal disturbance value the system can tolerate: we call this numeric value \texttt{delta}.
+Consider the (discrete) state space model:
+\begin{flalign}\label{eq:statespacemodel}
+& x_{k+1} = A\statevar + Bu_{k}
+%& y_{k} = C\statevar\nonumber
+\end{flalign}
 
-\texttt{delta} has to be an upper bound for both errors generated by the system itself (e.g. noise from sensors) and disturbance coming from sources external to the system (e.g. friction).
+where $\statevar\in\mathbb{R}_{n}$ is the state variable at time $k$, $u_{k}$ is the scalar control input, and $A\in\mathbb{R}^{nxn}$ and $B\in\mathbb{R}^{n}$ guarantee the stability of the system at runtime.
 
-The system is then designed to be robust against any kind of disturbance up to a maximal value \texttt{delta}.
-
-Among the sources of disturbance targeting the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design property.
-
-In particular, (i) first we want to guarantee that the finite precision implementation of the controller produces an approximation error that is at most equal to delta.
-
-(ii) Second, we want to take advantage of this disturbance delta, and reduce the arithmetic precision used for computations and storage, while still guarantee that the approximation error is bounded by delta.
-Our intuition is that a greater value for delta allows for a reduced precision for computations (e.g.
-with respect to 32bits precision).
-
-Given an initial delta, we find the right controller for a system by solving an off-line optimization problem.
+The controller $u_{k}$ for (\ref{eq:statespacemodel}) is found by solving an off-line optimization problem.
 We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}.
-The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called a region.
+The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called region.
 A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar<=K_{i}$.
 
-We call \statespace\space the union of all regions $i$ is the domain of the state variable $x_{k}$:
+We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
 \begin{equation}
@@
 \end{lstlisting}
+
+At design time, the designer specifies the maximal disturbance value the controller can tolerate: we call this numerical value \texttt{delta}.
+
+\texttt{delta} has to be an upper bound for both errors generated by the system itself (e.g.
+noise from sensors) and disturbance coming from sources external to the system (e.g.
+friction).
+The controller is then designed to be robust against any kind of disturbance up to a maximal value \texttt{delta}.
+
+Among the sources of disturbance targeting the output of the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design property.
+
+In particular, (i) first we want to guarantee that the finite precision implementation of the controller produces an approximation error that is at most equal to delta.
+
+(ii) Second, we want to take advantage of this disturbance delta, and reduce the arithmetic precision used for computations and storage, while still guarantee that the approximation error is bounded by delta.
+Our intuition is that a greater value for delta allows for a reduced precision for computations (e.g.
+with respect to 32bits precision).
 

### 2019-04-02 emsoft-2019/Motiv.tex
seperating_tex_files

\section{Motivation}
	In this section, we use a classical control example to explain the motivation behind this work. Consider the problem of designing stablizing control for an inverted pendulum which takes (polytopic) constraints over state variables and control inputs into account. The linearized continuous-time description for the open-loop system's dynamics is as follows:
	\begin{equation}
		\begin{bmatrix}
			\dot \theta\\
			\dot \omega
		\end{bmatrix}=
		\begin{bmatrix}
			0 & 1\\
			\frac{g}{l}& \frac{-b}{ml^2}		
		\end{bmatrix}
		\begin{bmatrix}
			\theta\\
			\omega
		\end{bmatrix}+
		\begin{bmatrix}
			0\\
			\frac{1}{ml^2}
		\end{bmatrix}u
		\label{eq:pendul_ss}
	\end{equation}
	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitional acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient and $L$ the length of the bar. To design the controller, one has to first descretize the dynamics in $\eqref{eq:pendul_ss}$ with respect to an appropriate sample time $T_s$. Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point while always $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$. While there are many control schemes which can be used to stablize the system (e.g. LQR, state feedback), adding polytopic constraints, MPC schemes will be the best choice. 
	%In literature, many control schemes are proposed for stablizing the system around the equilibrium point. 
	%In order to design a controller which takes additional safety constraints are taken into account, model predictive control (MPC) schemes seem to be best candidate. 
	However, one major challenge for implementing model predictive controllers over embedded systems will be to solve MPC optimality problem within each time step. Since the system under consideration is LTI, one can use explicit MPC scheme proposed in [Bemporad:2002] which computes partitions over state space together with affine functions which computes the optimal control input over their corresponding partition. For the inverted-pedulum example, the computed optimal control contains $14$ partitions shown in Fig \ref{fig:pendulum_reg}.
	%To overcome this issue, in [Bemporad:2002], explicite MPC, a multi-parametric programming based approach is proposed for LTI systems. 
	In practice, EMPC will be implemented over relatively low-price embedded systems which have limited memory capacity and computational power. Computing the optimal control input can be efficiently done using for example binary tree search. However, the memory limit is more serious as it increases proportional to the number of partitions.	Therefore, one direction is to explore ways to reduce required memory.
	On the other hand, most of the industrial embedded systems over which EMPC is implemented, only support fixed point arithmetic. Using fixed point arithmetic, will cause approximation error that is inversely proportional to the number of bits used. This approximation error must be considered since it might lead into violation of problem constraints. Therefore, one need to formulate the problem as robust MPC to count for disturbance input $|\omega|\leq \bar\omega$. Setting the number of bits for storing different variables, one can compute the upper bound for approximation error, $\bar\omega$. However, we would like to achieve the minimum number of bits that reduces memory requirements. To that end, one approach is to start with an initial $\bar \omega$; design an explicit robust MPC controller with respect to $\bar \omega$ and to use state of the art fixed-point error analyzers to decide for the number of required bits for saving each parameter. Again, back to inverted pendulum example, choosing $\bar \omega=0.1$, we design a robust MPC controller with partitions given in Fig. \ref{fig:pendulum_reg} (b). Now, in order to decide for the smallest number of bits, we use the floating point analysing tool, Daisy, to provide us with minimal uniform and mixed fixed-point reperesentation.

%	\begin{figure}
%		\includegraphics[width=.25\textwidth]{Figs/partition_order2_noise.eps};
%	\end{figure}

	\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
	minimum height=3em, minimum width=6em]
	\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	\begin{figure*}[t]
		\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
			\centering
			\node [block, pin={[pinstyle]above:$\delta=\delta_0$},
			node distance=5cm] (RMPC) {Robust MPC design};
			%\node[right of=RMPC](partitions){\includegraphics[width=.25\textwidth]{Figs/partition_order2_noise.pdf}};
			\node [block, right of=RMPC,
			node distance=5cm,text width=3cm] (mixed) {Mixed precision analysis};
			\node [draw, fill=blue!20, diamond, 
			minimum height=3em, minimum width=3em, right of=mixed,
			node distance=5cm] (decide) {Is memory violated?};
			\node [block, right of=decide,
			node distance=3cm] (done) {Done};
			\node [block, below of= decide,
			node distance=3cm] (delta) {increase $\delta$};

			\draw [draw,->] (RMPC) -- node [pos=-.1] {}(mixed);
			\draw [->] (mixed) -- node [name=aaa] {}(decide);
			\draw [->] (decide) -- node [above,pos=.3] {Yes} (done);
			\draw [->] (decide) -- node[pos=0.99] {} 
			node [] {No} (delta);
			\draw [->] (delta) -| node [above] {$\delta$} (RMPC);

	\end{tikzpicture}
	\caption{high level description of RMPC with Daisy}
	\label{fig:overview}
\end{figure*}

### 2019-04-02 emsoft-2019/Motiv.tex
some updates

@@
 	\end{equation}
-	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitional acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient and $L$ the length of the bar.
+	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitational acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient and $L$ the length of the bar.
 To design the controller, one has to first descretize the dynamics in $\eqref{eq:pendul_ss}$ with respect to an appropriate sample time $T_s$.
 Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point while always $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$.
-While there are many control schemes which can be used to stablize the system (e.g.
-LQR, state feedback), adding polytopic constraints, MPC schemes will be the best choice.
+\\
+	While there are many control schemes which can be used to stablize the system (e.g. LQR, state feedback), adding polytopic constraints, MPC schemes will be the best choice. 
 	%In literature, many control schemes are proposed for stablizing the system around the equilibrium point. 
@@
 	However, one major challenge for implementing model predictive controllers over embedded systems will be to solve MPC optimality problem within each time step.
-Since the system under consideration is LTI, one can use explicit MPC scheme proposed in [Bemporad:2002] which computes partitions over state space together with affine functions which computes the optimal control input over their corresponding partition.
-For the inverted-pedulum example, the computed optimal control contains $14$ partitions shown in Fig \ref{fig:pendulum_reg}.
+Since the system under consideration is LTI, one can use explicit MPC scheme proposed in [Bemporad:2002] which computes partitions over state space together with affine functions which are used to compute the optimal control input over their corresponding partition.
+For the inverted-pendulum example, the computed controller contains $12$, over each an affine function is provided for generating the control input.\\
 	%To overcome this issue, in [Bemporad:2002], explicite MPC, a multi-parametric programming based approach is proposed for LTI systems. 
@@
 Computing the optimal control input can be efficiently done using for example binary tree search.
-However, the memory limit is more serious as it increases proportional to the number of partitions.	Therefore, one direction is to explore ways to reduce required memory.
+However, the memory limit is more cruicial as it increases proportional to the number of partitions.	Therefore, we would like to explore ways to reduce required memory for saving different coefficients corresponding to the controllers.
 	On the other hand, most of the industrial embedded systems over which EMPC is implemented, only support fixed point arithmetic.
-Using fixed point arithmetic, will cause approximation error that is inversely proportional to the number of bits used.
-This approximation error must be considered since it might lead into violation of problem constraints.
-Therefore, one need to formulate the problem as robust MPC to count for disturbance input $|\omega|\leq \bar\omega$.
-Setting the number of bits for storing different variables, one can compute the upper bound for approximation error, $\bar\omega$.
-However, we would like to achieve the minimum number of bits that reduces memory requirements.
-To that end, one approach is to start with an initial $\bar \omega$; design an explicit robust MPC controller with respect to $\bar \omega$ and to use state of the art fixed-point error analyzers to decide for the number of required bits for saving each parameter.
-Again, back to inverted pendulum example, choosing $\bar \omega=0.1$, we design a robust MPC controller with partitions given in Fig.
-\ref{fig:pendulum_reg} (b).
-Now, in order to decide for the smallest number of bits, we use the floating point analysing tool, Daisy, to provide us with minimal uniform and mixed fixed-point reperesentation.
-
-%	\begin{figure}
-%		\includegraphics[width=.25\textwidth]{Figs/partition_order2_noise.eps};
-%	\end{figure}
+Using fixed point arithmetic, will cause approximation error that is inversely proportional to the number of bits used for representing each variable.
+It is necessary to count for approximation error as it might lead into violation of the constraints.
+Therefore, one needs to formulate the problem as robust EMPC to count for disturbance input $|\delta|\leq \Delta$ which is summed up with the control input torque $u$ in each time step.
+%Setting the number of bits for storing different variables, one can compute the upper bound for approximation error, $\bar\omega$.
+	%However, we would like to achieve the minimum number of bits to reduce memory requirements.
+	Overlay, we would like to design a robust explicit model predictive controller, taking into account errors resulted by fixed-point arithmetic and more importantly, to come up with a set of varying precision assignment that covers all the coefficients that must be saved over the embedded system.
+To that end, one approach is to start with an initial $\Delta$; design a robust explicit MPC controller with respect to $\Delta$ and to use state of the art fixed-point error analyzers to decide for the number of bits for saving every parameter characterizing the controller.
+Figure \ref{fig:overview} gives an overview of our proposed setup.\\
+	Again, back to inverted pendulum example, choosing $\Delta=0$, we design an explicit MPC which contains $12$ regions and the same number of controllers.
+However, this value for $\Delta$ is not realizable as error resulted from fixed-point implementation cannot become zero.
+Therefore, we go ahead and choose $\Delta=0.1$.
+Solving Robust EMPC problem for the new disturbance bound gives $14$ controllers.
+Next, we ask Daisy to provide us with fixed-point precisions for every variable that respects $\Delta$.
+Using the output of Daisy, we are able to reduce memory requirements for the embedded systems up-to $20\%$ comparing to the case that uniform fixed-point precision is used.
 
@@
 			node distance=5cm] (RMPC) {Robust MPC design};
-			%\node[right of=RMPC](partitions){\includegraphics[width=.25\textwidth]{Figs/partition_order2_noise.pdf}};
+			\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
 			\node [block, right of=RMPC,
@@
 			node [] {No} (delta);
-			\draw [->] (delta) -| node [above] {$\delta$} (RMPC);
+			\draw [->] (delta) -| node [above] {} (RMPC);
 

### 2019-04-02 emsoft-2019/main.tex
modified:   main.tex
some updates

--- 2019-03-26 emsoft-2019/main.tex
@@
 \usepackage{amsmath}
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows}
+\usepackage{graphicx}
 
@@
 
-\section{Introduction}
-\section{Background}
-\section{Problem Description}
-In this work we present an innovative method for the off-line design of robust MPC controllers (explicit), for linear time invariant systems.
-
-To guarantee stability of the system at runtime, at design time the designer specifies the maximal disturbance value the system can tolerate: we call this numeric value \texttt{delta}.
-This delta has to be an upper bound for both errors generated by the system itself (e.g.
-noise from sensors) and disturbance coming from sources external to the system (e.g.
-friction).
-
-The system is then designed to be robust against a maximal disturbance of value \texttt{delta}.
-
-Among the sources of disturbance targeting the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design value \texttt{delta}.
-
-In particular, (i) first we want to guarantee that the finite precision implementation of the controller produces an approximation error that is at most equal to delta.
-
-(ii) Second, we want to take advantage of this disturbance delta, and reduce the arithmetic precision used for computations and storage, while still guarantee that the approximation error generated is bounded by delta.
-Our intuition is that a greater value for delta allows for a reduced precision for computations (e.g.
-with respect to 32bits).
-
-Given an initial delta, we design the controller by solving an off-line optimization problem.
-We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}.
-The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in this partitioning is called a region.
-A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities $H_{i}\statevar<=K_{i}$.
-
-We call \statespace\space the union of all regions $i$ is the domain of the state variable $x_{k}$:
-\begin{equation}
-\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
-\end{equation}
-
-Each region $i$ is associated with an activation function $u_{i,k}=F_{i}x_{k}+G_{i}$.
-
-%https://en.wikipedia.org/wiki/Polyhedron
-%https://en.wikipedia.org/wiki/Polytope
-
-A drawback in the design of explicit MPC is that both regions boundaries (H and K) and activation functions (F and G), have to be stored on the micro-controller.
-Usually these devices have limited memory in the order of KBs.
-
-At runtime, the value of state variable \statevarmath  is compared against the polytopes bounds stored on the device: depending on the region containing \statevarmath, the corresponding activation function is computed.
-
-This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.
-
-\begin{lstlisting}[escapeinside={(*}{*)},label={lst:caseof}, caption=switch for region selection]
-switch((*\statevarmath*)):
-  case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{1}$*)
-  case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}$*)
-  case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}$*)
-  ...
-  case (*$ H_{n}\statevar<=K_{n}$*) then (*$u_{n}$*)
-\end{lstlisting}
-
-\section{Error Analysis}
-Since (i) any measurement of the plant comes with some uncertainty (e.g.
-uncertainty from sensors) but also (ii) due to analog-digital conversion, the value of state variable \statevarmath comes with some numerical errors.
-The equation for \statevarmath is than defined as:
-\begin{equation}
-\qstatevar=\statevar + \texttt{err}
-\end{equation}
-where \statevarmath is the true (unknown) measure of the plant, while \qstatevarmath is the actual value.
-
-\texttt{err} generates instability when it is time to verify which region \qstatevarmath belongs to: given the value of \statevarmath the region should be $i$, but because of \texttt{err}, actually region $j$ is selected.
-This scenario becomes more intuitive when \qstatevarmath falls \texttt{close} to the border between two generic regions $i$ and $j$, but in general it depends on the magnitude of \texttt{err}.
-
-Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.
-
-Our goal is to build a feasible geometrical space around the border between regions $i$ and $j$, where actually it is feasible that \statevarmath belongs to region $i$ but \qstatevarmath follows in region $j$.
-
-We call this geometrical space the \texttt{tube}.
-
-There are two main sources of error affecting the size of the \texttt{tube}: (i) the first one is caused by analog-digital conversion, happening just before the controller receives an estimation of the plant from the sensors.
-We call this error $\varepsilon_{A/D}$:
-
-\begin{equation}\nonumber
-\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
-\end{equation}
-
-Where $V_{cc}$ is the reference voltage of the converter (e.g. typical 5V) and $p$ represents the number of bit of the processor.
-
-The second error affecting the size of the \texttt{tube} is caused by (ii) the quantization of region bounds in the memory of the micro-controller.
-We call this error $\varepsilon_{Q}$ for error quantization.
-
-While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries.
-This second error can be regulated based on a trade-off among accuracy of the storage and memory save~\cite{memoryMPC}.
-
-The total size of the \texttt{tube} is then:
-\begin{equation}\label{eq:epsilontot}
-\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
-\end{equation}
-\section{Finite Precision Implementation}
-The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), while (ii) is the approximation error deriving from the finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.
-
-The effect of selecting the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}.
-Suppose an hypothetic scenario where all the measurements were done in infinite precision and without any uncertainty: the controller $i$ would be activated.
-
-Instead, because of these limitations controller $j$ is selected. The resulting error is then the difference between the output of the two branches $i$ and $j$.
-
-The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa) only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
-
-In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:
-\begin{flalign}
-\label{eq:maximization}
-&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
-&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
-\end{flalign}
-
-Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$, $j$ it is enough to evaluate function (\ref{eq:maximization}) at the corners of the \texttt{tube}.
-
-%The geometrical space where $\hat{X}$ activates $U_{i}$, while X would activate $U_{j}$ can be bounded thanks to a preliminary knowledge of the error $\varepsilon$: the distance between region $i$ and $j$ such that:
-%\begin{equation}
-%\hat{X}-X <= \varepsilon
-%\end{equation}
-%and $\hat{X}$ belongs to region $i$ but $X$ to $j$ (or vice-versa).
-
-We compute (\ref{eq:maximization}) for all pairs of neighbor regions $i$ and $j$. Two regions are neighbors when they share at least a border.
-
-In formula $\exists\; m,n \;$such that:
-\begin{equation}
-(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
-\end{equation}
-where $m$ and $n$ are the index of the two matching borders. We label with $border_{i,j}$ the matching border shared among the two regions.
-
-Starting from the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute (\ref{eq:maximization}) with: 
-\begin{equation}
-\begin{aligned}
-border_{i,j} >= -\varepsilon\\
-border_{i,j} <= \varepsilon
-\end{aligned} 
-\end{equation}
-where $\varepsilon$ is defined in (\ref{eq:epsilontot}).
-
-We call such geometrical space the \texttt{tube} between $i$ and $j$.
-
-When \qstatevarmath belongs to the \texttt{tube}, it might be that $u_{i}$ is activated instead of $u_{j}$ (or vice-versa).
-Otherwise, when \qstatevarmath does not belong to the tube, no matter the error \texttt{err}, the right activation function is activated, and we consider only the error deriving from the computation itself.
-
-Since computing $u_{i}$ introduces approximation error because of finite precision arithmetic, the system has to be robust against an error that is:
-
-\begin{equation}\label{eq:fperror}
-err(u_{i})_{p}=|(\hat{F}_{p}-F)\qstatevar+(\hat{G}_{p}-G)|
-\end{equation}
-
-where $\hat{F}$ and $\hat{G}$ represent the rounded values (in p bits) for the infinite precision values $F$ and $G$.
-
-In (7) the domain of \qstatevarmath are all the points in region $i$, but also all the values in the \texttt{tube} between region $i$ and any of the neighbors of $i$.
-Even for values that do not belong to region $i$ it might be the case that $u_{i}$ is (erroneously) activated.
-In particular, this is true for values in the \texttt{tube}.
-
-We compute (\ref{eq:fperror}) for all regions in \statespace\space and we take the maximum value:
-
-\begin{equation}\label{eq:maxfperror}
-\max_{\forall \regionimath{i}\;in\;\statespace} err(u_{i})_{p}
-\end{equation}
-
-The disturbance \texttt{delta} then has to be an upper bound to the summation of (\ref{eq:maximization}) and (\ref{eq:fperror}).
-
-In formula:
-\begin{flalign}
-\label{eq:delta}
-&delta >= \\
-&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| + \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
-\end{flalign}
-
-\section{Precision Tuning}
-In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is generated by the quantization of hyperplanes $H\statevar<=K$ in a finite number of bits.
-This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
-The rule for $\varepsilon_{Q}$ is the following:
-\begin{equation}\label{eq:quantizationlines}
-\varepsilon_{Q} > (H-(\hat{H})_{p})\qstatevar+(K-(\hat{K})_{p})
-\end{equation}
-This inequality assures that the distance between any hyperplane represented in infinite precision, and its counter-part quantized in p bits, is bounded by $\varepsilon_{Q}$.
-
-Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: find the minimal-precision p such that the inequality holds.
-
-The main advantage in doing this (compared to fixing the precision a priori), is that the value of p can be tuned based on the memory available in the micro-controller.
-
-To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, able to provide a sound upper-bound to the maximal approximation error of an expression with respect to its real (infinite precision) counterpart.
-Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.
-
-Since the state variable \statevarmath is bounded, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.
-
-In a similar way, we use Daisy to solve the inequality in (\ref{eq:delta}) with respect to p.
-
-\begin{flalign}
-\label{eq:deltaminusmax}
-&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
-& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
-\end{flalign}
-We want to point out that the left side of the inequality is not parametrized in p.
-Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p.
-We encode the inequality (\ref{eq:deltaminusmax}) in Daisy, to detect what is the minimal precision that satisfy the inequality.
-
-\section{Algorithm}
-
-\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},caption=design of robust MPC with verification and precision tuning,label={lst:alg}]
- delta=input()
- (*$\varepsilon_{Q}$*)=input()
- assert (delta>=0 and (*$\varepsilon_{Q}$*)>0)
- epsilon=(*$\varepsilon_{A/D}$*)+(*$\varepsilon_{Q}$*) #size of the tubes
-
- while True:
-   design_robust_MPC(delta)
-   maxUij = compute (*(\ref{eq:maximization})*) with size(tube)=(*$\varepsilon$*)
-   if delta > maxUij:
-     max_err=delta-maxUij
-     UNI_MIX_precision(F,G,max_err)
-     UNI_MIX_precision(H,K,(*$\varepsilon_{Q}$*))
-     break
-   else:
-     delta=maxUij+(*$\varepsilon_{SAFE}$*)
-
-\end{lstlisting}
-In Listing \ref{lst:alg} we describe the procedure used to design an MPC controller robust to both (\ref{eq:maximization}) and (\ref{eq:maxfperror}).
-
-First, the designer fixes the initial values for delta and $\varepsilon_{Q}$.
-
-Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization: it is going to fail the analysis at least once because the error in (\ref{eq:maxfperror}) is going to be greater than zero (even in case (\ref{eq:maximization}) is zero).
-A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.
-
-On the other hand, the value for $\varepsilon_{Q}$ has to be strictly greater than zero, otherwise we could rely on infinite precision for p in (\ref{eq:quantizationlines}).
-
-Once input parameters are verified, we use MATLAB toolbox to design a controller with robustness value equal to delta.
-
-Then, we compute (\ref{eq:maximization}) and we compare the result with delta: we are aware that the computation of (\ref{eq:maximization}) is not exact (even if it is done in 64bits precision), but usually the computation of (\ref{eq:maximization}) results in a value that is several orders of magnitude greater than the error of the computation itself.
-For this reason we consider this approximation error negligible from the point of view of our analysis.
-
-Again, in the conditional inside the loop, delta has to be strictly greater than \texttt{maxUij} otherwise we do not have space for computing the precision for (\ref{eq:deltaminusmax}).
-
-In case the conditional statement is verified,
-the precision tuning phase starts.
-For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is because we still need to satisfy (\ref{eq:delta}).
-On the other hand, the quantization of polytopes borders (the region bounds in \statespace) can produce an error that is at most $\varepsilon_{Q}$, in this way we satisfy 
-(\ref{eq:quantizationlines}).
-
-In case the conditional fails and \texttt{maxUij} is greater than delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}.
-The same consideration done for the initialization of input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value delta for the controller, to a value slightly greater than \texttt{maxUij}.
-In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop.
-Otherwise, in case of $\varepsilon_{SAFE}$ equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision values p, usually greater than 32 bits.
-We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions: in case the analysis outputs a precision greater than 32bits, we fail in our goal.
-Then, with a minimal alteration to the upper bound of delta, we sensibly reduce the precision needed for $F$ and $G$, with respect to the standard 32 bits precision.
-
-\section{Experimental Results}
-
-\subsection{Case of study: Inverted Pendulum}
-%\begin{landscape}
-%\begin{table*}[t]
-%	\centering
-%	\caption{Inverted Pendolum: delta}
-%	\label{tab:ipd}
-%	\begin{tabular}{r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
-%		\multicolumn{4}{c}{} &
-%		\multicolumn{2}{c}{Xbounds} &
-%		\multicolumn{2}{c}{} &
-%		\multicolumn{4}{c}{F and G} &
-%		\multicolumn{4}{c}{H and K} 
-%		\\
-%		\multicolumn{1}{c}{delta}&
-%		\multicolumn{1}{c}{eps} &
-%		\multicolumn{1}{c}{regs} &
-%		\multicolumn{1}{c}{hyps} &
-%		\multicolumn{1}{c}{X0}&
-%		\multicolumn{1}{c}{X1}&
-%		\multicolumn{1}{c}{max\_Uij} &
-%		\multicolumn{1}{c}{err} &
-%		\multicolumn{1}{c}{tot.uni32}&
-%		\multicolumn{1}{c}{tot.uni}&
-%		\multicolumn{1}{c}{tot.mix}&
-%		\multicolumn{1}{c}{\% saved}&
-%		\multicolumn{1}{c}{tot.uni32}&
-%		\multicolumn{1}{c}{tot.uni}&
-%		\multicolumn{1}{c}{tot.mix}&
-%		\multicolumn{1}{c}{\% saved}
-%		%\multicolumn{1}{c}{\multirow{2}{*}{max|Ui-Uj|}} &
-%		%\multicolumn{1}{c}{\multirow{2}{*}{FP\_err}} &
-%		%\multicolumn{4}{c}{F and G} &
-%		%\multicolumn{4}{c}{H and K} \\
-%		%\cline{5-6}\cline{9-12}\cline{13-16} &
-%		%\multicolumn{1}{c}{X0}
-%		%\multicolumn{1}{c}{X1} &
-%		
-%	\end{tabular}
-%\end{table*}
-%\end{landscape}
-
-\subsection{Case of study: 4d example}
-\section{Related Work}
-\section{Conclusions}
-
-%\begin{table*}
-%  \caption{Some Typical Commands}
-%  \label{tab:commands}
-%  \begin{tabular}{ccl}
-%    \toprule
-%    Command &A Number & Comments\\
-%    \midrule
-%    \texttt{{\char'134}author} & 100& Author \\
-%    \texttt{{\char'134}table}& 300 & For tables\\
-%    \texttt{{\char'134}table*}& 400& For wider tables\\
-%    \bottomrule
-%  \end{tabular}
-%\end{table*}
-
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=\linewidth]{sample-franklin}
-%  \caption{1907 Franklin Model D roadster. Photograph by Harris \& Ewing, Inc. [Public domain], via Wikimedia Commons. (\url{https://goo.gl/VLCRBB}).}
-%  \Description{The 1907 Franklin Model D roadster.}
-%\end{figure}
-
-%Some examples.
-A paginated journal article \cite{Abril07}, an enumerated journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series (see 2a in spec.
-document)
+\input{intro}
+\input{motiv}
+\input{RMPC_Daisy}
+\input{Methodology}
+\input{experiments}
+\input{Conclusion}
 

### 2019-04-04 emsoft-2019/Motiv.tex

@@
 			\centering
-			\node [block, pin={[pinstyle]above:$\delta=\delta_0$},
+			\node [block, pin={[pinstyle]above:$\Delta=\Delta_0$},
 			node distance=5cm] (RMPC) {Robust MPC design};
@@
 			\node [block, below of= decide,
-			node distance=3cm] (delta) {increase $\delta$};
+			node distance=3cm] (delta) {increase $\Delta$};
 

### 2019-04-04 emsoft-2019/abstract.tex
First abstract

We propose an optimization for space-efficient implementations of explicit model-predictive controllers (MPC)
for robust control of linear time invariant (LTI) systems on embedded platforms. 
We obtain an explicit-form robust model-predictive controller as a solution to a multi-parametric 
linear programming problem.
The structure of the controller is a polyhedral decomposition of the control domain,
with an affine map for each domain.
While explicit MPC is suited for embedded devices with low computational power, the memory requirements
for such controllers can be high.
We provide an optimization algorithm for a mixed-precision implementation of the controller,
where the deviation of the implemented controller from the original one is within the robustness
margin of the robust control problem.
The core of the mixed-precision optimization is an iterative static analysis that co-designs
a robust controller and a low-bitwidth approximation 
that is statically guaranteed to always be within the robustness margin to the original controller.
We have implemented our algorithm and show, on a set of Simulink benchmarks, that our optimization
can reduce space requirements by up to 20\% (and about 10\% on average), compared to a fixed precision
implementation of the original controller.

### 2019-04-04 emsoft-2019/abstract.tex
small edit to abstract

@@
 We have implemented our algorithm and show, on a set of Simulink benchmarks, that our optimization
-can reduce space requirements by up to 20\% (and about 10\% on average), compared to a fixed precision
+can reduce space requirements by up to 20\% (and about 10\% on average), compared to a uniform precision
 implementation of the original controller.

### 2019-04-04 emsoft-2019/Motiv.tex
updates

@@
 		\begin{bmatrix}
-			\dot \theta\\
-			\dot \omega
+			 \theta_{k+1}\\
+			\omega_{k+1}
 		\end{bmatrix}=
 		\begin{bmatrix}
-			0 & 1\\
-			\frac{g}{l}& \frac{-b}{ml^2}		
+			1 & T_s\\
+			\frac{T_sg}{l}& (1-\frac{T_sb}{ml^2})		
 		\end{bmatrix}
 		\begin{bmatrix}
-			\theta\\
-			\omega
+			\theta_k\\
+			\omega_k
 		\end{bmatrix}+
@@
 			0\\
-			\frac{1}{ml^2}
-		\end{bmatrix}u
+			\frac{T_s}{ml^2}
+		\end{bmatrix}u_k
 		\label{eq:pendul_ss}
 	\end{equation}
-	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitational acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient and $L$ the length of the bar.
-To design the controller, one has to first descretize the dynamics in $\eqref{eq:pendul_ss}$ with respect to an appropriate sample time $T_s$.
+	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitational acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient, $L$ the length of the bar and $T_s$ an appropriate sample time.
 Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point while always $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$.

### 2019-04-04 emsoft-2019/abstract.tex
updates

--- 2019-04-04 emsoft-2019/abstract.tex
@@
 that is statically guaranteed to always be within the robustness margin to the original controller.
-We have implemented our algorithm and show, on a set of Simulink benchmarks, that our optimization
-can reduce space requirements by up to 20\% (and about 10\% on average), compared to a fixed precision
+We have implemented our algorithm and show, on a set of benchmarks, that our optimization
+can reduce space requirements by up to 20\% (and about 10\% on average), compared to a uniform precision
 implementation of the original controller.

### 2019-04-04 emsoft-2019/main.tex
First abstract
title...
making paper anonymous

@@
 % The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf]{acmart}
+\documentclass[sigconf,review,anonymous]{acmart}
 \usepackage{listings}
@@
 \usepackage{graphicx}
-
-%
-% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
@@
 % These commands are for a PROCEEDINGS abstract or paper.
-\copyrightyear{2018}
-\acmYear{2018}
-\setcopyright{acmlicensed}
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
-\acmDOI{10.1145/1122445.1122456}
-\acmISBN{978-1-4503-9999-9/18/06}
+% \copyrightyear{2018}
+% \acmYear{2018}
+% \setcopyright{acmlicensed}
+% \acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
+% \acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
+% \acmPrice{15.00}
+% \acmDOI{10.1145/1122445.1122456}
+% \acmISBN{978-1-4503-9999-9/18/06}
 
@@
 % The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
-\title{The Name of the Title is Hope}
+\title{Memory-efficient Mixed-Precision Implementations for\\Robust Explicit MPC}
 
@@
 % used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
-\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
-\affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
-}
 
-\author{Lars Th{\o}rv{\"a}ld}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
-
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
-}
-
-\author{Aparna Patel}
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
+% \author{Ben Trovato}
+% \authornote{Both authors contributed equally to this research.}
+% \email{trovato@corporation.com}
+% \orcid{1234-5678-9012}
+% \author{G.K.M. Tobin}
+% \authornotemark[1]
+% \email{webmaster@marysville-ohio.com}
+% \affiliation{%
+%   \institution{Institute for Clarity in Documentation}
+%   \streetaddress{P.O. Box 1212}
+%   \city{Dublin}
+%   \state{Ohio}
+%   \postcode{43017-6221}
+% }
 
@@
 % of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+%\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
 
@@
 \begin{abstract}
-
+\input{abstract}
 \end{abstract}
@@
 %
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
+% \begin{CCSXML}
+% <ccs2012>
+%  <concept>
+%   <concept_id>10010520.10010553.10010562</concept_id>
+%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+%   <concept_significance>500</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>10010520.10010575.10010755</concept_id>
+%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
+%   <concept_significance>300</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>10010520.10010553.10010554</concept_id>
+%   <concept_desc>Computer systems organization~Robotics</concept_desc>
+%   <concept_significance>100</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>10003033.10003083.10003095</concept_id>
+%   <concept_desc>Networks~Network reliability</concept_desc>
+%   <concept_significance>100</concept_significance>
+%  </concept>
+% </ccs2012>
+% \end{CCSXML}
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+% \ccsdesc[500]{Computer systems organization~Embedded systems}
+% \ccsdesc[300]{Computer systems organization~Redundancy}
+% \ccsdesc{Computer systems organization~Robotics}
+% \ccsdesc[100]{Networks~Network reliability}
 
@@
 % presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
-%\keywords{datasets, neural networks, gaze detection, text tagging}
+\keywords{model-predictive control, robustness, fixed-point arithmetic}
 
-%
-% A "teaser" image appears between the author and affiliation information and the body 
-% of the document, and typically spans the page. 
-%\begin{teaserfigure}
-%  \includegraphics[width=\textwidth]{sampleteaser}
-%  \caption{Seattle Mariners at Spring Training, 2010.}
-%  \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
-%  \label{fig:teaser}
-%\end{teaserfigure}
-
-%
-% This command processes the author and affiliation and title information and builds
-% the first part of the formatted document.
 \maketitle

### 2019-04-04 emsoft-2019/experiments.tex
First draft of tables; Removed fake authors

\section{Experimental Results}
\subsection{Case of study: inverted pendulum}

\begin{landscape}
	\pagestyle{empty}
\begin{table}[p]
	\centering
	\caption{Inverted Pendolum}
	\label{tab:ipd}
	\begin{tabular}{rrrrrrrrrrrrrrrr}
		\cline{7-11}
		\cline{12-16}
		\multicolumn{4}{c}{} &
		\multicolumn{2}{c}{} &
		\multicolumn{5}{c|}{F and G} &
		\multicolumn{5}{c}{H and K} \\
		\hline
		%\cline{5-6}
		%\cline{9-12}
		%\cline{13-16}
		\multicolumn{1}{c}{Delta}&
		\multicolumn{1}{c}{Eps} &
		\multicolumn{1}{c}{Regs} &
		\multicolumn{1}{c}{Hyps} &
		\multicolumn{1}{c}{$max|U_{i}-U_{j}|$} &
		\multicolumn{1}{c}{Err-Bound} &
		\multicolumn{1}{c}{Uni32}&
		\multicolumn{1}{c}{Uni}&
		\multicolumn{1}{c}{Mix}&
		\multicolumn{1}{c}{\%32vsU}&
		\multicolumn{1}{c}{\%UvsM}&
		\multicolumn{1}{c}{Uni32}&
		\multicolumn{1}{c}{Uni}&
		\multicolumn{1}{c}{Mix}&
		\multicolumn{1}{c}{\%32vsU}&
		\multicolumn{1}{c}{\%UvsM} \\
		\hline

		\color{red}{0.30} & 0.001 & 14 & 58 & 0.019898948 & 0.280101052 & 2688 & 924 (uni11) & 759 & 65.63\% & 17.85\% & 11136 & 5568 (uni16) & 4991 & 50.00\% & 10.36\% \\

		\color{red}{0.20} & 0.001 & 14 & 58 & 0.019898948 & 0.180101052 & 2688 & 924 (uni11) & 806 & 65.63\% & 12.77\% & 11136 & 5568 (uni16)& 4992 & 50.00\% & 10.34\% \\

		\color{red}{0.10} & 0.001 & 14 & 58 & 0.019898948 & 0.080101052 & 2688 & 1008 (uni12) & 908 & 65.50\% & 9.92\% & 11136 & 5568 (uni16)& 4992 & 50.00\% & 10.34\% \\

		\color{red}{0.08} & 0.001 & 14 & 58 & 0.019898948 & 0.080101052 &2688 & 1092 (uni13) & 946 & 59.38\% & 13.36\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\

		\color{red}{0.05} & 0.001 & 14 & 58 & 0.019898948 & 0.030101052 & 2688 & 1176 (uni14) & 1030 & 56.25\% & 12.41\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\ \\

		% Starts Epsilon

		0.1 & \color{red}{0.0006} & 14 & 58 & 0.011939369 & 0.088060631 & 2688 & 1008 (uni12) & 891 & 62.50\% & 11.60\% & 11136 & 5916 (uni17) & 5261 & 46.88\% & 11.07\% \\

		0.1 & \color{red}{0.0008} & 14 & 58 & 0.015919159 & 0.084080841 & 2688 & 1008 (uni12) & 901 & 62.50\% & 10.61\% & 11136 & 5568 (uni16) & 5135 & 50.00\% & 7.77\% \\

		0.1 & \color{red}{0.0010} & 14 & 58 & 0.019898948 & 0.080101052 & 2688 & 1008 (uni12) & 908 & 62.50\% & 9.92\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\

		0.1 & \color{red}{0.0030} & 14 & 58 & 0.059696845 & 0.040303155 & 2688 &  1092 (uni13) & 993 & 59.38\% & 9.06\% & 11136 & 4872 (uni14) & 4462 & 56.25\% & 8.41\% \\

		0.1 & \color{red}{0.0050} & 14 & 58 & 0.099494741 & 0.000505259 & 2688 & 1680 (uni20) & 1527 & 37.50\% & 9.10\% & 11136 & 4872 (uni14) & 4204 & 56.25\% & 13.71\% \\

	\end{tabular}
	\vspace*{1 cm}
	\centering
	\caption{Aircraft}
	\label{tab:aircraft}
	\begin{tabular}{rrrrrrrrrrrrrrrr}
		\cline{7-11}
		\cline{12-16}
		\multicolumn{4}{c}{} &
		\multicolumn{2}{c}{} &
		\multicolumn{5}{c|}{F and G} &
		\multicolumn{5}{c}{H and K} \\
		\hline
		%\cline{5-6}
		%\cline{9-12}
		%\cline{13-16}
		\multicolumn{1}{c}{Delta}&
		\multicolumn{1}{c}{Eps} &
		\multicolumn{1}{c}{Regs} &
		\multicolumn{1}{c}{Hyps} &
		\multicolumn{1}{c}{$max|U_{i}-U_{j}|$} &
		\multicolumn{1}{c}{Err-Bound} &
		\multicolumn{1}{c}{Uni32}&
		\multicolumn{1}{c}{Uni}&
		\multicolumn{1}{c}{Mix}&
		\multicolumn{1}{c}{\%32vsU}&
		\multicolumn{1}{c}{\%UvsM}&
		\multicolumn{1}{c}{Uni32}&
		\multicolumn{1}{c}{Uni}&
		\multicolumn{1}{c}{Mix}&
		\multicolumn{1}{c}{\%32vsU}&
		\multicolumn{1}{c}{\%UvsM} \\
		\hline

		\color{red}{0.30} & 0.001 & 26 & 208 & 0.036944218 & 0.263055781 & 9984 & 6864 (uni22) & 6210 & 31.25\% & 9.52\% & 79872 & 64896 (uni16) & 53059 & 18.75\% & 18.23\% \\

		\color{red}{0.20} & 0.001 & 27 & 216 & 0.036944218 & 0.163055781 & 10368 & 7452 (uni23) & 6725 & 28.13\% & 9.75\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\

		\color{red}{0.10} & 0.001 & 27 & 216 & 0.036944218 & 0.063055781 & 10368 & 7776 (uni24) & 7134 & 25.00\% & 8.25\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\

		\color{red}{0.08} & 0.001 & 27 & 216 & 0.036944218 & 0.043055781 & 10368 & 7776 (uni24) & 7275 & 25.00\% & 6.44\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\

		\color{red}{0.05} & 0.001 & 27 & 216 & 0.036944218 & 0.013055781 & 10368 & 8424 (uni26) & 7840 & 18.75\% & 6.93\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\\\

		% Starts Epsilon

		0.1 & \color{red}{0.0006} & 27 & 216 & 0.022166935 & 0.077833064 & 10368 & 7776 (uni24) & 7047 & 25.00\% & 9.38\% & 82944 & 69984 (uni27) & 55705 & 15.63\% & 20.40\% \\

		0.1 & \color{red}{0.0008} & 27 & 216 & 0.029555577 & 0.070444422 & 10368 & 7776 (uni24) & 7125 & 25.00\% & 8.37\% & 82944 & 69984 (uni27) & 57859 & 15.63\% & 17.32\% \\

		0.1 & \color{red}{0.0010} & 27 & 216 & 0.036944218 & 0.063055781 & 10368 & 7776 (uni24) & 7134 & 25.00\% & 8.25\% & 82944 & 67392 (uni26) & 55098 & 18.75\% & 18.24\% \\

		0.112 & \color{red}{0.0030} & 27 & 216 & 0.110830633 & 0.001000000068 & 10368 &  9720 (uni30) & 9051 & 6.25\% & 6.88\% & 82944 & 64800 (uni25) & 52754 & 21.86\% & 18.58\% \\

		0.185 &\color{red}{0.0050} & 27 & 216 & 0.184717048 & 0.001000000090 & 10368 & 9720 (uni30) & 9051 & 6.25\% & 6.88\% & 82944 & 62208 (uni24) & 47877 & 25.00\%& 23.03\% \\

	\end{tabular}
	\vspace*{1 cm}
	\centering
	\caption{Double Integrator}
	\label{tab:di}
	\begin{tabular}{rrrrrrrrrrrrrrrr}
		\cline{7-11}
		\cline{12-16}
		\multicolumn{4}{c}{} &
		\multicolumn{2}{c}{} &
		\multicolumn{5}{c|}{F and G} &
		\multicolumn{5}{c}{H and K} \\
		\hline
		%\cline{5-6}
		%\cline{9-12}
		%\cline{13-16}
		\multicolumn{1}{c}{Delta}&
		\multicolumn{1}{c}{Eps} &
		\multicolumn{1}{c}{Regs} &
		\multicolumn{1}{c}{Hyps} &
		\multicolumn{1}{c}{$max|U_{i}-U_{j}|$} &
		\multicolumn{1}{c}{Err-Bound} &
		\multicolumn{1}{c}{Uni32}&
		\multicolumn{1}{c}{Uni}&
		\multicolumn{1}{c}{Mix}&
		\multicolumn{1}{c}{\%32vsU}&
		\multicolumn{1}{c}{\%UvsM}&
		\multicolumn{1}{c}{Uni32}&
		\multicolumn{1}{c}{Uni}&
		\multicolumn{1}{c}{Mix}&
		\multicolumn{1}{c}{\%32vsU}&
		\multicolumn{1}{c}{\%UvsM} \\
		\hline
		\color{red}{0.1} & \color{red}{0.001} & 1299 & 23382 & 0.05 & 0.05 & 249408 & 109116 (uni14) & 80524 & 56.25\% & 26.20\% & 2992896 & 1589976 (uni17) & 1355675 & 46.88\% & 14.73\% \\
	\end{tabular}
\end{table}
\end{landscape}

\subsection{Case of study: aircraft}
\subsection{Case of study: double integrator}

### 2019-04-05 emsoft-2019/experiments.tex
experiments update

@@
 \section{Experimental Results}
+This section reports experiments with the prototype described in Listing\ref{lst:alg} applied to three different benchmarks: in the former two, we evaluate the full pipeline to produce in output a complete controller.
+In the last one, we empirically show the scalability of our approach on one artificial controller sample.
+The design of controllers is done on a machine with Intel i7-6700HQ CPU at 2.60GHz, with 16GB of RAM. 
+Only the last evaluation runs on a cluster with 48 cores Intel Xeon v2 @ 3.00GHz with 1TB of RAM.
+
 \subsection{Case of study: inverted pendulum}
+In Table \ref{tab:ipd} we report the evaluation of our approach on the inverted pendulum problem described in the motivation section.
+We report the design procedure for 10 different controllers, for various combinations of Delta and Eps.
+We divide the table int two evaluation blocks: in the first, we fix the value for Eps and we tune the robustness value Delta, while in the second we do the opposite.
+
+The first evaluation block shows that the input Delta does not impact the maximal error among regions.
+In this example, we verify that a variation for delta (in the order of $\pm$ 0.1) results in a minimal alteration to the size of the region (in the order of $10^{-10}$), not enough to affect the maximization value.
+Since maxUiUj is constant, the space for approximation error Err-Bound decreases together with the value of delta.
+The memory requirement for storage of F and G depends only on Err-Bound, and it is clear from the table that the smaller the value for delta, the more demanding is the precision required for computations.
+In average, more than 50\% of memory is saved between fixed-32 (all arithmetic is done in 32 bits), and Uni, the minimal precision word-length found with our analysis.
+While, using mixed-precision (Mix) reduces (in average) more than 10\% memory consumption compare to Uni.
+The storage of hyperplanes H and K depends only on the value of Eps (the size of the tubes).
+For a constant value of Eps, we save 50\% from fixed-32 to Uni and 10\% from Uni to Mixed.
+
+The second evaluation block shows how for the same robustness design delta, the value of Eps determines the precision needed for F, G and H, K.
+Increasing the size of the tubes epsilon produces a greater value for max Ui-Uj.
+
+\subsection{Case of study: aircraft}
+\subsection{Case of study: double integrator}
 
@@
 	\centering
-	\caption{Inverted Pendolum}
+	\caption{Inverted Pendolum.
+Delta is the disturbance used to design the controller, and Eps the size of the uncertainty between two generic regions (\texttt{tube}).
+For each pair Delta, Eps we obtain a controller with Regs number of regions divided by Hyps hyperplanes.
+The maximal error due to the wrong activation function is maxUiUj and Err-Bound is Delta - maxUiUj.
+Uni32 is the total number of bits for the controller completely designed in fixed-32 bit precision.
+Uni is the total number of bits returned by our analysis, together with the format (p=format).
+Mix is the total number of bits for the same controller in mixed-precision.
+\%32vsU is the difference between the baseline Uni32 and the number of bits used in U (in percentage), then \%UvsM is the difference between Uni and Mix.
+F, G and H, K represent the memory requirements for activation functions, and polytopes borders.
+	}
 	\label{tab:ipd}
@@
 
-		\color{red}{0.30} & 0.001 & 14 & 58 & 0.019898948 & 0.280101052 & 2688 & 924 (uni11) & 759 & 65.63\% & 17.85\% & 11136 & 5568 (uni16) & 4991 & 50.00\% & 10.36\% \\
+		\color{red}{0.30} & 0.001 & 14 & 58 & 0.02 & 0.28 & 2688 & 924 (p=11) & 759 & 65.6\% & 17.9\% & 11136 & 5568 (p=16) & 4991 & 50\% & 10.7\% \\
 
-		\color{red}{0.20} & 0.001 & 14 & 58 & 0.019898948 & 0.180101052 & 2688 & 924 (uni11) & 806 & 65.63\% & 12.77\% & 11136 & 5568 (uni16)& 4992 & 50.00\% & 10.34\% \\
+		\color{red}{0.20} & 0.001 & 14 & 58 & 0.02 & 0.18 & 2688 & 924 (p=11) & 806 & 65.6\% & 12.8\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
 
-		\color{red}{0.10} & 0.001 & 14 & 58 & 0.019898948 & 0.080101052 & 2688 & 1008 (uni12) & 908 & 65.50\% & 9.92\% & 11136 & 5568 (uni16)& 4992 & 50.00\% & 10.34\% \\
+		\color{red}{0.10} & 0.001 & 14 & 58 & 0.02 & 0.08 & 2688 & 1008 (p=12) & 908 & 65.5\% & 10\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
 
-		\color{red}{0.08} & 0.001 & 14 & 58 & 0.019898948 & 0.080101052 &2688 & 1092 (uni13) & 946 & 59.38\% & 13.36\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\
+		\color{red}{0.08} & 0.001 & 14 & 58 & 0.02 & 0.06 & 2688 & 1092 (p=13) & 946 & 59.4\% & 13.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
 
-		\color{red}{0.05} & 0.001 & 14 & 58 & 0.019898948 & 0.030101052 & 2688 & 1176 (uni14) & 1030 & 56.25\% & 12.41\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\ \\
+		\color{red}{0.05} & 0.001 & 14 & 58 & 0.02 & 0.03 & 2688 & 1176 (p=14) & 1030 & 56.3\% & 12.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\ \\
 
@@
 
-		0.1 & \color{red}{0.0006} & 14 & 58 & 0.011939369 & 0.088060631 & 2688 & 1008 (uni12) & 891 & 62.50\% & 11.60\% & 11136 & 5916 (uni17) & 5261 & 46.88\% & 11.07\% \\
+		0.1 & \color{red}{0.0006} & 14 & 58 & 0.012 & 0.088 & 2688 & 1008 (p=12) & 891 & 62.5\% & 11.6\% & 11136 & 5916 (p=17) & 5261 & 46.9\% & 11\% \\
 
-		0.1 & \color{red}{0.0008} & 14 & 58 & 0.015919159 & 0.084080841 & 2688 & 1008 (uni12) & 901 & 62.50\% & 10.61\% & 11136 & 5568 (uni16) & 5135 & 50.00\% & 7.77\% \\
+		0.1 & \color{red}{0.0008} & 14 & 58 & 0.016 & 0.084 & 2688 & 1008 (p=12) & 901 & 62.5\% & 10.6\% & 11136 & 5568 (p=16) & 5135 & 50\% & 7.77\% \\
 
-		0.1 & \color{red}{0.0010} & 14 & 58 & 0.019898948 & 0.080101052 & 2688 & 1008 (uni12) & 908 & 62.50\% & 9.92\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\
+		0.1 & \color{red}{0.0010} & 14 & 58 & 0.019 & 0.081 & 2688 & 1008 (p=12) & 908 & 62.5\% & 10\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
 
-		0.1 & \color{red}{0.0030} & 14 & 58 & 0.059696845 & 0.040303155 & 2688 &  1092 (uni13) & 993 & 59.38\% & 9.06\% & 11136 & 4872 (uni14) & 4462 & 56.25\% & 8.41\% \\
+		0.1 & \color{red}{0.0030} & 14 & 58 & 0.059 & 0.041 & 2688 &  1092 (p=13) & 993 & 59.4\% & 9.1\% & 11136 & 4872 (p=14) & 4462 & 56.3\% & 8.4\% \\
 
-		0.1 & \color{red}{0.0050} & 14 & 58 & 0.099494741 & 0.000505259 & 2688 & 1680 (uni20) & 1527 & 37.50\% & 9.10\% & 11136 & 4872 (uni14) & 4204 & 56.25\% & 13.71\% \\
+		0.1 & \color{red}{0.0050} & 14 & 58 & 0.099 & 0.001 & 2688 & 1680 (p=20) & 1527 & 37.5\% & 9.1\% & 11136 & 4872 (p=14) & 4204 & 56.3\% & 13.7\% \\
 
@@
 	\centering
-	\caption{Aircraft}
+	\caption{Aircraft. For the description of each column see Table \ref{tab:ipd}.\\
+	* In the last two samples the original value for delta was equal to 0.1, but our analysis returns a controller robust to a greater disturbance.}
 	\label{tab:aircraft}
@@
 
-		\color{red}{0.30} & 0.001 & 26 & 208 & 0.036944218 & 0.263055781 & 9984 & 6864 (uni22) & 6210 & 31.25\% & 9.52\% & 79872 & 64896 (uni16) & 53059 & 18.75\% & 18.23\% \\
+		\color{red}{0.30} & 0.001 & 26 & 208 & 0.037 & 0.263 & 9984 & 6864 (p=22) & 6210 & 31.3\% & 9.5\% & 79872 & 64896 (p=16) & 53059 & 18.8\% & 18.2\% \\
 
-		\color{red}{0.20} & 0.001 & 27 & 216 & 0.036944218 & 0.163055781 & 10368 & 7452 (uni23) & 6725 & 28.13\% & 9.75\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\
+		\color{red}{0.20} & 0.001 & 27 & 216 & 0.037 & 0.163 & 10368 & 7452 (p=23) & 6725 & 28.1\% & 9.8\% & 82944 & 67392 (p=16) & 55098 & 18.8\% & 18.2\% \\
 
-		\color{red}{0.10} & 0.001 & 27 & 216 & 0.036944218 & 0.063055781 & 10368 & 7776 (uni24) & 7134 & 25.00\% & 8.25\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\
+		\color{red}{0.10} & 0.001 & 27 & 216 & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=16) & 55098 & 18.8\% & 18.2\% \\
 
-		\color{red}{0.08} & 0.001 & 27 & 216 & 0.036944218 & 0.043055781 & 10368 & 7776 (uni24) & 7275 & 25.00\% & 6.44\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\
+		\color{red}{0.08} & 0.001 & 27 & 216 & 0.037 & 0.043 & 10368 & 7776 (p=24) & 7275 & 25\% & 6.4\% & 82944 & 67392 (p=16) & 55098 & 18.8\% & 18.2\% \\
 
-		\color{red}{0.05} & 0.001 & 27 & 216 & 0.036944218 & 0.013055781 & 10368 & 8424 (uni26) & 7840 & 18.75\% & 6.93\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\\\
+		\color{red}{0.05} & 0.001 & 27 & 216 & 0.037 & 0.013 & 10368 & 8424 (p=26) & 7840 & 18.8\% & 6.9\% & 82944 & 67392 (p=16) & 55098 & 18.8\% & 18.3\% \\\\
 
@@
 
-		0.1 & \color{red}{0.0006} & 27 & 216 & 0.022166935 & 0.077833064 & 10368 & 7776 (uni24) & 7047 & 25.00\% & 9.38\% & 82944 & 69984 (uni27) & 55705 & 15.63\% & 20.40\% \\
+		0.1 & \color{red}{0.0006} & 27 & 216 & 0.022 & 0.078 & 10368 & 7776 (p=24) & 7047 & 25\% & 9.4\% & 82944 & 69984 (p=27) & 55705 & 15.6\% & 20.4\% \\
 
-		0.1 & \color{red}{0.0008} & 27 & 216 & 0.029555577 & 0.070444422 & 10368 & 7776 (uni24) & 7125 & 25.00\% & 8.37\% & 82944 & 69984 (uni27) & 57859 & 15.63\% & 17.32\% \\
+		0.1 & \color{red}{0.0008} & 27 & 216 & 0.030 & 0.071 & 10368 & 7776 (p=24) & 7125 & 25\% & 8.4\% & 82944 & 69984 (p=27) & 57859 & 15.6\% & 17.3\% \\
 
-		0.1 & \color{red}{0.0010} & 27 & 216 & 0.036944218 & 0.063055781 & 10368 & 7776 (uni24) & 7134 & 25.00\% & 8.25\% & 82944 & 67392 (uni26) & 55098 & 18.75\% & 18.24\% \\
+		0.1 & \color{red}{0.0010} & 27 & 216 & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
 
-		0.112 & \color{red}{0.0030} & 27 & 216 & 0.110830633 & 0.001000000068 & 10368 &  9720 (uni30) & 9051 & 6.25\% & 6.88\% & 82944 & 64800 (uni25) & 52754 & 21.86\% & 18.58\% \\
+		0.112* & \color{red}{0.0030} & 27 & 216 & 0.111 & 0.001000000068 & 10368 &  9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 64800 (p=25) & 52754 & 21.9\% & 18.6\% \\
 
-		0.185 &\color{red}{0.0050} & 27 & 216 & 0.184717048 & 0.001000000090 & 10368 & 9720 (uni30) & 9051 & 6.25\% & 6.88\% & 82944 & 62208 (uni24) & 47877 & 25.00\%& 23.03\% \\
+		0.185* &\color{red}{0.0050} & 27 & 216 & 0.185 & 0.001000000090 & 10368 & 9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 62208 (p=24) & 47877 & 25\%& 23.1\% \\
 
@@
 	\centering
-	\caption{Double Integrator}
+	\caption{For the description of each column see Table \ref{tab:ipd}.}
 	\label{tab:di}
@@
 		\hline
-		\color{red}{0.1} & \color{red}{0.001} & 1299 & 23382 & 0.05 & 0.05 & 249408 & 109116 (uni14) & 80524 & 56.25\% & 26.20\% & 2992896 & 1589976 (uni17) & 1355675 & 46.88\% & 14.73\% \\
+		\color{red}{0.1} & \color{red}{0.001} & 1299 & 23382 & 0.05 & 0.05 & 249408 & 109116 (p=14) & 80524 & 56.3\% & 26.2\% & 2992896 & 1589976 (p=17) & 1355675 & 46.9\% & 14.7\% \\
 	\end{tabular}
@@
 \end{landscape}
-
-\subsection{Case of study: aircraft}
-\subsection{Case of study: double integrator}

### 2019-04-06 emsoft-2019/experiments.tex
init experiments

--- 2019-04-04 emsoft-2019/experiments.tex
@@
 \section{Experimental Results}
-\subsection{Case of study: inverted pendulum}
+
+This section reports experiments with the prototype described in Listing\ref{lst:alg} applied to three different benchmarks: in the former two, we evaluate the complete pipeline (design and precision tuning) to produce in output a complete controller.
+In the last one, we empirically show the scalability of our approach on one artificial sample.
+For the design of controllers we rely on MATLAB toolbox (YALMIP and 
+The design of controllers is done on a laptop with Intel i7-6700HQ CPU at 2.60GHz, with 16GB of RAM. 
+Only the last evaluation runs on a cluster with 48 cores Intel Xeon v2 @ 3.00GHz with 1TB of RAM, even if the memory consumption of the analysis never exceed 11GB.
+
+\subsection{Results}
+
+In Table \ref{tab:ipd} we report the evaluation of our approach on both: the inverted pendulum problem described in the motivation section, and a well-known 4D example for aircraft controller design.
+
+Describe 4D setup.
+
+For each one of the benchmarks, we report the results for ten different combinations of Delta and Eps.
+We dived them in two halves: in the  first we fix the value for Delta and we try different Eps combinations, while in the second halve we do the opposite.
+
+In the pendulum, for all the combinations of Delta and Eps, MATLAB Toolbox returns a controller with 14 regions and 58 hyperplanes, Delta spans the interval 0.05 - 0.3, while Eps is in the interval 0.0006 - 0.0050.
+In the pendulum section of Table \ref{tab:ipd}, the first halve shows that Delta does not affect the maximal error among regions \maxUij.
+We verify that a variation for delta (typically in the order of $\pm$ 0.1) results in a minimal alteration to the domain of regions X (in the order of $\pm 10^{-10}$), not enough to produce a sensitive variation to \maxUij.
+When \maxUij is constant, the error for imprecisions Err-Bound behaves the same as Delta.
+The domain of X for the pendulum is always in the bounded range $X_{0} \in (-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$.
+The memory required for the storage of F and G depends on Err-Bound: the smaller the value for Err-Bound, the more demanding is the precision required for computations.
+In average, more than 50\% of memory is saved between fixed-32, where the all arithmetic is done in fixed precision 32 bits, and Uni, the minimal uniform precision word-length found with our analysis.
+Using mixed-precision (Mix) reduces in average 10\% of memory consumption with respect to Uni baseline.
+The storage of hyperplanes H and K depends only on the size of the tubes Eps.
+When we fix the value for Eps, and we try different delta, we save always 50\% from fixed-32 and about 10\% from Uni to Mixed.
+While in the second halve of the table, we fix the value for Delta and we try different Eps.
+When we increase the safe space between two regions by Eps, the value for \maxUij is computed for new corner points.
+It happens because of the continuity of PWA activation functions: when \statevarmath is on the border between two generic regions $i$, $j$ the value for \maxUij is close to zero.
+The more Eps moves \statevarmath far from the border, the more \maxUij increases.
+When \maxUij is almost equal to delta, the space for Err-Bound is minimized, and the controller requires high precision for computations (see last line of pendulum section in Table\ref{tab:ipd}).
+On the other hand, when the value of Eps increases the analysis can reduce the memory requirements for the storage of borders (see column Uni and Mix for the second halve of pendulum).
+
+In the aircraft section of Table\ref{tab:ipd}, we report the results for the aircraft benchmark.
+MATLAB designs each time a controller with 27 regions and 217 hyperplanes, except for one case.
+In general, when the disturbance value raises, two things can happen: the state domain X shrinks, to be robust against a greater disturbance, or the number of regions reduces.
+Other than that, the behaviors discussed for the pendulum are confirmed: when delta is small, the activation functions (F, G) are memory demanding.
+While when the value of Eps increases, the precision tuning phase can reduce the memory requirements for H, K.
+Anyway, there are two main differences with respect to the pendulum: the precision for F and G is almost double, this is because the magnitude of F and G is in the order of $10^{3}$ while for the pendulum is in the order of several units (note that the precision gain from Uni to Mix is only slightly less than the one for the pendulum).
+The second difference is in the last two lines in Table\ref{tab:ipd}.
+When Eps=0.0030, the \maxUij exceeds Delta=0.1 and we iterate again the design phase in Listing\ref{}.
+The final controller converges after 5 iterations with a Delta=0.112.
+Note the Err-Bound contains the safe coefficient epsilon to reduce the memory consumption.
+Otherwise the resulting controller would be expensive in memory (more than Fixed-64).
+
+The last evaluation is done on an artificial controller designed for an aircraft control system.
+This controller consists of 1300 regions an about 25000 hyperplanes. In \ref{tab:di} we collect the results.
+The design of the controller in MATLAB takes few minutes, then the precision tuning phase starts.
+In average the analysis of a controller takes less than a minute and consumes less than 500MB of memory.
+In average the execution time of Daisy is less than 2 minutes for a single controller.
+In total we run 24681 analysis.
+The cluster where we run the evaluation comes with 48 cores.
+In average the memory consumption on the cluster is less than 15GB.
+We run the analysis in parallel on the cluster, because each activation function or hyperplane can be analyzed separately.
 
@@
 	\centering
-	\caption{Inverted Pendolum}
+	\caption{Inverted Pendulum and Aircraft.\textmd{ Delta is the disturbance used to design the controller, and Eps the size of the safe space between two generic regions (\texttt{tube}).
+The values in red For each pair Delta, Eps we obtain a controller with Regs number of regions divided by Hyps hyperplanes.
+The maximal error due to a wrong activation function is \maxUij and Err-Bound = Delta - maxUiUj.
+F, G and H, K represent the memory requirements for activation functions, and polytopes borders.
+Uni32 is the total number of bits for the controller, completely designed in fixed-32 bit precision.
+Uni is the uniform precision detected by our analysis, together with the format (p=format).
+Mix is the total number of bits for the controller in mixed-precision.
+\%32vsU is the difference between the baseline Uni32 and the number of bits used in U (in percentage), then \%UvsM is the difference between Uni and Mix.}}
 	\label{tab:ipd}
-	\begin{tabular}{rrrrrrrrrrrrrrrr}
-		\cline{7-11}
-		\cline{12-16}
+	\begin{tabular}{|l|rrrrrrrrrrrrrrrr|}
+		\cline{8-12}
+		\cline{12-17}
+		\multicolumn{1}{c}{} & %name of the sample
 		\multicolumn{4}{c}{} &
 		\multicolumn{2}{c}{} &
-		\multicolumn{5}{c|}{F and G} &
-		\multicolumn{5}{c}{H and K} \\
-		\hline
+		\multicolumn{5}{|c|}{F and G} &
+		\multicolumn{5}{c|}{H and K} \\
+		\cline{2-17}
 		%\cline{5-6}
@@
 		%\cline{13-16}
-		\multicolumn{1}{c}{Delta}&
+		\multicolumn{1}{c}{\multirow{14}{*}{\rotatebox{90}{pendulum}}} &
+		\multicolumn{1}{|c}{Delta}&
 		\multicolumn{1}{c}{Eps} &
@@
 		\multicolumn{1}{c}{\%32vsU}&
-		\multicolumn{1}{c}{\%UvsM} \\
-		\hline
+		\multicolumn{1}{c|}{\%UvsM} \\
+		\cline{1-17}
+		& \color{red}{0.30} & 0.001 & 14 & 58 & 0.02 & 0.28 & 2688 & 924 (p=11) & 759 & 65.6\% & 17.9\% & 11136 & 5568 (p=16) & 4991 & 50\% & 10.7\% \\
 
-		\color{red}{0.30} & 0.001 & 14 & 58 & 0.019898948 & 0.280101052 & 2688 & 924 (uni11) & 759 & 65.63\% & 17.85\% & 11136 & 5568 (uni16) & 4991 & 50.00\% & 10.36\% \\
+		& \color{red}{0.20} & 0.001 & 14 & 58 & 0.02 & 0.18 & 2688 & 924 (p=11) & 806 & 65.6\% & 12.8\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
 
-		\color{red}{0.20} & 0.001 & 14 & 58 & 0.019898948 & 0.180101052 & 2688 & 924 (uni11) & 806 & 65.63\% & 12.77\% & 11136 & 5568 (uni16)& 4992 & 50.00\% & 10.34\% \\
+		& \color{red}{0.10} & 0.001 & 14 & 58 & 0.02 & 0.08 & 2688 & 1008 (p=12) & 908 & 65.5\% & 10\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
 
-		\color{red}{0.10} & 0.001 & 14 & 58 & 0.019898948 & 0.080101052 & 2688 & 1008 (uni12) & 908 & 65.50\% & 9.92\% & 11136 & 5568 (uni16)& 4992 & 50.00\% & 10.34\% \\
+		& \color{red}{0.08} & 0.001 & 14 & 58 & 0.02 & 0.06 & 2688 & 1092 (p=13) & 946 & 59.4\% & 13.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
 
-		\color{red}{0.08} & 0.001 & 14 & 58 & 0.019898948 & 0.080101052 &2688 & 1092 (uni13) & 946 & 59.38\% & 13.36\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\
+		& \color{red}{0.05} & 0.001 & 14 & 58 & 0.02 & 0.03 & 2688 & 1176 (p=14) & 1030 & 56.3\% & 12.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
 
-		\color{red}{0.05} & 0.001 & 14 & 58 & 0.019898948 & 0.030101052 & 2688 & 1176 (uni14) & 1030 & 56.25\% & 12.41\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\ \\
+		% Empy Line
+		& & & & & & & & & & & & & & & & \\
+		% Empy Line
 
-		% Starts Epsilon
+		& 0.1 & \color{red}{0.0006} & 14 & 58 & 0.012 & 0.088 & 2688 & 1008 (p=12) & 891 & 62.5\% & 11.6\% & 11136 & 5916 (p=17) & 5261 & 46.9\% & 11\% \\
 
-		0.1 & \color{red}{0.0006} & 14 & 58 & 0.011939369 & 0.088060631 & 2688 & 1008 (uni12) & 891 & 62.50\% & 11.60\% & 11136 & 5916 (uni17) & 5261 & 46.88\% & 11.07\% \\
+		& 0.1 & \color{red}{0.0008} & 14 & 58 & 0.016 & 0.084 & 2688 & 1008 (p=12) & 901 & 62.5\% & 10.6\% & 11136 & 5568 (p=16) & 5135 & 50\% & 7.77\% \\
 
-		0.1 & \color{red}{0.0008} & 14 & 58 & 0.015919159 & 0.084080841 & 2688 & 1008 (uni12) & 901 & 62.50\% & 10.61\% & 11136 & 5568 (uni16) & 5135 & 50.00\% & 7.77\% \\
+		& 0.1 & \color{red}{0.0010} & 14 & 58 & 0.019 & 0.081 & 2688 & 1008 (p=12) & 908 & 62.5\% & 10\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
 
-		0.1 & \color{red}{0.0010} & 14 & 58 & 0.019898948 & 0.080101052 & 2688 & 1008 (uni12) & 908 & 62.50\% & 9.92\% & 11136 & 5568 (uni16) & 4992 & 50.00\% & 10.34\% \\
+		& 0.1 & \color{red}{0.0030} & 14 & 58 & 0.059 & 0.041 & 2688 &  1092 (p=13) & 993 & 59.4\% & 9.1\% & 11136 & 4872 (p=14) & 4462 & 56.3\% & 8.4\% \\
 
-		0.1 & \color{red}{0.0030} & 14 & 58 & 0.059696845 & 0.040303155 & 2688 &  1092 (uni13) & 993 & 59.38\% & 9.06\% & 11136 & 4872 (uni14) & 4462 & 56.25\% & 8.41\% \\
+		& 0.1 & \color{red}{0.0050} & 14 & 58 & 0.099 & 0.001 & 2688 & 1680 (p=20) & 1527 & 37.5\% & 9.1\% & 11136 & 4872 (p=14) & 4204 & 56.3\% & 13.7\% \\
 
-		0.1 & \color{red}{0.0050} & 14 & 58 & 0.099494741 & 0.000505259 & 2688 & 1680 (uni20) & 1527 & 37.50\% & 9.10\% & 11136 & 4872 (uni14) & 4204 & 56.25\% & 13.71\% \\
+	%\end{tabular}
+	%\vspace*{1 cm}
+	%\centering
+	%\caption{Aircraft. For the description of each column see Table \ref{tab:ipd}.\\
+	%* In the last two samples the original value for delta was equal to 0.1, but our analysis returns a controller robust to a greater disturbance.}
+	%\label{tab:aircraft}
+	%\begin{tabular}{rrrrrrrrrrrrrrrr}
+	%	\cline{7-11}
+	%	\cline{12-16}
+	%	\multicolumn{4}{c}{} &
+	%	\multicolumn{2}{c}{} &
+	%	\multicolumn{5}{c|}{F and G} &
+	%	\multicolumn{5}{c}{H and K} \\
+	%	\hline
+		%\cline{5-6}
+		%\cline{9-12}
+		%\cline{13-16}
+	%	\multicolumn{1}{c}{Delta}&
+	%	\multicolumn{1}{c}{Eps} &
+	%	\multicolumn{1}{c}{Regs} &
+	%	\multicolumn{1}{c}{Hyps} &
+	%	\multicolumn{1}{c}{$max|U_{i}-U_{j}|$} &
+	%	\multicolumn{1}{c}{Err-Bound} &
+	%	\multicolumn{1}{c}{Uni32}&
+	%	\multicolumn{1}{c}{Uni}&
+	%	\multicolumn{1}{c}{Mix}&
+	%	\multicolumn{1}{c}{\%32vsU}&
+	%	\multicolumn{1}{c}{\%UvsM}&
+	%	\multicolumn{1}{c}{Uni32}&
+	%	\multicolumn{1}{c}{Uni}&
+	%	\multicolumn{1}{c}{Mix}&
+	%	\multicolumn{1}{c}{\%32vsU}&
+	%	\multicolumn{1}{c}{\%UvsM} \\
+	%	\hline
+	%	
+		\cline{1-17}
+		\multirow{12}{*}{\rotatebox{90}{aircraft}}
+		& \color{red}{0.30} & 0.001 & 26 & 208 & 0.037 & 0.263 & 9984 & 6864 (p=22) & 6210 & 31.3\% & 9.5\% & 79872 & 64896 (p=26) & 53059 & 18.8\% & 18.2\% \\
 
+		& \color{red}{0.20} & 0.001 & 27 & 216 & 0.037 & 0.163 & 10368 & 7452 (p=23) & 6725 & 28.1\% & 9.8\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
+
+		& \color{red}{0.10} & 0.001 & 27 & 216 & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
+
+		& \color{red}{0.08} & 0.001 & 27 & 216 & 0.037 & 0.043 & 10368 & 7776 (p=24) & 7275 & 25\% & 6.4\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
+
+		& \color{red}{0.05} & 0.001 & 27 & 216 & 0.037 & 0.013 & 10368 & 8424 (p=26) & 7840 & 18.8\% & 6.9\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.3\% \\
+
+		% Empy Line
+		& & & & & & & & & & & & & & & & \\
+		% Empy Line
+
+		& 0.1 & \color{red}{0.0006} & 27 & 216 & 0.022 & 0.078 & 10368 & 7776 (p=24) & 7047 & 25\% & 9.4\% & 82944 & 69984 (p=27) & 55705 & 15.6\% & 20.4\% \\
+
+		& 0.1 & \color{red}{0.0008} & 27 & 216 & 0.030 & 0.071 & 10368 & 7776 (p=24) & 7125 & 25\% & 8.4\% & 82944 & 69984 (p=27) & 57859 & 15.6\% & 17.3\% \\
+
+		& 0.1 & \color{red}{0.0010} & 27 & 216 & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
+
+		& 0.112* & \color{red}{0.0030} & 27 & 216 & 0.111 & 0.001000000068 & 10368 &  9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 64800 (p=25) & 52754 & 21.9\% & 18.6\% \\
+
+		& 0.185* &\color{red}{0.0050} & 27 & 216 & 0.185 & 0.001000000090 & 10368 & 9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 62208 (p=24) & 47877 & 25\%& 23.1\% \\
+		\cline{1-17}
 	\end{tabular}
@@
 	\centering
-	\caption{Aircraft}
-	\label{tab:aircraft}
-	\begin{tabular}{rrrrrrrrrrrrrrrr}
-		\cline{7-11}
-		\cline{12-16}
-		\multicolumn{4}{c}{} &
-		\multicolumn{2}{c}{} &
+	\caption{For the description of each column see Table \ref{tab:ipd}.}
+	\label{tab:di}
+	\begin{tabular}{rrrrrrrrrrrrrr}
+		\cline{4-8}
+		\cline{8-13}
+		\multicolumn{3}{c}{} &
+		%\multicolumn{2}{c}{} &
 		\multicolumn{5}{c|}{F and G} &
@@
 		%\cline{13-16}
-		\multicolumn{1}{c}{Delta}&
-		\multicolumn{1}{c}{Eps} &
+		\multicolumn{1}{c}{Exe-Time}&
+		%\multicolumn{1}{c}{Eps} &
 		\multicolumn{1}{c}{Regs} &
 		\multicolumn{1}{c}{Hyps} &
-		\multicolumn{1}{c}{$max|U_{i}-U_{j}|$} &
-		\multicolumn{1}{c}{Err-Bound} &
+		%\multicolumn{1}{c}{\maxUij} &
+		%\multicolumn{1}{c}{Err-Bound} &
 		\multicolumn{1}{c}{Uni32}&
@@
 		\hline
-
-		\color{red}{0.30} & 0.001 & 26 & 208 & 0.036944218 & 0.263055781 & 9984 & 6864 (uni22) & 6210 & 31.25\% & 9.52\% & 79872 & 64896 (uni16) & 53059 & 18.75\% & 18.23\% \\
-
-		\color{red}{0.20} & 0.001 & 27 & 216 & 0.036944218 & 0.163055781 & 10368 & 7452 (uni23) & 6725 & 28.13\% & 9.75\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\
-
-		\color{red}{0.10} & 0.001 & 27 & 216 & 0.036944218 & 0.063055781 & 10368 & 7776 (uni24) & 7134 & 25.00\% & 8.25\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\
-
-		\color{red}{0.08} & 0.001 & 27 & 216 & 0.036944218 & 0.043055781 & 10368 & 7776 (uni24) & 7275 & 25.00\% & 6.44\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\
-
-		\color{red}{0.05} & 0.001 & 27 & 216 & 0.036944218 & 0.013055781 & 10368 & 8424 (uni26) & 7840 & 18.75\% & 6.93\% & 82944 & 67392 (uni16) & 55098 & 18.75\% & 18.24\% \\\\
-
-		% Starts Epsilon
-
-		0.1 & \color{red}{0.0006} & 27 & 216 & 0.022166935 & 0.077833064 & 10368 & 7776 (uni24) & 7047 & 25.00\% & 9.38\% & 82944 & 69984 (uni27) & 55705 & 15.63\% & 20.40\% \\
-
-		0.1 & \color{red}{0.0008} & 27 & 216 & 0.029555577 & 0.070444422 & 10368 & 7776 (uni24) & 7125 & 25.00\% & 8.37\% & 82944 & 69984 (uni27) & 57859 & 15.63\% & 17.32\% \\
-
-		0.1 & \color{red}{0.0010} & 27 & 216 & 0.036944218 & 0.063055781 & 10368 & 7776 (uni24) & 7134 & 25.00\% & 8.25\% & 82944 & 67392 (uni26) & 55098 & 18.75\% & 18.24\% \\
-
-		0.112 & \color{red}{0.0030} & 27 & 216 & 0.110830633 & 0.001000000068 & 10368 &  9720 (uni30) & 9051 & 6.25\% & 6.88\% & 82944 & 64800 (uni25) & 52754 & 21.86\% & 18.58\% \\
-
-		0.185 &\color{red}{0.0050} & 27 & 216 & 0.184717048 & 0.001000000090 & 10368 & 9720 (uni30) & 9051 & 6.25\% & 6.88\% & 82944 & 62208 (uni24) & 47877 & 25.00\%& 23.03\% \\
-
-	\end{tabular}
-	\vspace*{1 cm}
-	\centering
-	\caption{Double Integrator}
-	\label{tab:di}
-	\begin{tabular}{rrrrrrrrrrrrrrrr}
-		\cline{7-11}
-		\cline{12-16}
-		\multicolumn{4}{c}{} &
-		\multicolumn{2}{c}{} &
-		\multicolumn{5}{c|}{F and G} &
-		\multicolumn{5}{c}{H and K} \\
-		\hline
-		%\cline{5-6}
-		%\cline{9-12}
-		%\cline{13-16}
-		\multicolumn{1}{c}{Delta}&
-		\multicolumn{1}{c}{Eps} &
-		\multicolumn{1}{c}{Regs} &
-		\multicolumn{1}{c}{Hyps} &
-		\multicolumn{1}{c}{$max|U_{i}-U_{j}|$} &
-		\multicolumn{1}{c}{Err-Bound} &
-		\multicolumn{1}{c}{Uni32}&
-		\multicolumn{1}{c}{Uni}&
-		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vsU}&
-		\multicolumn{1}{c}{\%UvsM}&
-		\multicolumn{1}{c}{Uni32}&
-		\multicolumn{1}{c}{Uni}&
-		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vsU}&
-		\multicolumn{1}{c}{\%UvsM} \\
-		\hline
-		\color{red}{0.1} & \color{red}{0.001} & 1299 & 23382 & 0.05 & 0.05 & 249408 & 109116 (uni14) & 80524 & 56.25\% & 26.20\% & 2992896 & 1589976 (uni17) & 1355675 & 46.88\% & 14.73\% \\
+		445 min
+		&1299 & 23382 & 249408 & 109116 (p=14) & 80524 & 56.3\% & 26.2\% & 2992896 & 1589976 (p=17) & 1355675 & 46.9\% & 14.7\% \\
 	\end{tabular}

### 2019-04-07 emsoft-2019/main.tex
First draft of tables; Removed fake authors
DOuble blind

@@
 % The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,review,anonymous]{acmart}
+\documentclass[sigconf,review,anonymous,dvipsnames]{acmart}
 \usepackage{listings}
@@
 \usepackage{graphicx}
+\usepackage[T1]{fontenc} 
+\usepackage[scaled=0.80]{beramono}
+\usepackage{graphicx} % http://ctan.org/pkg/graphicx
+\usepackage{booktabs} % http://ctan.org/pkg/booktabs
+\usepackage{xparse}
+\setlength{\tabcolsep}{0.5em} % for the horizontal padding
+{\renewcommand{\arraystretch}{1.1}% for the vertical padding
+%\usepackage[dvipsnames]{xcolor}
+\usepackage[backgroundcolor=Apricot, textsize=footnotesize]{todonotes}
+\newcommand*{\eva}[1]{\todo[author=Eva,inline,caption={}]{#1}}
 
@@
 \newcommand{\regionimath}[1]{X_{{#1}}}
+\newcommand{\maxUij}{$max|U_{i}-U_{j}|$}
 % Rights management information. 
@@
 % used to denote shared contribution to the research.
-
-% \author{Ben Trovato}
-% \authornote{Both authors contributed equally to this research.}
-% \email{trovato@corporation.com}
-% \orcid{1234-5678-9012}
-% \author{G.K.M. Tobin}
-% \authornotemark[1]
-% \email{webmaster@marysville-ohio.com}
-% \affiliation{%
+%\author{Ben Trovato}
+%\authornote{Both authors contributed equally to this research.}
+%\email{trovato@corporation.com}
+%\orcid{1234-5678-9012}
+%\author{G.K.M. Tobin}
+%\authornotemark[1]
+%\email{webmaster@marysville-ohio.com}
+%\affiliation{%
 %  \institution{Institute for Clarity in Documentation}
@@
 %  \postcode{43017-6221}
-% }
+%}
+
+%\author{Lars Th{\o}rv{\"a}ld}
+%\affiliation{%
+%  \institution{The Th{\o}rv{\"a}ld Group}
+%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
+%  \city{Hekla}
+%  \country{Iceland}}
+%\email{larst@affiliation.org}
+
+%\author{Valerie B\'eranger}
+%\affiliation{%
+%  \institution{Inria Paris-Rocquencourt}
+%  \city{Rocquencourt}
+%  \country{France}
+%}
+
+%\author{Aparna Patel}
+%\affiliation{%
+% \institution{Rajiv Gandhi University}
+% \streetaddress{Rono-Hills}
+% \city{Doimukh}
+% \state{Arunachal Pradesh}
+% \country{India}}
 
@@
 %\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+
+\renewcommand{\shortauthors}{}
 
@@
 \input{intro}
-\input{motiv}
+\input{Motiv}
 \input{RMPC_Daisy}
+\section{Error Analysis}
+\eva{Assuming a given precision, how to compute the error for a given controller}
+\section{Controller Synthesis}
+\eva{How we actually get the controller, including feedback loop and mixed-precision tuning}
 \input{Methodology}
 \input{experiments}
-\input{Conclusion}
+\input{related}
+\input{conclusion}
 

### 2019-04-07 emsoft-2019/abstract.tex
test

@@
 We propose an optimization for space-efficient implementations of explicit model-predictive controllers (MPC)
-for robust control of linear time invariant (LTI) systems on embedded platforms. 
+for robust control of linear time-invariant (LTI) systems on embedded platforms. 
 We obtain an explicit-form robust model-predictive controller as a solution to a multi-parametric 

### 2019-04-07 emsoft-2019/RMPC_Daisy.tex
section 3 is updated

\section{Robust MPC and Finite Precision}
\subsection{Robust Explicit MPC}
\def\reals{\mathbb{R}}
We consider class of discrete time linreat time invariant systems
\begin{equation}
\label{eq:DSS}
x_{k+1}=Ax_k+Bu_k+Ew_k
\end{equation}
where, $x\in \reals^{n\times 1}$ is state vector, $u\in \reals^{m\times 1}$ the control input vector, $w\in \reals^{d\times 1}$ the disturbance vector, $A\in \reals^{n\times n}$ the state matrix, $B\in \reals^{n\times m}$ the input matrix, $E\in \reals^{n\times d}$, $k$ the time instant and the pair $(A,B)$ is stablizable. Knowing that $w\in\mathcal{W}$, where $\mathcal{W}$ is a polyhedral set, we try to solve for the following optimization problem:
\begin{align}
\label{eq:RMPC_prob}
\min_{u_0,\cdots,u_{N-1}}\max_{w_0,\cdots,w_{N-1}}& x_N^TQ_Fx_N+\sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i)\nonumber\\
\text{s.t.}\quad\forall i\in\{0,1,\cdots,&N-1\}:\nonumber\\
&x_{i+1}=Ax_i+Bu_i\nonumber\\
&x_i\in\mathcal{X},\quad u_i\in \mathcal{U}	
\end{align}
where, $\mathcal U$ and $\mathcal X$ are polyhedral sets, $Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon. By making use of the fact that $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$, one can translate \eqref{eq:RMPC_prob} into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$. Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polydedral regions:
\begin{equation}
K(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a ploytob determined by  a set of linear inequalities $H_ix\leq K_i$. To find the controller $K$ we rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}
Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong. Several algorithms are proposed to solve for this problem [references?]. This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.

\begin{lstlisting}[escapeinside={(*}{*)},label={lst:caseof}, caption=switch for region selection]
switch((*\statevarmath*)):
case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{1}$*)
case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}$*)
case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}$*)
...
case (*$ H_{n}\statevar<=K_{n}$*) then (*$u_{n}$*)
\end{lstlisting}
Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves symmation and multiplication.

A main issue with implimentation of explicit MPC is that all the products of off-line optimization, including regions' boundaries ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s), have to be stored on the micro-controller. However, these embudded systems have limited memory, in the order of KBs and hence, it is of our interest to minimize the occupied memory.

### 2019-04-07 emsoft-2019/RMPC_Daisy.tex
updates

@@
 Several algorithms are proposed to solve for this problem [references?].
-This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.
+The simplest technique to verify which region \statevarmath belongs to is to make a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.
 

### 2019-04-07 emsoft-2019/Methodology.tex
updates

\section{Methodology}
In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.

%Consider the (discrete) state space model:
%\begin{flalign}\label{eq:statespacemodel}
%& x_{k+1} = A\statevar + Bu_{k}
%%& y_{k} = C\statevar\nonumber
%\end{flalign}

%where $\statevar\in\mathbb{R}_{n}$ is the state variable at time $k$, $u_{k}$ is the scalar control input, and $A\in\mathbb{R}^{nxn}$ and $B\in\mathbb{R}^{n}$ guarantee the stability of the system at runtime.

%The controller $u_{k}$ for (\ref{eq:statespacemodel}) is found by solving an off-line optimization problem. We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. 
%The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called region.
%A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar<=K_{i}$.

%We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
%\begin{equation}
%\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
%\end{equation}

%https://en.wikipedia.org/wiki/Polyhedron
%https://en.wikipedia.org/wiki/Polytope

%Each region $i$ is associated with an activation function $u_{i,k}=F_{i}x_{k}+G_{i}$. At runtime, the value of state variable \statevarmath  is compared against the polytopes bounds: depending on the region $i$ containing \statevarmath, the corresponding activation function $u_{i}$ is computed.

%A drawback in the design of explicit MPC is that both regions boundaries (H and K) and activation functions (F and G), have to be stored on the micro-controller. Usually these devices have limited memory, in the order of KBs.

%This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.
%
%\begin{lstlisting}[escapeinside={(*}{*)},label={lst:caseof}, caption=switch for region selection]
%switch((*\statevarmath*)):
%case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{1}$*)
%case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}$*)
%case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}$*)
%...
%case (*$ H_{n}\statevar<=K_{n}$*) then (*$u_{n}$*)
%\end{lstlisting}

At design time, the designer specifies the maximal disturbance value the controller can tolerate: we call this numerical value \texttt{delta}.

\texttt{delta} has to be an upper bound for both errors generated by the system itself (e.g. noise from sensors) and disturbance coming from sources external to the system (e.g. friction). The controller is then designed to be robust against any kind of disturbance up to a maximal value \texttt{delta}.

Among the sources of disturbance targeting the output of the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design property.

In particular, (i) first we want to guarantee that the finite precision implementation of the controller produces an approximation error that is at most equal to delta.

(ii) Second, we want to take advantage of this disturbance delta, and reduce the arithmetic precision used for computations and storage, while still guarantee that the approximation error is bounded by delta. Our intuition is that a greater value for delta allows for a reduced precision for computations (e.g. with respect to 32bits precision).

\subsection{Error Analysis}
Since (i) any measurement of the plant comes with some uncertainty (e.g. uncertainty from sensors) but also (ii) due to analog-digital conversion, the value of state variable \statevarmath comes with some numerical errors. The equation for \statevarmath is than defined as:
\begin{equation}
\qstatevar=\statevar + \texttt{err}
\end{equation}
where \statevarmath is the true (unknown) measure of the plant, while \qstatevarmath is the actual value.

\texttt{err} generates instability when it is time to verify which region \qstatevarmath belongs to: it can happen that \statevarmath satisfies the bounds of region $i$, but because of \texttt{err}, \qstatevarmath belongs to region $j$. This scenario becomes more intuitive when \qstatevarmath falls \texttt{close} to the border between two neighbor regions $i$ and $j$, but in general this instability depends on the magnitude of error \texttt{err}.

Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.

Our goal is to build a feasible geometrical space around the border between two neighbor regions $i$ and $j$, where actually it is feasible that \statevarmath belongs to region $i$ but \qstatevarmath follows in region $j$ (or vice-versa).
We call this geometrical space the \texttt{tube}.

There are two main sources of error affecting the size of the \texttt{tube}: (i) the first one is caused by analog-digital conversion, happening just before the controller receives an estimation of the plant from the sensors. We call this error $\varepsilon_{A/D}$:

\begin{equation}\nonumber
\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
\end{equation}

Where $V_{cc}$ is the reference voltage of the converter (e.g. typical 5V) and $p$ represents the number of bit of the processor.

The second error affecting the size of the \texttt{tube} is caused by (ii) the quantization of region bounds in the memory of the micro-controller. We call this error $\varepsilon_{Q}$ for error quantization.

While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries. This second error can be regulated based on a trade-off among accuracy of the storage and memory save~\cite{memoryMPC}.

The total size of the \texttt{tube} is then:
\begin{equation}\label{eq:epsilontot}
\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
\end{equation}
\subsection{Finite Precision Implementation}
The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of $\varepsilon$ in (\ref{eq:epsilontot}), and (ii) the approximation error deriving from finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.

The effect of picking the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}.

In an hypothetic scenario where all the measurements were done in infinite precision arithmetic and without any uncertainty, we assume the controller $i$ would be activated. Instead, because we cannot rely on infinite precision, controller $j$ is selected.

The error committed is the difference between the output of the two branches $i$ and $j$.

The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa), only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions. Moveover, we are interested in the worst case scenario where is maximized the difference between the activation functions of any two neighbor regions.

In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:
\begin{flalign}
\label{eq:maximization}
&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
\end{flalign}
where \statevarmath belongs to the \texttt{tube} between region $i$ and $j$.
Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$ and $j$, it is enough to evaluate function (\ref{eq:maximization}) at the corner points of the \texttt{tube}, instead of solving a maximization problem.

%The geometrical space where $\hat{X}$ activates $U_{i}$, while X would activate $U_{j}$ can be bounded thanks to a preliminary knowledge of the error $\varepsilon$: the distance between region $i$ and $j$ such that:
%\begin{equation}
%\hat{X}-X <= \varepsilon
%\end{equation}
%and $\hat{X}$ belongs to region $i$ but $X$ to $j$ (or vice-versa).

We compute (\ref{eq:maximization}) for all pairs of neighbor regions $i$ and $j$. Two regions are neighbors when they share at least a border.

In formula $\exists\; m,n \;$such that:
\begin{equation}
(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
\end{equation}
where $m$ and $n$ are the index of the two matching borders. We label with $border_{i,j}$ the matching border shared among the two regions.

Starting from the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute (\ref{eq:maximization}) with: 
\begin{equation}
\begin{aligned}
(border_{i,j} >= -\varepsilon) \land
(border_{i,j} <= \varepsilon)
\end{aligned} 
\end{equation}
where $\varepsilon$ is defined in (\ref{eq:epsilontot}). We call such geometrical space the \texttt{tube} between $i$ and $j$.

When \qstatevarmath belongs to the \texttt{tube}, it might be that $u_{i}$ is activated instead of $u_{j}$ (or vice-versa). Otherwise, when \qstatevarmath does not belong to the tube, no matter the error $\varepsilon$, the right activation function is activated, and we consider only the error deriving from the computation itself.

Since computing $u_{i}$ introduces approximation error because of finite precision arithmetic, the system has to be robust against an error that is:

\begin{equation}\label{eq:fperror}
err(u_{i})_{p}=|(\hat{F}_{p}-F)\qstatevar+(\hat{G}_{p}-G)|
\end{equation}

where $\hat{F}$ and $\hat{G}$ represent the rounded values (in p bits) for the infinite precision values $F$ and $G$.

In (7) the domain of \qstatevarmath are all the points in region $i$, but also all the values in the \texttt{tube} between region $i$ and any of the neighbors of $i$. Even if some points in the tube do not belong to region $i$, it might that $u_{i}$ is (erroneously) activated.

We compute (\ref{eq:fperror}) for all regions in \statespace\space and we take the maximum value of the error (worst case):

\begin{equation}\label{eq:maxfperror}
\max_{\forall \regionimath{i}\;in\;\statespace} err(u_{i})_{p}
\end{equation}

The disturbance \texttt{delta}  has to be an upper bound to the summation of (\ref{eq:maximization}) and (\ref{eq:maxfperror}).

In formula:
\begin{flalign}
\label{eq:delta}
&delta >= \\
&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| + \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}

\subsection{Precision Tuning}
In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is generated by the quantization of hyperplanes $H\statevar<=K$ in a finite number of bits.
This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
The rule for $\varepsilon_{Q}$ is the following:
\begin{equation}\label{eq:quantizationlines}
\varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
\end{equation}
This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$.

Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: assign an arbitrary value to $\varepsilon_{Q}$ and find the minimal-precision p such that the inequality holds.

The main advantage in this approach (compared to fixing the precision p a priori), is that the value of p can be tuned based on the memory availability in the micro-controller.

To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, ables to provide a sound upper-bound to the maximal approximation error of a formula with respect to its real (infinite precision) counterpart. Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.

Since the state variable \statevarmath is bounded by \statespace, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.

In a similar way, we use Daisy to solve the inequality in (\ref{eq:delta}) with respect to p:
\begin{flalign}
\label{eq:deltaminusmax}
&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
\end{flalign}

Be aware that the left side of the inequality is not parametrized in p. Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p. After we come up with a numerical value for the left side of the inequality, we encode (\ref{eq:deltaminusmax}) in Daisy in the same way done for (\ref{eq:quantizationlines}).

\subsection{Algorithm}

\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},caption=design of robust MPC with verification and precision tuning,label={lst:alg}]
delta=input()
(*$\varepsilon_{Q}$*)=input()
assert (delta>=0 and (*$\varepsilon_{Q}$*)>0)
(*$\varepsilon$*)=(*$\varepsilon_{A/D}$*)+(*$\varepsilon_{Q}$*)

while True:
design_robust_MPC(delta)
maxUij = compute (*(\ref{eq:maximization})*) with size(tube)=(*$\varepsilon$*)
if delta > maxUij:
max_err=delta-maxUij
UNI_MIX_precision(F,G,max_err)
UNI_MIX_precision(H,K,(*$\varepsilon_{Q}$*))
break
else:
delta=maxUij+(*$\varepsilon_{SAFE}$*)
\end{lstlisting}
In Listing \ref{lst:alg} we describe the procedure used to design a robust MPC controller such that (\ref{eq:delta}) is respected.

First, the designer fixes the initial values for delta and $\varepsilon_{Q}$.

Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization value: it is going to fail the analysis (at least) for the first iteration because the error in (\ref{eq:maxfperror}) is going to be greater than zero (in the remote scenario where  (\ref{eq:maximization}) is equal to zero). A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.

On the other hand, the value for $\varepsilon_{Q}$ has to be strictly greater than zero, otherwise we could rely on infinite precision for p in (\ref{eq:quantizationlines}).

Once input parameters are verified, we use MATLAB toolbox to design a controller with robustness value equal to delta.

Then, we compute (\ref{eq:maximization}) and we compare the result with delta: we are aware that the computation of (\ref{eq:maximization}) is not exact (even if it is done in 64bits precision), but usually the computation of (\ref{eq:maximization}) results in a value that is several orders of magnitude greater than the error of the computation itself. For this reason we consider this approximation error negligible from the point of view of our analysis.

Again, in the conditional inside the loop, delta has to be strictly greater than \texttt{maxUij} otherwise we do not have space for computing the precision for (\ref{eq:deltaminusmax}).

In case the conditional statement is verified,
the precision tuning phase starts.
For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is exactly what is described in (\ref{eq:deltaminusmax}).

On the other hand, the quantization of polytopes borders (the region bounds in \statespace) can produce an error that is at most $\varepsilon_{Q}$, in this way we satisfy 
(\ref{eq:quantizationlines}).

In case the conditional fails and \texttt{maxUij} is greater than (or equal to) delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}. The same consideration done for the initialization of input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value for delta, to a value slightly greater than \texttt{maxUij}. In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop. Otherwise, in case $\varepsilon_{SAFE}$ is equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision value for p, usually greater than 32 bits. 
We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions: in case the analysis outputs a precision greater than 32bits, we fail in our goal.
Then, with a minimal alteration to the upper bound of delta, we sensibly reduce the precision needed for $F$ and $G$, with respect to the standard 32 bits precision.

### 2019-04-07 emsoft-2019/Motiv.tex

@@
+% !TEX root = main.tex
 \section{Motivation}
+
+Model Predictive Control (MPC) refers to the class of control strategies that design control actions by solving a finite horizon optimal control problem at each sampling instant.
+While each optimization gives a sequence of optimal control actions, only the first action is applied to the process.
+The same procedure is applied in the next time instance after receiving the updated value of the process state.
+MPC has shown to be successful in industrial applications since it is able to handle large number of states and control actions and automatically considers constraints in the optimization.
+
+The optimization of each time instance uses a dynamic model of the process to predict the future states and find the optimal sequence of actions that satisfies all the constraints.
+The objective function of the optimization is usually linear or quadratic.
+The resulting optimization problem can be cast as a linear program (LP) or quadratic program (LP), respectively, if the dynamic model is linear.
+For hybrid models with linear dynamics in each mode, the optimization problem can be cast as a mixed integer linear or quadratic program (MILP/MIQP).
+
+ The main difference between MPC and conventional control is in the nature of the function that maps the measured outputs to control actions.
+The former computes such a function online but the latter pre-computes it off-line.
+The required online computations in MPC limits its applicability to slow processes: the sampling time should be large enough to allow enough time for solving the optimization and obtaining the optimal action for the next time instance.
+Moreover, the optimization solver needs to be certified for using MPC in safety critical applications.
+ % while the  therefore that in the latter the control function is pre-computed off-line.
+These issues can be tackled using \emph{Explicit MPC} under proper assumptions on the model, constraints and the objective function.
+Explicit MPC solves the optimization problem off-line over a bounded domain of the state variables by using multiparametric programming techniques.
+The output of Explicit MPC is the optimal control actions as an ?explicit?
+function of the states which is piecewise affine.
+This expands the class of systems being controlled by MPC strategies since the implementation requires only storing a lookup table of linear gains and performing an affine computation using the appropriate gains at each time instance.
+A survey on Explicit MPC can be found in \cite{Alessio2009}.
+\Sadegh{fix the reference.}
+
 In this section, we use a classical control example to explain the motivation behind this work.

### 2019-04-07 emsoft-2019/Cont_Syn.tex
adding new sec. 4&5

\section{Controller Synthesis}
\eva{How we actually get the controller, including feedback loop and mixed-precision tuning}

### 2019-04-07 emsoft-2019/Error_Analysis.tex
adding new sec. 4&5

\section{Error Analysis}
\eva{Assuming a given precision, how to compute the error for a given controller}

### 2019-04-07 emsoft-2019/experiments.tex
Experiments

@@
 
-This section reports experiments with the prototype described in Listing\ref{lst:alg} applied to three different benchmarks: in the former two, we evaluate the complete pipeline (design and precision tuning) to produce in output a complete controller.
+This section reports experiments with the prototype described in Listing\ref{lst:alg} applied to three different benchmarks: in the former two, we evaluate the complete pipeline (design and memory optimization) to produce in output a complete controller.
 In the last one, we empirically show the scalability of our approach on one artificial sample.
-For the design of controllers we rely on MATLAB toolbox (YALMIP and 
+For the design of controllers we rely on MATLAB MPC toolbox.
+The outputs of the suite are vectors F, G and H, K for activation functions, and hyperplanes equations.
+We encode both of them in Daisy for finite-precision optimization.
 The design of controllers is done on a laptop with Intel i7-6700HQ CPU at 2.60GHz, with 16GB of RAM. 
-Only the last evaluation runs on a cluster with 48 cores Intel Xeon v2 @ 3.00GHz with 1TB of RAM, even if the memory consumption of the analysis never exceed 11GB.
+The analysis for the last benchmark runs on a cluster with 48 cores Intel Xeon v2 @ 3.00GHz with 1TB of RAM. Note that the memory consumption of our analysis never exceed 15GB of memory.
 
@@
 
-In Table \ref{tab:ipd} we report the evaluation of our approach on both: the inverted pendulum problem described in the motivation section, and a well-known 4D example for aircraft controller design.
+In Table \ref{tab:ipd} we report the evaluation of our approach on both the inverted pendulum problem described in the motivation section, and a well-known 4D example for aircraft controller design.
+For each benchmark, we report the results for ten different combinations of Delta and Eps.
+We divided them in two halves: in the  first we fix the value for Delta and we try different Eps combinations, while in the second halve we do the opposite.
 
-Describe 4D setup.
-
-For each one of the benchmarks, we report the results for ten different combinations of Delta and Eps.
-We dived them in two halves: in the  first we fix the value for Delta and we try different Eps combinations, while in the second halve we do the opposite.
-
-In the pendulum, for all the combinations of Delta and Eps, MATLAB Toolbox returns a controller with 14 regions and 58 hyperplanes, Delta spans the interval 0.05 - 0.3, while Eps is in the interval 0.0006 - 0.0050.
-In the pendulum section of Table \ref{tab:ipd}, the first halve shows that Delta does not affect the maximal error among regions \maxUij.
-We verify that a variation for delta (typically in the order of $\pm$ 0.1) results in a minimal alteration to the domain of regions X (in the order of $\pm 10^{-10}$), not enough to produce a sensitive variation to \maxUij.
-When \maxUij is constant, the error for imprecisions Err-Bound behaves the same as Delta.
-The domain of X for the pendulum is always in the bounded range $X_{0} \in (-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$.
+In the pendulum section of Table \ref{tab:ipd}, MATLAB returns a controller with 14 regions and 58 hyperplanes for each of the combinations of Delta and Eps.
+Delta spans the interval from 0.05 to 0.3, while Eps from 0.0006 to 0.0050.
+The domain of X for the pendulum is in the bounded range $X_{0} \in (-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$.
+The first halve of the section, shows that Delta does not affect the maximal error among regions \maxUij.
+We verify that a variation for Delta (typically in the order of $\pm$ 0.1) results in a minimal alteration to the domain of regions X (in the order of $\pm 10^{-10}$), not enough to produce a sensitive variation to \maxUij.
+When \maxUij is constant, the error for imprecisions Err-Bound behaves the same as Delta (they both decrease).
 The memory required for the storage of F and G depends on Err-Bound: the smaller the value for Err-Bound, the more demanding is the precision required for computations.
@@
 When we fix the value for Eps, and we try different delta, we save always 50\% from fixed-32 and about 10\% from Uni to Mixed.
-While in the second halve of the table, we fix the value for Delta and we try different Eps.
+In the second halve of the table, we fix the value for Delta and we try different Eps.
 When we increase the safe space between two regions by Eps, the value for \maxUij is computed for new corner points.
@@
 In the aircraft section of Table\ref{tab:ipd}, we report the results for the aircraft benchmark.
-MATLAB designs each time a controller with 27 regions and 217 hyperplanes, except for one case.
+MATLAB returns a controller with 27 regions and 217 hyperplanes, except for one combination of Delta and Eps.
 In general, when the disturbance value raises, two things can happen: the state domain X shrinks, to be robust against a greater disturbance, or the number of regions reduces.
-Other than that, the behaviors discussed for the pendulum are confirmed: when delta is small, the activation functions (F, G) are memory demanding.
-While when the value of Eps increases, the precision tuning phase can reduce the memory requirements for H, K.
-Anyway, there are two main differences with respect to the pendulum: the precision for F and G is almost double, this is because the magnitude of F and G is in the order of $10^{3}$ while for the pendulum is in the order of several units (note that the precision gain from Uni to Mix is only slightly less than the one for the pendulum).
-The second difference is in the last two lines in Table\ref{tab:ipd}.
-When Eps=0.0030, the \maxUij exceeds Delta=0.1 and we iterate again the design phase in Listing\ref{}.
-The final controller converges after 5 iterations with a Delta=0.112.
-Note the Err-Bound contains the safe coefficient epsilon to reduce the memory consumption.
-Otherwise the resulting controller would be expensive in memory (more than Fixed-64).
+The behaviors discussed for the pendulum are confirmed: when delta is small, the activation functions (F, G) are memory demanding.
+While when the value of Eps increases, the memory requirements for H, K can be relaxed.
+There are two main differences with respect to the pendulum: here the precision for F and G is almost double, this is because the magnitude of F and G is in the order of $10^{3}$ while for the pendulum is in the order of several units (note that the precision gain from Uni to Mix is only slightly less than the one for the pendulum).
+The second difference consists in the last two lines in Table\ref{tab:ipd}.
+When Eps=0.0030, the \maxUij exceeds Delta=0.1 and we need to design again the controller (it corresponds to the else branch in Listing\ref{fig:overview}).
+The analysis converges after 5 iterations with Delta=0.112.
+After each iteration, the new delta is the last \maxUij\space plus a constant value in the order of $10^{-3}$.
+In this way we sensibly reduce memory demand at the expense of slightly more disturbance.
+When Eps=0.0050 the analysis converges after 4 iterations and the same discussion holds.
 
-The last evaluation is done on an artificial controller designed for an aircraft control system.
-This controller consists of 1300 regions an about 25000 hyperplanes. In \ref{tab:di} we collect the results.
-The design of the controller in MATLAB takes few minutes, then the precision tuning phase starts.
-In average the analysis of a controller takes less than a minute and consumes less than 500MB of memory.
-In average the execution time of Daisy is less than 2 minutes for a single controller.
-In total we run 24681 analysis.
-The cluster where we run the evaluation comes with 48 cores.
-In average the memory consumption on the cluster is less than 15GB.
-We run the analysis in parallel on the cluster, because each activation function or hyperplane can be analyzed separately.
+The last benchmark is the double integrator, a canonical example of a second order control system. In Table\ref{tab:di} we collect the results.
+
+We introduce another parameter m, the prediction horizon of the controller. In this example, the number of regions is highly correlated with the prediction horizon m.
+Moreover, we fix the values for Delta to 0.1 and Eps to 0.001. In this experiment we focus on execution time of the analysis and memory optimization.
+
+The design of the controller in MATLAB takes few minutes, then it is is encoded in Daisy for memory optimization.
+In average the analysis of a controller in Daisy requires less than a minute, and less than 500MB of memory.
+The execution time of Daisy on a single activation function is less than 2 minutes.
+The cluster used for the evaluation comes with 48 cores, and the memory consumption on the cluster is always bounded in 15GB.
+The task is highly parallelizable, because any controller or hyperplane can be analyzed independently.
 
@@
 	\caption{Inverted Pendulum and Aircraft.\textmd{ Delta is the disturbance used to design the controller, and Eps the size of the safe space between two generic regions (\texttt{tube}).
-The values in red For each pair Delta, Eps we obtain a controller with Regs number of regions divided by Hyps hyperplanes.
+We fix Eps and try different Delta (in red) and vice-versa.
+For each pair Delta and Eps we obtain a controller with Regs number of regions divided by Hyps hyperplanes.
 The maximal error due to a wrong activation function is \maxUij and Err-Bound = Delta - maxUiUj.
-F, G and H, K represent the memory requirements for activation functions, and polytopes borders.
-Uni32 is the total number of bits for the controller, completely designed in fixed-32 bit precision.
-Uni is the uniform precision detected by our analysis, together with the format (p=format).
+F, G and H, K represent the memory requirements for activation functions, and hyperplanes.
+Uni32 is the total number of bits for the controller using 32 bits precision.
+Uni is the uniform precision found by our analysis, together with the format.
 Mix is the total number of bits for the controller in mixed-precision.
-\%32vsU is the difference between the baseline Uni32 and the number of bits used in U (in percentage), then \%UvsM is the difference between Uni and Mix.}}
+\%32vsU is the difference between the baseline Uni32 and Uni (in percentage), then \%UvsM is the difference between Uni and Mix.}}
 	\label{tab:ipd}
@@
 		\multicolumn{1}{c}{Hyps} &
-		\multicolumn{1}{c}{$max|U_{i}-U_{j}|$} &
+		\multicolumn{1}{c}{\maxUij} &
 		\multicolumn{1}{c}{Err-Bound} &
@@
 		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vsU}&
-		\multicolumn{1}{c}{\%UvsM}&
+		\multicolumn{1}{c}{\%32vU}&
+		\multicolumn{1}{c}{\%UvM}&
 		\multicolumn{1}{c}{Uni32}&
@@
 		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vsU}&
-		\multicolumn{1}{c|}{\%UvsM} \\
+		\multicolumn{1}{c}{\%32vU}&
+		\multicolumn{1}{c|}{\%UvM} \\
 		\cline{1-17}
@@
 	\end{tabular}
-	\vspace*{1 cm}
+\end{table}
+\end{landscape}
+
+\begin{table*}[ht]
 	\centering
-	\caption{For the description of each column see Table \ref{tab:ipd}.}
+	\caption{Double Integrator.\textmd{ Hrz is the prediction horizon in RMPC, Time is the execution time in minutes, Regs is the number of regions of the controller with Hyps hyperplanes.
+Uni32 is the total number of bits when all operations are in 32 bits, Uni the minimal uniform precision required, Mix is mixed-precision, \%32vU and UvM are the benefit of uniform and mixed precisions.}}
 	\label{tab:di}
-	\begin{tabular}{rrrrrrrrrrrrrr}
-		\cline{4-8}
+	\begin{tabular}{rrrrrrrrrrrrrrr}
+		\cline{5-8}
 		\cline{8-13}
-		\multicolumn{3}{c}{} &
+		\multicolumn{4}{c}{} &
 		%\multicolumn{2}{c}{} &
@@
 		%\cline{13-16}
-		\multicolumn{1}{c}{Exe-Time}&
+		\multicolumn{1}{c}{Hrz}&
+		\multicolumn{1}{c}{Time}&
 		%\multicolumn{1}{c}{Eps} &
@@
 		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vsU}&
-		\multicolumn{1}{c}{\%UvsM} \\
+		\multicolumn{1}{c}{\%32vU}&
+		\multicolumn{1}{c}{\%UvM} \\
 		\hline
-		445 min
-		&1299 & 23382 & 249408 & 109116 (p=14) & 80524 & 56.3\% & 26.2\% & 2992896 & 1589976 (p=17) & 1355675 & 46.9\% & 14.7\% \\
+		2 & 2 & 9 & 72 & 1728 & 810 (p=15) & 628 &  & 22.5\% & 13824 & 7776 (p=18) & 7280 & & 6.3\% \\
+		5 & 9 & 53 & 424 & 10176 & 5088 (p=16) & 3623 &  & 28.8\% & 81408 & 45792 (p=18) & 42656 & & 6.8\% \\
+		8 & 23 & 143 & 1144 & 27456 & 13728 (p=16) & 9864 &  & 28.1\% & 219648 & 123552 (p=18) & 114948 & & 7.0\% \\
+		11 & 47 & 277 & 2216 & 53184 & 26592 (p=16) & 18980 &  & 28.6\% & 425472 & 239328 (p=18) & 222616 & & 7.0\% \\
+
+		14 & 73 & 431& 3446& 82752& 41376(p=16)& 28685&  & 30\% & 661632& 372168 (p=18)& 346020& &7.0\% \\
+
+		17 & & & & & & & & & & & & & \\
+
+		21 & & & & & & & & & & & & & \\
+
+		25 & 445 &1299 & 23382 & 249408 & 109116 (p=14) & 80524 & 56.3\% & 26.2\% & 2992896 & 1589976 (p=17) & 1355675 & 46.9\% & 14.7\% \\
+
 	\end{tabular}
-\end{table}
-\end{landscape}
+\end{table*}

### 2019-04-07 emsoft-2019/Cont_Syn.tex
Distributing Rocco's texts between sec. 4&5; minor updates to sec. 2&3

@@
 \eva{How we actually get the controller, including feedback loop and mixed-precision tuning}
+In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.
+
+In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is generated by the quantization of hyperplanes $H\statevar<=K$ in a finite number of bits.
+This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
+The rule for $\varepsilon_{Q}$ is the following:
+\begin{equation}\label{eq:quantizationlines}
+\varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
+\end{equation}
+This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$.
+
+Our goal is to solve (\ref{eq:quantizationlines}) with respect to p: assign an arbitrary value to $\varepsilon_{Q}$ and find the minimal-precision p such that the inequality holds.
+
+The main advantage in this approach (compared to fixing the precision p a priori), is that the value of p can be tuned based on the memory availability in the micro-controller.
+
+To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, ables to provide a sound upper-bound to the maximal approximation error of a formula with respect to its real (infinite precision) counterpart.
+Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.
+
+Since the state variable \statevarmath is bounded by \statespace, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.
+
+In a similar way, we use Daisy to solve the inequality in (\ref{eq:delta}) with respect to p:
+\begin{flalign}
+\label{eq:deltaminusmax}
+&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
+& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
+\end{flalign}
+
+Be aware that the left side of the inequality is not parametrized in p.
+Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p.
+After we come up with a numerical value for the left side of the inequality, we encode (\ref{eq:deltaminusmax}) in Daisy in the same way done for (\ref{eq:quantizationlines}).
+
+\subsection{Algorithm}
+
+\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},caption=design of robust MPC with verification and precision tuning,label={lst:alg}]
+delta=input()
+(*$\varepsilon_{Q}$*)=input()
+assert (delta>=0 and (*$\varepsilon_{Q}$*)>0)
+(*$\varepsilon$*)=(*$\varepsilon_{A/D}$*)+(*$\varepsilon_{Q}$*)
+
+while True:
+design_robust_MPC(delta)
+maxUij = compute (*(\ref{eq:maximization})*) with size(tube)=(*$\varepsilon$*)
+if delta > maxUij:
+max_err=delta-maxUij
+UNI_MIX_precision(F,G,max_err)
+UNI_MIX_precision(H,K,(*$\varepsilon_{Q}$*))
+break
+else:
+delta=maxUij+(*$\varepsilon_{SAFE}$*)
+\end{lstlisting}
+In Listing \ref{lst:alg} we describe the procedure used to design a robust MPC controller such that (\ref{eq:delta}) is respected.
+
+First, the designer fixes the initial values for delta and $\varepsilon_{Q}$.
+
+Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization value: it is going to fail the analysis (at least) for the first iteration because the error in (\ref{eq:maxfperror}) is going to be greater than zero (in the remote scenario where  (\ref{eq:maximization}) is equal to zero).
+A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.
+
+On the other hand, the value for $\varepsilon_{Q}$ has to be strictly greater than zero, otherwise we could rely on infinite precision for p in (\ref{eq:quantizationlines}).
+
+Once input parameters are verified, we use MATLAB toolbox to design a controller with robustness value equal to delta.
+
+Then, we compute (\ref{eq:maximization}) and we compare the result with delta: we are aware that the computation of (\ref{eq:maximization}) is not exact (even if it is done in 64bits precision), but usually the computation of (\ref{eq:maximization}) results in a value that is several orders of magnitude greater than the error of the computation itself.
+For this reason we consider this approximation error negligible from the point of view of our analysis.
+
+Again, in the conditional inside the loop, delta has to be strictly greater than \texttt{maxUij} otherwise we do not have space for computing the precision for (\ref{eq:deltaminusmax}).
+
+In case the conditional statement is verified,
+the precision tuning phase starts.
+For the precision tuning of activation functions, we allow an error that is bounded by \texttt{max\_err}. This is exactly what is described in (\ref{eq:deltaminusmax}).
+
+On the other hand, the quantization of polytopes borders (the region bounds in \statespace) can produce an error that is at most $\varepsilon_{Q}$, in this way we satisfy 
+(\ref{eq:quantizationlines}).
+
+In case the conditional fails and \texttt{maxUij} is greater than (or equal to) delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \texttt{maxUij}.
+The same consideration done for the initialization of input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value for delta, to a value slightly greater than \texttt{maxUij}.
+In this way, we aim to give some space to the precision tuning phase in the next iteration of the loop.
+Otherwise, in case $\varepsilon_{SAFE}$ is equal to zero, the next iteration of the precision tuning phase is going to require unnecessarily wide precision value for p, usually greater than 32 bits.
+We remark that the point of the analysis is to find a low precision configuration for bounds and activation functions: in case the analysis outputs a precision greater than 32bits, we fail in our goal.
+Then, with a minimal alteration to the upper bound of delta, we sensibly reduce the precision needed for $F$ and $G$, with respect to the standard 32 bits precision.

### 2019-04-07 emsoft-2019/Error_Analysis.tex
Distributing Rocco's texts between sec. 4&5; minor updates to sec. 2&3

@@
 \eva{Assuming a given precision, how to compute the error for a given controller}
+The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of imperfect implementation of point location algorithm, and (ii) the approximation error deriving from finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.\\
+In an hypothetic scenario where all the measurements were done in infinite precision arithmetic and without any uncertainty, we assume the controller $i$ would be activated.
+Instead, because we cannot rely on infinite precision, controller $j$ is selected.
+The error committed is the difference between the output of the two branches $i$ and $j$.
+
+The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa), only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
+Moveover, we are interested in the worst case scenario where is maximized the difference between the activation functions of any two neighbor regions.
+Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.
+
+Our goal is to build a feasible geometrical space around the border between two neighbor regions $i$ and $j$, where actually it is feasible that \statevarmath belongs to region $i$ but \qstatevarmath follows in region $j$ (or vice-versa).
+We call this geometrical space the \texttt{tube}.
+
+There are two main sources of error affecting the size of the \texttt{tube}: (i) the first one is caused by analog-digital conversion, happening just before the controller receives an estimation of the plant from the sensors.
+We call this error $\varepsilon_{A/D}$:
+
+\begin{equation}\nonumber
+\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
+\end{equation}
+
+Where $V_{cc}$ is the reference voltage of the converter (e.g. typical 5V) and $p$ represents the number of bit of the processor.
+
+The second error affecting the size of the \texttt{tube} is caused by (ii) the quantization of region bounds in the memory of the micro-controller.
+We call this error $\varepsilon_{Q}$ for error quantization.
+
+While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries.
+This second error can be regulated based on a trade-off among accuracy of the storage and memory save~\cite{memoryMPC}.
+
+The total size of the \texttt{tube} is then:
+\begin{equation}\label{eq:epsilontot}
+\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
+\end{equation}
+%\subsection{Finite Precision Implementation}
+
+The effect of picking the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}.
+
+In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:
+\begin{flalign}
+\label{eq:maximization}
+&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
+&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
+\end{flalign}
+where \statevarmath belongs to the \texttt{tube} between region $i$ and $j$.
+Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$ and $j$, it is enough to evaluate function (\ref{eq:maximization}) at the corner points of the \texttt{tube}, instead of solving a maximization problem.
+
+We compute (\ref{eq:maximization}) for all pairs of neighbor regions $i$ and $j$. Two regions are neighbors when they share at least a border.
+
+In formula $\exists\; m,n \;$such that:
+\begin{equation}
+(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
+\end{equation}
+where $m$ and $n$ are the index of the two matching borders. We label with $border_{i,j}$ the matching border shared among the two regions.
+
+Starting from the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute (\ref{eq:maximization}) with: 
+\begin{equation}
+\begin{aligned}
+(border_{i,j} >= -\varepsilon) \land
+(border_{i,j} <= \varepsilon)
+\end{aligned} 
+\end{equation}
+where $\varepsilon$ is defined in (\ref{eq:epsilontot}). We call such geometrical space the \texttt{tube} between $i$ and $j$.
+
+When \qstatevarmath belongs to the \texttt{tube}, it might be that $u_{i}$ is activated instead of $u_{j}$ (or vice-versa).
+Otherwise, when \qstatevarmath does not belong to the tube, no matter the error $\varepsilon$, the right activation function is activated, and we consider only the error deriving from the computation itself.
+
+Since computing $u_{i}$ introduces approximation error because of finite precision arithmetic, the system has to be robust against an error that is:
+
+\begin{equation}\label{eq:fperror}
+err(u_{i})_{p}=|(\hat{F}_{p}-F)\qstatevar+(\hat{G}_{p}-G)|
+\end{equation}
+
+where $\hat{F}$ and $\hat{G}$ represent the rounded values (in p bits) for the infinite precision values $F$ and $G$.
+
+In (7) the domain of \qstatevarmath are all the points in region $i$, but also all the values in the \texttt{tube} between region $i$ and any of the neighbors of $i$.
+Even if some points in the tube do not belong to region $i$, it might that $u_{i}$ is (erroneously) activated.
+
+We compute (\ref{eq:fperror}) for all regions in \statespace\space and we take the maximum value of the error (worst case):
+
+\begin{equation}\label{eq:maxfperror}
+\max_{\forall \regionimath{i}\;in\;\statespace} err(u_{i})_{p}
+\end{equation}
+
+The disturbance \texttt{delta}  has to be an upper bound to the summation of (\ref{eq:maximization}) and (\ref{eq:maxfperror}).
+
+In formula:
+\begin{flalign}
+\label{eq:delta}
+&delta >= \\
+&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| + \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
+\end{flalign}

### 2019-04-07 emsoft-2019/Methodology.tex
Distributing Rocco's texts between sec. 4&5; minor updates to sec. 2&3

@@
 
-%Consider the (discrete) state space model:
-%\begin{flalign}\label{eq:statespacemodel}
-%& x_{k+1} = A\statevar + Bu_{k}
-%%& y_{k} = C\statevar\nonumber
-%\end{flalign}
+Consider the (discrete) state space model:
+\begin{flalign}\label{eq:statespacemodel}
+& x_{k+1} = A\statevar + Bu_{k}
+%& y_{k} = C\statevar\nonumber
+\end{flalign}
 
-%where $\statevar\in\mathbb{R}_{n}$ is the state variable at time $k$, $u_{k}$ is the scalar control input, and $A\in\mathbb{R}^{nxn}$ and $B\in\mathbb{R}^{n}$ guarantee the stability of the system at runtime.
+where $\statevar\in\mathbb{R}_{n}$ is the state variable at time $k$, $u_{k}$ is the scalar control input, and $A\in\mathbb{R}^{nxn}$ and $B\in\mathbb{R}^{n}$ guarantee the stability of the system at runtime.
 
-%The controller $u_{k}$ for (\ref{eq:statespacemodel}) is found by solving an off-line optimization problem.
+The controller $u_{k}$ for (\ref{eq:statespacemodel}) is found by solving an off-line optimization problem.
 We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}.
-%The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called region.
-%A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar<=K_{i}$.
+The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called region.
+A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar<=K_{i}$.
 
-%We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
-%\begin{equation}
-%\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
-%\end{equation}
+We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
+\begin{equation}
+\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
+\end{equation}
 
@@
 
-%Each region $i$ is associated with an activation function $u_{i,k}=F_{i}x_{k}+G_{i}$.
+Each region $i$ is associated with an activation function $u_{i,k}=F_{i}x_{k}+G_{i}$.
 At runtime, the value of state variable \statevarmath  is compared against the polytopes bounds: depending on the region $i$ containing \statevarmath, the corresponding activation function $u_{i}$ is computed.
 
-%A drawback in the design of explicit MPC is that both regions boundaries (H and K) and activation functions (F and G), have to be stored on the micro-controller.
+A drawback in the design of explicit MPC is that both regions boundaries (H and K) and activation functions (F and G), have to be stored on the micro-controller.
 Usually these devices have limited memory, in the order of KBs.
 
-%This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.
-%
-%\begin{lstlisting}[escapeinside={(*}{*)},label={lst:caseof}, caption=switch for region selection]
-%switch((*\statevarmath*)):
-%case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{1}$*)
-%case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}$*)
-%case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}$*)
-%...
-%case (*$ H_{n}\statevar<=K_{n}$*) then (*$u_{n}$*)
-%\end{lstlisting}
+This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.
+
+\begin{lstlisting}[escapeinside={(*}{*)},label={lst:caseof}, caption=switch for region selection]
+switch((*\statevarmath*)):
+case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{1}$*)
+case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}$*)
+case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}$*)
+...
+case (*$ H_{n}\statevar<=K_{n}$*) then (*$u_{n}$*)
+\end{lstlisting}
 

### 2019-04-07 emsoft-2019/Motiv.tex
Distributing Rocco's texts between sec. 4&5; minor updates to sec. 2&3

@@
 	Overlay, we would like to design a robust explicit model predictive controller, taking into account errors resulted by fixed-point arithmetic and more importantly, to come up with a set of varying precision assignment that covers all the coefficients that must be saved over the embedded system.
-To that end, one approach is to start with an initial $\Delta$; design a robust explicit MPC controller with respect to $\Delta$ and to use state of the art fixed-point error analyzers to decide for the number of bits for saving every parameter characterizing the controller.
+To that end, one approach is to start with an initial $\Delta$; design a robust explicit MPC controller with respect to $\Delta$ and to use state of the art fixed-point error analyzers to decide for the number of bits for saving every parameter of the controller.
 Figure \ref{fig:overview} gives an overview of our proposed setup.\\
@@
 Therefore, we go ahead and choose $\Delta=0.1$.
-Solving Robust EMPC problem for the new disturbance bound gives $14$ controllers.
+Solving robust EMPC problem for the new disturbance bound gives $14$ controllers.
 Next, we ask Daisy to provide us with fixed-point precisions for every variable that respects $\Delta$.
@@
 
-	\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
+	\tikzstyle{block} = [draw, rectangle, 
 	minimum height=3em, minimum width=6em]
-	\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
+	\tikzstyle{sum} = [draw,  circle, node distance=1cm]
 	\tikzstyle{input} = [coordinate]
@@
 			\centering
-			\node [block, pin={[pinstyle]above:$\Delta=\Delta_0$},
-			node distance=5cm] (RMPC) {Robust MPC design};
+			\node [block,scale=.8, pin={[pinstyle]above:$\Delta=\Delta_0$},
+			node distance=5cm] (RMPC) {RMPC design (MATLAB)};
 			\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
-			\node [block, right of=RMPC,
-			node distance=5cm,text width=3cm] (mixed) {Mixed precision analysis};
-			\node [draw, fill=blue!20, diamond, 
+			\node [block, scale=1,right of=RMPC,
+			node distance=5cm,text width=3cm] (mixed) {Mixed precision computation (Daisy)};
+			\node [draw, diamond, 
 			minimum height=3em, minimum width=3em, right of=mixed,
-			node distance=5cm] (decide) {Is memory violated?};
+			node distance=5cm] (decide) {$N_b\leq \bar N_b$};
 			\node [block, right of=decide,
@@
 			node distance=3cm] (delta) {increase $\Delta$};
+			\node [scale=.3] at (2.25,-.5)  {
+				$
+				K(x_k)=
+				\begin{cases}
+				F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
+				F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
+				\vdots\\
+				F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
+				\end{cases} 
+				$
+			};
+		\node at (7.5,-.35) {$N_b$};
 
@@
 	\end{tikzpicture}
-	\caption{high level description of RMPC with Daisy}
+	\caption{high level description of the proposed memory-efficient robust MPC design}
 	\label{fig:overview}

### 2019-04-07 emsoft-2019/RMPC_Daisy.tex
Distributing Rocco's texts between sec. 4&5; minor updates to sec. 2&3

@@
 \end{lstlisting}
-Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves symmation and multiplication.
+Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.
 

### 2019-04-08 emsoft-2019/Error_Analysis.tex
minor updates

@@
 The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa), only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
-Moveover, we are interested in the worst case scenario where is maximized the difference between the activation functions of any two neighbor regions.
+Moreover, we are interested in the worst case scenario where is maximized the difference between the activation functions of any two neighbor regions.
 Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.

### 2019-04-08 emsoft-2019/Motiv.tex
minor updates

@@
 Consider the problem of designing stablizing control for an inverted pendulum which takes (polytopic) constraints over state variables and control inputs into account.
-The linearized continuous-time description for the open-loop system's dynamics is as follows:
+The linearized descrete-time description for the open-loop system's dynamics is as follows:
 	\begin{equation}
@@
 Computing the optimal control input can be efficiently done using for example binary tree search.
-However, the memory limit is more cruicial as it increases proportional to the number of partitions.	Therefore, we would like to explore ways to reduce required memory for saving different coefficients corresponding to the controllers.
+However, the memory limit is more crucial as it increases proportional to the number of partitions.	Therefore, we would like to explore ways to reduce required memory for saving different coefficients corresponding to the controllers.
 	On the other hand, most of the industrial embedded systems over which EMPC is implemented, only support fixed point arithmetic.

### 2019-04-08 emsoft-2019/RMPC_Daisy.tex
minor updates

@@
 \def\reals{\mathbb{R}}
-We consider class of discrete time linreat time invariant systems
+We consider class of discrete time linear time invariant systems
 \begin{equation}
@@
 By making use of the fact that $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$, one can translate \eqref{eq:RMPC_prob} into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$.
-Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polydedral regions:
+Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polyhedral regions:
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{R}_i$ is a ploytob determined by  a set of linear inequalities $H_ix\leq K_i$.
+where $\mathcal{R}_i$ is a ploytop determined by  a set of linear inequalities $H_ix\leq K_i$.
 To find the controller $K$ we rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}.
@@
 
-A main issue with implimentation of explicit MPC is that all the products of off-line optimization, including regions' boundaries ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s), have to be stored on the micro-controller.
-However, these embudded systems have limited memory, in the order of KBs and hence, it is of our interest to minimize the occupied memory.
+A main issue with implementation of explicit MPC is that all the products of off-line optimization, including regions' boundaries ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s), have to be stored on the micro-controller.
+However, these embedded systems have limited memory, in the order of KBs and hence, it is of our interest to minimize the occupied memory.

### 2019-04-08 emsoft-2019/experiments.tex
a few comments on experiments section

@@
+%!TEX root = main.tex
 \section{Experimental Results}
@@
 \subsection{Results}
+\eva{I'd split this into two subsections, one for the end-to-end experiments, and
+one for demonstrating scalability (and use the subsection names as well to make this clear)}
+\eva{Is the 4D aircraft example introduced/explained before? If not, this should be done first,
+including a citation.}
 
@@
 We divided them in two halves: in the  first we fix the value for Delta and we try different Eps combinations, while in the second halve we do the opposite.
+\eva{To make Table 1 fit without a rotation, remove at least all constant info (like the number
+of regions). The two columns with the errors are probably also not needed.}
+\eva{Use the same symbol for Delta and Eps as used in the technical section.}
 
+\eva{In the following, I'd discuss the two examples together and structure the 
+discussion as follows:
+\begin{itemize}
+	\item give the constant info (number of regions etc.) for both benchmarks
+	\item explain the variation of delta and eps (ideally with a motivation for why this is interesting)
+	\item discuss the improvements we get (i.e. first discuss the metric we care about most)
+	\item discuss other interesting details
+\end{itemize}
+Discussing the two examples together let's us compare their results easier, i.e.
+point out differences or commonalities.
+}
+\eva{Add running times of the analysis in Table 1 (possibly as a separate small table)}
 In the pendulum section of Table \ref{tab:ipd}, MATLAB returns a controller with 14 regions and 58 hyperplanes for each of the combinations of Delta and Eps.

### 2019-04-08 emsoft-2019/RMPC_Daisy.tex

@@
-\section{Robust MPC and Finite Precision}
+% !TEX root = main.tex
+\section{Explicit MPC and Finite Precision}
 \subsection{Robust Explicit MPC}
 \def\reals{\mathbb{R}}
-We consider class of discrete time linear time invariant systems
+We consider the class of linear time-invariant (LTI) systems characterized by the difference equation
 \begin{equation}
 \label{eq:DSS}
-x_{k+1}=Ax_k+Bu_k+Ew_k
+x_{k+1}=Ax_k+Bu_k+Ew_k,\quad  k=0,1,2,\ldots
 \end{equation}
-where, $x\in \reals^{n\times 1}$ is state vector, $u\in \reals^{m\times 1}$ the control input vector, $w\in \reals^{d\times 1}$ the disturbance vector, $A\in \reals^{n\times n}$ the state matrix, $B\in \reals^{n\times m}$ the input matrix, $E\in \reals^{n\times d}$, $k$ the time instant and the pair $(A,B)$ is stablizable.
-Knowing that $w\in\mathcal{W}$, where $\mathcal{W}$ is a polyhedral set, we try to solve for the following optimization problem:
+where $x\in \reals^{n\times 1}$ is the state, $u\in \reals^{m\times 1}$ is the control input and $w\in \reals^{d\times 1}$ is the disturbance.
+Matrices $A\in \reals^{n\times n}$, $B\in \reals^{n\times m}$ and $E\in \reals^{n\times d}$ are capturing respectively the effects of current state, input and disturbance on the next state.
+We assume the pair $(A,B)$ is stablizable.
+\Sadegh{Where do you need this assumption?}
+We assume that the disturbance $w$ belongs to the set $\mathcal{W}$ where $\mathcal{W}$ is a polyhedral set.
+In this paper, we focus on robust formulation of MPC which at each time step, minimizes the worst-case value of the objective function with respect to the disturbances.
+We also consider the objective function to be quadratic with respect to the states and inputs.
+The constrained optimization of each step can be written as
 \begin{align}
 \label{eq:RMPC_prob}
-\min_{u_0,\cdots,u_{N-1}}\max_{w_0,\cdots,w_{N-1}}& x_N^TQ_Fx_N+\sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i)\nonumber\\
-\text{s.t.}\quad\forall i\in\{0,1,\cdots,&N-1\}:\nonumber\\
-&x_{i+1}=Ax_i+Bu_i\nonumber\\
-&x_i\in\mathcal{X},\quad u_i\in \mathcal{U}	
+\min_{u_0,\cdots,u_{N-1}}& \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
+\text{s.t.} \quad &x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\\
+&x_i\in\mathcal{X},\quad u_i\in \mathcal{U},\nonumber
 \end{align}
-where, $\mathcal U$ and $\mathcal X$ are polyhedral sets, $Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon.
-By making use of the fact that $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$, one can translate \eqref{eq:RMPC_prob} into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$.
+\Sadegh{The role of disturbance is missing in the inequalities. We should say, we want to satisfy the inequalities for all possible values of the disturbance.}
+
+where $\mathcal U$ and $\mathcal X$ are polyhedral sets as feasible sets of inputs and states.
+$Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon.
+\begin{theorem}[\Sadegh{add reference}]
+The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$.
 Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polyhedral regions:
@@
 \end{equation}
-where $\mathcal{R}_i$ is a ploytop determined by  a set of linear inequalities $H_ix\leq K_i$.
-To find the controller $K$ we rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}.
+where $\mathcal{R}_i$ is a ploytope determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
+\end{theorem}
+The essential idea of this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and .... 
+\Sadegh{What is a multi-parametric quadratic problem? Not defined.}
+
+\Sadegh{Adding a remark and saying that the approach works as long as the solution of formulated optimization has a piecewise affine form?}
+
+The controller $K$ can be computed using multi-parametric toolbox of MATLAB~\cite{matlabMPT, matlabYALMIP}.
 We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
@@
 \end{equation}
-Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong.
-Several algorithms are proposed to solve for this problem [references?].
-The simplest technique to verify which region \statevarmath belongs to is to make a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.
+\Sadegh{Is this set different from $\mathcal X$? We should explain why it is different.}
+
+The actual implementation of the controller requires storing the matrices $F_i,G_i,H_i,K_i$ for all $i\in\{1,2,\ldots,P\}$.
+At each time step $k$, the current state $x_k$ is used to detect the right polytope $i$ such that $H_i x_k\le K_i$.
+Then the control action $u_k = F_i x_k + G_i$ is computed and applied to the system.
+
+%Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong.
+Several algorithms are proposed in the literature \Sadegh{[references?]} to find the right polytope $i$ to which the state $x_k$ belong.
+The most straightforward technique is a linear search over all polytopes in \Sadegh{\statespace\space} using a switch/case conditional statement of Listing \ref{lst:caseof}.
+\Sadegh{Perhaps we can mention another approach here? add references.}
 
@@
 \end{lstlisting}
-Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.
+%Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.
 
-A main issue with implementation of explicit MPC is that all the products of off-line optimization, including regions' boundaries ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s), have to be stored on the micro-controller.
-However, these embedded systems have limited memory, in the order of KBs and hence, it is of our interest to minimize the occupied memory.
+To keep the costs of implementation down, low-end microcontrollers usually have limited memory and computational power.
+Therefore, implementation of the above explicit MPC on microcontrollers will bring some issues since all regions' matrices ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s) have to be stored on the microcontroller.
+The goal of our paper is present an approach for minimizing the memeory usage of the implementation while satisfying the hard constraints on the states.
+
+\section{Finite Precision Implementation}
+\Sadegh{To be included by Rocco}

### 2019-04-08 emsoft-2019/Motiv.tex
updating sec. 2

@@
 This expands the class of systems being controlled by MPC strategies since the implementation requires only storing a lookup table of linear gains and performing an affine computation using the appropriate gains at each time instance.
-A survey on Explicit MPC can be found in \cite{Alessio2009}.
-\Sadegh{fix the reference.}
-
+A survey on Explicit MPC can be found in \cite{Alessio2009}.\\
+\begin{figure}[t]
+	\includegraphics[width=3cm,height=5cm]{Figs/inv_pend.png}
+	\label{fig:inverted_pendulum}
+	\caption{Inverted pendulum}
+\end{figure}
 In this section, we use a classical control example to explain the motivation behind this work.
 Consider the problem of designing stablizing control for an inverted pendulum which takes (polytopic) constraints over state variables and control inputs into account.
-The linearized descrete-time description for the open-loop system's dynamics is as follows:
+The linearized descrete-time description for the inverted pendulum depicted in Fig.
+\ref{fig:inverted_pendulum} is as follows:
 	\begin{equation}
@@
 			1 & T_s\\
-			\frac{T_sg}{l}& (1-\frac{T_sb}{ml^2})		
+			\frac{T_sg}{L}& (1-\frac{T_sb}{mL^2})		
 		\end{bmatrix}
@@
 			0\\
-			\frac{T_s}{ml^2}
+			\frac{T_s}{mL^2}
 		\end{bmatrix}u_k
@@
 	\end{equation}
-	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitational acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient, $L$ the length of the bar and $T_s$ an appropriate sample time.
+	where, $\theta$, $\omega$ and $u=\tau$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitational acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient, $L$ the length of the bar and $T_s$ an appropriate sample time.
 Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point while always $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$.
@@
 It is necessary to count for approximation error as it might lead into violation of the constraints.
-Therefore, one needs to formulate the problem as robust EMPC to count for disturbance input $|\delta|\leq \Delta$ which is summed up with the control input torque $u$ in each time step.
-%Setting the number of bits for storing different variables, one can compute the upper bound for approximation error, $\bar\omega$.
+Therefore, one needs to formulate the problem as robust EMPC to count for disturbance input $|\delta|\leq \Delta$ which is summed up with the control input torque $u$ in each time step.\\ %Setting the number of bits for storing different variables, one can compute the upper bound for approximation error, $\bar\omega$.
 	%However, we would like to achieve the minimum number of bits to reduce memory requirements.
-	Overlay, we would like to design a robust explicit model predictive controller, taking into account errors resulted by fixed-point arithmetic and more importantly, to come up with a set of varying precision assignment that covers all the coefficients that must be saved over the embedded system.
-To that end, one approach is to start with an initial $\Delta$; design a robust explicit MPC controller with respect to $\Delta$ and to use state of the art fixed-point error analyzers to decide for the number of bits for saving every parameter of the controller.
-Figure \ref{fig:overview} gives an overview of our proposed setup.\\
-	Again, back to inverted pendulum example, choosing $\Delta=0$, we design an explicit MPC which contains $12$ regions and the same number of controllers.
-However, this value for $\Delta$ is not realizable as error resulted from fixed-point implementation cannot become zero.
-Therefore, we go ahead and choose $\Delta=0.1$.
-Solving robust EMPC problem for the new disturbance bound gives $14$ controllers.
-Next, we ask Daisy to provide us with fixed-point precisions for every variable that respects $\Delta$.
-Using the output of Daisy, we are able to reduce memory requirements for the embedded systems up-to $20\%$ comparing to the case that uniform fixed-point precision is used.
+	Overlay, we would like to design a robust explicit model predictive controller, taking errors resulted by fixed-point arithmetic into account and to come up with a minimal set of mixed precision assignments for all the coefficients that must be stored over the embedded system.
+Let us denote the total number of bits required for implementation of RMPC by $N_b$.
+Given the maximum memory budget denoted by $\bar N_b$, the overal goal will be to design a robust EMPC that (i) achieves performance objectives such as stability, safety and so on; (ii) it is implemented in a way that $N_b\leq \bar N_b$ while the error resulted by fixed-point arithmetic is smaller than the error bound $\Delta$.
+To that end, our approach is to start with an initial $\Delta$; design a robust explicit MPC controller with respect to $\Delta$ and to use state of the art fixed-point error analyzers to come up with the minimum total number of bits for storing the controller into the embedded system.\\
+
+	Figure \ref{fig:overview} gives a high-level overview of our proposed setup.
+We start with definint the memory budget $\bar N_b$ and an initial error bound $\Delta_0$.
+Again, back to the inverted pendulum example, we choose $\bar N_b=6000$ and $\Delta_0=0$.
+To design robust explicit MPC for the error bound $\Delta$, MATLAB is run and the output controller is computed.
+Next, we ask Daisy to provide us with a mixed precision scheme respecting the error bound $\Delta=0$.
+However, $\Delta=0$ is not realizable as error resulted from fixed-point implementation is always greater than zero.
+Therefore, we go ahead and choose $\Delta=0.05$.
+Solving robust EMPC problem for the new disturbance bound gives the new controller.
+Next, we ask Daisy to provide us with fixed-point precision for all the parameters such that $\Delta=0.05$ is respected.
+The mixed precision scheme given by Daisy results in total number of bits $N_b=6084$ and since $N_b>\bar N_b$, we increase $\Delta$ again.
+Choosing $\Delta=0.1$, Daisy provides us with a mixed precision scheme with $N_b=5900$ for the correponding robust EMPC.
+As $N_b<\bar N_b$ the design goals are satisfied and the loop stops here.
+Surprisingly, the mixed precision implementation takes $11\%$ less memory comparing to the smallest uniform precision that respects $\Delta$.
+%	Using the output of Daisy, we are able to reduce memory requirements for the embedded systems up-to $20\%$ comparing to the case that uniform fixed-point precision is used.
 
@@
 	\end{tikzpicture}
-	\caption{high level description of the proposed memory-efficient robust MPC design}
+	\caption{high-level description of the proposed memory-efficient robust MPC design}
 	\label{fig:overview}

### 2019-04-08 emsoft-2019/Motiv.tex

@@
 \begin{figure}[t]
-	\includegraphics[width=3cm,height=5cm]{Figs/inv_pend.png}
 	\label{fig:inverted_pendulum}
-	\caption{Inverted pendulum}
+	\begin{tabular}{cc}
+	\includegraphics[width=2cm,height=4cm]{Figs/inv_pend.png}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
+	(a)&(b)
+	\end{tabular}
+	\caption{(a) Inverted pendulum; (b) 2-D plot of explicit MPC polyhedral partitions for the inverted pendulum}
 \end{figure}
@@
 Consider the problem of designing stablizing control for an inverted pendulum which takes (polytopic) constraints over state variables and control inputs into account.
-The linearized descrete-time description for the inverted pendulum depicted in Fig.
-\ref{fig:inverted_pendulum} is as follows:
+The linearized discrete-time description for the inverted pendulum depicted in Fig.
+\ref{fig:inverted_pendulum} (a) is as follows:
 	\begin{equation}
@@
 	where, $\theta$, $\omega$ and $u=\tau$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitational acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient, $L$ the length of the bar and $T_s$ an appropriate sample time.
-Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point while always $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$.
+Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point ($\theta=0$ and $\omega=0$) while $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$ within the time horizon $N=2$.
 \\
@@
 	However, one major challenge for implementing model predictive controllers over embedded systems will be to solve MPC optimality problem within each time step.
-Since the system under consideration is LTI, one can use explicit MPC scheme proposed in [Bemporad:2002] which computes partitions over state space together with affine functions which are used to compute the optimal control input over their corresponding partition.
+Since the system under consideration is LTI, one can use explicit MPC scheme proposed in \cite{Bemporad:2002} which computes partitions over state space together with affine functions which are used to compute the optimal control input over their corresponding partition.
 For the inverted-pendulum example, the computed controller contains $12$, over each an affine function is provided for generating the control input.\\
@@
 Let us denote the total number of bits required for implementation of RMPC by $N_b$.
-Given the maximum memory budget denoted by $\bar N_b$, the overal goal will be to design a robust EMPC that (i) achieves performance objectives such as stability, safety and so on; (ii) it is implemented in a way that $N_b\leq \bar N_b$ while the error resulted by fixed-point arithmetic is smaller than the error bound $\Delta$.
+Given the maximum memory budget denoted by $\bar N_b$, the overall goal will be to design a robust EMPC that (i) achieves performance objectives such as stability, safety and so on; (ii) it is implemented in a way that $N_b\leq \bar N_b$ while the error resulted by fixed-point arithmetic is smaller than the error bound $\Delta$.
 To that end, our approach is to start with an initial $\Delta$; design a robust explicit MPC controller with respect to $\Delta$ and to use state of the art fixed-point error analyzers to come up with the minimum total number of bits for storing the controller into the embedded system.\\
@@
 	Figure \ref{fig:overview} gives a high-level overview of our proposed setup.
-We start with definint the memory budget $\bar N_b$ and an initial error bound $\Delta_0$.
+We start with defining the memory budget $\bar N_b$ and an initial error bound $\Delta_0$.
 Again, back to the inverted pendulum example, we choose $\bar N_b=6000$ and $\Delta_0=0$.
@@
 The mixed precision scheme given by Daisy results in total number of bits $N_b=6084$ and since $N_b>\bar N_b$, we increase $\Delta$ again.
-Choosing $\Delta=0.1$, Daisy provides us with a mixed precision scheme with $N_b=5900$ for the correponding robust EMPC.
+Choosing $\Delta=0.1$, Daisy provides us with a mixed precision scheme with $N_b=5900$ for the corresponding robust EMPC.
 As $N_b<\bar N_b$ the design goals are satisfied and the loop stops here.

### 2019-04-08 emsoft-2019/RMPC_Daisy.tex
seperating 3.1 and 3.2

@@
 \end{theorem}
-The essential idea of this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and .... 
-\Sadegh{What is a multi-parametric quadratic problem? Not defined.}
+The essential idea of this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ of the following form:
+\begin{align}
+	&\min_{U_N}U_N^TZU_N+x_0^TVU_N+x_0^TYx_0\nonumber\\
+	&s.t.\quad JU_N\leq s+Dx_0
+\end{align} 
+where, $Z\in \reals^{mN\times mN}$, $V\in\reals^{n\times mN}$, $Y\in\reals^{n\times n}$, $J\in\reals^{q\times mN}$, $s\in\reals^{q}$, $D\in\reals^{q\times n}$ and $q$ is the number of inequalities.
+%\Sadegh{What is a multi-parametric quadratic problem? Not defined.}
 
-\Sadegh{Adding a remark and saying that the approach works as long as the solution of formulated optimization has a piecewise affine form?}
+%\Sadegh{Adding a remark and saying that the approach works as long as the solution of formulated optimization has a piecewise affine form?}
 
@@
 The goal of our paper is present an approach for minimizing the memeory usage of the implementation while satisfying the hard constraints on the states.
-
-\section{Finite Precision Implementation}
-\Sadegh{To be included by Rocco}
+%\section{Finite Precision Implementation}
+%\Sadegh{To be included by Rocco}

### 2019-04-09 emsoft-2019/finite_precision.tex
draft of finite-precision background

%!TEX root = main.tex
\subsection{Finite Precision Implementation}

The controller has to be stored and implemented on the microcontroller in
finite-precision, since infinite-precision real values cannot be stored on
today's digital computers.
The standard choice for low-power platforms is fixed-point arithmetic. Unlike
floating-point arithmetic, fixed-point arithmetic can be implemented efficiently
without complex hardware support using only integer operations. It requires,
however, more compilation effort as, certain operations (that the floating-point
hardware unit performs dynamically) now have to be determined statically at
compile time.

% general blob about fixed-point arithmetic
\eva{Need to mention somewhere that we need input ranges}
The main task at compile time is to select the fixed-point format for each value
in the program. The format specifies the total word length and how many bits are
available for the integer part of the number. To choose a sufficient number of
integer bits to avoid overflow, but to not overprovision unnecessarily, we can
use a range analysis which estimates the possibles ranges of all values
in the program. The remaining bits of the total word length are represent the
fractional part of a number, i.e. more fractional bits result in precise
computations.
Fixed-point arithmetic implementations can choose different rounding modes; here
we consider standard and efficient truncation.

% introduces roundoff errors, these can be tracked with a dataflow analysis
Finite precision unavoidably introduces roundoff errors when storing and
performing arithmetic, which can accumulate during the course of a computation.
A sound static roundoff error analysis computes a guaranteed upper bound on the
error of the result by tracking worst-case errors at every operation. Given a
word length for each value, several tools~\cite{} compute roundoff errors using
a dataflow analysis.
They track real-valued ranges at every intermediate operation. These ranges
determine the fixed-point formats and thus also the individual roundoff errors,
which are captured and tracked separately from the ranges. To ensure guaranteed
error bounds, both the ranges and errors are tracked using interval~\cite{} or
affine arithmetic~\cite{} which compute sound enclosures. Since intervals do not
track correlations between variables and affine arithmetic tracks only linear
ones, the resulting ranges and errors are over-approximated.
A standard technique to increase accuracy of the computed errors is interval
subdivision, which divides the input domain into equally-sized subdomains and
runs roundoff error analysis separately for each subdomain. The
over-approximations on each subdomain tend to be smaller, which increases the
overall tightness of range and error bounds.

% mixed-precision tuning
To reduce memory usage and increase efficiency, we want to choose as short word
lengths as possible, ideally different word lengths for different values (i.e.
mixed-precision instead of a uniform word length). Due to the complexity of
fixed-point arithmetic and the error analysis, this is challenging to do
manually.
Automated mixed-precision tuning tools usually perform a search: they repeatedly
select a candidate mixed-precision assignment (i.e. different word lengths for
different values) and check whether the assignment satisfies a given error
bound.

### 2019-04-09 emsoft-2019/finite_precision.tex
finite precision background without refs for now

@@
 %!TEX root = main.tex
-\subsection{Finite Precision Implementation}
+\subsection{Finite-Precision Implementation}
 
-The controller has to be stored and implemented on the microcontroller in
-finite-precision, since infinite-precision real values cannot be stored on
+The controller has to be stored and evaluated on a microcontroller in
+finite precision, since infinite-precision real values cannot be stored on
 today's digital computers.
@@
 without complex hardware support using only integer operations. It requires,
-however, more compilation effort as, certain operations (that the floating-point
-hardware unit performs dynamically) now have to be determined statically at
-compile time.
+however, more compilation effort to determine certain operations statically at
+compile time (that the floating-point hardware unit performs dynamically).
 
 % general blob about fixed-point arithmetic
-\eva{Need to mention somewhere that we need input ranges}
 The main task at compile time is to select the fixed-point format for each value
 in the program. The format specifies the total word length and how many bits are
-available for the integer part of the number. To choose a sufficient number of
-integer bits to avoid overflow, but to not overprovision unnecessarily, we can
-use a range analysis which estimates the possibles ranges of all values
-in the program. The remaining bits of the total word length are represent the
-fractional part of a number, i.e. more fractional bits result in precise
-computations.
-Fixed-point arithmetic implementations can choose different rounding modes; here
-we consider standard and efficient truncation.
+available for the integer part of the number. Given ranges on program inputs, a
+range analysis estimates possibles ranges of all intermediate values in the
+program, which in turn determine how many integer bits are sufficient to
+avoid overflow. The remaining bits of the total word length represent the
+fractional part of a number; more fractional bits provide more precision.
 
 % introduces roundoff errors, these can be tracked with a dataflow analysis
-Finite precision unavoidably introduces roundoff errors when storing and
-performing arithmetic, which can accumulate during the course of a computation.
+Finite precision unavoidably introduces roundoff errors, which can accumulate
+during the course of a computation.
 A sound static roundoff error analysis computes a guaranteed upper bound on the
 error of the result by tracking worst-case errors at every operation. Given a
-word length for each value, several tools~\cite{} compute roundoff errors using
-a dataflow analysis.
+word length for each value, several tools~\cite{} automatically determine the number of
+integer bits needed and compute roundoff errors using a dataflow analysis.
 They track real-valued ranges at every intermediate operation. These ranges
-determine the fixed-point formats and thus also the individual roundoff errors,
-which are captured and tracked separately from the ranges. To ensure guaranteed
-error bounds, both the ranges and errors are tracked using interval~\cite{} or
+determine the fixed-point formats and thus also the individual worst-case roundoff errors,
+which the analyses track separately from the ranges. To ensure guaranteed
+error bounds, both the ranges and errors are computed using interval~\cite{} or
 affine arithmetic~\cite{} which compute sound enclosures. Since intervals do not
@@
 ones, the resulting ranges and errors are over-approximated.
-A standard technique to increase accuracy of the computed errors is interval
-subdivision, which divides the input domain into equally-sized subdomains and
-runs roundoff error analysis separately for each subdomain. The
-over-approximations on each subdomain tend to be smaller, which increases the
-overall tightness of range and error bounds.
+% A standard technique to increase accuracy of the computed errors is interval
+% subdivision, which divides the input domain into equally-sized subdomains and
+% runs roundoff error analysis separately for each subdomain. The
+% over-approximations on each subdomain tend to be smaller, which increases the
+% overall tightness of range and error bounds.
 
@@
 To reduce memory usage and increase efficiency, we want to choose as short word
-lengths as possible, ideally different word lengths for different values (i.e.
-mixed-precision instead of a uniform word length). Due to the complexity of
-fixed-point arithmetic and the error analysis, this is challenging to do
-manually.
+lengths as possible. Mixed-precision tuning tools automatically determine possibly different
+word lengths for different values. Compared to uniform precision (or word length),
+mixed-precision often leads to improved resource usage, but due to the complexity of
+fixed-point arithmetic and the error analysis, is challenging to do manually.  
 Automated mixed-precision tuning tools usually perform a search: they repeatedly
@@
 different values) and check whether the assignment satisfies a given error
-bound.
+bound. The candidate assignments are chosen based on a heuristic which guides
+the search towards promising candidates, e.g. using delta-debugging~\cite{} or
+simulated annealing~\cite{}.
+
+In this work, we use the tool Daisy~\cite{} which implements roundoff error
+analysis and mixed-precision tuning~\cite{} for fixed-point arithmetic, and is
+available as open-source. Fixed-point arithmetic implementations can choose different
+rounding modes; here we consider truncation, which is more efficient than
+rounding.

### 2019-04-09 emsoft-2019/finite_precision.tex
fixed refs

@@
 The standard choice for low-power platforms is fixed-point arithmetic. Unlike
-floating-point arithmetic, fixed-point arithmetic can be implemented efficiently
+floating-point arithmetic~\cite{ieee75408}, fixed-point arithmetic can be implemented efficiently
 without complex hardware support using only integer operations. It requires,
@@
 error of the result by tracking worst-case errors at every operation. Given a
-word length for each value, several tools~\cite{} automatically determine the number of
+word length for each value, several tools~\cite{Daisy,Gappa} automatically determine the number of
 integer bits needed and compute roundoff errors using a dataflow analysis.
@@
 which the analyses track separately from the ranges. To ensure guaranteed
-error bounds, both the ranges and errors are computed using interval~\cite{} or
-affine arithmetic~\cite{} which compute sound enclosures. Since intervals do not
+error bounds, both the ranges and errors are computed using interval~\cite{intervals} or
+affine arithmetic~\cite{affineArithmetic} which compute sound enclosures. Since intervals do not
 track correlations between variables and affine arithmetic tracks only linear
@@
 bound. The candidate assignments are chosen based on a heuristic which guides
-the search towards promising candidates, e.g. using delta-debugging~\cite{} or
-simulated annealing~\cite{}.
+the search towards promising candidates, e.g. using delta-debugging~\cite{DaisyTuning} or
+simulated annealing~\cite{}. \eva{add missing refs}
 
-In this work, we use the tool Daisy~\cite{} which implements roundoff error
-analysis and mixed-precision tuning~\cite{} for fixed-point arithmetic, and is
+In this work, we use the tool Daisy which implements roundoff error
+analysis and mixed-precision tuning~\cite{DaisyTuning} for fixed-point arithmetic, and is
 available as open-source. Fixed-point arithmetic implementations can choose different

### 2019-04-09 emsoft-2019/experiments.tex

@@
 \section{Experimental Results}
-
-This section reports experiments with the prototype described in Listing\ref{lst:alg} applied to three different benchmarks: in the former two, we evaluate the complete pipeline (design and memory optimization) to produce in output a complete controller.
-In the last one, we empirically show the scalability of our approach on one artificial sample.
-For the design of controllers we rely on MATLAB MPC toolbox.
-The outputs of the suite are vectors F, G and H, K for activation functions, and hyperplanes equations.
-We encode both of them in Daisy for finite-precision optimization.
-The design of controllers is done on a laptop with Intel i7-6700HQ CPU at 2.60GHz, with 16GB of RAM. 
-The analysis for the last benchmark runs on a cluster with 48 cores Intel Xeon v2 @ 3.00GHz with 1TB of RAM. Note that the memory consumption of our analysis never exceed 15GB of memory.
-
-\subsection{Results}
-\eva{I'd split this into two subsections, one for the end-to-end experiments, and
-one for demonstrating scalability (and use the subsection names as well to make this clear)}
-\eva{Is the 4D aircraft example introduced/explained before? If not, this should be done first,
-including a citation.}
-
-In Table \ref{tab:ipd} we report the evaluation of our approach on both the inverted pendulum problem described in the motivation section, and a well-known 4D example for aircraft controller design.
-For each benchmark, we report the results for ten different combinations of Delta and Eps.
-We divided them in two halves: in the  first we fix the value for Delta and we try different Eps combinations, while in the second halve we do the opposite.
-\eva{To make Table 1 fit without a rotation, remove at least all constant info (like the number
-of regions). The two columns with the errors are probably also not needed.}
-\eva{Use the same symbol for Delta and Eps as used in the technical section.}
-
-\eva{In the following, I'd discuss the two examples together and structure the 
-discussion as follows:
-\begin{itemize}
-	\item give the constant info (number of regions etc.) for both benchmarks
-	\item explain the variation of delta and eps (ideally with a motivation for why this is interesting)
-	\item discuss the improvements we get (i.e. first discuss the metric we care about most)
-	\item discuss other interesting details
-\end{itemize}
-Discussing the two examples together let's us compare their results easier, i.e.
-point out differences or commonalities.
-}
-\eva{Add running times of the analysis in Table 1 (possibly as a separate small table)}
-In the pendulum section of Table \ref{tab:ipd}, MATLAB returns a controller with 14 regions and 58 hyperplanes for each of the combinations of Delta and Eps.
-Delta spans the interval from 0.05 to 0.3, while Eps from 0.0006 to 0.0050.
-The domain of X for the pendulum is in the bounded range $X_{0} \in (-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$.
-The first halve of the section, shows that Delta does not affect the maximal error among regions \maxUij.
-We verify that a variation for Delta (typically in the order of $\pm$ 0.1) results in a minimal alteration to the domain of regions X (in the order of $\pm 10^{-10}$), not enough to produce a sensitive variation to \maxUij.
-When \maxUij is constant, the error for imprecisions Err-Bound behaves the same as Delta (they both decrease).
-The memory required for the storage of F and G depends on Err-Bound: the smaller the value for Err-Bound, the more demanding is the precision required for computations.
-In average, more than 50\% of memory is saved between fixed-32, where the all arithmetic is done in fixed precision 32 bits, and Uni, the minimal uniform precision word-length found with our analysis.
-Using mixed-precision (Mix) reduces in average 10\% of memory consumption with respect to Uni baseline.
-The storage of hyperplanes H and K depends only on the size of the tubes Eps.
-When we fix the value for Eps, and we try different delta, we save always 50\% from fixed-32 and about 10\% from Uni to Mixed.
-In the second halve of the table, we fix the value for Delta and we try different Eps.
-When we increase the safe space between two regions by Eps, the value for \maxUij is computed for new corner points.
-It happens because of the continuity of PWA activation functions: when \statevarmath is on the border between two generic regions $i$, $j$ the value for \maxUij is close to zero.
-The more Eps moves \statevarmath far from the border, the more \maxUij increases.
-When \maxUij is almost equal to delta, the space for Err-Bound is minimized, and the controller requires high precision for computations (see last line of pendulum section in Table\ref{tab:ipd}).
-On the other hand, when the value of Eps increases the analysis can reduce the memory requirements for the storage of borders (see column Uni and Mix for the second halve of pendulum).
-
-In the aircraft section of Table\ref{tab:ipd}, we report the results for the aircraft benchmark.
-MATLAB returns a controller with 27 regions and 217 hyperplanes, except for one combination of Delta and Eps.
-In general, when the disturbance value raises, two things can happen: the state domain X shrinks, to be robust against a greater disturbance, or the number of regions reduces.
-The behaviors discussed for the pendulum are confirmed: when delta is small, the activation functions (F, G) are memory demanding.
-While when the value of Eps increases, the memory requirements for H, K can be relaxed.
-There are two main differences with respect to the pendulum: here the precision for F and G is almost double, this is because the magnitude of F and G is in the order of $10^{3}$ while for the pendulum is in the order of several units (note that the precision gain from Uni to Mix is only slightly less than the one for the pendulum).
-The second difference consists in the last two lines in Table\ref{tab:ipd}.
-When Eps=0.0030, the \maxUij exceeds Delta=0.1 and we need to design again the controller (it corresponds to the else branch in Listing\ref{fig:overview}).
-The analysis converges after 5 iterations with Delta=0.112.
-After each iteration, the new delta is the last \maxUij\space plus a constant value in the order of $10^{-3}$.
-In this way we sensibly reduce memory demand at the expense of slightly more disturbance.
-When Eps=0.0050 the analysis converges after 4 iterations and the same discussion holds.
-
-The last benchmark is the double integrator, a canonical example of a second order control system. In Table\ref{tab:di} we collect the results.
-
-We introduce another parameter m, the prediction horizon of the controller. In this example, the number of regions is highly correlated with the prediction horizon m.
-Moreover, we fix the values for Delta to 0.1 and Eps to 0.001. In this experiment we focus on execution time of the analysis and memory optimization.
-
-The design of the controller in MATLAB takes few minutes, then it is is encoded in Daisy for memory optimization.
-In average the analysis of a controller in Daisy requires less than a minute, and less than 500MB of memory.
-The execution time of Daisy on a single activation function is less than 2 minutes.
-The cluster used for the evaluation comes with 48 cores, and the memory consumption on the cluster is always bounded in 15GB.
-The task is highly parallelizable, because any controller or hyperplane can be analyzed independently.
-
-\begin{landscape}
-	\pagestyle{empty}
-\begin{table}[p]
+\begin{table*}[ht]
 	\centering
-	\caption{Inverted Pendulum and Aircraft.\textmd{ Delta is the disturbance used to design the controller, and Eps the size of the safe space between two generic regions (\texttt{tube}).
-We fix Eps and try different Delta (in red) and vice-versa.
-For each pair Delta and Eps we obtain a controller with Regs number of regions divided by Hyps hyperplanes.
-The maximal error due to a wrong activation function is \maxUij and Err-Bound = Delta - maxUiUj.
+	\caption{Inverted Pendulum and Aircraft.\textmd{ delta is the disturbance used to design the controller, and $\varepsilon$ the size of the safe space between two generic regions (\texttt{tube}).
+We fix $\varepsilon$ and try different delta (in red) and vice-versa.
+The maximal error due to a wrong activation function is \maxUij and the error bound for finite precision activation functions $err(u_{i})$.
 F, G and H, K represent the memory requirements for activation functions, and hyperplanes.
@@
 	\label{tab:ipd}
-	\begin{tabular}{|l|rrrrrrrrrrrrrrrr|}
-		\cline{8-12}
-		\cline{12-17}
+	\begin{tabular}{|l|rrrrrrrrrrrrrr|}
+		\cline{6-15}
 		\multicolumn{1}{c}{} & %name of the sample
 		\multicolumn{4}{c}{} &
-		\multicolumn{2}{c}{} &
 		\multicolumn{5}{|c|}{F and G} &
 		\multicolumn{5}{c|}{H and K} \\
-		\cline{2-17}
+		\cline{2-15}
 		%\cline{5-6}
@@
 		\multicolumn{1}{c}{\multirow{14}{*}{\rotatebox{90}{pendulum}}} &
-		\multicolumn{1}{|c}{Delta}&
-		\multicolumn{1}{c}{Eps} &
-		\multicolumn{1}{c}{Regs} &
-		\multicolumn{1}{c}{Hyps} &
-		\multicolumn{1}{c}{\maxUij} &
-		\multicolumn{1}{c}{Err-Bound} &
+		\multicolumn{1}{|c}{delta}&
+		\multicolumn{1}{c}{$\varepsilon$} &
+		\multicolumn{1}{c}{max} &
+		\multicolumn{1}{c}{$err(u_{i})$} &
 		\multicolumn{1}{c}{Uni32}&
@@
 		\multicolumn{1}{c|}{\%UvM} \\
-		\cline{1-17}
-		& \color{red}{0.30} & 0.001 & 14 & 58 & 0.02 & 0.28 & 2688 & 924 (p=11) & 759 & 65.6\% & 17.9\% & 11136 & 5568 (p=16) & 4991 & 50\% & 10.7\% \\
+		\cline{1-15}
+		& \color{red}{0.30} & 0.001 & 0.02 & 0.28 & 2688 & 924 (p=11) & 759 & 65.6\% & 17.9\% & 11136 & 5568 (p=16) & 4991 & 50\% & 10.7\% \\
 
-		& \color{red}{0.20} & 0.001 & 14 & 58 & 0.02 & 0.18 & 2688 & 924 (p=11) & 806 & 65.6\% & 12.8\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
+		& \color{red}{0.20} & 0.001 & 0.02 & 0.18 & 2688 & 924 (p=11) & 806 & 65.6\% & 12.8\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
 
-		& \color{red}{0.10} & 0.001 & 14 & 58 & 0.02 & 0.08 & 2688 & 1008 (p=12) & 908 & 65.5\% & 10\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
+		& \color{red}{0.10} & 0.001 & 0.02 & 0.08 & 2688 & 1008 (p=12) & 908 & 65.5\% & 10\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
 
-		& \color{red}{0.08} & 0.001 & 14 & 58 & 0.02 & 0.06 & 2688 & 1092 (p=13) & 946 & 59.4\% & 13.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
+		& \color{red}{0.08} & 0.001 & 0.02 & 0.06 & 2688 & 1092 (p=13) & 946 & 59.4\% & 13.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
 
-		& \color{red}{0.05} & 0.001 & 14 & 58 & 0.02 & 0.03 & 2688 & 1176 (p=14) & 1030 & 56.3\% & 12.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
+		& \color{red}{0.05} & 0.001 & 0.02 & 0.03 & 2688 & 1176 (p=14) & 1030 & 56.3\% & 12.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
 
 		% Empy Line
-		& & & & & & & & & & & & & & & & \\
+		& & & & & & & & & & & & & &\\
 		% Empy Line
 
-		& 0.1 & \color{red}{0.0006} & 14 & 58 & 0.012 & 0.088 & 2688 & 1008 (p=12) & 891 & 62.5\% & 11.6\% & 11136 & 5916 (p=17) & 5261 & 46.9\% & 11\% \\
+		& 0.1 & \color{red}{0.0006} & 0.012 & 0.088 & 2688 & 1008 (p=12) & 891 & 62.5\% & 11.6\% & 11136 & 5916 (p=17) & 5261 & 46.9\% & 11\% \\
 
-		& 0.1 & \color{red}{0.0008} & 14 & 58 & 0.016 & 0.084 & 2688 & 1008 (p=12) & 901 & 62.5\% & 10.6\% & 11136 & 5568 (p=16) & 5135 & 50\% & 7.77\% \\
+		& 0.1 & \color{red}{0.0008} & 0.016 & 0.084 & 2688 & 1008 (p=12) & 901 & 62.5\% & 10.6\% & 11136 & 5568 (p=16) & 5135 & 50\% & 7.77\% \\
 
-		& 0.1 & \color{red}{0.0010} & 14 & 58 & 0.019 & 0.081 & 2688 & 1008 (p=12) & 908 & 62.5\% & 10\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
+		& 0.1 & \color{red}{0.0010} & 0.019 & 0.081 & 2688 & 1008 (p=12) & 908 & 62.5\% & 10\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
 
-		& 0.1 & \color{red}{0.0030} & 14 & 58 & 0.059 & 0.041 & 2688 &  1092 (p=13) & 993 & 59.4\% & 9.1\% & 11136 & 4872 (p=14) & 4462 & 56.3\% & 8.4\% \\
+		& 0.1 & \color{red}{0.0030} & 0.059 & 0.041 & 2688 &  1092 (p=13) & 993 & 59.4\% & 9.1\% & 11136 & 4872 (p=14) & 4462 & 56.3\% & 8.4\% \\
 
-		& 0.1 & \color{red}{0.0050} & 14 & 58 & 0.099 & 0.001 & 2688 & 1680 (p=20) & 1527 & 37.5\% & 9.1\% & 11136 & 4872 (p=14) & 4204 & 56.3\% & 13.7\% \\
+		& 0.1 & \color{red}{0.0050} & 0.099 & 0.001 & 2688 & 1680 (p=20) & 1527 & 37.5\% & 9.1\% & 11136 & 4872 (p=14) & 4204 & 56.3\% & 13.7\% \\
+		\cline{1-15}
+		\multirow{12}{*}{\rotatebox{90}{aircraft}}
+		& \color{red}{0.30} & 0.001 & 0.037 & 0.263 & 9984 & 6864 (p=22) & 6210 & 31.3\% & 9.5\% & 79872 & 64896 (p=26) & 53059 & 18.8\% & 18.2\% \\
 
-	%\end{tabular}
-	%\vspace*{1 cm}
-	%\centering
-	%\caption{Aircraft. For the description of each column see Table \ref{tab:ipd}.\\
-	%* In the last two samples the original value for delta was equal to 0.1, but our analysis returns a controller robust to a greater disturbance.}
-	%\label{tab:aircraft}
-	%\begin{tabular}{rrrrrrrrrrrrrrrr}
-	%	\cline{7-11}
-	%	\cline{12-16}
-	%	\multicolumn{4}{c}{} &
-	%	\multicolumn{2}{c}{} &
-	%	\multicolumn{5}{c|}{F and G} &
-	%	\multicolumn{5}{c}{H and K} \\
-	%	\hline
-		%\cline{5-6}
-		%\cline{9-12}
-		%\cline{13-16}
-	%	\multicolumn{1}{c}{Delta}&
-	%	\multicolumn{1}{c}{Eps} &
-	%	\multicolumn{1}{c}{Regs} &
-	%	\multicolumn{1}{c}{Hyps} &
-	%	\multicolumn{1}{c}{$max|U_{i}-U_{j}|$} &
-	%	\multicolumn{1}{c}{Err-Bound} &
-	%	\multicolumn{1}{c}{Uni32}&
-	%	\multicolumn{1}{c}{Uni}&
-	%	\multicolumn{1}{c}{Mix}&
-	%	\multicolumn{1}{c}{\%32vsU}&
-	%	\multicolumn{1}{c}{\%UvsM}&
-	%	\multicolumn{1}{c}{Uni32}&
-	%	\multicolumn{1}{c}{Uni}&
-	%	\multicolumn{1}{c}{Mix}&
-	%	\multicolumn{1}{c}{\%32vsU}&
-	%	\multicolumn{1}{c}{\%UvsM} \\
-	%	\hline
-	%	
-		\cline{1-17}
-		\multirow{12}{*}{\rotatebox{90}{aircraft}}
-		& \color{red}{0.30} & 0.001 & 26 & 208 & 0.037 & 0.263 & 9984 & 6864 (p=22) & 6210 & 31.3\% & 9.5\% & 79872 & 64896 (p=26) & 53059 & 18.8\% & 18.2\% \\
+		& \color{red}{0.20} & 0.001 & 0.037 & 0.163 & 10368 & 7452 (p=23) & 6725 & 28.1\% & 9.8\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
 
-		& \color{red}{0.20} & 0.001 & 27 & 216 & 0.037 & 0.163 & 10368 & 7452 (p=23) & 6725 & 28.1\% & 9.8\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
+		& \color{red}{0.10} & 0.001 & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
 
-		& \color{red}{0.10} & 0.001 & 27 & 216 & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
+		& \color{red}{0.08} & 0.001 & 0.037 & 0.043 & 10368 & 7776 (p=24) & 7275 & 25\% & 6.4\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
 
-		& \color{red}{0.08} & 0.001 & 27 & 216 & 0.037 & 0.043 & 10368 & 7776 (p=24) & 7275 & 25\% & 6.4\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
-
-		& \color{red}{0.05} & 0.001 & 27 & 216 & 0.037 & 0.013 & 10368 & 8424 (p=26) & 7840 & 18.8\% & 6.9\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.3\% \\
+		& \color{red}{0.05} & 0.001 & 0.037 & 0.013 & 10368 & 8424 (p=26) & 7840 & 18.8\% & 6.9\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.3\% \\
 
 		% Empy Line
-		& & & & & & & & & & & & & & & & \\
+		& & & & & & & & & & & & & &\\
 		% Empy Line
 
-		& 0.1 & \color{red}{0.0006} & 27 & 216 & 0.022 & 0.078 & 10368 & 7776 (p=24) & 7047 & 25\% & 9.4\% & 82944 & 69984 (p=27) & 55705 & 15.6\% & 20.4\% \\
+		& 0.1 & \color{red}{0.0006} & 0.022 & 0.078 & 10368 & 7776 (p=24) & 7047 & 25\% & 9.4\% & 82944 & 69984 (p=27) & 55705 & 15.6\% & 20.4\% \\
 
-		& 0.1 & \color{red}{0.0008} & 27 & 216 & 0.030 & 0.071 & 10368 & 7776 (p=24) & 7125 & 25\% & 8.4\% & 82944 & 69984 (p=27) & 57859 & 15.6\% & 17.3\% \\
+		& 0.1 & \color{red}{0.0008} & 0.030 & 0.071 & 10368 & 7776 (p=24) & 7125 & 25\% & 8.4\% & 82944 & 69984 (p=27) & 57859 & 15.6\% & 17.3\% \\
 
-		& 0.1 & \color{red}{0.0010} & 27 & 216 & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
+		& 0.1 & \color{red}{0.0010} & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
 
-		& 0.112* & \color{red}{0.0030} & 27 & 216 & 0.111 & 0.001000000068 & 10368 &  9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 64800 (p=25) & 52754 & 21.9\% & 18.6\% \\
+		& 0.112* & \color{red}{0.0030} & 0.111 & 0.001000000068 & 10368 &  9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 64800 (p=25) & 52754 & 21.9\% & 18.6\% \\
 
-		& 0.185* &\color{red}{0.0050} & 27 & 216 & 0.185 & 0.001000000090 & 10368 & 9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 62208 (p=24) & 47877 & 25\%& 23.1\% \\
-		\cline{1-17}
+		& 0.185* &\color{red}{0.0050} & 0.185 & 0.001000000090 & 10368 & 9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 62208 (p=24) & 47877 & 25\%& 23.1\% \\
+		\cline{1-15}
 	\end{tabular}
-\end{table}
-\end{landscape}
+\end{table*}
 
@@
 	\label{tab:di}
-	\begin{tabular}{rrrrrrrrrrrrrrr}
-		\cline{5-8}
-		\cline{8-13}
+	\begin{tabular}{|rrrrrrrrrrrrrr|}
+		\cline{5-14}
 		\multicolumn{4}{c}{} &
 		%\multicolumn{2}{c}{} &
-		\multicolumn{5}{c|}{F and G} &
-		\multicolumn{5}{c}{H and K} \\
+		\multicolumn{5}{|c|}{F and G} &
+		\multicolumn{5}{c|}{H and K} \\
 		\hline
@@
 		%\cline{13-16}
-		\multicolumn{1}{c}{Hrz}&
+		\multicolumn{1}{|c}{Hrz}&
 		\multicolumn{1}{c}{Time}&
@@
 		\multicolumn{1}{c}{\%32vU}&
-		\multicolumn{1}{c}{\%UvM} \\
+		\multicolumn{1}{c|}{\%UvM} \\
 		\hline
-		2 & 2 & 9 & 72 & 1728 & 810 (p=15) & 628 &  & 22.5\% & 13824 & 7776 (p=18) & 7280 & & 6.3\% \\
-		5 & 9 & 53 & 424 & 10176 & 5088 (p=16) & 3623 &  & 28.8\% & 81408 & 45792 (p=18) & 42656 & & 6.8\% \\
-		8 & 23 & 143 & 1144 & 27456 & 13728 (p=16) & 9864 &  & 28.1\% & 219648 & 123552 (p=18) & 114948 & & 7.0\% \\
-		11 & 47 & 277 & 2216 & 53184 & 26592 (p=16) & 18980 &  & 28.6\% & 425472 & 239328 (p=18) & 222616 & & 7.0\% \\
+		2 & 2 & 9 & 72 & 1728 & 810 (p=15) & 628 & 53.1\% & 22.5\% & 13824 & 7776 (p=18) & 7280 & 43.8\%& 6.3\% \\
+		5 & 9 & 53 & 424 & 10176 & 5088 (p=16) & 3623 & 50\% & 28.8\% & 81408 & 45792 (p=18) & 42656 & 43.8\% & 6.8\% \\
+		8 & 23 & 143 & 1144 & 27456 & 13728 (p=16) & 9864 & 50\%  & 28.1\% & 219648 & 123552 (p=18) & 114948 & 43.8\% & 7.0\% \\
+		11 & 47 & 277 & 2216 & 53184 & 26592 (p=16) & 18980 & 50\% & 28.6\% & 425472 & 239328 (p=18) & 222616 & 43.8\% & 7.0\% \\
 
-		14 & 73 & 431& 3446& 82752& 41376(p=16)& 28685&  & 30\% & 661632& 372168 (p=18)& 346020& &7.0\% \\
+		14 & 73 & 431& 3446& 82752& 41376 (p=16)& 28685& 50\% & 30\% & 661632& 372168 (p=18)& 346020& 43.8\% &7.0\% \\
 
-		17 & & & & & & & & & & & & & \\
+		17 & 106 & 621 & 4968 & 119232 & 59616 (p=16) & 40503 & 50\% & 32\% & 953856& 536544 (p=18)& 498668& 43.8\% & 7.0\% \\
 
-		21 & & & & & & & & & & & & & \\
+		21 & 150 & 928 & 7432 & 178368 & 89184 (p=16) & 59409 & 50\% & 31.38\% & 1426944 & 802656 (p=18) & 745936 & 43.8\% & 7\%  \\
 
-		25 & 445 &1299 & 23382 & 249408 & 109116 (p=14) & 80524 & 56.3\% & 26.2\% & 2992896 & 1589976 (p=17) & 1355675 & 46.9\% & 14.7\% \\
+		25 & & & & & & & & & & & & & \\
 
+		%25 & 445 &1299 & 23382 & 249408 & 109116 (p=14) & 80524 & 56.3\% & 26.2\% & 2992896 & 1589976 (p=17) & 1355675 & 46.9\% & 14.7\% \\
+		\hline
 	\end{tabular}
 \end{table*}
+This section reports experiments with the prototype described in Listing\ref{lst:alg} applied to three different benchmarks: in the former two, we evaluate the complete pipeline (design and memory optimization) to produce in output a complete controller.
+In the last experiment, we want to show the scalability of our approach when the number of regions and hyperplanes are in the order of tens of thousands.
+For the design of controllers, we rely on MATLAB MPC toolbox.
+The outputs of the suite are vectors F, G and H, K for activation functions and hyperplanes equations.
+We encode both of them in Daisy for finite-precision optimization.
+The design of controllers is done on a laptop with Intel i7-6700HQ CPU at 2.60GHz, with 16GB of RAM. 
+The evaluation of the last benchmark runs on a cluster with 48 cores Intel Xeon v2 @ 3.00GHz with 1TB of RAM. Note that the memory consumption of our analysis never exceed 15GB of memory.
+
+\subsection{End-to-end analyses}
+\eva{I'd split this into two subsections, one for the end-to-end experiments, and one for demonstrating scalability (and use the subsection names as well to make this clear)}
+\eva{Is the 4D aircraft example introduced/explained before? If not, this should be done first,
+including a citation.}
+
+In \autoref{tab:ipd} we report the evaluation of our approach on both the inverted pendulum problem described in the motivation section, and a well-known 4D example for aircraft controller design.
+(Describe aircraft).
+For each benchmark, we report the results for ten different combinations of delta and $\varepsilon$.
+We divided them in two halves: in the  first, we fix the value for delta and we try different $\varepsilon$ combinations, while in the second halve we do the opposite.
+\eva{To make Table 1 fit without a rotation, remove at least all constant info (like the numbervof regions). The two columns with the errors are probably also not needed.}
+\eva{Use the same symbol for Delta and Eps as used in the technical section.}
+
+\eva{In the following, I'd discuss the two examples together and structure the 
+discussion as follows:
+\begin{itemize}
+	\item give the constant info (number of regions etc.) for both benchmarks
+	\item explain the variation of delta and eps (ideally with a motivation for why this is interesting)
+	\item discuss the improvements we get (i.e. first discuss the metric we care about most)
+	\item discuss other interesting details
+\end{itemize}
+Discussing the two examples together let's us compare their results easier, i.e.
+point out differences or commonalities.}
+\eva{Add running times of the analysis in Table 1 (possibly as a separate small table)}
+For the pendulum problem, MATLAB designs a controller with 14 regions and 58 hyperplanes for each combination of delta and $\varepsilon$.
+delta spans the interval from 0.05 to 0.3, while $\varepsilon$ from 0.0006 to 0.0050.
+The domain of X is bounded in the range $X_{0} \in (-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$.
+For the aircraft, MATLAB returns a controller with 27 regions and 217 hyperplanes, except when delta=0.30 and $\varepsilon$=0.001 where the controller has 26 regions and 208 hyperplanes.
+In general, when the disturbance value raises, two things can happen: the state domain X shrinks to be robust against a greater disturbance, or the number of regions reduces.
+The domain of X is bounded in the range $X_{0} \in (-10000, 10000)$, $X_{1}\in (-734, 734)$, $X_{2}\in (-10000, 10000)$ and $X_{3}\in (-790, 790)$.
+
+For the pendulum, the execution time of the analysis is 10 minutes no matter the initial values for delta and $\varepsilon$, while for the aircraft is 36 minutes.
+\rocco{maybe table for execution times}
+%In the aircraft section of Table\ref{tab:ipd}, we report the results for the aircraft benchmark.
+
+The first halves of both pendulum and aircraft sections in \autoref{tab:ipd}, show how delta does not affect the maximal error among regions \maxUij.
+We verify that a variation for delta (typically in the order of $\pm$ 0.1) results in a minimal alteration to the domain of regions X (in the order of $\pm 10^{-10}$), not enough to produce a sensitive variation to \maxUij.
+Then, when \maxUij\space is constant the error bound for computations $err(u_{i})$ decreases together with delta.
+The memory required for the storage of F and G depends on $err(u_{i})$: the smaller the value for $err(u_{i})$, the more precise has to be the arithmetic for activation functions.
+
+In the second halves in \autoref{tab:ipd}, we fix the value for delta and we try different $\varepsilon$.
+When we increase the safe space between two regions by $\varepsilon$, the value for \maxUij is computed for new corner points.
+It happens because of the continuity of PWA activation functions: when \statevarmath is on the border between two generic regions $i$, $j$ the value for \maxUij is close to zero.
+The more $\varepsilon$ moves \statevarmath far from the border, the more \maxUij increases.
+When \maxUij is almost equal to delta, the space for $err(u_{i})$ is minimized, and the controller requires high precision for computations (see last lines for pendulum and aircraft in Table\ref{tab:ipd}).
+On the other hand, when $\varepsilon$ increases, the analysis can reduce the memory requirements for the storage of borders (see columns Uni and Mix in the second halves of both benchmarks).
+
+In the pendulum, more than 50\% of memory is saved (in average) between fixed precision in 32 bits (Uni32) and the minimal uniform precision word-length found with our analysis (Uni).
+Using mixed-precision (Mix) further reduces by 10\% (in average) the memory consumption with respect to uniform baseline.
+The memory requirements for the storage of hyperplanes H and K depends only on the size of the tubes $\varepsilon$.
+We save 50\% of memory (in average) from uniform precision in 32bits to minimal uniform, and 10\% (in average) from uniform to mixed precision.
+
+In the aircraft, we save 20\% (in average) of memory when activation functions are in minimal uniform precision, and an additional 7\% (in average) when we use mixed precision.
+For the storage of hyperplanes equations, we save more than 19\% of memory (in average) from uniform precision in 32bits to minimal uniform precision, and an additional 19\% (in average) from uniform to mixed precision.
+
+We noticed the following common behavior in the two benchmarks: when delta is small, the activation functions (F, G) are memory demanding, because the space for approximation error is minimized.
+While, when the value of $\varepsilon$ grows, the memory requirements for H, K can be relaxed.
+This is the obvious consequence when we allow for a greater approximation error.
+
+We also report two key differences among these two benchmarks: in the aircraft, the precision for F and G is almost double with respect to the pendulum.
+This is because the magnitude of F and G is in the order of $10^{3}$ while for the pendulum is in the order of several units (note that for F and G the memory gain from Uni to Mix (\%UvM) is only slightly less than the one for the pendulum).
+The second difference consists in the last two lines in Table\ref{tab:ipd}.
+In the aircraft, when $\varepsilon$=0.0030, the \maxUij exceeds delta=0.1 and we need to design again the controller (it corresponds to the else branch in Listing\ref{fig:overview}).
+The loop converges after 5 iterations (\texttt{then} branch of the conditional) with delta=0.112.
+After each iteration, the new value for delta is the last \maxUij\space plus a constant value in the order of $10^{-3}$.
+Thanks to this $\varepsilon_{SAFE}$ we sensibly reduce memory demand at the expense of slightly more disturbance for the controller.
+When $\varepsilon$=0.0050 the analysis converges after 4 iterations and the same discussion holds.
+
+\subsection{Performance evaluation}
+The benchmark in this experiment is the double integrator, a canonical example of a second order control system. In Table\ref{tab:di} we collect the results of the analysis.
+
+In this evaluation, we consider also the prediction horizon m, as an input parameter for the analysis.
+At design time, the prediction horizon of the controller m models how many future iterations of the feed-forward system are considered in the optimization problem (infinite horizon would correspond to the optimal controller).
+Note that in this example, the number of regions is highly correlated with the prediction horizon m of the controller.
+Even if this is a general behavior, it is not the rule.
+We fix the values for Delta to 0.1 and $\varepsilon$ to 0.001.
+In addition to memory optimization, we move the focus also to the execution time of the analysis.
+
+The design of the controller in MATLAB takes few minutes, then controllers and hyperplanes are encoded in Daisy for memory optimization.
+In average, the analysis of a controller or an hyperplane in Daisy, requires less than two minutes and less than 500MB of memory.
+The cluster used for the evaluation comes with 48 cores, and the memory consumption on the cluster is always bounded in 15GB.
+The task is highly parallelizable, because any controller or hyperplane can be analyzed independently.
+Our analysis can scale up to 1200 controllers and 25000 hyperplanes in few hours.
+\autoref{tab:di} shows the stability of memory tuning in Daisy is constant with respect to the number of controllers or hyperplanes.
+This is true for both F, G and H, K.
+Indeed, the memory gain from uniform in 32bits and minimal uniform (\%32vU) is constant among different input values m.
+The same holds for (\%UvM).

### 2019-04-09 emsoft-2019/Error_Analysis.tex
Rocco - Control Analysis and Controller Synthesis

--- 2019-04-07 emsoft-2019/Error_Analysis.tex
@@
 \section{Error Analysis}
+\label{sec:Error_Analysis}
 \eva{Assuming a given precision, how to compute the error for a given controller}
+
+The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of imperfect implementation of point location algorithm, and (ii) the approximation error deriving from finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.\\
+The disturbance value $\Delta$ has to be an upper bound for the summation of both imprecisions. In formula:
+\begin{flalign}
+\label{eq:delta}
+&\Delta >= \max_{\forall i,j\;|\;neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i\;|\mathcal{R}_{i}\;in\;\mathcal{R}} err(u_{i})_{p}
+\end{flalign}
+where $i,j$ are the indexes of two generic regions $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$, \\ $neighbour(\mathcal{R}_{i},\mathcal{R}_{j})$ states when two regions share at least a point (later is defined in details), $u_{i}$ is the activation function for controller $i$ (same for $u_{j}$), $err(u_{i})_{p}$ is the approximation error for computing $u_{i}$ using precision p.
+
+The finite-precision implementation of the point location algorithm introduces some error $\epsilon$ on the top of the exact value of $x_{k}$.
+Assuming that any point in region $i$ could be erroneously assigned to region $j$, without any  knowledge of the actual magnitude of $\epsilon$, is a too wide over-approximation of the existing instability.
+%In an hypothetic scenario where all the measurements were done in infinite precision arithmetic and without any uncertainty, we assume the controller $i$ would be activated.
+Instead, because we cannot rely on infinite precision, controller $j$ is selected.
+%The error committed is the difference between the output of the two branches $i$ and $j$.
+%The controller has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa), only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
+There are two main sources of error affecting the magnitude of $\epsilon$: (i) the first one is caused by analog-digital conversion $\varepsilon_{A/D}$
+%, happening just before the controller receives an estimation of the plant from the sensors. We call this error $\varepsilon_{A/D}$:
+
+\begin{equation}\nonumber
+\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
+\end{equation}
+
+Where $V_{cc}$ is the reference voltage of the converter (e.g. typical 5V) and $p$ represents the number of bits.
+
+The second error affecting $\epsilon$ is caused by (ii) the quantization of region bounds $\mathcal{R}$ in memory. We call this error $\varepsilon_{Q}$ for error quantization.
+
+While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries.
+This second error can be tuned based on a trade-off among accuracy of the storage and memory save~\cite{memoryMPC}.
+The rule for $\varepsilon_{Q}$ is the following:
+\begin{equation}\label{eq:quantizationlines}
+\varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
+\end{equation}
+This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($\hat{H}_{p}$ and $\hat{K}_{p}$), is bounded by $\varepsilon_{Q}$.
+
+The final formula for $\epsilon$ is then:
+\begin{equation}\label{eq:epsilontot}
+\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
+\end{equation}
+%\subsection{Finite Precision Implementation}
+We use epsilon to build a safe space around the hyperplanes of regions $\mathcal{R}$, such that the maximization function is computed only when \statevarmath follows inside this space among two neighbour regions.
+Two regions are neighbors when they share at least a border.
+
+In formula $\exists\; m,n \;$such that:
+\begin{equation}
+(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
+\end{equation}
+where $m$ and $n$ are the indexes of the two hyperplanes. We label with $border_{i,j}$ the matching border shared among the two regions.
+
+From the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute the first maximization problem in (\ref{eq:delta}) with the intersection of two half-spaces: 
+\begin{equation}\label{eq:tube}
+\begin{aligned}
+(border_{i,j} >= -\varepsilon) \land
+(border_{i,j} <= \varepsilon)
+\end{aligned} 
+\end{equation}
+where $\varepsilon$ is defined in (\ref{eq:epsilontot}).
+Sometimes later we refer at (\ref{eq:tube}) as the \texttt{tube}, due to its shape for 2D problems.
+We can easily extend this model to the case when two regions share only a single point.
+
+The effect of selecting the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}.
+In case all the arithmetic were exact (infinite precision) and without any uncertainty from hardware measurements, we assume the controller $i$ would be activated.
+Instead, because of approximation errors, controller $j$ is selected.
+In the following, given $i$ and $j$ the index of two generic regions in $\mathcal{R}$:
+\begin{flalign}
+\label{eq:maximization}
+&\max_{\forall i,j\;|\;neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|=\\
+&\max_{\forall i,j\;|\;neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
+\end{flalign}
+where \statevarmath satisfies (\ref{eq:tube}) between two regions $i$ and $j$.
+%Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$ and $j$, it is enough to evaluate function (\ref{eq:maximization}) at the corner points of the \texttt{tube}, instead of solving a maximization problem.
+We compute (\ref{eq:maximization}) for all pairs of neighbor regions $i$ and $j$.
+
+%When \qstatevarmath belongs to the \texttt{tube}, it might be that $u_{i}$ is activated instead of $u_{j}$ (or vice-versa).
+Otherwise, when \qstatevarmath does not belong to the tube, no matter the error $\varepsilon$, the right activation function is activated, and we consider only the error deriving from the computation itself.
+
+Since computing $u_{i}$ itself introduces some imprecision because of finite precision arithmetic, the system has to be robust against an error that is:
+
+\begin{equation}\label{eq:fperror}
+err(u_{i})_{p}=|(\hat{F}_{p}-F)\statevar+(\hat{G}_{p}-G)|
+\end{equation}
+
+where $\hat{F}$ and $\hat{G}$ represent the rounded values (in p bits) for the infinite precision values $F$ and $G$.
+
+In (\ref{eq:fperror}) the domain for \statevarmath are all the points in region $i$, together with all the values in the \texttt{tube} between region $i$ and any of the neighbors of $i$.
+Even if some points in the tube do not belong to region $i$, it might that $u_{i}$ is (erroneously) activated.
+We compute (\ref{eq:fperror}) for all regions in $\mathcal{R}$ and we take the maximum value of the error.
+
+%\begin{equation}\label{eq:maxfperror}
+%\max_{\forall \regionimath{i}\;in\;\statespace} err(u_{i})_{p}
+%\end{equation}

### 2019-04-10 emsoft-2019/experiments.tex
edits and comments for experiment

@@
 \section{Experimental Results}
-\begin{table*}[ht]
-	\centering
-	\caption{Inverted Pendulum and Aircraft.\textmd{ delta is the disturbance used to design the controller, and $\varepsilon$ the size of the safe space between two generic regions (\texttt{tube}).
-We fix $\varepsilon$ and try different delta (in red) and vice-versa.
-The maximal error due to a wrong activation function is \maxUij and the error bound for finite precision activation functions $err(u_{i})$.
-F, G and H, K represent the memory requirements for activation functions, and hyperplanes.
-Uni32 is the total number of bits for the controller using 32 bits precision.
-Uni is the uniform precision found by our analysis, together with the format.
-Mix is the total number of bits for the controller in mixed-precision.
-\%32vsU is the difference between the baseline Uni32 and Uni (in percentage), then \%UvsM is the difference between Uni and Mix.}}
-	\label{tab:ipd}
-	\begin{tabular}{|l|rrrrrrrrrrrrrr|}
-		\cline{6-15}
-		\multicolumn{1}{c}{} & %name of the sample
-		\multicolumn{4}{c}{} &
-		\multicolumn{5}{|c|}{F and G} &
-		\multicolumn{5}{c|}{H and K} \\
-		\cline{2-15}
-		%\cline{5-6}
-		%\cline{9-12}
-		%\cline{13-16}
-		\multicolumn{1}{c}{\multirow{14}{*}{\rotatebox{90}{pendulum}}} &
-		\multicolumn{1}{|c}{delta}&
-		\multicolumn{1}{c}{$\varepsilon$} &
-		\multicolumn{1}{c}{max} &
-		\multicolumn{1}{c}{$err(u_{i})$} &
-		\multicolumn{1}{c}{Uni32}&
-		\multicolumn{1}{c}{Uni}&
-		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vU}&
-		\multicolumn{1}{c}{\%UvM}&
-		\multicolumn{1}{c}{Uni32}&
-		\multicolumn{1}{c}{Uni}&
-		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vU}&
-		\multicolumn{1}{c|}{\%UvM} \\
-		\cline{1-15}
-		& \color{red}{0.30} & 0.001 & 0.02 & 0.28 & 2688 & 924 (p=11) & 759 & 65.6\% & 17.9\% & 11136 & 5568 (p=16) & 4991 & 50\% & 10.7\% \\
+\input{table_pendulum_aircraft}
+\input{table_integrator}
 
-		& \color{red}{0.20} & 0.001 & 0.02 & 0.18 & 2688 & 924 (p=11) & 806 & 65.6\% & 12.8\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
+We evaluate a prototype implementation of the algorithm in~\autoref{lst:alg}
+on three examples. For the first two, we apply the complete pipeline (design and memory optimization)
+which returns an end-to-end robust controller. With the third example, we evaluate
+the scalability of our approach when the number of regions and hyperplanes are in
+the order of tens of thousands.
 
-		& \color{red}{0.10} & 0.001 & 0.02 & 0.08 & 2688 & 1008 (p=12) & 908 & 65.5\% & 10\% & 11136 & 5568 (p=16)& 4992 & 50\% & 10.3\% \\
+% This section reports experiments with the prototype described
+% in~\autoref{lst:alg} applied to three different benchmarks: in the former two,
+% we evaluate the complete pipeline (design and memory optimization) to produce in
+% output a complete controller. In the last experiment, we want to show the
+% scalability of our approach when the number of regions and hyperplanes are in
+% the order of tens of thousands.
 
-		& \color{red}{0.08} & 0.001 & 0.02 & 0.06 & 2688 & 1092 (p=13) & 946 & 59.4\% & 13.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
+% For the design of controllers, we rely on MATLAB MPC toolbox. The outputs of the
+% suite are vectors F, G and H, K for activation functions and hyperplanes
+% equations. We encode both of them in Daisy for finite-precision optimization.
+The design of end-to-end robust controllers has been performed on a laptop with Intel i7-6700HQ CPU at
+2.60GHz, with 16GB of RAM. The evaluation of the last benchmark runs on a
+cluster with 48 Intel Xeon v2 @ 3.00GHz cores with 1TB of RAM, of which our analysis
+only used 15GB.
+%Note that the memory consumption of our analysis never exceed 15GB of memory.
 
-		& \color{red}{0.05} & 0.001 & 0.02 & 0.03 & 2688 & 1176 (p=14) & 1030 & 56.3\% & 12.4\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
-
-		% Empy Line
-		& & & & & & & & & & & & & &\\
-		% Empy Line
-
-		& 0.1 & \color{red}{0.0006} & 0.012 & 0.088 & 2688 & 1008 (p=12) & 891 & 62.5\% & 11.6\% & 11136 & 5916 (p=17) & 5261 & 46.9\% & 11\% \\
-
-		& 0.1 & \color{red}{0.0008} & 0.016 & 0.084 & 2688 & 1008 (p=12) & 901 & 62.5\% & 10.6\% & 11136 & 5568 (p=16) & 5135 & 50\% & 7.77\% \\
-
-		& 0.1 & \color{red}{0.0010} & 0.019 & 0.081 & 2688 & 1008 (p=12) & 908 & 62.5\% & 10\% & 11136 & 5568 (p=16) & 4992 & 50\% & 10.3\% \\
-
-		& 0.1 & \color{red}{0.0030} & 0.059 & 0.041 & 2688 &  1092 (p=13) & 993 & 59.4\% & 9.1\% & 11136 & 4872 (p=14) & 4462 & 56.3\% & 8.4\% \\
-
-		& 0.1 & \color{red}{0.0050} & 0.099 & 0.001 & 2688 & 1680 (p=20) & 1527 & 37.5\% & 9.1\% & 11136 & 4872 (p=14) & 4204 & 56.3\% & 13.7\% \\
-		\cline{1-15}
-		\multirow{12}{*}{\rotatebox{90}{aircraft}}
-		& \color{red}{0.30} & 0.001 & 0.037 & 0.263 & 9984 & 6864 (p=22) & 6210 & 31.3\% & 9.5\% & 79872 & 64896 (p=26) & 53059 & 18.8\% & 18.2\% \\
-
-		& \color{red}{0.20} & 0.001 & 0.037 & 0.163 & 10368 & 7452 (p=23) & 6725 & 28.1\% & 9.8\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
-
-		& \color{red}{0.10} & 0.001 & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
-
-		& \color{red}{0.08} & 0.001 & 0.037 & 0.043 & 10368 & 7776 (p=24) & 7275 & 25\% & 6.4\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
-
-		& \color{red}{0.05} & 0.001 & 0.037 & 0.013 & 10368 & 8424 (p=26) & 7840 & 18.8\% & 6.9\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.3\% \\
-
-		% Empy Line
-		& & & & & & & & & & & & & &\\
-		% Empy Line
-
-		& 0.1 & \color{red}{0.0006} & 0.022 & 0.078 & 10368 & 7776 (p=24) & 7047 & 25\% & 9.4\% & 82944 & 69984 (p=27) & 55705 & 15.6\% & 20.4\% \\
-
-		& 0.1 & \color{red}{0.0008} & 0.030 & 0.071 & 10368 & 7776 (p=24) & 7125 & 25\% & 8.4\% & 82944 & 69984 (p=27) & 57859 & 15.6\% & 17.3\% \\
-
-		& 0.1 & \color{red}{0.0010} & 0.037 & 0.063 & 10368 & 7776 (p=24) & 7134 & 25\% & 8.3\% & 82944 & 67392 (p=26) & 55098 & 18.8\% & 18.2\% \\
-
-		& 0.112* & \color{red}{0.0030} & 0.111 & 0.001000000068 & 10368 &  9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 64800 (p=25) & 52754 & 21.9\% & 18.6\% \\
-
-		& 0.185* &\color{red}{0.0050} & 0.185 & 0.001000000090 & 10368 & 9720 (p=30) & 9051 & 6.3\% & 6.9\% & 82944 & 62208 (p=24) & 47877 & 25\%& 23.1\% \\
-		\cline{1-15}
-	\end{tabular}
-\end{table*}
-
-\begin{table*}[ht]
-	\centering
-	\caption{Double Integrator.\textmd{ Hrz is the prediction horizon in RMPC, Time is the execution time in minutes, Regs is the number of regions of the controller with Hyps hyperplanes.
-Uni32 is the total number of bits when all operations are in 32 bits, Uni the minimal uniform precision required, Mix is mixed-precision, \%32vU and UvM are the benefit of uniform and mixed precisions.}}
-	\label{tab:di}
-	\begin{tabular}{|rrrrrrrrrrrrrr|}
-		\cline{5-14}
-		\multicolumn{4}{c}{} &
-		%\multicolumn{2}{c}{} &
-		\multicolumn{5}{|c|}{F and G} &
-		\multicolumn{5}{c|}{H and K} \\
-		\hline
-		%\cline{5-6}
-		%\cline{9-12}
-		%\cline{13-16}
-		\multicolumn{1}{|c}{Hrz}&
-		\multicolumn{1}{c}{Time}&
-		%\multicolumn{1}{c}{Eps} &
-		\multicolumn{1}{c}{Regs} &
-		\multicolumn{1}{c}{Hyps} &
-		%\multicolumn{1}{c}{\maxUij} &
-		%\multicolumn{1}{c}{Err-Bound} &
-		\multicolumn{1}{c}{Uni32}&
-		\multicolumn{1}{c}{Uni}&
-		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vU}&
-		\multicolumn{1}{c}{\%UvM}&
-		\multicolumn{1}{c}{Uni32}&
-		\multicolumn{1}{c}{Uni}&
-		\multicolumn{1}{c}{Mix}&
-		\multicolumn{1}{c}{\%32vU}&
-		\multicolumn{1}{c|}{\%UvM} \\
-		\hline
-		2 & 2 & 9 & 72 & 1728 & 810 (p=15) & 628 & 53.1\% & 22.5\% & 13824 & 7776 (p=18) & 7280 & 43.8\%& 6.3\% \\
-		5 & 9 & 53 & 424 & 10176 & 5088 (p=16) & 3623 & 50\% & 28.8\% & 81408 & 45792 (p=18) & 42656 & 43.8\% & 6.8\% \\
-		8 & 23 & 143 & 1144 & 27456 & 13728 (p=16) & 9864 & 50\%  & 28.1\% & 219648 & 123552 (p=18) & 114948 & 43.8\% & 7.0\% \\
-		11 & 47 & 277 & 2216 & 53184 & 26592 (p=16) & 18980 & 50\% & 28.6\% & 425472 & 239328 (p=18) & 222616 & 43.8\% & 7.0\% \\
-
-		14 & 73 & 431& 3446& 82752& 41376 (p=16)& 28685& 50\% & 30\% & 661632& 372168 (p=18)& 346020& 43.8\% &7.0\% \\
-
-		17 & 106 & 621 & 4968 & 119232 & 59616 (p=16) & 40503 & 50\% & 32\% & 953856& 536544 (p=18)& 498668& 43.8\% & 7.0\% \\
-
-		21 & 150 & 928 & 7432 & 178368 & 89184 (p=16) & 59409 & 50\% & 31.38\% & 1426944 & 802656 (p=18) & 745936 & 43.8\% & 7\%  \\
-
-		25 & & & & & & & & & & & & & \\
-
-		%25 & 445 &1299 & 23382 & 249408 & 109116 (p=14) & 80524 & 56.3\% & 26.2\% & 2992896 & 1589976 (p=17) & 1355675 & 46.9\% & 14.7\% \\
-		\hline
-	\end{tabular}
-\end{table*}
-This section reports experiments with the prototype described in Listing\ref{lst:alg} applied to three different benchmarks: in the former two, we evaluate the complete pipeline (design and memory optimization) to produce in output a complete controller.
-In the last experiment, we want to show the scalability of our approach when the number of regions and hyperplanes are in the order of tens of thousands.
-For the design of controllers, we rely on MATLAB MPC toolbox.
-The outputs of the suite are vectors F, G and H, K for activation functions and hyperplanes equations.
-We encode both of them in Daisy for finite-precision optimization.
-The design of controllers is done on a laptop with Intel i7-6700HQ CPU at 2.60GHz, with 16GB of RAM. 
-The evaluation of the last benchmark runs on a cluster with 48 cores Intel Xeon v2 @ 3.00GHz with 1TB of RAM. Note that the memory consumption of our analysis never exceed 15GB of memory.
-
-\subsection{End-to-end analyses}
-\eva{I'd split this into two subsections, one for the end-to-end experiments, and one for demonstrating scalability (and use the subsection names as well to make this clear)}
-\eva{Is the 4D aircraft example introduced/explained before? If not, this should be done first,
-including a citation.}
-
-In \autoref{tab:ipd} we report the evaluation of our approach on both the inverted pendulum problem described in the motivation section, and a well-known 4D example for aircraft controller design.
-(Describe aircraft).
-For each benchmark, we report the results for ten different combinations of delta and $\varepsilon$.
-We divided them in two halves: in the  first, we fix the value for delta and we try different $\varepsilon$ combinations, while in the second halve we do the opposite.
-\eva{To make Table 1 fit without a rotation, remove at least all constant info (like the numbervof regions). The two columns with the errors are probably also not needed.}
+\subsection{End-to-end Robust Controller}
 \eva{Use the same symbol for Delta and Eps as used in the technical section.}
 
-\eva{In the following, I'd discuss the two examples together and structure the 
-discussion as follows:
-\begin{itemize}
-	\item give the constant info (number of regions etc.) for both benchmarks
-	\item explain the variation of delta and eps (ideally with a motivation for why this is interesting)
-	\item discuss the improvements we get (i.e. first discuss the metric we care about most)
-	\item discuss other interesting details
-\end{itemize}
-Discussing the two examples together let's us compare their results easier, i.e.
-point out differences or commonalities.}
-\eva{Add running times of the analysis in Table 1 (possibly as a separate small table)}
-For the pendulum problem, MATLAB designs a controller with 14 regions and 58 hyperplanes for each combination of delta and $\varepsilon$.
-delta spans the interval from 0.05 to 0.3, while $\varepsilon$ from 0.0006 to 0.0050.
-The domain of X is bounded in the range $X_{0} \in (-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$.
-For the aircraft, MATLAB returns a controller with 27 regions and 217 hyperplanes, except when delta=0.30 and $\varepsilon$=0.001 where the controller has 26 regions and 208 hyperplanes.
-In general, when the disturbance value raises, two things can happen: the state domain X shrinks to be robust against a greater disturbance, or the number of regions reduces.
-The domain of X is bounded in the range $X_{0} \in (-10000, 10000)$, $X_{1}\in (-734, 734)$, $X_{2}\in (-10000, 10000)$ and $X_{3}\in (-790, 790)$.
+We evaluate our complete pipeline on two benchmarks: the inverted pendulum
+described in~\autoref{sec:example} and a well-known 4D example for aircraft
+controller design.
+\eva{Describe aircraft example, add citation}
 
-For the pendulum, the execution time of the analysis is 10 minutes no matter the initial values for delta and $\varepsilon$, while for the aircraft is 36 minutes.
-\rocco{maybe table for execution times}
-%In the aircraft section of Table\ref{tab:ipd}, we report the results for the aircraft benchmark.
+For the pendulum problem, the domain of X is bounded in the range $X_{0} \in
+(-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$. MATLAB designs a controller with 14
+regions and 58 hyperplanes for each combination of delta and $\varepsilon$.
+% delta spans the interval from 0.05 to 0.3, while $\varepsilon$ from 0.0006 to 0.0050.  % it's in the table
+For the aircraft problem, the domain of X is bounded in the range $X_{0} \in
+(-10000, 10000)$, $X_{1}\in (-734, 734)$, $X_{2}\in (-10000, 10000)$ and
+$X_{3}\in (-790, 790)$. MATLAB returns a controller with 27 regions and 217
+hyperplanes, except when delta=0.30 and $\varepsilon$=0.001 where the controller
+has 26 regions and 208 hyperplanes. In general, when the disturbance value
+increases, the state domain X shrinks to be robust against a greater
+disturbance, or the number of regions reduces.
 
+\eva{Explain why we choose 32 bits uniform as baseline}
+\eva{Explain why we don't compare against other tools (resp. the one)}
+\autoref{tab:ipd} shows the total number of bits required to implement each
+controller using different precision options: uniform 32 bit precision
+(`Uni32'), uniform but custom precision (`Uni', chosen precision in parentheses)
+and mixed precision (`Mix'). We split the memory requirement into the bits
+required for storing F and G and H and K. We show the results for each benchmark
+for ten different combinations of delta and $\varepsilon$, varying one while
+keeping the other fixed.
+For the pendulum, the execution time of the analysis is 10 minutes no matter the
+initial values for delta and $\varepsilon$, while for the aircraft it is 36
+minutes. \rocco{maybe table for execution times}
+
+% In \autoref{tab:ipd} we report the evaluation of our approach on both the
+% inverted pendulum problem described in the motivation section, and a well-known
+% 4D example for aircraft controller design. (Describe aircraft). For each
+% benchmark, we report the results for ten different combinations of delta and
+% $\varepsilon$. We divided them in two halves: in the  first, we fix the value
+% for delta and we try different $\varepsilon$ combinations, while in the second
+% halve we do the opposite.
+
+% \eva{In the following, I'd discuss the two examples together and structure the 
+% discussion as follows:
+% \begin{itemize}
+% 	\item give the constant info (number of regions etc.) for both benchmarks
+% 	\item explain the variation of delta and eps (ideally with a motivation for why this is interesting)
+% 	\item discuss the improvements we get (i.e. first discuss the metric we care about most)
+% 	\item discuss other interesting details
+% \end{itemize}
+% Discussing the two examples together let's us compare their results easier, i.e.
+% point out differences or commonalities.}
+
+\eva{Fix Table 1 caption. It's not the difference, but savings. Difference is absolute.}
+\eva{Compute the actual averages for all F, G, H, K and not only approximations}
+For the inverted pendulum, minimal uniform precision saves ???\% of memory
+compared to a uniform 32 bit baseline (column `\%32vU' in~\autoref{tab:ipd}) on
+average overall (for F, G, H and K together). Mixed-precision further reduces the memory
+requirement by ???\% on average with respect to the minimal uniform baseline
+(column `\%UvM' in~\autoref{tab:ipd}). 
+\autoref{tab:ipd} shows a more detailed breakdown of the memory requirement
+between F and G and H and K. The memory requirements for the storage of
+hyperplanes H and K depends only on the size of the tubes $\varepsilon$ so that
+memory requirements remain constant for fixed $\varepsilon$.
+
+\eva{Compute actual and overall averages here too}
+For the aircraft example, minimal uniform precision saves on average ???\%
+overall w.r.t. a uniform 32 bit baseline, and mixed-precision saves an
+additional ???\% w.r.t. minimal uniform precision. We observe higher relative
+memory savings by mixed-precision for storing H and K.
+
+% we save 20\% (in average) of memory when activation functions
+% are in minimal uniform precision, and an additional 7\% (in average) when we use
+% mixed precision. For the storage of hyperplanes equations, we save more than
+% 19\% of memory (in average) from uniform precision in 32bits to minimal uniform
+% precision, and an additional 19\% (in average) from uniform to mixed precision.
+
+%We noticed the following common behavior in the two benchmarks: 
+As expected, when delta decreases, the activation functions (F, G) need to be
+more precise and require more memory, because the space for approximation error
+is reduced. Similarly, when the value of $\varepsilon$ increases, the memory
+requirements for H, K can be relaxed.
+
+We note two differences among these two benchmarks.
+In the aircraft,
+the precision for F and G is almost double with respect to the pendulum. This is
+because the magnitude of F and G is on the order of $10^{3}$ while for the
+pendulum it is on the order of several units (note that for F and G the memory gain
+from Uni to Mix (\%UvM) is only slightly less than the one for the pendulum).
+
+\eva{The below explanation only mentions aircraft. What is the difference to pendulum?}
+The second difference consists in the last two lines in Table\ref{tab:ipd}.
+In the aircraft, when $\varepsilon$=0.0030, the \maxUij exceeds delta=0.1 and we
+need to design again the controller (it corresponds to the else branch in
+Listing\ref{fig:overview}). The loop converges after 5 iterations (\texttt{then}
+branch of the conditional) with delta=0.112. After each iteration, the new value
+for delta is the last \maxUij\space plus a constant value in the order of
+$10^{-3}$. Thanks to this $\varepsilon_{SAFE}$ we sensibly reduce memory demand
+at the expense of slightly more disturbance for the controller. When
+$\varepsilon$=0.0050 the analysis converges after 4 iterations and the same
+discussion holds.
+
+\eva{It is still not clear to me whether we need this discussion or the columns `max' and `$err(u_i)$'
+in the table. These are internal computations and it seems that they do not really show anything
+surprising/different than the number of bits show?}
 The first halves of both pendulum and aircraft sections in \autoref{tab:ipd}, show how delta does not affect the maximal error among regions \maxUij.
@@
 
-In the pendulum, more than 50\% of memory is saved (in average) between fixed precision in 32 bits (Uni32) and the minimal uniform precision word-length found with our analysis (Uni).
-Using mixed-precision (Mix) further reduces by 10\% (in average) the memory consumption with respect to uniform baseline.
-The memory requirements for the storage of hyperplanes H and K depends only on the size of the tubes $\varepsilon$.
-We save 50\% of memory (in average) from uniform precision in 32bits to minimal uniform, and 10\% (in average) from uniform to mixed precision.
+\subsection{Scalability}
+The benchmark in this experiment is the double integrator, a canonical example
+of a second order control system. 
+\eva{More details about this + citation}
 
-In the aircraft, we save 20\% (in average) of memory when activation functions are in minimal uniform precision, and an additional 7\% (in average) when we use mixed precision.
-For the storage of hyperplanes equations, we save more than 19\% of memory (in average) from uniform precision in 32bits to minimal uniform precision, and an additional 19\% (in average) from uniform to mixed precision.
+For this example, we fix the values for Delta to 0.1 and $\varepsilon$ to 0.001,
+but we consider also the prediction horizon m, as an input parameter for the
+analysis. At design time, the prediction horizon of the controller m models how
+many future iterations of the feed-forward system are considered in the
+optimization problem (infinite horizon would correspond to the optimal
+controller). Note that in this example, the number of regions is highly
+correlated with the prediction horizon m of the controller: the number of regions
+increases with larger m, and thus also increases the execution time of our analysis.
+Even if this is a general behavior, it is not the rule.
+\eva{What does the above sentence mean?}
 
-We noticed the following common behavior in the two benchmarks: when delta is small, the activation functions (F, G) are memory demanding, because the space for approximation error is minimized.
-While, when the value of $\varepsilon$ grows, the memory requirements for H, K can be relaxed.
-This is the obvious consequence when we allow for a greater approximation error.
+The design of the controller in MATLAB takes few minutes, then controllers and
+hyperplanes are encoded in Daisy for memory optimization. On average, the
+analysis of a controller or an hyperplane in Daisy, requires less than two
+minutes and less than 500MB of memory. The cluster used for the evaluation has
+48 cores, and the memory consumption on the cluster is always bounded by
+15GB. Memory optimization is trivially parallelizable, because any controller or
+hyperplane can be analyzed independently.
+\eva{There should be an explanation why this is not providing end-to-end robustness}
 
-We also report two key differences among these two benchmarks: in the aircraft, the precision for F and G is almost double with respect to the pendulum.
-This is because the magnitude of F and G is in the order of $10^{3}$ while for the pendulum is in the order of several units (note that for F and G the memory gain from Uni to Mix (\%UvM) is only slightly less than the one for the pendulum).
-The second difference consists in the last two lines in Table\ref{tab:ipd}.
-In the aircraft, when $\varepsilon$=0.0030, the \maxUij exceeds delta=0.1 and we need to design again the controller (it corresponds to the else branch in Listing\ref{fig:overview}).
-The loop converges after 5 iterations (\texttt{then} branch of the conditional) with delta=0.112.
-After each iteration, the new value for delta is the last \maxUij\space plus a constant value in the order of $10^{-3}$.
-Thanks to this $\varepsilon_{SAFE}$ we sensibly reduce memory demand at the expense of slightly more disturbance for the controller.
-When $\varepsilon$=0.0050 the analysis converges after 4 iterations and the same discussion holds.
-
-\subsection{Performance evaluation}
-The benchmark in this experiment is the double integrator, a canonical example of a second order control system. In Table\ref{tab:di} we collect the results of the analysis.
-
-In this evaluation, we consider also the prediction horizon m, as an input parameter for the analysis.
-At design time, the prediction horizon of the controller m models how many future iterations of the feed-forward system are considered in the optimization problem (infinite horizon would correspond to the optimal controller).
-Note that in this example, the number of regions is highly correlated with the prediction horizon m of the controller.
-Even if this is a general behavior, it is not the rule.
-We fix the values for Delta to 0.1 and $\varepsilon$ to 0.001.
-In addition to memory optimization, we move the focus also to the execution time of the analysis.
-
-The design of the controller in MATLAB takes few minutes, then controllers and hyperplanes are encoded in Daisy for memory optimization.
-In average, the analysis of a controller or an hyperplane in Daisy, requires less than two minutes and less than 500MB of memory.
-The cluster used for the evaluation comes with 48 cores, and the memory consumption on the cluster is always bounded in 15GB.
-The task is highly parallelizable, because any controller or hyperplane can be analyzed independently.
-Our analysis can scale up to 1200 controllers and 25000 hyperplanes in few hours.
-\autoref{tab:di} shows the stability of memory tuning in Daisy is constant with respect to the number of controllers or hyperplanes.
-This is true for both F, G and H, K.
-Indeed, the memory gain from uniform in 32bits and minimal uniform (\%32vU) is constant among different input values m.
-The same holds for (\%UvM).
+\autoref{tab:di} shows the details of this experiment.
+We observe that our analysis scales up to 1200 controllers and 25000 hyperplanes in few
+hours. 
+\eva{Compute and say something about the overall savings for F, G, H, K, and proper average (at least for UvM)}
+We further observe that relative savings remain largely constant for different 
+prediction horizons.
+% \autoref{tab:di} shows the stability of memory tuning in Daisy is
+% constant with respect to the number of controllers or hyperplanes. This is true
+% for both F, G and H, K. Indeed, the memory gain from uniform in 32bits and
+% minimal uniform (\%32vU) is constant among different input values m. The same
+% holds for (\%UvM).

### 2019-04-10 emsoft-2019/Cont_Syn.tex

--- 2019-04-07 emsoft-2019/Cont_Syn.tex
@@
 \eva{How we actually get the controller, including feedback loop and mixed-precision tuning}
+%In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.
+We need to solve the two inequalities in (\ref{eq:delta}) (\ref{eq:quantizationlines}) in order to build a controller with guarantees of robustness.
+%The equation for $\varepsilon$ in (\ref{eq:epsilontot}),  contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is the error generated from the quantization of hyperplanes $\mathcal{R}$ in a finite number of bits.
+%This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
+%The rule for $\varepsilon_{Q}$ is the following:
+%\begin{equation}\label{eq:quantizationlines}
+%\varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
+%\end{equation}
+%This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$.
+We use Daisy to solve inequality (\ref{eq:quantizationlines}) with respect to p: we assign an arbitrary value to $\varepsilon_{Q}$ and find the minimal-precision p such that the inequality holds.
+The main advantage of using this approach (compared to fixing the precision p a priori), is that the value for $\varepsilon_{Q}$ can be regulated based on micro-controller specifications (e.g.
+memory availability).
+%To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, ables to provide a sound upper-bound to the maximal approximation error of a formula with respect to its real (infinite precision) counterpart.
+Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.
+In a similar way, we solve the inequality in (\ref{eq:delta}) with respect to p:
+\begin{flalign}
+\label{eq:deltaminusmax}
+&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
+& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
+\end{flalign}
+
+Be aware that the left side of (\ref{eq:deltaminusmax}) is not parametrized in p (it is a plain number).
+Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p.
+We compute the left side of the inequality using large enough precision p (e.g.
+64 bits) such that we can safely ignore the error resulting from the computation.
+Then, we encode (\ref{eq:deltaminusmax}) in Daisy to detect precision p. Note that p used to solve (\ref{eq:quantizationlines}) can be different from $p'$ used to solve (\ref{eq:deltaminusmax}).
+
+\subsection{Algorithm}
+In Listing \ref{lst:alg} we describe the procedure used to design a robust MPC controller such that (\ref{eq:deltaminusmax}) is satisfied.
+
+\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},caption=design of robust MPC with precision tuning,label={lst:alg}]
+ delta = input()
+ (*$\varepsilon_{Q}$*) = input()
+ assert (delta >= 0 and (*$\varepsilon_{Q}$*) > 0)
+ (*$\varepsilon$*) = (*$\varepsilon_{A/D}$*) + (*$\varepsilon_{Q}$*)
+
+ while True:
+   (*\maxUij*) = design_robust_MPC(delta, (*$\varepsilon$*))
+   if delta > (*\maxUij*):
+     (*$err_{max}(u_{i})_{p}$*) = delta-(*\maxUij*)
+     UNI_MIX_precision(F, G, (*$err_{max}(u_{i})_{p}$*))
+     UNI_MIX_precision(H, K, (*$\varepsilon_{Q}$*))
+     break
+   else:
+     delta=(*\maxUij*)+(*$\varepsilon_{SAFE}$*)
+\end{lstlisting}
+
+First, the designer of the controller provides the initial values for delta and $\varepsilon_{Q}$.
+Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization value: it is going to fail the analysis (at least) for the first iteration, because the error in (\ref{eq:maxfperror}) is going to be greater than zero.
+A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.
+
+On the other hand, the value for $\varepsilon_{Q}$ has to be strictly greater than zero, otherwise we could rely on infinite precision for p in (\ref{eq:quantizationlines}).
+
+Once input parameters are verified, we design the controller in MATLAB.
+
+We compute (\ref{eq:maximization}) and we compare the result with delta.
+Again, in the conditional inside the loop, delta has to be strictly greater than \maxUij\space otherwise we do not have space for computing the precision for (\ref{eq:deltaminusmax}).
+In case the conditional is true,
+the precision tuning phase starts.
+For the precision tuning of activation functions, we allow an error that is bounded by the left side of inequality (\autoref{eq:deltaminusmax}).
+While for the quantization of hyperplanes the error bound is $\varepsilon_{Q}$.
+
+In case the conditional fails and \maxUij is greater than or equal to delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \maxUij.
+The same suggestion for input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value for delta, to a value slightly greater than \maxUij.
+In this way, we relax the constraint used in the next iteration of precision tuning.
+Otherwise, in case $\varepsilon_{SAFE}$ is equal to zero, the next iteration of the loop is going to predict unnecessarily wide precision value for p, usually greater than 32 bits.

### 2019-04-10 emsoft-2019/main.tex
main
adding new sec. 4&5
Distributing Rocco's texts between sec. 4&5; minor updates to sec. 2&3
Rocco experiments

@@
 \newcommand*{\eva}[1]{\todo[author=Eva,inline,caption={}]{#1}}
+\newcommand*{\rocco}[1]{\todo[author=Rocco,inline,caption={}]{#1}}
+
+\newcommand{\Sadegh}{\textcolor{blue}}
 
@@
 % The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
-\title{Memory-efficient Mixed-Precision Implementations for\\Robust Explicit MPC}
+\title{Memory-Efficient Mixed-Precision Implementations for\\Robust Explicit MPC}
 
@@
 \input{RMPC_Daisy}
-\section{Error Analysis}
-\eva{Assuming a given precision, how to compute the error for a given controller}
-\section{Controller Synthesis}
-\eva{How we actually get the controller, including feedback loop and mixed-precision tuning}
-\input{Methodology}
+\input{finite_precision}%temporary
+\input{Error_Analysis}
+\input{Cont_Syn}
+%\input{Methodology}
 \input{experiments}

### 2019-04-10 emsoft-2019/RMPC_Daisy.tex
sec. 3 is updated

@@
 We assume the pair $(A,B)$ is stablizable.
-\Sadegh{Where do you need this assumption?}
 We assume that the disturbance $w$ belongs to the set $\mathcal{W}$ where $\mathcal{W}$ is a polyhedral set.
+The control input will be of the form $u_k=Kx_k+v_k$, where $K_1$ is selected such that some desired property such as stability is satisfied and $v_k=\kappa(x_k)$ denotes the output of model predictive controller.
 In this paper, we focus on robust formulation of MPC which at each time step, minimizes the worst-case value of the objective function with respect to the disturbances.
@@
 \label{eq:RMPC_prob}
-\min_{u_0,\cdots,u_{N-1}}& \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
-\text{s.t.} \quad &x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\\
-&x_i\in\mathcal{X},\quad u_i\in \mathcal{U},\nonumber
+J^{\ast}(x_0)=\min_{u_0,\cdots,u_{N-1}}& \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
+\text{s.t.} \quad &x_{i+1}=\bar Ax_i+Bv_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
 \end{align}
-\Sadegh{The role of disturbance is missing in the inequalities. We should say, we want to satisfy the inequalities for all possible values of the disturbance.}
+%\Sadegh{The role of disturbance is missing in the inequalities. We should say, we want to satisfy the inequalities for all possible values of the disturbance.}
 
-where $\mathcal U$ and $\mathcal X$ are polyhedral sets as feasible sets of inputs and states.
-$Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon.
-\begin{theorem}[\Sadegh{add reference}]
-The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$.
-Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polyhedral regions:
+where $\bar A=A+BK$, $\mathcal U$ and $\mathcal X$ are polyhedral sets as feasible sets of inputs and states.
+$Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ and $N$ denotes the length of prediction horizon.
+\begin{theorem}[\cite{delaPea:2005}]
+The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K_2(x_0)$.
+Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $\kappa$ is a continuous piecewise affine (PWA) function over polyhedral regions:
 \begin{equation}
-K(x_k)=
+\kappa(x_k)=
 \begin{cases}
@@
 \end{theorem}
-The essential idea of this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ of the following form:
-\begin{align}
-	&\min_{U_N}U_N^TZU_N+x_0^TVU_N+x_0^TYx_0\nonumber\\
-	&s.t.\quad JU_N\leq s+Dx_0
-\end{align} 
-where, $Z\in \reals^{mN\times mN}$, $V\in\reals^{n\times mN}$, $Y\in\reals^{n\times n}$, $J\in\reals^{q\times mN}$, $s\in\reals^{q}$, $D\in\reals^{q\times n}$ and $q$ is the number of inequalities.
+The essential idea of this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and to come up with the following quadratic program that is equivalent to \eqref{eq:RMPC_prob}:
+%\begin{align}
+%	&\min_{U_N}U_N^TZU_N+x_0^TVU_N+x_0^TYx_0\nonumber\\
+%	&s.t.\quad JU_N\leq s+Dx_0
+%\end{align} 
+\begin{align*}
+\label{eq:multi_param_prog}
+&J^{\ast}(x_0)=x_0^TYx_0+\min_{z,\gamma}\frac{1}{2}z^THz+\gamma
+\end{align*}
+subject to
+\begin{align*}
+&G_mz+g_m\gamma\leq W_m+S_mx_0,\\
+&G_cz\leq W_c+S_cx_0
+\end{align*} 
+where, $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables and matrices $Y$, $H$, $G_m$, $G_c$,$S_m$, $S_c$, $W_m$, $W_c$, $g_m$ are matrices of proper sizes that can be easily obtained based on problem parameters (\cite{delaPea:2005}).
+\eqref{eq:multi_param_prog} can be solved efficiently using multi-parametric techniques to compute explicite form of robust MPC.
 %\Sadegh{What is a multi-parametric quadratic problem? Not defined.}
@@
 
-The controller $K$ can be computed using multi-parametric toolbox of MATLAB~\cite{matlabMPT, matlabYALMIP}.
-We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
+The controller $\kappa$ can be computed using multi-parametric toolbox of MATLAB~\cite{matlabMPT, matlabYALMIP}. The feasible set of the problem is defined as union of all regions $\mathcal{R}_{i}$:
 \begin{equation}
@@
 \end{equation}
-\Sadegh{Is this set different from $\mathcal X$? We should explain why it is different.}
 
@@
 %Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong.
-Several algorithms are proposed in the literature \Sadegh{[references?]} to find the right polytope $i$ to which the state $x_k$ belong.
+Several algorithms are proposed in the literature [\cite{Mnnigmann:2011,Jones:2006}] to find the right polytope $i$ to which the state $x_k$ belong.
 The most straightforward technique is a linear search over all polytopes in \Sadegh{\statespace\space} using a switch/case conditional statement of Listing \ref{lst:caseof}.
-\Sadegh{Perhaps we can mention another approach here? add references.}
+%\Sadegh{Perhaps we can mention another approach here? add references.}
 
@@
 switch((*\statevarmath*)):
-case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{1}$*)
-case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}$*)
-case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}$*)
+case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{k}=F_1x_k+G_1 $*)
+case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}=F_2x_k+G_2$*)
+case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}=F_3x_k+G_3$*)
 ...
-case (*$ H_{n}\statevar<=K_{n}$*) then (*$u_{n}$*)
+case (*$ H_{P}\statevar<=K_{P}$*) then (*$u_{P}=F_Px_k+G_P$*)
 \end{lstlisting}
@@
 Therefore, implementation of the above explicit MPC on microcontrollers will bring some issues since all regions' matrices ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s) have to be stored on the microcontroller.
-The goal of our paper is present an approach for minimizing the memeory usage of the implementation while satisfying the hard constraints on the states.
+The goal of our paper is present an approach for minimizing the memory usage of the implementation while satisfying the hard constraints on the states.
 %\section{Finite Precision Implementation}

### 2019-04-10 emsoft-2019/RMPC_Daisy.tex
updates on sec. 3

@@
 \begin{theorem}[\cite{delaPea:2005}]
-The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K_2(x_0)$.
+The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution $U_N=\kappa(x_0)$.
 Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $\kappa$ is a continuous piecewise affine (PWA) function over polyhedral regions:
@@
 subject to
-\begin{align*}
-&G_mz+g_m\gamma\leq W_m+S_mx_0,\\
+\begin{align}
+&G_mz+g_m\gamma\leq W_m+S_mx_0,\nonumber\\
 &G_cz\leq W_c+S_cx_0
-\end{align*} 
+\end{align} 
 where, $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables and matrices $Y$, $H$, $G_m$, $G_c$,$S_m$, $S_c$, $W_m$, $W_c$, $g_m$ are matrices of proper sizes that can be easily obtained based on problem parameters (\cite{delaPea:2005}).
@@
 At each time step $k$, the current state $x_k$ is used to detect the right polytope $i$ such that $H_i x_k\le K_i$.
-Then the control action $u_k = F_i x_k + G_i$ is computed and applied to the system.
+Then the control action $v_k = F_i x_k + G_i$ is computed and applied to the system.
 
@@
 Several algorithms are proposed in the literature [\cite{Mnnigmann:2011,Jones:2006}] to find the right polytope $i$ to which the state $x_k$ belong.
-The most straightforward technique is a linear search over all polytopes in \Sadegh{\statespace\space} using a switch/case conditional statement of Listing \ref{lst:caseof}.
+The most straightforward technique is a linear search over all polytopes in \statespace\space using a switch/case conditional statement of Listing \ref{lst:caseof}.
 %\Sadegh{Perhaps we can mention another approach here? add references.}
@@
 switch((*\statevarmath*)):
-case (*$ H_{1}\statevar<=K_{1}$*) then (*$u_{k}=F_1x_k+G_1 $*)
-case (*$ H_{2}\statevar<=K_{2}$*) then (*$u_{2}=F_2x_k+G_2$*)
-case (*$ H_{3}\statevar<=K_{3}$*) then (*$u_{3}=F_3x_k+G_3$*)
+case (*$ H_{1}\statevar<=K_{1}$*) then (*$v_{k}=F_1x_k+G_1 $*)
+case (*$ H_{2}\statevar<=K_{2}$*) then (*$v_{k}=F_2x_k+G_2$*)
+case (*$ H_{3}\statevar<=K_{3}$*) then (*$v_{k}=F_3x_k+G_3$*)
 ...
-case (*$ H_{P}\statevar<=K_{P}$*) then (*$u_{P}=F_Px_k+G_P$*)
+case (*$ H_{P}\statevar<=K_{P}$*) then (*$v_{k}=F_Px_k+G_P$*)
 \end{lstlisting}

### 2019-04-10 emsoft-2019/Error_Analysis.tex
edits and comments for section 4

--- 2019-04-08 emsoft-2019/Error_Analysis.tex
@@
+%!TEX root = main.tex
 \section{Error Analysis}
-\eva{Assuming a given precision, how to compute the error for a given controller}
-The output of the controller can be affected by two main errors: (i) the controller chooses the wrong activation function because of imperfect implementation of point location algorithm, and (ii) the approximation error deriving from finite precision arithmetic used to compute the activation function itself~\cite{imperialrmpc}.\\
-In an hypothetic scenario where all the measurements were done in infinite precision arithmetic and without any uncertainty, we assume the controller $i$ would be activated.
-Instead, because we cannot rely on infinite precision, controller $j$ is selected.
-The error committed is the difference between the output of the two branches $i$ and $j$.
+\label{sec:Error_Analysis}
 
-The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa), only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions.
-Moreover, we are interested in the worst case scenario where is maximized the difference between the activation functions of any two neighbor regions.
-Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.
+We first present our error analysis assuming given fixed-point word lengths,
+before explaining our optimization algorithm which determines suitable word
+lengths fully automatically in~\autoref{sec:Controller_Synthesis}.
+\eva{The `p' below is the fixed/uniform word length? If so, please explain here}
+\eva{Should we mention here the paper which does the LP-based analysis, i.e.
+contrast our approach?}
 
-Our goal is to build a feasible geometrical space around the border between two neighbor regions $i$ and $j$, where actually it is feasible that \statevarmath belongs to region $i$ but \qstatevarmath follows in region $j$ (or vice-versa).
-We call this geometrical space the \texttt{tube}.
+The output of the controller is affected by two main sources errors which an error
+analysis has to capture: 
+\begin{itemize}
+  \item[(i)] \emph{incorrect region selection}: an incorrect control action can be chosen
+    due to analog-digital conversion and quantization of $H_i$ and $K_i$,
 
-There are two main sources of error affecting the size of the \texttt{tube}: (i) the first one is caused by analog-digital conversion, happening just before the controller receives an estimation of the plant from the sensors.
-We call this error $\varepsilon_{A/D}$:
+  \item[(ii)] \emph{approximate control output}: the control output is computed
+    using quantized $F_i$ and $G_i$, accumulating errors.
+\end{itemize}
 
-\begin{equation}\nonumber
-\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
+We thus have to ensure that these errors remain below the error bound $\Delta$
+used to design the robust MPC controller:
+\begin{align}\label{eq:delta}
+  \max_{\forall i,j. neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i.\mathcal{R}_{i}\in\mathcal{R}} err(u_{i})_{p} \le \Delta
+\end{align}
+where $i,j$ are the indexes of two generic regions $\mathcal{R}_{i}$ and
+$\mathcal{R}_{j}$, \\ $neighbour(\mathcal{R}_{i},\mathcal{R}_{j})$ states that
+two regions share at least a point, $u_{i}$ is the
+control action for controller $i$, and $err(u_{i})_{p}$ is
+the approximation error for computing $u_{i}$ using precision p.
+
+\paragraph{Incorrect Region Selection}
+
+The first part of the error in~\autoref{eq:delta} captures the error due to
+selection of the wrong control action, i.e. with infinite-precision arithmetic
+and in the absence of any uncertainty from hardware measurements we would choose
+control action $u_i$, but due to uncertainties we actually choose control action $u_j$:
+\begin{align} \label{eq:maximization}
+  &\max_{\forall i,j.neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|= \\
+  &\max_{\forall i,j.neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
+\end{align}
+
+%Because of the linearity of the function $u_{i}-u_{j}$, and because of the
+%convexity of the regions $i$ and $j$, it is enough to evaluate function
+%(\ref{eq:maximization}) at the corner points of the \texttt{tube}, instead of
+%solving a maximization problem.
+
+A naive computation of this error would consider all possible values of $x_k$.
+This would lead to a gross over-approximation, however, since the controller
+will choose a wrong region only in a relative narrow neighbourhood, or
+\emph{tube}, around the boundary between two regions $R_i$ and $R_j$.
+In~\autoref{eq:maximization}, we thus constrain $x_k$ to be within an appropriate tube:
+\begin{equation}\label{eq:tube}
+(border_{i,j} >= -\varepsilon) \land (border_{i,j} <= \varepsilon)
 \end{equation}
+where $border_{i,j}$ constrains $x_k$ to be on the border between two regions
+$R_i$ and $R_j$ and $\varepsilon$ captures the uncertainty in computing the
+correct region.
 
-Where $V_{cc}$ is the reference voltage of the converter (e.g. typical 5V) and $p$ represents the number of bit of the processor.
-
-The second error affecting the size of the \texttt{tube} is caused by (ii) the quantization of region bounds in the memory of the micro-controller.
-We call this error $\varepsilon_{Q}$ for error quantization.
-
-While $\varepsilon_{A/D}$ is intrinsic in the capabilities of the device, $\varepsilon_{Q}$ depends on the precision used to store the boundaries.
-This second error can be regulated based on a trade-off among accuracy of the storage and memory save~\cite{memoryMPC}.
-
-The total size of the \texttt{tube} is then:
-\begin{equation}\label{eq:epsilontot}
-\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
-\end{equation}
-%\subsection{Finite Precision Implementation}
-
-The effect of picking the wrong activation function are similar to instability in the switch reported in Listing \ref{lst:caseof}.
-
-In the following, we assume $i$ and $j$ are the index of two generic regions in \statespace:
-\begin{flalign}
-\label{eq:maximization}
-&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| = \\
-&\max_{\forall i,j\;|\;neighbour(i,j)}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
-\end{flalign}
-where \statevarmath belongs to the \texttt{tube} between region $i$ and $j$.
-Because of the linearity of the function $u_{i}-u_{j}$, and because of the convexity of the regions $i$ and $j$, it is enough to evaluate function (\ref{eq:maximization}) at the corner points of the \texttt{tube}, instead of solving a maximization problem.
-
-We compute (\ref{eq:maximization}) for all pairs of neighbor regions $i$ and $j$. Two regions are neighbors when they share at least a border.
-
+\eva{The below, I believe, is somehow defining $border_{i,j}$, but I don't understand
+how. Please explicitly define $border_{i,j}$.}
 In formula $\exists\; m,n \;$such that:
@@
 \end{equation}
-where $m$ and $n$ are the index of the two matching borders. We label with $border_{i,j}$ the matching border shared among the two regions.
+where $m$ and $n$ are the indexes of the two hyperplanes. We label with $border_{i,j}$ the matching border shared among the two regions.
 
-Starting from the equation of $border_{i,j}$, we delimit the geometrical space where it makes sense to compute (\ref{eq:maximization}) with: 
-\begin{equation}
-\begin{aligned}
-(border_{i,j} >= -\varepsilon) \land
-(border_{i,j} <= \varepsilon)
-\end{aligned} 
-\end{equation}
-where $\varepsilon$ is defined in (\ref{eq:epsilontot}). We call such geometrical space the \texttt{tube} between $i$ and $j$.
-
-When \qstatevarmath belongs to the \texttt{tube}, it might be that $u_{i}$ is activated instead of $u_{j}$ (or vice-versa).
-Otherwise, when \qstatevarmath does not belong to the tube, no matter the error $\varepsilon$, the right activation function is activated, and we consider only the error deriving from the computation itself.
-
-Since computing $u_{i}$ introduces approximation error because of finite precision arithmetic, the system has to be robust against an error that is:
-
-\begin{equation}\label{eq:fperror}
-err(u_{i})_{p}=|(\hat{F}_{p}-F)\qstatevar+(\hat{G}_{p}-G)|
+The width of the tube $\varepsilon$, i.e. the uncertainty in computing $x_k$ and
+thus the correct region, is due to two sources of errors: analog-to-digital
+conversion $\varepsilon_{A/D}$ and the quantization of region bounds
+$\mathcal{R}$ in memory $\varepsilon_{Q}$:
+\begin{equation}\label{eq:epsilontot}
+  \varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
 \end{equation}
 
+Analog conversion happens just before the controller receives the sensor input from the plant
+and is given by:
+\begin{equation*}
+\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
+\end{equation*}
+where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V) and
+$p$ represents the number of bits.
+\eva{which bits, who determines these?}
+
+While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
+$\varepsilon_{Q}$ depends on the precision used to store the boundaries. This
+second error can be tuned based on a trade-off between accuracy of the storage and
+memory storage needed~\cite{memoryMPC}.
+%
+$\varepsilon_{Q}$ is given by:
+\begin{equation}\label{eq:quantizationlines}
+  \varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
+\end{equation}
+\eva{Shouldn't this equation have some absolute values in it?}
+\eva{The equation above does not give any hint for how to compute it. I would prefer to
+add the inequality to \autoref{eq:epsilontot} and give an equality here that explicitly
+shows how to compute this. I assume there is some maximization going on here. Then also rephrase the below}
+This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($\hat{H}_{p}$ and $\hat{K}_{p}$), is bounded by $\varepsilon_{Q}$.
+
+\paragraph{Approximate Control Output}
+
+Computing $u_{i}$ itself introduces imprecision because $u_i$ needs to be evaluated 
+in finite precision arithmetic:
+\begin{equation}\label{eq:fperror}
+  err(u_{i})_{p}=|(\hat{F}_{p}-F)\statevar+(\hat{G}_{p}-G)|
+\end{equation}
 where $\hat{F}$ and $\hat{G}$ represent the rounded values (in p bits) for the infinite precision values $F$ and $G$.
 
-In (7) the domain of \qstatevarmath are all the points in region $i$, but also all the values in the \texttt{tube} between region $i$ and any of the neighbors of $i$.
-Even if some points in the tube do not belong to region $i$, it might that $u_{i}$ is (erroneously) activated.
+In (\ref{eq:fperror}) the domain for \statevarmath are all the points in region
+$i$, together with all the values in the tube between region $i$ and
+any of the neighbors of $i$. Even if some points in the tube do not belong to
+region $i$, it might that $u_{i}$ is (erroneously) activated. 
+\eva{$u_{i}$, or some $u_{j}$?}
 
-We compute (\ref{eq:fperror}) for all regions in \statespace\space and we take the maximum value of the error (worst case):
-
-\begin{equation}\label{eq:maxfperror}
-\max_{\forall \regionimath{i}\;in\;\statespace} err(u_{i})_{p}
-\end{equation}
-
-The disturbance \texttt{delta}  has to be an upper bound to the summation of (\ref{eq:maximization}) and (\ref{eq:maxfperror}).
-
-In formula:
-\begin{flalign}
-\label{eq:delta}
-&delta >= \\
-&\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}| + \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
-\end{flalign}
+\eva{This section so far says nothing about how we actually compute these errors (incl. with which tools). 
+This should come here}
+\paragraph{Implementation}

### 2019-04-10 emsoft-2019/Motiv.tex
edits and comments for experiment
section 2

--- 2019-04-08 emsoft-2019/Motiv.tex
@@
 The objective function of the optimization is usually linear or quadratic.
-The resulting optimization problem can be cast as a linear program (LP) or quadratic program (LP), respectively, if the dynamic model is linear.
+The resulting optimization problem can be cast as a linear program (LP) or quadratic program (QP), respectively, if the dynamic model is linear.
 For hybrid models with linear dynamics in each mode, the optimization problem can be cast as a mixed integer linear or quadratic program (MILP/MIQP).
@@
 A survey on Explicit MPC can be found in \cite{Alessio2009}.
-\Sadegh{fix the reference.}
 
-In this section, we use a classical control example to explain the motivation behind this work.
-Consider the problem of designing stablizing control for an inverted pendulum which takes (polytopic) constraints over state variables and control inputs into account.
-The linearized descrete-time description for the open-loop system's dynamics is as follows:
+\begin{figure}[t]
+	\begin{tabular}{cc}
+	\includegraphics[width=2cm,height=4cm]{Figs/inv_pend.png}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
+	(a)&(b)
+	\end{tabular}
+	\caption{(a) Inverted pendulum; (b) 2-D plot of polyhedral partitions for an explicit MPC applied to the inverted pendulum.\Sadegh{Scale the figures better to resemble the actual image, it is now squeezed horizontally.}}
+	\label{fig:inverted_pendulum}
+\end{figure}
+
+As an example of a dynamical system, consider the problem of designing a controller for an inverted pendulum depicted in Fig.~\ref{fig:inverted_pendulum}~{(a)}.
+The goal of the controller is to keep the pendulum at the vertical position while satisfying hard constraints on the state variables and control inputs.
+A model of the system can be constructed using physical principles. After linearization and time discretization, the model is
 	\begin{equation}
@@
 			0\\
-			\frac{T_s}{ml^2}
-		\end{bmatrix}u_k
+			\frac{T_s}{mL^2}
+		\end{bmatrix}u_k + w_k
 		\label{eq:pendul_ss}
 	\end{equation}
-	where, $\theta$, $\omega$ and $u$ denote angular position, angular speed and input torque respectively; $g=9.81 m/s^2$ is the gravitational acceleration, $m$ the ball mass, $b$ the rotational fraction coefficient, $L$ the length of the bar and $T_s$ an appropriate sample time.
-Starting from an initial state, we would like the system's trajectory to converge into its equilibrium point while always $\theta\in[-\pi,\pi]$ and $\omega\in[-\pi/8,\pi/8]$.
-\\
-	While there are many control schemes which can be used to stablize the system (e.g. LQR, state feedback), adding polytopic constraints, MPC schemes will be the best choice. 
+	where $\theta_k$, $\omega_k$ and $u_k$ denote respectively the angular position, angular speed and the input torque at time $kT_s$ with $T_s$ being an appropriate sample time.
+	The disturbance $w_k\in\mathbb R^2$ bounded with $\|w_k\|\leq \Delta$ captures the modeling error due to linearization and discretization.
+The parameter $g=9.81 [m/s^2]$ is the gravitational acceleration, $m$ is the ball mass, $b$ is the rotational fraction coefficient and $L$ is the length of the bar.
+Starting from an initial state $(\theta_0,\omega_0)$, we would like the system's trajectory to converge to its equilibrium point $\theta=0$ and $\omega=0$, while $\theta_k\in[-\pi,\pi]$ and $\omega_k\in[-\pi/8,\pi/8]$ in all time instances.\\
+	There are many control schemes that can guarantee convergence of the trajectories to the rest position (e.g., state feedback or linear quadratic regulator), but fail to ensure hard constraints on the states at all time instances.
+The main feature of MPC schemes is to automatically include these constraints in the design of control actions.
+	%
+	%  adding polytopic constraints, MPC schemes will be the best choice. 
 	%In literature, many control schemes are proposed for stablizing the system around the equilibrium point. 
 	%In order to design a controller which takes additional safety constraints are taken into account, model predictive control (MPC) schemes seem to be best candidate. 
-	However, one major challenge for implementing model predictive controllers over embedded systems will be to solve MPC optimality problem within each time step.
-Since the system under consideration is LTI, one can use explicit MPC scheme proposed in [Bemporad:2002] which computes partitions over state space together with affine functions which are used to compute the optimal control input over their corresponding partition.
-For the inverted-pendulum example, the computed controller contains $12$, over each an affine function is provided for generating the control input.\\
+	One major challenge of implementing model predictive controllers over embedded systems is to solve the related optimization within each sampled time inerval.
+Since the system under consideration is LTI, one can use explicit MPC \cite{Bemporad:2002} that computes partitions over state space together with affine functions which are then used to compute the optimal control input over their corresponding partition.
+For the inverted-pendulum example, the computed controller contains $12$ partition presented in Fig.~\ref{fig:inverted_pendulum}~{(b)}, each with an affine function that gives the control action over that partition.
+
 	%To overcome this issue, in [Bemporad:2002], explicite MPC, a multi-parametric programming based approach is proposed for LTI systems. 
-	In practice, EMPC will be implemented over relatively low-price embedded systems which have limited memory capacity and computational power.
-Computing the optimal control input can be efficiently done using for example binary tree search.
-However, the memory limit is more crucial as it increases proportional to the number of partitions.	Therefore, we would like to explore ways to reduce required memory for saving different coefficients corresponding to the controllers.
-	On the other hand, most of the industrial embedded systems over which EMPC is implemented, only support fixed point arithmetic.
-Using fixed point arithmetic, will cause approximation error that is inversely proportional to the number of bits used for representing each variable.
-It is necessary to count for approximation error as it might lead into violation of the constraints.
-Therefore, one needs to formulate the problem as robust EMPC to count for disturbance input $|\delta|\leq \Delta$ which is summed up with the control input torque $u$ in each time step.
+	In many practical applications, explicit MPC is implemented over relatively low-price embedded systems with limited memory capacity and computational power.
+The partitions together with the affine functions should be stored on the embedded system.
+	Computing the control action, i.e., evaluating the affine function for a specific state, can be performed efficiently using for example binary tree search.
+However, the memory limitations is more crucial since the memory usage increases linearly with the number of partitions.
+	In this paper we discuss a method for reducing the memory usage in applying explicit MPC to LTI dynamical systems.
+	%The goal of this paper is to propose a mTherefore, we would like to explore ways to reduce the required memory for storing the controller efficiently.
+
+	Many low-end embedded systems only support fixed point arithmetic which causes errors that is inversely proportional to the number of bits used for representing each variable.
+It is necessary to account for such errors in the design stage of the controllers to be able to enforce hard constraints on the states at the final implementation of the controller.
+Our proposed method iteratively solves a robust version of the MPC with varying bound on the disturbance to include such errors.
+%Therefore, one needs to formulate the problem as robust EMPC to count for disturbance input $|\delta|\leq \Delta$ which is summed up with the control input torque $u$ in each time step.
 	 %Setting the number of bits for storing different variables, one can compute the upper bound for approximation error, $\bar\omega$.
 	%However, we would like to achieve the minimum number of bits to reduce memory requirements.
-	Overlay, we would like to design a robust explicit model predictive controller, taking into account errors resulted by fixed-point arithmetic and more importantly, to come up with a set of varying precision assignment that covers all the coefficients that must be saved over the embedded system.
-To that end, one approach is to start with an initial $\Delta$; design a robust explicit MPC controller with respect to $\Delta$ and to use state of the art fixed-point error analyzers to decide for the number of bits for saving every parameter of the controller.
-Figure \ref{fig:overview} gives an overview of our proposed setup.\\
-	Again, back to inverted pendulum example, choosing $\Delta=0$, we design an explicit MPC which contains $12$ regions and the same number of controllers.
-However, this value for $\Delta$ is not realizable as error resulted from fixed-point implementation cannot become zero.
-Therefore, we go ahead and choose $\Delta=0.1$.
-Solving robust EMPC problem for the new disturbance bound gives $14$ controllers.
-Next, we ask Daisy to provide us with fixed-point precisions for every variable that respects $\Delta$.
-Using the output of Daisy, we are able to reduce memory requirements for the embedded systems up-to $20\%$ comparing to the case that uniform fixed-point precision is used.
+
+	In summary, we design a robust explicit MPC, taking fixed-point arithmetic errors into account and find a minimal set of mixed precision assignments for all the quantities that must be stored on the embedded system.
+Denote the total number of bits required for implementation of RMPC by $N_b$.
+Given the maximum memory budget denoted by $\bar N_b$, the overall goal will be to design a robust MPC that (i) achieves the performance objectives including hard constraints and (ii) is implemented in a way that $N_b\leq \bar N_b$.
+	%while the error resulted by fixed-point arithmetic is smaller than the error bound $\Delta$.
+	Our approach iteratively expand the bound on disturbance $\Delta+\Delta_0$, designs a robust explicit MPC controller with this bound and uses state-of-the-art fixed-point error analyzers to find the minimum total number of bits for storing the controller into the embedded system with maximum error $\Delta_0$.\\
+
+	Figure \ref{fig:overview} gives a high-level overview of our proposed setup.
+We start with defining the memory budget $\bar N_b$ and an initial bound $\Delta_0$.
+For the inverted pendulum example, we choose $\bar N_b=6000$ and $\Delta_0=0$.
+To design robust explicit MPC, MATLAB is run and the output controller is computed.
+Next, we ask Daisy to provide us with a mixed-precision scheme respecting the error bound $\Delta$.
+However, $\Delta_0=0$ is not realizable as error resulted from fixed-point implementation is always greater than zero.
+Therefore, we go ahead and increase $\Delta$ by \Sadegh{$0.05$}.
+\Sadegh{Is there a way to justify this choice?} Solving the robust explicit MPC problem for the new disturbance bound gives the new controller.
+Next, we ask Daisy to provide us with fixed-point precision for all the parameters such that the new bound is respected.
+The mixed-precision scheme given by Daisy results in total number of bits $N_b=6084$ and since $N_b>\bar N_b$, we increase $\Delta$ again.
+Increasing $\Delta$ by $0.1$, Daisy provides us with a mixed-precision scheme with $N_b=5900$ for the corresponding robust explicit MPC.
+As $N_b<\bar N_b$ the algorithm stops.
+The mixed precision implementation takes $11\%$ less memory compare to the smallest uniform precision that respects $\Delta$.
+%	Using the output of Daisy, we are able to reduce memory requirements for the embedded systems up-to $20\%$ comparing to the case that uniform fixed-point precision is used.
 

### 2019-04-10 emsoft-2019/Cont_Syn.tex
edits and comments for section 4
comments on section 5

@@
-\section{Controller Synthesis}
-\eva{How we actually get the controller, including feedback loop and mixed-precision tuning}
+%!TEX root = main.tex
+\section{Controller Synthesis}\label{sec:Controller_Synthesis}
+
+\begin{figure}
+\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},basicstyle=\small\ttfamily]
+ delta = input()
+ (*$\varepsilon_{Q}$*) = input()
+ assert (delta >= 0 and (*$\varepsilon_{Q}$*) > 0)
+ (*$\varepsilon$*) = (*$\varepsilon_{A/D}$*) + (*$\varepsilon_{Q}$*)
+
+ while True:
+   (*\maxUij*) = design_robust_MPC(delta, (*$\varepsilon$*))
+   if delta > (*\maxUij*):
+     (*$err_{max}(u_{i})_{p}$*) = delta-(*\maxUij*)
+     UNI_MIX_precision(F, G, (*$err_{max}(u_{i})_{p}$*))
+     UNI_MIX_precision(H, K, (*$\varepsilon_{Q}$*))
+     break
+   else:
+     delta=(*\maxUij*)+(*$\varepsilon_{SAFE}$*)
+\end{lstlisting}
+\caption{design of robust MPC with precision tuning}
+\label{lst:alg}
+\end{figure}
+
+\eva{The algorithm in \autoref{lst:alg} needs to be fixed:
+\begin{itemize}
+  \item Use the math symbol for Delta to be consistent with the rest of the paper
+  \item the function design\_robust\_MPC seems to do a lot more than just designing
+    the controller, i.e. it seems to return an error bound instead of a controller.
+    Split into more steps.
+  \item \maxUij and $err_{max}(u_{i})_{p}$ are not good variable names, use a proper variable name
+  \item UNI\_MIX\_precision should also be renamed to something more helpful, e.g. tune\_precision?
+\end{itemize}
+}
+
+In the previous section, we assumed a given precision $p$. In this section we
+present our algorithm for deriving a suitable value of $p$ fully automatically.
+
+\subsection{Algorithm}
+\eva{This section needs to structure the explanation in the order in which it
+appears in the algorithm (i.e. starting from the input and explaining why for
+instance $\epsilon_Q$ is an input), and should reference the lines in the
+algorithm, not only the equations from the previous section}
+
+\eva{The precision tuning, which is the main contribution of the paper is not explained.}
+
+\subsection{Implementation}
+\eva{Some notes about how this is implemented}
+
+\eva{Below is the previous text:}
 %In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.
@@
 
-\subsection{Algorithm}
 In Listing \ref{lst:alg} we describe the procedure used to design a robust MPC controller such that (\ref{eq:deltaminusmax}) is satisfied.
-
-\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},caption=design of robust MPC with precision tuning,label={lst:alg}]
- delta = input()
- (*$\varepsilon_{Q}$*) = input()
- assert (delta >= 0 and (*$\varepsilon_{Q}$*) > 0)
- (*$\varepsilon$*) = (*$\varepsilon_{A/D}$*) + (*$\varepsilon_{Q}$*)
-
- while True:
-   (*\maxUij*) = design_robust_MPC(delta, (*$\varepsilon$*))
-   if delta > (*\maxUij*):
-     (*$err_{max}(u_{i})_{p}$*) = delta-(*\maxUij*)
-     UNI_MIX_precision(F, G, (*$err_{max}(u_{i})_{p}$*))
-     UNI_MIX_precision(H, K, (*$\varepsilon_{Q}$*))
-     break
-   else:
-     delta=(*\maxUij*)+(*$\varepsilon_{SAFE}$*)
-\end{lstlisting}
 

### 2019-04-10 emsoft-2019/related.tex

% !TEX root = main.tex
\section{Related Work}

Any digital controller can be implemented using a wide range of available platforms. Large-size manufacturers use industrial digital computers called \emph{programmable logic controller (PLC)} for such implementations. A PLC is able to perform the computations required by a digital controller using floating-point arithmetic.  Low-end applications utilize microcontrollers with limited memory capacity and computational power to keep the costs of the implementation down.

A digital controller is implemented as an input-output relation or as a state-space representation.
A controller specifies a unique input-output behaviour but has uncountably many state-space representations that are mathematically equivalent.  However, the actual finite-precision implementations of these equivalent representations will result in different errors. See~\cite{ParkPSL17} for an analysis of the finite-precision error in the implementations of different state-space representations and \cite{Anta10} for a software tool that can check system stability under finite-precision implementation errors.

The problem of controller synthesis under safety requirements on the states has
been investigated mostly for Model Predictive Control (MPC)~\cite{camacho2013model} (also called receding horizon control).
Researchers have investigated designing MPC controllers for satisfying safety requirements expressed as temporal logic formulas 
\cite{FMPS18,KaramanSF08,raman2014model,WongpiromsarnTM12,pant2017smooth,kim2017dynamic}.
%,LiNSXL17, SadighK16,
\Sadegh{We can reduce the references.}
The main technique is to optimize the robust satisfaction of 
the formula~\cite{donze2010robust} (i.e., a quantitative measure of satisfaction).
These works utilize MPC an an online method that requires solving at runtime often computationally 
expensive optimization problems. In contrast, the explicit MPC used in our work performs controller synthesis at the design time.

\Sadegh{adding a few references on explicit MPC.}

### 2019-04-10 emsoft-2019/RMPC_Daisy.tex
section 3

@@
 Matrices $A\in \reals^{n\times n}$, $B\in \reals^{n\times m}$ and $E\in \reals^{n\times d}$ are capturing respectively the effects of current state, input and disturbance on the next state.
-We assume the pair $(A,B)$ is stablizable.
-We assume that the disturbance $w$ belongs to the set $\mathcal{W}$ where $\mathcal{W}$ is a polyhedral set.
-The control input will be of the form $u_k=Kx_k+v_k$, where $K_1$ is selected such that some desired property such as stability is satisfied and $v_k=\kappa(x_k)$ denotes the output of model predictive controller.
-In this paper, we focus on robust formulation of MPC which at each time step, minimizes the worst-case value of the objective function with respect to the disturbances.
+We assume the disturbance $w$ belongs to a set $\mathcal{W}$ where $\mathcal{W}$ is a polyhedral set.
+In this paper, we focus on robust formulation of MPC which at each time step, minimizes the worst-case value of the objective function with respect to the disturbances over the control inputs.
 We also consider the objective function to be quadratic with respect to the states and inputs.
-The constrained optimization of each step can be written as
+To reduce the the conservativeness of the optimization and enlarge the set of feasible input trajectories, we assume the pair $(A,B)$ is stablizable and
+$u_k=Kx_k+v_k$, where $K$ is selected such that some desired property such as stability is satisfied, and synthesize $v_k$ for the system.
+%The modifed state evolution of the system will be $x_{k+1}=\bar Ax_k+Bv_k+Ew_k$ with $\bar A := A +BK$.
+% and $v_k=\kappa(x_k)$ denotes the output of model predictive controller.  
+The constrained optimization at each time step is of the form
 \begin{align}
 \label{eq:RMPC_prob}
-J^{\ast}(x_0)=\min_{u_0,\cdots,u_{N-1}}& \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
-\text{s.t.} \quad &x_{i+1}=\bar Ax_i+Bv_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
-&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+J^{\ast}(x_0)=\min_{v_0,\cdots,v_{N-1}}& \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
+\text{s.t.} \quad &x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+\quad &u_i=Kx_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+&u_i\in\mathcal{U},\quad \forall w_i\in\mathcal{W}, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
 &x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
@@
 %\Sadegh{The role of disturbance is missing in the inequalities. We should say, we want to satisfy the inequalities for all possible values of the disturbance.}
-
-where $\bar A=A+BK$, $\mathcal U$ and $\mathcal X$ are polyhedral sets as feasible sets of inputs and states.
-$Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ and $N$ denotes the length of prediction horizon.
+%
+where $\mathcal U$ and $\mathcal X$ are polyhedral sets as feasible sets of inputs and states.
+Matrices $Q\in\reals^{n\times n}$ and $Q_F\in\reals^{n\times n}$ are positive definite, $R\in\reals^{m\times m}$ is positive semidefinite and $N$ denotes the length of the prediction horizon.
 \begin{theorem}[\cite{delaPea:2005}]
-The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution $U_N=\kappa(x_0)$.
-Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $\kappa$ is a continuous piecewise affine (PWA) function over polyhedral regions:
+The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution.
+Furthermore, for the case that $R>0$, the controller is $u_k = K x_k + \kappa(x_k)$ with $\kappa(\cdot)$ being a continuous piecewise affine (PWA) function over polyhedral regions:
 \begin{equation}
@@
 \end{theorem}
-The essential idea of this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and to come up with the following quadratic program that is equivalent to \eqref{eq:RMPC_prob}:
+The essential idea behind this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and transform the optimization \eqref{eq:RMPC_prob} into the following quadratic program:
 %\begin{align}
@@
 %\end{align} 
-\begin{align*}
+\begin{align}
 \label{eq:multi_param_prog}
-&J^{\ast}(x_0)=x_0^TYx_0+\min_{z,\gamma}\frac{1}{2}z^THz+\gamma
-\end{align*}
-subject to
-\begin{align}
-&G_mz+g_m\gamma\leq W_m+S_mx_0,\nonumber\\
-&G_cz\leq W_c+S_cx_0
+J^{\ast}(x_0)=\min_{z,\gamma}& \left[x_0^TYx_0+\frac{1}{2}z^THz+\gamma\right]\\
+\text{s.t.} \quad &G_mz+g_m\gamma\leq W_m+S_mx_0,\nonumber\\
+&G_cz\leq W_c+S_cx_0\nonumber
 \end{align}
-where, $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables and matrices $Y$, $H$, $G_m$, $G_c$,$S_m$, $S_c$, $W_m$, $W_c$, $g_m$ are matrices of proper sizes that can be easily obtained based on problem parameters (\cite{delaPea:2005}).
-\eqref{eq:multi_param_prog} can be solved efficiently using multi-parametric techniques to compute explicite form of robust MPC.
-%\Sadegh{What is a multi-parametric quadratic problem? Not defined.}
+where, $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables and $Y$, $H$, $G_m$, $G_c$,$S_m$, $S_c$, $W_m$, $W_c$, $g_m$ are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).
 
@@
 
-The controller $\kappa$ can be computed using multi-parametric toolbox of MATLAB~\cite{matlabMPT, matlabYALMIP}. The feasible set of the problem is defined as union of all regions $\mathcal{R}_{i}$:
+The optimization \eqref{eq:multi_param_prog} can be solved using multi-parametric techniques to compute the explicit form of $\kappa(\cdot)$.
+Efficient implementation of such computations is available in multi-parametric toolbox of MATLAB~\cite{matlabMPT, matlabYALMIP}.
+Let us denote the set of states $x_0$ for which the optimization  \eqref{eq:multi_param_prog} is feasible by $\mathcal X_s$.
+Then $\mathcal X_s\subseteq \mathcal X$ and is is the union of all regions $\mathcal{R}_{i}$:
 \begin{equation}
-\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
+\mathcal X_s = \bigcup_{i}(H_{i}\statevar<=K_{i}).
 \end{equation}
@@
 %Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong.
-Several algorithms are proposed in the literature [\cite{Mnnigmann:2011,Jones:2006}] to find the right polytope $i$ to which the state $x_k$ belong.
+Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polytope $i$ to which the state $x_k$ belong.
 The most straightforward technique is a linear search over all polytopes in \statespace\space using a switch/case conditional statement of Listing \ref{lst:caseof}.

### 2019-04-10 emsoft-2019/experiments.tex
fixed subsection capitalization
updating sec. 6...

@@
 
-\subsection{End-to-end Robust Controller}
+\subsection{End-to-End Robust Controller}
 \eva{Use the same symbol for Delta and Eps as used in the technical section.}
@@
 
-For the pendulum problem, the domain of X is bounded in the range $X_{0} \in
-(-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$. MATLAB designs a controller with 14
-regions and 58 hyperplanes for each combination of delta and $\varepsilon$.
-% delta spans the interval from 0.05 to 0.3, while $\varepsilon$ from 0.0006 to 0.0050.  % it's in the table
-For the aircraft problem, the domain of X is bounded in the range $X_{0} \in
-(-10000, 10000)$, $X_{1}\in (-734, 734)$, $X_{2}\in (-10000, 10000)$ and
-$X_{3}\in (-790, 790)$. MATLAB returns a controller with 27 regions and 217
-hyperplanes, except when delta=0.30 and $\varepsilon$=0.001 where the controller
-has 26 regions and 208 hyperplanes. In general, when the disturbance value
-increases, the state domain X shrinks to be robust against a greater
-disturbance, or the number of regions reduces.
+\Mahmoud{For the inverted pendulum problem depicted in Section \ref{sec:example}, we set  $m=.344$ kg, $b=0.48$ N s/m, $L=1.703$ m and $T_s=0.1$ s.
+The gain $K$ is selected such the $\bar A$ has poles at $-0.1$ and $-0.5$.
+Moreover, we select $N=2$, $R=1$ and $Q=Q_F=100\mathbf{\it I}$, where $\mathbf{ \it I}$ denotes the identity matrix of proper size.
+The aircraft 4-D model is borrowed from \cite{Kapasouris:1998}.
+Using the gain $K$, the poles of $\bar A$ are placed at $-5$, $-3$, $-1$ and $-2$.
+The robust MPC problem is solved for $N=2$, $R=\mathbf{\it I}$ and $Q=Q_F=5\mathbf{\it I}$.
+Note that for both of the examples, matrices $R$, $Q$ and $Q_F$ are selected such that convergrnce to the origin is given more weight comparing to the control effort as long as constraints are satisfied.
+\\
+We use MATLAB and MPT toolbox software (\cite{matlabMPT})  to compute the explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}).
+For the set of $\varepsilon$ and $\delta$ listed in the Table \ref{tab:ipd}, the off-line computed controller consists of $14$ regions with $58$ 2-D hyperplanes in total.
+Similarly, for the aircraft model MATLAB computed a robust EMPC with $27$ regions and $217$ 4-D hyperplanes.
+The only exception is when $\delta=0.30$ and $\varepsilon$=0.001 for which, we got $26$ regions having $208$ hyperplanes.
+In general, we expect that increasing $\delta$ results in shrinking of feasible set size.}
+
+%the feasible domain $X$ is bounded in the range $X_{0} \in
+%(-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$. MATLAB designs a controller with 14
+%regions and 58 hyperplanes for each combination of delta and $\varepsilon$.
+%% delta spans the interval from 0.05 to 0.3, while $\varepsilon$ from 0.0006 to 0.0050.  % it's in the table
+%For the aircraft problem, the domain of X is bounded in the range $X_{0} \in
+%(-10000, 10000)$, $X_{1}\in (-734, 734)$, $X_{2}\in (-10000, 10000)$ and
+%$X_{3}\in (-790, 790)$. MATLAB returns a controller with 27 regions and 217
+%hyperplanes, except when delta=0.30 and $\varepsilon$=0.001 where the controller
+%has 26 regions and 208 hyperplanes. In general, when the disturbance value
+%increases, the state domain X shrinks to be robust against a greater
+%disturbance, or the number of regions reduces.
 
@@
 keeping the other fixed.
-For the pendulum, the execution time of the analysis is 10 minutes no matter the
+For the pendulum, the execution time of the whole analysis is 10 minutes no matter the
 initial values for delta and $\varepsilon$, while for the aircraft it is 36
@@
 \subsection{Scalability}
+\Mahmoud{The goal of experiments in this section is to show that our algorithm works well even for the case that the controller consists of thousands of PWA functions and regions. 
+%Using the algorithm described in Section \ref{???}, the minimum number of bits for storing the controller is computed such that $\delta$ and $\varepsilon$ are respected. 
+This experiment is different from the end-to-end case in the sense that designing robust EMPC for the error bound $\delta$ is replaced with designing EMPC that might not count for $\delta$.
+Given an EMPC, one can perform robustness analysis to come up with an input error bound $\delta$ under which the performance specifications are satisfied.
+From the implementation point of view, this helps us to scale up-to controllers with thousands of regions, skiping the restrictions for designing robust EMPC with longer time horizons.
+At this point, our algorithm takes $\delta$ (along with a properly selected $\varepsilon$) and produces the optimum mixed precision that results in significant memory save.\\
 The benchmark in this experiment is the double integrator, a canonical example
-of a second order control system. 
+of a second order control system. Following gives the state space descreption for the discrete time version of double integrator
+\begin{equation}
+x_{k+1}=
+\begin{bmatrix}
+1 & T_s\\
+0& 1	
+\end{bmatrix}
+x_k+
+\begin{bmatrix}
+0\\
+T_s
+\end{bmatrix}u_k
+\label{eq:int2_ss}
+\end{equation}
+where, $T_s=0.1$ is the sample time. The state and input constraints are
+\begin{align*}
+	\begin{bmatrix}
+		-5\\-5
+	\end{bmatrix}\leq&
+	x_k\leq
+	\begin{bmatrix}
+	5\\5
+	\end{bmatrix}\\
+	-1\leq& u_k \leq 1
+\end{align*}}
 \eva{More details about this + citation}
 
-For this example, we fix the values for Delta to 0.1 and $\varepsilon$ to 0.001,
-but we consider also the prediction horizon m, as an input parameter for the
-analysis. At design time, the prediction horizon of the controller m models how
-many future iterations of the feed-forward system are considered in the
-optimization problem (infinite horizon would correspond to the optimal
-controller). Note that in this example, the number of regions is highly
-correlated with the prediction horizon m of the controller: the number of regions
-increases with larger m, and thus also increases the execution time of our analysis.
-Even if this is a general behavior, it is not the rule.
+\Mahmoud{For this example, $\delta$ and $\varepsilon$ are fixed into $0.1$ and $0.001$, respectively.
+However, by changing the time horizon $N$ we evaluate scalability of our approach for controllers with very large number of regions.
+Generally, increasing $N$ results in higher number of regions for the output controller.
+To compute the explicit model predictive controllers for different time horizons, we use MATLAB MPC toolbox.}
+
+%For this example, we fix the values for $\delta$ to $0.1$ and $\varepsilon$ to $0.001$,
+%but we consider also the prediction horizon $N$, as an input parameter for the
+%analysis. At design time, the prediction horizon of the controller m models how
+%many future iterations of the feed-forward system are considered in the
+%optimization problem (infinite horizon would correspond to the optimal
+%controller). Note that in this example, the number of regions is highly
+%correlated with the prediction horizon m of the controller: the number of regions
+%increases with larger m, and thus also increases the execution time of our analysis.
+%Even if this is a general behavior, it is not the rule.
 \eva{What does the above sentence mean?}

### 2019-04-10 emsoft-2019/related.tex
more related work

@@
 
-Any digital controller can be implemented using a wide range of available platforms.
-Large-size manufacturers use industrial digital computers called \emph{programmable logic controller (PLC)} for such implementations.
-A PLC is able to perform the computations required by a digital controller using floating-point arithmetic.
-Low-end applications utilize microcontrollers with limited memory capacity and computational power to keep the costs of the implementation down.
+Any digital controller can be implemented using a wide range of available
+platforms. Large-size manufacturers use industrial digital computers called
+\emph{programmable logic controller (PLC)} for such implementations. A PLC is
+able to perform the computations required by a digital controller using
+floating-point arithmetic.  Low-end applications utilize microcontrollers with
+limited memory capacity and computational power to keep the costs of the
+implementation down.
 
-A digital controller is implemented as an input-output relation or as a state-space representation.
-A controller specifies a unique input-output behaviour but has uncountably many state-space representations that are mathematically equivalent.
+% most relevant work: considers both control and finite-precision
+\paragraph{Verification of Finite-precision Controller Implementations}
+% A digital controller is implemented as an input-output relation or as a state-space representation.
+% A controller specifies a unique input-output behaviour but has uncountably many state-space representations that are mathematically equivalent.
 However, the actual finite-precision implementations of these equivalent representations will result in different errors.
@@
 
+While control design algorithms often consider disturbance or noise, they
+usually assume an ideal infinite-precision implementation of the controller.
+Several works have explicitly considered the effects of finite-precision
+implementations on controller robustness.
+
+Given a precision by the user, \citet{imperialrmpc} present an algorithm which
+iteratively designs a robust MPC controller. Similar to our loop, each iteration
+bounds the implementation error due to fixed-point arithmetic and if it exceeds
+the initial disturbance used for the design, repeats the process with an
+adjusted disturbance. This approach does not optimize for the precision and
+bounds implementation errors by reduction to an approximate LP problem. The
+authors further note that the iterations may diverge, i.e. a controller may not
+be found. Since our algorithm optimizes and adjust precision dynamically it will
+eventually find an implementation.
+
+\citet{Anta10} take an existing controller and its implementation, derive safe
+bounds from the controller under which stability is guarantees and verify that
+the implementation in fixed-point arithmetic satisfies this error bound.
+Similarly, \citet{ParkPSL17} takes an existing floating-point controller
+implementation, reconstructs the controller and verifies that roundoff errors
+due to finite precision remain below a user-given error bound.
+
+Unlike previous work which assumed a given implementation precision, the
+approach presented in this paper synthesizes both the controller and the
+fixed-point implementation \emph{at the same time} and thus provides
+a fully automated approach.
+
+\citet{Abate2017} design safe feedback controllers with counterexample guided
+inductive synthesis (CEGIS). Safety verification needs to consider quantization
+errors in the controller and in the plant model as the algorithm is based on
+bounded model checking (BMC) and tracks roundoff errors with interval
+arithmetic. While this algorithm generates the controller and its
+implementation, due to limitations in BMC it only considers uniform fixed-point
+word length in steps of 8.
+\eva{I guess it also does not consider robustness? Not sure how this is related.}
+
+\citet{memoryMPC} propose to use universal numbers (unums) instead of
+traditional floating-point or fixed-point arithmetic for implementing robust
+controllers, but without an error analysis. While unums can reduce memory
+footprint w.r.t. a floating-point implementation, their comparison against
+fixed-point arithmetic in terms of memory and performance is unclear.
+
+% control-only
+\paragraph{Controller Synthesis}
 The problem of controller synthesis under safety requirements on the states has
@@
 \Sadegh{adding a few references on explicit MPC.}
+
+% finite-precision only
+\paragraph{Finite-Precision Optimization}
+General-purpose techniques for synthesizing fixed-point implementations of 
+arithmetic expressions have been developed in the space of embedded systems,
+where resource efficiency is generally important.
+Some work has used dynamic analyses for estimating
+errors~\cite{Gaffar2004,Mallik2007}, which, however, do not provide guarantees.
+Several approaches~\cite{Lee2006,Osborne2007,Kinsman2009,Pang2011} use sound
+error analysis techniques, similar to the ones implemented in the tool Daisy
+which we use.

### 2019-04-10 emsoft-2019/related.tex

@@
 \citet{Anta10} take an existing controller and its implementation, derive safe
-bounds from the controller under which stability is guarantees and verify that
+bounds from the controller under which stability is guaranteed and verify that
 the implementation in fixed-point arithmetic satisfies this error bound.
@@
 \eva{I guess it also does not consider robustness? Not sure how this is related.}
+\Sadegh{Eva, You explanation is good.
+I think the way we look at the problem is different from \cite{Abate2017}: \cite{Abate2017} assumes a fixed precision is given and tries to design the controller with the specific precision such that the safety constraints are satisfied, so no discussion on robustness or memory usage.
+In our case we don't fix a precision.
+We find a controller together with a mixed precision that satisfies the constraints and respects the memory budget.}
 
@@
 %,LiNSXL17, SadighK16,
-\Sadegh{We can reduce the references.}
+%\Sadegh{We can reduce the references.}
 The main technique is to optimize the robust satisfaction of 
@@
 
-\Sadegh{adding a few references on explicit MPC.}
+%\Sadegh{adding a few references on explicit MPC.}
 

### 2019-04-10 emsoft-2019/Motiv.tex
sec. 2 is updated

@@
 % !TEX root = main.tex
-\section{Motivation}
+\section{Motivation}\label{sec:example}
 
@@
 	\begin{tabular}{cc}
-	\includegraphics[width=2cm,height=4cm]{Figs/inv_pend.png}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
+	\includegraphics[width=2cm,height=3cm]{Figs/inv_pend.png}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
 	(a)&(b)
 	\end{tabular}
-	\caption{(a) Inverted pendulum; (b) 2-D plot of polyhedral partitions for an explicit MPC applied to the inverted pendulum.\Sadegh{Scale the figures better to resemble the actual image, it is now squeezed horizontally.}}
+	\caption{(a) Inverted pendulum; (b) 2-D plot of polyhedral partitions for an explicit MPC applied to the inverted pendulum.}
 	\label{fig:inverted_pendulum}
@@
 	In summary, we design a robust explicit MPC, taking fixed-point arithmetic errors into account and find a minimal set of mixed precision assignments for all the quantities that must be stored on the embedded system.
-Denote the total number of bits required for implementation of RMPC by $N_b$.
+Denote the overall error produced by the fixed finite precision implementation by $e$.
+	%Denote the total number of bits required for implementation of RMPC by $N_b$.
 Given the maximum memory budget denoted by $\bar N_b$, the overall goal will be to design a robust MPC that (i) achieves the performance objectives including hard constraints and (ii) is implemented in a way that $N_b\leq \bar N_b$.
+   The overall goal will be to (i) design a robust MPC that achieves the performance objectives including hard constraints while the error because of the fixed-point implementation is taken into account and (ii) to minimize the total number of bits that are required for storing the computed RMPC over the embedded system while $e\leq \Delta$ is satisfied.
 	%while the error resulted by fixed-point arithmetic is smaller than the error bound $\Delta$.
@@
 	Figure \ref{fig:overview} gives a high-level overview of our proposed setup. 
-We start with defining the memory budget $\bar N_b$ and an initial bound $\Delta_0$.
-For the inverted pendulum example, we choose $\bar N_b=6000$ and $\Delta_0=0$.
-To design robust explicit MPC, MATLAB is run and the output controller is computed.
+	%We start with defining the memory budget $\bar N_b$ and an initial bound $\Delta_0$. For the inverted pendulum example, we choose $\bar N_b=6000$ and $\Delta_0=0$. 
+	We start with defining an initial bound $\Delta_0$.
+For the inverted pendulum example, we choose $\Delta_0=0$.
+To design robust explicit MPC, MATLAB is run and the output of the controller is computed.
 Next, we ask Daisy to provide us with a mixed-precision scheme respecting the error bound $\Delta$.
 However, $\Delta_0=0$ is not realizable as error resulted from fixed-point implementation is always greater than zero.
-Therefore, we go ahead and increase $\Delta$ by \Sadegh{$0.05$}.
-\Sadegh{Is there a way to justify this choice?} Solving the robust explicit MPC problem for the new disturbance bound gives the new controller.
+Therefore, we go ahead and increase $\Delta$ by $0.05$.
+Solving the robust explicit MPC problem for the new disturbance bound gives the new controller.
 Next, we ask Daisy to provide us with fixed-point precision for all the parameters such that the new bound is respected.
-The mixed-precision scheme given by Daisy results in total number of bits $N_b=6084$ and since $N_b>\bar N_b$, we increase $\Delta$ again.
+The mixed-precision scheme given by Daisy results in total number of bits $6084$ for the corresponding robust explicit MPC.
+The mixed precision implementation takes about $10\%$ less memory compare to the smallest uniform precision that respects $\Delta$.
+	%The mixed-precision scheme given by Daisy results in total number of bits $N_b=6084$ and since $N_b>\bar N_b$, we increase $\Delta$ again.
 Increasing $\Delta$ by $0.1$, Daisy provides us with a mixed-precision scheme with $N_b=5900$ for the corresponding robust explicit MPC.
@@
 			\centering
-			\node [block,scale=.8, pin={[pinstyle]above:$\Delta=\Delta_0$},
-			node distance=5cm] (RMPC) {RMPC design (MATLAB)};
-			\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
-			\node [block, scale=1,right of=RMPC,
-			node distance=5cm,text width=3cm] (mixed) {Mixed precision computation (Daisy)};
+			\node [block,scale=1,,text width=3.5cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
+			node distance=1cm] (RMPC) {Robust explicit MPC design (computed by MATLAB)};
+			%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
+			\node [block, scale=1,right=2.5cm of RMPC,
+			node distance=5cm,text width=4cm] (mixed) {Finite precision implementation (computed by Daisy)};
 			\node [draw, diamond, 
-			minimum height=3em, minimum width=3em, right of=mixed,
-			node distance=5cm] (decide) {$N_b\leq \bar N_b$};
+			minimum height=3em, minimum width=3em, right =1cm of mixed,
+			node distance=5cm] (decide) {$e\leq \bar \Delta$};
 			\node [block, right of=decide,
@@
 			node distance=3cm] (delta) {increase $\Delta$};
-			\node [scale=.3] at (2.25,-.5)  {
-				$
-				K(x_k)=
-				\begin{cases}
-				F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
-				F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
-				\vdots\\
-				F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
-				\end{cases} 
-				$
+			\node [scale=1] at (3,-.25)  {
+				$u(x)=Kx+v$
 			};
-		\node at (7.5,-.35) {$N_b$};
+		\node at (9,-.25) {$e$};
 

### 2019-04-10 emsoft-2019/Motiv.tex
First draft of intro. Please read comments in Sec 1, 2 and fix them

@@
 
-Model Predictive Control (MPC) refers to the class of control strategies that design control actions by solving a finite horizon optimal control problem at each sampling instant.
+% Model Predictive Control (MPC) refers to the class of control strategies that design control actions by solving a finite horizon optimal control problem at each sampling instant.
 While each optimization gives a sequence of optimal control actions, only the first action is applied to the process.
@@
 MPC has shown to be successful in industrial applications since it is able to handle large number of states and control actions and automatically considers constraints in the optimization.
-
-The optimization of each time instance uses a dynamic model of the process to predict the future states and find the optimal sequence of actions that satisfies all the constraints.
+% 
+% The optimization of each time instance uses a dynamic model of the process to predict the future states and find the optimal sequence of actions that satisfies all the constraints.
 The objective function of the optimization is usually linear or quadratic.
@@
 For hybrid models with linear dynamics in each mode, the optimization problem can be cast as a mixed integer linear or quadratic program (MILP/MIQP).
-
- The main difference between MPC and conventional control is in the nature of the function that maps the measured outputs to control actions.
-The former computes such a function online but the latter pre-computes it off-line.
-The required online computations in MPC limits its applicability to slow processes: the sampling time should be large enough to allow enough time for solving the optimization and obtaining the optimal action for the next time instance.
-Moreover, the optimization solver needs to be certified for using MPC in safety critical applications.
- % while the  therefore that in the latter the control function is pre-computed off-line.
-These issues can be tackled using \emph{Explicit MPC} under proper assumptions on the model, constraints and the objective function.
-Explicit MPC solves the optimization problem off-line over a bounded domain of the state variables by using multiparametric programming techniques.
-The output of Explicit MPC is the optimal control actions as an ?explicit?
-function of the states which is piecewise affine.
-This expands the class of systems being controlled by MPC strategies since the implementation requires only storing a lookup table of linear gains and performing an affine computation using the appropriate gains at each time instance.
-A survey on Explicit MPC can be found in \cite{Alessio2009}.
 
@@
 
-As an example of a dynamical system, consider the problem of designing a controller for an inverted pendulum depicted in Fig.~\ref{fig:inverted_pendulum}~{(a)}.
+As a simple example, consider the problem of designing a controller for an inverted pendulum depicted in Fig.~\ref{fig:inverted_pendulum}~{(a)}.
 The goal of the controller is to keep the pendulum at the vertical position while satisfying hard constraints on the state variables and control inputs.
-A model of the system can be constructed using physical principles. After linearization and time discretization, the model is
+A model of the system can be constructed using physical principles. 
+After linearization and time discretization, the model is
 	\begin{equation}
@@
 	\end{equation}
-	where $\theta_k$, $\omega_k$ and $u_k$ denote respectively the angular position, angular speed and the input torque at time $kT_s$ with $T_s$ being an appropriate sample time.
-	The disturbance $w_k\in\mathbb R^2$ bounded with $\|w_k\|\leq \Delta$ captures the modeling error due to linearization and discretization.
-The parameter $g=9.81 [m/s^2]$ is the gravitational acceleration, $m$ is the ball mass, $b$ is the rotational fraction coefficient and $L$ is the length of the bar.
-Starting from an initial state $(\theta_0,\omega_0)$, we would like the system's trajectory to converge to its equilibrium point $\theta=0$ and $\omega=0$, while $\theta_k\in[-\pi,\pi]$ and $\omega_k\in[-\pi/8,\pi/8]$ in all time instances.\\
-	There are many control schemes that can guarantee convergence of the trajectories to the rest position (e.g., state feedback or linear quadratic regulator), but fail to ensure hard constraints on the states at all time instances.
+where $\theta_k$, $\omega_k$, and $u_k$ denote respectively the angular position, angular speed, 
+and the input torque at time $kT_s$ with $T_s$ being an appropriate sample time.
+The disturbance $w_k\in\mathbb R^2$ bounded with $\|w_k\|\leq \Delta$ captures the modeling error due to 
+linearization and discretization. 
+The parameter $g=9.81 [m/s^2]$ is the gravitational acceleration, $m$ is the ball mass, $b$ is the rotational fraction coefficient, 
+and $L$ is the length of the bar. 
+Starting from an initial state $(\theta_0,\omega_0)$, the control goal is to converge to the equilibrium point 
+$\theta=0$ and $\omega=0$.
+Additionally, we require the state constraints $\theta_k\in[-\pi,\pi]$ and $\omega_k\in[-\pi/8,\pi/8]$ to hold at all time instances.
+
+Our overall goal is to 
+(i) design a robust MPC that achieves the performance objectives including hard constraints in spite of a bounded
+distubrance $\Delta$ modeling the implementation error due to fixed precision;
+and at the same time
+(ii) to minimize the total number of bits that are required for storing the explicit controller 
+while ensuring the error $e\leq \Delta$ is satisfied by the implementation.
+
+% There are many control schemes that can guarantee convergence of the trajectories to the rest position (e.g., state feedback or linear quadratic regulator), but fail to ensure hard constraints on the states at all time instances.
 The main feature of MPC schemes is to automatically include these constraints in the design of control actions.
-	%
-	%  adding polytopic constraints, MPC schemes will be the best choice. 
-	%In literature, many control schemes are proposed for stablizing the system around the equilibrium point. 
-	%In order to design a controller which takes additional safety constraints are taken into account, model predictive control (MPC) schemes seem to be best candidate. 
-	One major challenge of implementing model predictive controllers over embedded systems is to solve the related optimization within each sampled time inerval.
+%	One major challenge of implementing model predictive controllers over embedded systems is to solve the related optimization within each sampled time inerval.
 Since the system under consideration is LTI, one can use explicit MPC \cite{Bemporad:2002} that computes partitions over state space together with affine functions which are then used to compute the optimal control input over their corresponding partition.
@@
 
-	%To overcome this issue, in [Bemporad:2002], explicite MPC, a multi-parametric programming based approach is proposed for LTI systems. 
-	In many practical applications, explicit MPC is implemented over relatively low-price embedded systems with limited memory capacity and computational power.
+%	In many practical applications, explicit MPC is implemented over relatively low-price embedded systems with limited memory capacity and computational power.
 The partitions together with the affine functions should be stored on the embedded system.
-	Computing the control action, i.e., evaluating the affine function for a specific state, can be performed efficiently using for example binary tree search.
+%	Computing the control action, i.e., evaluating the affine function for a specific state, can be performed efficiently using for example binary tree search.
 However, the memory limitations is more crucial since the memory usage increases linearly with the number of partitions.
-	In this paper we discuss a method for reducing the memory usage in applying explicit MPC to LTI dynamical systems.
-	%The goal of this paper is to propose a mTherefore, we would like to explore ways to reduce the required memory for storing the controller efficiently.
+%	In this paper we discuss a method for reducing the memory usage in applying explicit MPC to LTI dynamical systems.
 
-	Many low-end embedded systems only support fixed point arithmetic which causes errors that is inversely proportional to the number of bits used for representing each variable.
+%	Many low-end embedded systems only support fixed point arithmetic which causes errors that is inversely proportional to the number of bits used for representing each variable.
 It is necessary to account for such errors in the design stage of the controllers to be able to enforce hard constraints on the states at the final implementation of the controller.
@@
 
-	In summary, we design a robust explicit MPC, taking fixed-point arithmetic errors into account and find a minimal set of mixed precision assignments for all the quantities that must be stored on the embedded system.
-Denote the overall error produced by the fixed finite precision implementation by $e$.
-	%Denote the total number of bits required for implementation of RMPC by $N_b$.
-Given the maximum memory budget denoted by $\bar N_b$, the overall goal will be to design a robust MPC that (i) achieves the performance objectives including hard constraints and (ii) is implemented in a way that $N_b\leq \bar N_b$.
-   The overall goal will be to (i) design a robust MPC that achieves the performance objectives including hard constraints while the error because of the fixed-point implementation is taken into account and (ii) to minimize the total number of bits that are required for storing the computed RMPC over the embedded system while $e\leq \Delta$ is satisfied.
-	%while the error resulted by fixed-point arithmetic is smaller than the error bound $\Delta$.
-	Our approach iteratively expand the bound on disturbance $\Delta+\Delta_0$, designs a robust explicit MPC controller with this bound and uses state-of-the-art fixed-point error analyzers to find the minimum total number of bits for storing the controller into the embedded system with maximum error $\Delta_0$.\\
+%	In summary, we design a robust explicit MPC, taking fixed-point arithmetic errors into account and find a minimal set of mixed precision assignments for all the quantities that must be stored on the embedded system.
+% Denote the overall error produced by the fixed finite precision implementation by $e$.
+
+%Our approach iteratively expand the bound on disturbance $\Delta+\Delta_0$, designs a robust explicit MPC controller with this bound and 
+% uses state-of-the-art fixed-point error analyzers to find the minimum total number of bits for storing the controller into the embedded system with maximum error $\Delta_0$.
 
 Figure \ref{fig:overview} gives a high-level overview of our proposed setup. 
-	%We start with defining the memory budget $\bar N_b$ and an initial bound $\Delta_0$. For the inverted pendulum example, we choose $\bar N_b=6000$ and $\Delta_0=0$. 
-	We start with defining an initial bound $\Delta_0$.
-For the inverted pendulum example, we choose $\Delta_0=0$.
-To design robust explicit MPC, MATLAB is run and the output of the controller is computed.
-Next, we ask Daisy to provide us with a mixed-precision scheme respecting the error bound $\Delta$.
-However, $\Delta_0=0$ is not realizable as error resulted from fixed-point implementation is always greater than zero.
-Therefore, we go ahead and increase $\Delta$ by $0.05$.
-Solving the robust explicit MPC problem for the new disturbance bound gives the new controller.
-Next, we ask Daisy to provide us with fixed-point precision for all the parameters such that the new bound is respected.
-The mixed-precision scheme given by Daisy results in total number of bits $6084$ for the corresponding robust explicit MPC.
-The mixed precision implementation takes about $10\%$ less memory compare to the smallest uniform precision that respects $\Delta$.
-	%The mixed-precision scheme given by Daisy results in total number of bits $N_b=6084$ and since $N_b>\bar N_b$, we increase $\Delta$ again.
-Increasing $\Delta$ by $0.1$, Daisy provides us with a mixed-precision scheme with $N_b=5900$ for the corresponding robust explicit MPC.
-As $N_b<\bar N_b$ the algorithm stops.
-The mixed precision implementation takes $11\%$ less memory compare to the smallest uniform precision that respects $\Delta$.
-%	Using the output of Daisy, we are able to reduce memory requirements for the embedded systems up-to $20\%$ comparing to the case that uniform fixed-point precision is used.
+We start by defining an initial bound $\Delta_0$. 
+For our example, we choose $\Delta_0=0$. 
+We use MATLAB to find a robust explicit MPC with the bound $\Delta_0$ on the disturbance.
+Next, we ask Daisy \cite{Daisy} 
+to provide us with a mixed-precision scheme such that the implementation satisfies the error bound $\Delta$, that is,
+at all points in the control domain, the difference between the (infinite precision) controller function
+and its implementation in the mixed-precision scheme is at most $\Delta$.
+
+Unfortunately, $\Delta_0=0$ is not realizable,  as the error resulting from a fixed-point 
+implementation is always greater than zero. 
+Therefore, we increase $\Delta$ by $0.05$ and try again. 
+Solving the robust explicit MPC problem for the new disturbance bound gives the new controller,
+shown in Figure~\ref{fig:inverted_pendulum}(b).
+The controller has \RM{XX} regions.
+\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps}
+
+Next, we ask Daisy to provide us with mixed-precision implementation for all the parameters and to compute a static bound on the
+implementation error. 
+The mixed-precision scheme given by Daisy results in an implementation with $6084$ bits in all 
+for the corresponding robust explicit MPC.
+Daisy also computes a static error bound of \RM{what?}
+Since this error bound is less than our robustness margin $\Delta = 0.05$, we terminate the loop
+and return this implementation.
+The mixed precision implementation takes about $10\%$ less memory compared 
+to the smallest uniform precision implementation that respects $\Delta$,
+and about $XXX\%$ \RM{what} less memory than an implementation that uniformly uses
+32 bits per constant.
 
@@
 	\end{tikzpicture}
-	\caption{high-level description of the proposed memory-efficient robust MPC design}
+	\caption{high-level description of the proposed memory-efficient robust MPC design
+\RM{what is $\bar{\Delta}$}
+\RM{try to draw a better picture spanning only one column. the information in this pic is sparse}
+\RM{why is $u$ a single affine map?}
+\RM{why is Daisy only giving $e$? Shouldn't it also return the best mixed precision impl?}
+}
 	\label{fig:overview}

### 2019-04-10 emsoft-2019/Error_Analysis.tex

@@
 
-The output of the controller is affected by two main sources errors which an error
+In the same way described in \cite{imperialrmpc}, the output of the controller can be affected by two main sources errors which an error
 analysis has to capture: 
@@
 control action for controller $i$, and $err(u_{i})_{p}$ is
-the approximation error for computing $u_{i}$ using precision p.
-
+the approximation error for computing the activation function $u_{i}$ in fixed precision using p bits format.
 \paragraph{Incorrect Region Selection}
@@
 \begin{equation}
-(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
+border_{i,j}=(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
 \end{equation}
-where $m$ and $n$ are the indexes of the two hyperplanes. We label with $border_{i,j}$ the matching border shared among the two regions.
+where $m$ and $n$ are the indexes of the matching border respectively in $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$.
 
@@
 \end{equation*}
-where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V) and
-$p$ represents the number of bits.
+where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), p is the number of bits available to quantize the analog signal, and $2^{p}$ is the resolution of the converter.
+
 \eva{which bits, who determines these?}
@@
 While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
-$\varepsilon_{Q}$ depends on the precision used to store the boundaries. This
+$\varepsilon_{Q}$ depends on the precision used to store the boundaries, and it is user defined at compile time. This
 second error can be tuned based on a trade-off between accuracy of the storage and
-memory storage needed~\cite{memoryMPC}.
+memory storage required~\cite{memoryMPC}.
 %
@@
 \begin{equation}\label{eq:quantizationlines}
-  \varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
+  \varepsilon_{Q} > |(H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})|
 \end{equation}
 \eva{Shouldn't this equation have some absolute values in it?}
-\eva{The equation above does not give any hint for how to compute it. I would prefer to
-add the inequality to \autoref{eq:epsilontot} and give an equality here that explicitly
-shows how to compute this. I assume there is some maximization going on here. Then also rephrase the below}
-This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($\hat{H}_{p}$ and $\hat{K}_{p}$), is bounded by $\varepsilon_{Q}$.
+\eva{The equation above does not give any hint for how to compute it.
+I would prefer to add the inequality to \autoref{eq:epsilontot} and give an equality here that explicitly shows how to compute this.
+Then also rephrase the below}
+
+The inequality guarantees that the distance between any hyperplane in infinite precision (H and K), and its counter-part quantized in p bits precision ($\hat{H}_{p}$ and $\hat{K}_{p}$) is bounded by $\varepsilon_{Q}$.
 
@@
 
-In (\ref{eq:fperror}) the domain for \statevarmath are all the points in region
-$i$, together with all the values in the tube between region $i$ and
-any of the neighbors of $i$. Even if some points in the tube do not belong to
-region $i$, it might that $u_{i}$ is (erroneously) activated. 
-\eva{$u_{i}$, or some $u_{j}$?}
+In (\ref{eq:fperror}) the domain for \statevarmath are all the points in region $i$, together with all the values in the tube surrounding region $i$. 
+In this way we compute the error also for those points, that belong to a neighbor of $i$, but because of $\varepsilon$ they are erroneously located inside region $i$.
 
@@
 \paragraph{Implementation}
+
+The designer of the controller fixes the value for $epsilon$ at compile time before starting the analysis.
+$\varepsilon_{Q}$ is also a user dependent parameter fixed at compile time.
+The value for $\varepsilon_{Q}$ depends on the total amount of memory we can dedicate to the storage of H and K on the target controller.
+
+The first part of equation (7) is solved in MATLAB.
+Since the function $u_{i}-u_{j}$ is linear, and we define the tube as a convex region, we need to evaluate the function only at the corner points of the tube and keep the value with the maximal magnitude.
+
+The second part of equation (7), and the precision required for hyperplanes storage are both computed in Daisy. 
+The way we use the analyzer is the following: we give an error bound in input to Daisy together with the coefficients we want to quantize (H, K or F, G).
+Daisy iteratively tries different uniform precisions for the quantization of the coefficients, and stops when it finds the minimal word-length such that the error in input is satisfied.
+Daisy starts the search from unary word-length (1bit), and increases the precision with a one by one step at each iteration.
+It stops when the current (uniform) configuration introduces an approximation error that is bounded by the input error.
+This minimal word-length is going to be the baseline for the mixed-precision tuning phase.
+
+Our analysis returns the total memory (in bits) required by the configuration detected in Daisy.
+The designer can then tune the epsilon value based on the memory consumption of the current configuration.

### 2019-04-10 emsoft-2019/Error_Analysis.tex
Rocco: Error Analysis symbols

@@
 
-We thus have to ensure that these errors remain below the error bound $\Delta$
+We thus have to ensure that these errors remain below the error bound $\delta$
 used to design the robust MPC controller:
 \begin{align}\label{eq:delta}
-  \max_{\forall i,j. neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i.\mathcal{R}_{i}\in\mathcal{R}} err(u_{i})_{p} \le \Delta
+  \max_{\forall i,j. \mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i.\mathcal{R}_{i}\in\mathcal{R}} err(u_{i})_{p} \le \delta
 \end{align}
 where $i,j$ are the indexes of two generic regions $\mathcal{R}_{i}$ and
-$\mathcal{R}_{j}$, \\ $neighbour(\mathcal{R}_{i},\mathcal{R}_{j})$ states that
+$\mathcal{R}_{j}$, \\ $\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})$ states that
 two regions share at least a point, $u_{i}$ is the
@@
 \begin{align} \label{eq:maximization}
-  &\max_{\forall i,j.neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|= \\
-  &\max_{\forall i,j.neighbour(\mathcal{R}_{i},\mathcal{R}_{j})}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
+  &\max_{\forall i,j.\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|= \\
+  &\max_{\forall i,j.\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
 \end{align}
@@
 \begin{equation}\label{eq:tube}
-(border_{i,j} >= -\varepsilon) \land (border_{i,j} <= \varepsilon)
+(\mathit{border}_{i,j} \ge -\varepsilon) \land (\mathit{border}_{i,j} \le \varepsilon)
 \end{equation}
-where $border_{i,j}$ constrains $x_k$ to be on the border between two regions
+where $\mathit{border}_{i,j}$ constrains $x_k$ to be on the border between two regions
 $R_i$ and $R_j$ and $\varepsilon$ captures the uncertainty in computing the
@@
 \begin{equation}
-border_{i,j}=(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
+\mathit{border}_{i,j}=(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
 \end{equation}

### 2019-04-10 emsoft-2019/intro.tex

\section{Introduction}

Model predictive control (MPC) is a technique to design control actions by solving finite-horizon open-loop
optimal control problems at each sampling instant.
The result of each optimization gives a sequence of optimal control actions, only the first of which is applied
to the process.
The same procedure is applied in the next time instant with a shifted time horizon and a new initial state, 
after receiving the updated values of the process state.
The optimization problem in MPC uses a dynamic model of the process, encodes all input and output (state) constraints, and 
optimizes a performance index. 
MPC has shown to be successful in a wide variety of industrial applications, due to its 
ability to systematically handle processes with many state and input variables as well as constraints on them.

The main difference between MPC and conventional control is in the nature of the function that maps the measured outputs to control actions. 
MPC computes such a function \emph{online}, whereas a conventional controller pre-computes the function offline.
The online computations required in MPC limits its applicability to slow processes and fast computation platforms: 
the sampling time has to be large enough and the platform fast enough to allow enough time for solving the optimization problem
and obtaining the optimal action for the next time instance. 
Moreover, the optimization solver needs to be certified when using MPC in safety critical applications.

One way to tackle these problems is through \emph{explicit MPC} \cite{Bemporad:2002,Alessio2009}, which formulates the optimization
problem but computes offline a symbolic representation of the solution as a function of the state.
At run-time, the solution is evaluated on the current state as in conventional control.
For example, for linear time invariant models with linear constraints and quadratic costs, the optimization
problem for MPC can be modeled as a quadratic program, and explicit MPC techniques solve the optimization problem
using multi-parametric programming techniques.
The explicit solution is representable as a partition of the controller domain into a number of polyhedral region,
and an affine map for each region.
The implementation of explicit MPC stores a lookup table of the affine maps and performs a number of affine computations
online to find the appropriate region for the current state and to evaluate the control.  
Explicit MPC thus expands hte class of systems being controlled by MPC strategies, by taking out the need to compute fast online
or to certify a complex optimization routine.

However, there are still bottleneks in implementing explicit MPC on resource-constrained embedded micro-controllers.
First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
problem can involve many (often hundreds) of regions.
Since the memory consumption grows linearly with the number of regions, 
this can be a limited factor in using explicit MPC on resource-constrained micro-controllers.
Second, many low-end micro-controllers only support fixed point arithmetic.
Errors in the controller implementation are inversely proportional to the number of bits used for representing each variable. 
An implementation of explicit MPC has to be \emph{robust} to 
implementation errors to be able to enforce hard constraints on the states at run time.

In this paper, we consider the problem of implementing explicit MPC on low-end microcontrollers with fixed precision arithmetic
in a \emph{memory-efficient} and \emph{robust} way.
We propose an automatic controller and mixed-precision implementation co-design technique that computes a minimal set of mixed
precision assignments for all variables while ensuring the resulting implementation error remains within the robustness margin.

Our proposed method iteratively solves a robust version of the MPC which explicitly models fixed-point implementation errors
in the model; see Figure~\ref{fig:overview}.
Initially, we estimate a bound $\Delta = \Delta_0$ on the implementation error and solve a
min-max quadratic program for explicit robust MPC \cite{delaPea:2005}, where the system
model has an explicit disturbance bounded by $\Delta$.
The solution is represented as a piecewise affine map.
We use an automated mixeed precision tuning tool to find an approximate implementation of the piecewise affine
map and statically compute the error of the implementation.
If the error is at most $\Delta$, we are done: the implementation satisfies the robustness margin in the model.
If not, we increase the error bound $\Delta$ and run the loop again to find a new robust controller and find its best mixed-precision
implementation.

We have implemented our algorithm on top of Matlab's multi-parametric toolbox 
for robust explicit MPC \cite{Matlab-MPT?}
and the Daisy tool for muti-precision tuning and fixed-point error analysis \cite{Daisy}.
We have applied our technique on a number of standard benchmark examples.
Our implementation finds that our mixed-precision implementation can save up to 20\% memory (on average, XXX\%) in controller
implementations over a uniform-precision implementation (and a saving of XXX\% over a uniform 32-bit implementation), while
maintaining the correctness of the controller.
In absolute terms, the saving corresponds to YYY KB over a uniform precision implementation on our largest benchmark.
In each case, the analysis takes only a few minutes of computation.
We also demonstrate the scalability of our mixed-precision tuning and error bounds analysis:
we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes.

### 2019-04-10 emsoft-2019/Cont_Syn.tex
algorithm and error analysis

@@
 \begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},basicstyle=\small\ttfamily]
- delta = input()
+ (*$\delta$*) = input()
  (*$\varepsilon_{Q}$*) = input()
- assert (delta >= 0 and (*$\varepsilon_{Q}$*) > 0)
+ assert ((*$\delta$*) >= 0 and (*$\varepsilon_{Q}$*) > 0)
  (*$\varepsilon$*) = (*$\varepsilon_{A/D}$*) + (*$\varepsilon_{Q}$*)
@@
  while True:
-   (*\maxUij*) = design_robust_MPC(delta, (*$\varepsilon$*))
-   if delta > (*\maxUij*):
-     (*$err_{max}(u_{i})_{p}$*) = delta-(*\maxUij*)
-     UNI_MIX_precision(F, G, (*$err_{max}(u_{i})_{p}$*))
-     UNI_MIX_precision(H, K, (*$\varepsilon_{Q}$*))
+   F,G,H,K = design_robust_MPC((*$\delta$*), (*$\varepsilon$*))
+   errorChoise = compute_MaxUiUj(F,G,H,K)
+   if (*$\delta$*) > errorChoise:
+     errorAct = (*$\delta-$\maxUij*)
+     UNI_MIX_precision(F, G, errorAct)
+     UNI_MIX_precision(H, K, (*$\varepsilon$*))
      break
    else:
-     delta=(*\maxUij*)+(*$\varepsilon_{SAFE}$*)
+     (*$\delta$*)=errorChoise+(*$\varepsilon_{SAFE}$*)
 \end{lstlisting}

### 2019-04-10 emsoft-2019/Error_Analysis.tex
algorithm and error analysis

@@
 \paragraph{Implementation}
-
-The designer of the controller fixes the value for $epsilon$ at compile time before starting the analysis.
+%The designer of the controller fixes the value for $epsilon$ at compile time before starting the analysis.
 $\varepsilon_{Q}$ is also a user dependent parameter fixed at compile time.
@@
 
-The first part of equation (7) is solved in MATLAB.
-Since the function $u_{i}-u_{j}$ is linear, and we define the tube as a convex region, we need to evaluate the function only at the corner points of the tube and keep the value with the maximal magnitude.
+We used two software for implementing the analysis: MATLAB MPC Toolbox and Daisy. The two communicate through a Python interface.
 
-The second part of equation (7), and the precision required for hyperplanes storage are both computed in Daisy. 
-The way we use the analyzer is the following: we give an error bound in input to Daisy together with the coefficients we want to quantize (H, K or F, G).
-Daisy iteratively tries different uniform precisions for the quantization of the coefficients, and stops when it finds the minimal word-length such that the error in input is satisfied.
-Daisy starts the search from unary word-length (1bit), and increases the precision with a one by one step at each iteration.
-It stops when the current (uniform) configuration introduces an approximation error that is bounded by the input error.
+The region selection error is computed in MATLAB.
+Since the function $u_{i}-u_{j}$ is linear, and we defined the tube as a convex region, we need to evaluate the function only at the corner points of the tube, and keep the result with the maximal magnitude.
+
+The approximation error, and the precision required for borders are both computed in Daisy. 
+We provide in input to Daisy the expression we want to quantize together with the error bound we can tolerate.
+Daisy checks whether the input expression, quantized in unary uniform precision (1bit), introduces an error bounded by the input error.
+If this is not the case, Daisy increases the precision format by 1 bit and iterates again.
+The procedure terminates when the first valid format is matched.
 This minimal word-length is going to be the baseline for the mixed-precision tuning phase.
+The mixed-precision phase starts from the uniform precision detected in previous step (baseline).
 
-Our analysis returns the total memory (in bits) required by the configuration detected in Daisy.
+%Our analysis returns the total memory (in bits) required by the configuration detected in Daisy.
 The designer can then tune the epsilon value based on the memory consumption of the current configuration.

### 2019-04-11 emsoft-2019/Motiv.tex
comments for intro

@@
 % !TEX root = main.tex
-\section{Motivation}\label{sec:example}
+\section{Overview}\label{sec:example}
 
@@
 
-As a simple example, consider the problem of designing a controller for an inverted pendulum depicted in Fig.~\ref{fig:inverted_pendulum}~{(a)}.
+As a smaller example, consider the standard problem of designing a controller for an inverted pendulum depicted in~\autoref{fig:inverted_pendulum}~{(a)}.
 The goal of the controller is to keep the pendulum at the vertical position while satisfying hard constraints on the state variables and control inputs.
@@
 and the input torque at time $kT_s$ with $T_s$ being an appropriate sample time.
-The disturbance $w_k\in\mathbb R^2$ bounded with $\|w_k\|\leq \Delta$ captures the modeling error due to 
+The disturbance $w_k\in\mathbb R^2$, bounded by $\|w_k\|\leq \Delta$, captures the modeling error due to 
 linearization and discretization. 
@@
 Starting from an initial state $(\theta_0,\omega_0)$, the control goal is to converge to the equilibrium point 
-$\theta=0$ and $\omega=0$.
+$\theta=0, \omega=0$.
 Additionally, we require the state constraints $\theta_k\in[-\pi,\pi]$ and $\omega_k\in[-\pi/8,\pi/8]$ to hold at all time instances.
@@
 Our overall goal is to 
-(i) design a robust MPC that achieves the performance objectives including hard constraints in spite of a bounded
-distubrance $\Delta$ modeling the implementation error due to fixed precision;
+(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of a bounded
+disturbance $\Delta$ modeling the implementation error due to finite precision;
 and at the same time
+\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
 (ii) to minimize the total number of bits that are required for storing the explicit controller 
@@
 We use MATLAB to find a robust explicit MPC with the bound $\Delta_0$ on the disturbance.
-Next, we ask Daisy \cite{Daisy} 
+Next, we ask Daisy
 to provide us with a mixed-precision scheme such that the implementation satisfies the error bound $\Delta$, that is,
@@
 implementation error. 
-The mixed-precision scheme given by Daisy results in an implementation with $6084$ bits in all 
+The mixed-precision scheme given by Daisy results in an implementation with $6084$ bits in total 
 for the corresponding robust explicit MPC.
@@
 and return this implementation.
-The mixed precision implementation takes about $10\%$ less memory compared 
+The mixed-precision implementation takes about $10\%$ less memory compared 
 to the smallest uniform precision implementation that respects $\Delta$,
 and about $XXX\%$ \RM{what} less memory than an implementation that uniformly uses
-32 bits per constant.
+32 bits.
 

### 2019-04-11 emsoft-2019/intro.tex
comments for intro

@@
 \section{Introduction}
-
+\eva{General comment: it feels a bit long until the intro discusses the actual problem,
+but it reads nicely and motivates the problem well, so it's probably fine}
+\eva{General comment: should we add some more references to related work (and not only to MPC)?}
 Model predictive control (MPC) is a technique to design control actions by solving finite-horizon open-loop
@@
 using multi-parametric programming techniques.
-The explicit solution is representable as a partition of the controller domain into a number of polyhedral region,
+The explicit solution is representable as a partition of the controller domain into a number of polyhedral regions,
 and an affine map for each region.
@@
 online to find the appropriate region for the current state and to evaluate the control.  
-Explicit MPC thus expands hte class of systems being controlled by MPC strategies, by taking out the need to compute fast online
+Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to compute fast online
 or to certify a complex optimization routine.
@@
 this can be a limited factor in using explicit MPC on resource-constrained micro-controllers.
-Second, many low-end micro-controllers only support fixed point arithmetic.
+Second, many low-end micro-controllers only support fixed-point arithmetic.
 Errors in the controller implementation are inversely proportional to the number of bits used for representing each variable. 
@@
 
-In this paper, we consider the problem of implementing explicit MPC on low-end microcontrollers with fixed precision arithmetic
+In this paper, we consider the problem of implementing explicit MPC on low-end microcontrollers with fixed-point arithmetic
 in a \emph{memory-efficient} and \emph{robust} way.
-We propose an automatic controller and mixed-precision implementation co-design technique that computes a minimal set of mixed
+We propose an automatic controller and mixed-precision implementation co-design technique that computes a minimal set\todo{What is meant by minimal?} of mixed
 precision assignments for all variables while ensuring the resulting implementation error remains within the robustness margin.
 
-Our proposed method iteratively solves a robust version of the MPC which explicitly models fixed-point implementation errors
-in the model; see Figure~\ref{fig:overview}.
+Our proposed method iteratively solves a robust version of the MPC which explicitly considers fixed-point implementation errors
+in the model; see~\autoref{fig:overview}.
 Initially, we estimate a bound $\Delta = \Delta_0$ on the implementation error and solve a
@@
 The solution is represented as a piecewise affine map.
-We use an automated mixeed precision tuning tool to find an approximate implementation of the piecewise affine
+We use an automated mixed-precision tuning tool to find an approximate implementation of the piecewise affine
 map and statically compute the error of the implementation.
@@
 implementation.
+\eva{We bound all of the errors, including ones from choosing the wrong region. Worth mentioning here?}
 
@@
 We also demonstrate the scalability of our mixed-precision tuning and error bounds analysis:
-we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes.
+we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes\todo{Hours?}.

### 2019-04-11 emsoft-2019/RMPC_Daisy.tex
two more comments
comments and edits for section 3

@@
 \section{Explicit MPC and Finite Precision}
+In this section, we provide relevant background on robust explicit MPC and
+fixed-point arithmetic and error analysis.
+
 \subsection{Robust Explicit MPC}
@@
 We assume the disturbance $w$ belongs to a set $\mathcal{W}$ where $\mathcal{W}$ is a polyhedral set.
-In this paper, we focus on robust formulation of MPC which at each time step, minimizes the worst-case value of the objective function with respect to the disturbances over the control inputs.
-We also consider the objective function to be quadratic with respect to the states and inputs.
-To reduce the the conservativeness of the optimization and enlarge the set of feasible input trajectories, we assume the pair $(A,B)$ is stablizable and
+In this paper, we focus on the robust formulation of MPC which at each time step
+minimizes the worst-case value of the objective function\todo{which objective function? first mention here without explanation} with respect to the
+disturbances over the control inputs. We consider the objective function to
+be quadratic with respect to the states and inputs. To reduce the 
+conservativeness of the optimization and enlarge the set of feasible input
+trajectories, we assume the pair $(A,B)$ is stabilizable and
 $u_k=Kx_k+v_k$, where $K$ is selected such that some desired property such as stability is satisfied, and synthesize $v_k$ for the system.
+\eva{I don't understand the above sentence. Maybe split into several sentences? Where does $u_k$ come from (the sentence right now says you assume $u_k$)?}
 %The modifed state evolution of the system will be $x_{k+1}=\bar Ax_k+Bv_k+Ew_k$ with $\bar A := A +BK$.
@@
 \label{eq:RMPC_prob}
-J^{\ast}(x_0)=\min_{v_0,\cdots,v_{N-1}}& \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
+J^{\ast}(x_0)=&\min_{v_0,\cdots,v_{N-1}} \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
 \text{s.t.} \quad &x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
@@
 %
-where $\mathcal U$ and $\mathcal X$ are polyhedral sets as feasible sets of inputs and states.
-Matrices $Q\in\reals^{n\times n}$ and $Q_F\in\reals^{n\times n}$ are positive definite, $R\in\reals^{m\times m}$ is positive semidefinite and $N$ denotes the length of the prediction horizon.
+where $\mathcal U$ and $\mathcal X$ are polyhedral sets as\todo{of?} feasible
+sets of inputs and states. Matrices $Q\in\reals^{n\times n}$ and
+$Q_F\in\reals^{n\times n}$ are positive definite, $R\in\reals^{m\times m}$ is
+positive semidefinite and $N$ denotes the length of the prediction horizon.
+\eva{What are $Q, Q_F, R$ and where do they come from?}
+
 \begin{theorem}[\cite{delaPea:2005}]
@@
 \end{equation}
-where $\mathcal{R}_i$ is a ploytope determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
+where $\mathcal{R}_i$ is a ploytope\todo{polytope?} determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
 \end{theorem}
@@
 The optimization \eqref{eq:multi_param_prog} can be solved using multi-parametric techniques to compute the explicit form of $\kappa(\cdot)$.
-Efficient implementation of such computations is available in multi-parametric toolbox of MATLAB~\cite{matlabMPT, matlabYALMIP}.
+An efficient implementation of such computations is available in the multi-parametric toolbox of MATLAB~\cite{matlabMPT, matlabYALMIP}.
 Let us denote the set of states $x_0$ for which the optimization  \eqref{eq:multi_param_prog} is feasible by $\mathcal X_s$.
-Then $\mathcal X_s\subseteq \mathcal X$ and is is the union of all regions $\mathcal{R}_{i}$:
+Then $\mathcal X_s\subseteq \mathcal X$ and is the union of all regions $\mathcal{R}_{i}$:
 \begin{equation}
@@
 Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polytope $i$ to which the state $x_k$ belong.
-The most straightforward technique is a linear search over all polytopes in \statespace\space using a switch/case conditional statement of Listing \ref{lst:caseof}.
+The most straightforward technique is a linear search over all polytopes in \statespace\space using a switch/case conditional statement as shown in~\autoref{lst:caseof}.
 %\Sadegh{Perhaps we can mention another approach here? add references.}
 
-\begin{lstlisting}[escapeinside={(*}{*)},label={lst:caseof}, caption=switch for region selection]
-switch((*\statevarmath*)):
-case (*$ H_{1}\statevar<=K_{1}$*) then (*$v_{k}=F_1x_k+G_1 $*)
-case (*$ H_{2}\statevar<=K_{2}$*) then (*$v_{k}=F_2x_k+G_2$*)
-case (*$ H_{3}\statevar<=K_{3}$*) then (*$v_{k}=F_3x_k+G_3$*)
+\begin{figure}[t]
+\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={switch, case, then}]
+switch($\statevar$):
+  case ($H_{1}\statevar<=K_{1}$) then ($v_{k}=F_1x_k+G_1$)
+  case ($H_{2}\statevar<=K_{2}$) then ($v_{k}=F_2x_k+G_2$)
+  case ($H_{3}\statevar<=K_{3}$) then ($v_{k}=F_3x_k+G_3$)
     ...
-case (*$ H_{P}\statevar<=K_{P}$*) then (*$v_{k}=F_Px_k+G_P$*)
+  case ($ H_{P}\statevar<=K_{P}$) then ($v_{k}=F_Px_k+G_P$)
 \end{lstlisting}
+\caption{Structure of an explicit MPC controller}
+\label{lst:caseof}
+\end{figure}
 %Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.
 
-To keep the costs of implementation down, low-end microcontrollers usually have limited memory and computational power.
-Therefore, implementation of the above explicit MPC on microcontrollers will bring some issues since all regions' matrices ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s) have to be stored on the microcontroller.
-The goal of our paper is present an approach for minimizing the memory usage of the implementation while satisfying the hard constraints on the states.
+To keep the cost of implementation down, low-end microcontrollers usually have
+limited memory and computational power. Therefore, implementation of the above
+explicit MPC on microcontrollers will bring some issues since all regions'
+matrices ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s) have
+to be stored on the microcontroller. Our paper presents an
+approach for minimizing the memory usage of the implementation while satisfying
+the hard constraints on the states.
 %\section{Finite Precision Implementation}

### 2019-04-11 emsoft-2019/finite_precision.tex
comments and edits for section 3

@@
 % general blob about fixed-point arithmetic
-The main task at compile time is to select the fixed-point format for each value
+The main task at compile time is to select the fixed-point format for each input and intermediate value
 in the program. The format specifies the total word length and how many bits are
 available for the integer part of the number. Given ranges on program inputs, a
-range analysis estimates possibles ranges of all intermediate values in the
-program, which in turn determine how many integer bits are sufficient to
+range analysis is usually used to estimate ranges of all intermediate values in the
+program~\cite{Pang2011,Kinsman2009}, which in turn determine how many integer bits are sufficient to
 avoid overflow. The remaining bits of the total word length represent the
@@
 error of the result by tracking worst-case errors at every operation. Given a
-word length for each value, several tools~\cite{Daisy,Gappa} automatically determine the number of
-integer bits needed and compute roundoff errors using a dataflow analysis.
+word length for each value, several tools automatically determine the number of
+integer bits needed and compute roundoff errors using a dataflow analysis~\cite{Daisy,Gappa}.
 They track real-valued ranges at every intermediate operation. These ranges
@@
 error bounds, both the ranges and errors are computed using interval~\cite{intervals} or
-affine arithmetic~\cite{affineArithmetic} which compute sound enclosures. Since intervals do not
-track correlations between variables and affine arithmetic tracks only linear
-ones, the resulting ranges and errors are over-approximated.
+affine arithmetic~\cite{affineArithmetic} which compute sound enclosures. 
+Affine arithmetic tracks linear correlations between variables, so for linear expressions
+the computed ranges are as tight as possible (nonlinear arithmetic
+leads to over-approximations).
 % A standard technique to increase accuracy of the computed errors is interval
@@
 lengths as possible. Mixed-precision tuning tools automatically determine possibly different
-word lengths for different values. Compared to uniform precision (or word length),
+word lengths for different values~\cite{DaisyTuning,Lee2006}. Compared to uniform precision (or word length),
 mixed-precision often leads to improved resource usage, but due to the complexity of
@@
 the search towards promising candidates, e.g. using delta-debugging~\cite{DaisyTuning} or
-simulated annealing~\cite{}. \eva{add missing refs}
+simulated annealing~\cite{Lee2006}.
 

### 2019-04-11 emsoft-2019/intro.tex
two more comments
typos

@@
+% !TEX root = main.tex
 \section{Introduction}
@@
 
-However, there are still bottleneks in implementing explicit MPC on resource-constrained embedded micro-controllers.
+However, there are still bottlenecks in implementing explicit MPC on resource-constrained embedded micro-controllers.
 First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
@@
 in a \emph{memory-efficient} and \emph{robust} way.
-We propose an automatic controller and mixed-precision implementation co-design technique that computes a minimal set\todo{What is meant by minimal?} of mixed
+We propose an automatic controller and mixed-precision implementation co-design technique that computes a minimal set \todo{What is meant by minimal?} of mixed
 precision assignments for all variables while ensuring the resulting implementation error remains within the robustness margin.
@@
 \eva{We bound all of the errors, including ones from choosing the wrong region. Worth mentioning here?}
+\eva{According to sec 5, the loop is not due to mixed-tuning failing, but due to the region error being too large}
 
@@
 for robust explicit MPC \cite{Matlab-MPT?}
-and the Daisy tool for muti-precision tuning and fixed-point error analysis \cite{Daisy}.
+and the Daisy tool for multi-precision tuning and fixed-point error analysis \cite{Daisy}.
 We have applied our technique on a number of standard benchmark examples.

### 2019-04-11 emsoft-2019/related.tex
related work additions

@@
 implementation, reconstructs the controller and verifies that roundoff errors
-due to finite precision remain below a user-given error bound.
+due to finite precision remain below a user-given error bound. The LCV tool~\cite{Park2019}
+additionally checks that the generated code is equivalent (within an error bound)
+to a Simulink block diagram model.
 
@@
 Several approaches~\cite{Lee2006,Osborne2007,Kinsman2009,Pang2011} use sound
-error analysis techniques, similar to the ones implemented in the tool Daisy
-which we use.
+error analysis techniques and perform mixed-precision optimization~\cite{Lee2006,Pang2011},
+similar to the approach implemented in the tool Daisy which we use.

### 2019-04-11 emsoft-2019/Motiv.tex
two more comments
disturbance

@@
 % !TEX root = main.tex
-\section{Overview}\label{sec:example}
+\section{Overview}
+\label{sec:example}
 
@@
 and the input torque at time $kT_s$ with $T_s$ being an appropriate sample time.
-The disturbance $w_k\in\mathbb R^2$, bounded by $\|w_k\|\leq \Delta$, captures the modeling error due to 
-linearization and discretization. 
+The disturbance $w_k\in\mathbb R^2$, \Sadegh{bounded with a polyhedral set $w_k\in \mathcal W$, captures the modeling error due to 
+linearization and discretization}. 
 The parameter $g=9.81 [m/s^2]$ is the gravitational acceleration, $m$ is the ball mass, $b$ is the rotational fraction coefficient, 
@@
 Our overall goal is to 
-(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of a bounded
-disturbance $\Delta$ modeling the implementation error due to finite precision;
+(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of \Sadegh{an additional bounded
+disturbance $\Delta$ modeling the implementation error (both errors due to choosing a wrong region and the finite-precision computation of the control action);}
 and at the same time
-\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
+%\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
 (ii) to minimize the total number of bits that are required for storing the explicit controller 
-while ensuring the error $e\leq \Delta$ is satisfied by the implementation.
+while ensuring the implementation error $e\leq \Delta$ is satisfied by the implementation.
 
@@
 Figure \ref{fig:overview} gives a high-level overview of our proposed setup.
-We start by defining an initial bound $\Delta_0$. 
-For our example, we choose $\Delta_0=0$. 
-We use MATLAB to find a robust explicit MPC with the bound $\Delta_0$ on the disturbance.
+\Sadegh{
+We start by selecting an initial bound $\Delta_0$ on the implementation error and enlarge $\mathcal W$ with $\Delta_0$ as $\mathcal W_{\Delta_0}$, where
+\begin{equation}
+\mathcal W_{\Delta} := \{w_1+w_2 \,|\, w_1\in \mathcal W, \|w_2\|\le \Delta\}
+\quad\text{ for all } \Delta\ge 0.
+\end{equation}
+ }
+
+ \Sadegh{
+For our example, we choose $\Delta_0=0$ and $\mathcal W = \{0\}$. 
+We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$.
 Next, we ask Daisy
-to provide us with a mixed-precision scheme such that the implementation satisfies the error bound $\Delta$, that is,
-at all points in the control domain, the difference between the (infinite precision) controller function
-and its implementation in the mixed-precision scheme is at most $\Delta$.
+to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
+at all points in the control domain, the difference between the infinite-precision controller function
+and its mixed-precision implementation is at most $\Delta_0$.
+}
 
-Unfortunately, $\Delta_0=0$ is not realizable,  as the error resulting from a fixed-point 
-implementation is always greater than zero. 
-Therefore, we increase $\Delta$ by $0.05$ and try again. 
-Solving the robust explicit MPC problem for the new disturbance bound gives the new controller,
+\Sadegh{
+Unfortunately, $\Delta_0=0$ is not realizable, as the implementation error is always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
+%\eva{Is this the error due to mixed-precision or due to wrong regions?}
+Therefore, we define $\Delta_1 := \Delta_0 + \delta$ with $\delta$ being a fixed threshold (we chose $\delta = 0.05$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
+Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
 shown in Figure~\ref{fig:inverted_pendulum}(b).
@@
 \RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps} 
+}
 
@@
 Daisy also computes a static error bound of \RM{what?}
-Since this error bound is less than our robustness margin $\Delta = 0.05$, we terminate the loop
+Since this error bound is less than our robustness margin $\Delta_1 = 0.05$, we terminate the loop
 and return this implementation.
 The mixed-precision implementation takes about $10\%$ less memory compared 
-to the smallest uniform precision implementation that respects $\Delta$,
+to the smallest uniform precision implementation that respects $\Delta_1$,
 and about $XXX\%$ \RM{what} less memory than an implementation that uniformly uses

### 2019-04-11 emsoft-2019/experiments.tex
modifying sec. 6

@@
 \subsection{End-to-End Robust Controller}
-\eva{Use the same symbol for Delta and Eps as used in the technical section.}
+%\eva{Use the same symbol for Delta and Eps as used in the technical section.}
 
@@
 controller design.
-\eva{Describe aircraft example, add citation}
+%\eva{Describe aircraft example, add citation}
 
-\Mahmoud{For the inverted pendulum problem depicted in Section \ref{sec:example}, we set  $m=.344$ kg, $b=0.48$ N s/m, $L=1.703$ m and $T_s=0.1$ s.
+%\Mahmoud{
+For the inverted pendulum problem depicted in Section \ref{sec:example}, we set  $m=.344$ kg, $b=0.48$ N s/m, $L=1.703$ m and $T_s=0.1$ s.
 The gain $K$ is selected such the $\bar A$ has poles at $-0.1$ and $-0.5$.
@@
 The aircraft 4-D model is borrowed from \cite{Kapasouris:1998}.
+The control inputs are the elevator and flaperon angles, and the attack and pitch angles are the output states that need to be regulated.
+The open-loop system is unstable as it has a pole with positive real part.
+Both control inputs are constrained between $-/+25$ degrees.
+Both the outputs are only constrained during the first prediction horizon.
+You also specify scale factors for outputs.
 Using the gain $K$, the poles of $\bar A$ are placed at $-5$, $-3$, $-1$ and $-2$.
@@
 The only exception is when $\delta=0.30$ and $\varepsilon$=0.001 for which, we got $26$ regions having $208$ hyperplanes.
-In general, we expect that increasing $\delta$ results in shrinking of feasible set size.}
+In general, we expect that increasing $\delta$ results in shrinking of feasible set size.%}
 
@@
 required for storing F and G and H and K. We show the results for each benchmark
-for ten different combinations of delta and $\varepsilon$, varying one while
+for ten different combinations of $\delta$ and $\varepsilon$, varying one while
 keeping the other fixed.
 For the pendulum, the execution time of the whole analysis is 10 minutes no matter the
-initial values for delta and $\varepsilon$, while for the aircraft it is 36
+initial values for $\delta$ and $\varepsilon$, while for the aircraft it is 36
 minutes. \rocco{maybe table for execution times}
@@
 
-\eva{Fix Table 1 caption. It's not the difference, but savings. Difference is absolute.}
-\eva{Compute the actual averages for all F, G, H, K and not only approximations}
-For the inverted pendulum, minimal uniform precision saves ???\% of memory
+%\eva{Fix Table 1 caption. It's not the difference, but savings. Difference is absolute.}
+%\eva{Compute the actual averages for all F, G, H, K and not only approximations}
+For the inverted pendulum, minimal uniform precision saves $57.5\%$ of memory
 compared to a uniform 32 bit baseline (column `\%32vU' in~\autoref{tab:ipd}) on
 average overall (for F, G, H and K together). Mixed-precision further reduces the memory
-requirement by ???\% on average with respect to the minimal uniform baseline
+requirement by $10.4\%$ on average with respect to the minimal uniform baseline
 (column `\%UvM' in~\autoref{tab:ipd}). 
@@
 
-\eva{Compute actual and overall averages here too}
-For the aircraft example, minimal uniform precision saves on average ???\%
+%\eva{Compute actual and overall averages here too}
+For the aircraft example, minimal uniform precision saves on average $33.5\%$
 overall w.r.t. a uniform 32 bit baseline, and mixed-precision saves an
-additional ???\% w.r.t. minimal uniform precision. We observe higher relative
+additional $17.6\%$ w.r.t. minimal uniform precision. We observe higher relative
 memory savings by mixed-precision for storing H and K.
@@
 %We noticed the following common behavior in the two benchmarks: 
-As expected, when delta decreases, the activation functions (F, G) need to be
+As expected, when $\delta$ decreases, the activation functions (F, G) need to be
 more precise and require more memory, because the space for approximation error
@@
 The second difference consists in the last two lines in Table\ref{tab:ipd}.
-In the aircraft, when $\varepsilon$=0.0030, the \maxUij exceeds delta=0.1 and we
+In the aircraft, when $\varepsilon$=0.0030, the \maxUij exceeds $\delta=0.1$ and we
 need to design again the controller (it corresponds to the else branch in
 Listing\ref{fig:overview}). The loop converges after 5 iterations (\texttt{then}
-branch of the conditional) with delta=0.112. After each iteration, the new value
-for delta is the last \maxUij\space plus a constant value in the order of
+branch of the conditional) with $\delta=0.112$. After each iteration, the new value
+for $\delta$ is the last \maxUij\space plus a constant value in the order of
 $10^{-3}$. Thanks to this $\varepsilon_{SAFE}$ we sensibly reduce memory demand
@@
 surprising/different than the number of bits show?}
-The first halves of both pendulum and aircraft sections in \autoref{tab:ipd}, show how delta does not affect the maximal error among regions \maxUij.
-We verify that a variation for delta (typically in the order of $\pm$ 0.1) results in a minimal alteration to the domain of regions X (in the order of $\pm 10^{-10}$), not enough to produce a sensitive variation to \maxUij.
-Then, when \maxUij\space is constant the error bound for computations $err(u_{i})$ decreases together with delta.
+The first halves of both pendulum and aircraft sections in \autoref{tab:ipd}, show how $\delta$ does not affect the maximal error among regions \maxUij.
+We verify that a variation for $\delta$ (typically in the order of $\pm$ 0.1) results in a minimal alteration to the domain of regions X (in the order of $\pm 10^{-10}$), not enough to produce a sensitive variation to \maxUij.
+Then, when \maxUij\space is constant the error bound for computations $err(u_{i})$ decreases together with $\delta$.
 The memory required for the storage of F and G depends on $err(u_{i})$: the smaller the value for $err(u_{i})$, the more precise has to be the arithmetic for activation functions.
 
-In the second halves in \autoref{tab:ipd}, we fix the value for delta and we try different $\varepsilon$.
+In the second halves in \autoref{tab:ipd}, we fix the value for $\delta$ and we try different $\varepsilon$.
 When we increase the safe space between two regions by $\varepsilon$, the value for \maxUij is computed for new corner points.
@@
 The more $\varepsilon$ moves \statevarmath far from the border, the more \maxUij increases.
-When \maxUij is almost equal to delta, the space for $err(u_{i})$ is minimized, and the controller requires high precision for computations (see last lines for pendulum and aircraft in Table\ref{tab:ipd}).
+When \maxUij is almost equal to $\delta$, the space for $err(u_{i})$ is minimized, and the controller requires high precision for computations (see last lines for pendulum and aircraft in Table\ref{tab:ipd}).
 On the other hand, when $\varepsilon$ increases, the analysis can reduce the memory requirements for the storage of borders (see columns Uni and Mix in the second halves of both benchmarks).
@@
 \subsection{Scalability}
-\Mahmoud{The goal of experiments in this section is to show that our algorithm works well even for the case that the controller consists of thousands of PWA functions and regions. 
+%\Mahmoud{
+The goal of experiments in this section is to show that our algorithm works well even for the case that the controller consists of thousands of PWA functions and regions. 
 %Using the algorithm described in Section \ref{???}, the minimum number of bits for storing the controller is computed such that $\delta$ and $\varepsilon$ are respected. 
@@
 	-1\leq& u_k \leq 1
-\end{align*}}
-\eva{More details about this + citation}
+\end{align*}%}
+%\eva{More details about this + citation}
 
-\Mahmoud{For this example, $\delta$ and $\varepsilon$ are fixed into $0.1$ and $0.001$, respectively.
+%\Mahmoud{
+For this example, $\delta$ and $\varepsilon$ are fixed into $0.1$ and $0.001$, respectively.
 However, by changing the time horizon $N$ we evaluate scalability of our approach for controllers with very large number of regions.
 Generally, increasing $N$ results in higher number of regions for the output controller.
-To compute the explicit model predictive controllers for different time horizons, we use MATLAB MPC toolbox.}
+To compute the explicit model predictive controllers for different time horizons, we use MATLAB MPC toolbox.%}
 
@@
 %Even if this is a general behavior, it is not the rule.
-\eva{What does the above sentence mean?}
+%\eva{What does the above sentence mean?}
 
@@
 hyperplane can be analyzed independently.
-\eva{There should be an explanation why this is not providing end-to-end robustness}
+%\eva{There should be an explanation why this is not providing end-to-end robustness}
 
@@
 We observe that our analysis scales up to 1200 controllers and 25000 hyperplanes in few
-hours. 
-\eva{Compute and say something about the overall savings for F, G, H, K, and proper average (at least for UvM)}
+hours.  The computed minimal uniform precision saves $49.8\%$ of memory
+compared to a uniform $32$ bit baseline (column `\%32vU' in~\autoref{tab:di}) on
+average overall (for F, G, H and K together). Moreover, mixed-precision reduces the memory
+requirement by $9.6\%$ on average with respect to the minimal uniform baseline
+(column `\%UvM' in~\autoref{tab:di}). 
+%\eva{Compute and say something about the overall savings for F, G, H, K, and proper average (at least for UvM)}
 We further observe that relative savings remain largely constant for different 

### 2019-04-11 emsoft-2019/intro.tex
fixing references

@@
 We use an automated mixed-precision tuning tool to find an approximate implementation of the piecewise affine
-map and statically compute the error of the implementation.
+map. 
+We statically compute the error of the implementation, taking into account errors
+in evaluating the affine maps as well as choosing the wrong affine map due to quantization.
 If the error is at most $\Delta$, we are done: the implementation satisfies the robustness margin in the model.
@@
 implementation.
-\eva{We bound all of the errors, including ones from choosing the wrong region. Worth mentioning here?}
-\eva{According to sec 5, the loop is not due to mixed-tuning failing, but due to the region error being too large}
 

### 2019-04-11 emsoft-2019/related.tex
removing comment on related work

@@
 word length in steps of 8.
-\eva{I guess it also does not consider robustness? Not sure how this is related.}
-\Sadegh{Eva, You explanation is good.
+% \eva{I guess it also does not consider robustness? Not sure how this is related.}
+% \Sadegh{Eva, You explanation is good.
 I think the way we look at the problem is different from \cite{Abate2017}: \cite{Abate2017} assumes a fixed precision is given and tries to design the controller with the specific precision such that the safety constraints are satisfied, so no discussion on robustness or memory usage.

### 2019-04-11 emsoft-2019/Cont_Syn.tex
Rocco: 5.1 Algorithm

@@
  while True:
-   F,G,H,K = design_robust_MPC((*$\delta$*), (*$\varepsilon$*))
-   errorChoise = compute_MaxUiUj(F,G,H,K)
+   F,G,H,K = design_robust_MPC((*$\delta$*))
+   errorChoise = incorrect_region_error(F,G,H,K,(*$\varepsilon$*))
    if (*$\delta$*) > errorChoise:
-     errorAct = (*$\delta-$\maxUij*)
-     UNI_MIX_precision(F, G, errorAct)
-     UNI_MIX_precision(H, K, (*$\varepsilon$*))
+     errorAct = (*$\delta$*) - errorChoise
+     precision_tuning(F, G, errorAct)
+     precision_tuning(H, K, (*$\varepsilon$*))
      break
@@
 
-\eva{The algorithm in \autoref{lst:alg} needs to be fixed:
-\begin{itemize}
-  \item Use the math symbol for Delta to be consistent with the rest of the paper
-  \item the function design\_robust\_MPC seems to do a lot more than just designing
-    the controller, i.e. it seems to return an error bound instead of a controller.
-    Split into more steps.
-  \item \maxUij and $err_{max}(u_{i})_{p}$ are not good variable names, use a proper variable name
-  \item UNI\_MIX\_precision should also be renamed to something more helpful, e.g. tune\_precision?
-\end{itemize}
-}
+%\eva{The algorithm in \autoref{lst:alg} needs to be fixed:
+%\begin{itemize}
+  %\item Use the math symbol for Delta to be consistent with the rest of the paper
+  %\item the function design\_robust\_MPC seems to do a lot more than just designing the controller, i.e. it seems to return an error bound instead of a controller. Split into more steps.
+  %\item \maxUij and $err_{max}(u_{i})_{p}$ are not good variable names, use a proper variable name
+  %$\item UNI\_MIX\_precision should also be renamed to something more helpful, e.g. tune\_precision?
+%\end{itemize}
+%}
 
@@
 appears in the algorithm (i.e. starting from the input and explaining why for
-instance $\epsilon_Q$ is an input), and should reference the lines in the
+instance $\varepsilon_Q$ is an input), and should reference the lines in the
 algorithm, not only the equations from the previous section}
+\autoref{lst:alg} reports the optimization algorithm we implemented to build robust MPC controllers with guaranteed error bounds.
+
+From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$.
+$\delta$ is the maximal disturbance coefficient the controller has to be designed for.
+It is a problem dependent parameter, and thus can be any positive number.
+Typically, it is in the order of 0.1.
+$\varepsilon_{Q}$ is the imprecision error-bound for the quantization of borders. 
+The latter has to be strictly greater than zero, otherwise we could rely on infinite precision for storage of borders. Usually, the value for $\varepsilon_{Q}$ is in the order of 0.001.
+
+In line 4, we compute the error $\varepsilon$ as described in (11), where $\varepsilon_{A/D}$ is a constant parameter dependent on the specific of the converter.
+
+Once input parameters are verified, in line 7 we design the controller in MATLAB MPC Toolbox.
+The suite receives in input the coefficient $\delta$, and the state space model for the plant (e.g.
+inverted pendulum or aircraft) we need to control.
+The suite returns a piecewise affine function (F and G) together with a polytopes region partitioning (H and K).
+
+In line 8, we compute the incorrect region error: we build the tube regions around the borders (\ref{eq:tube})  using $\varepsilon$ and we compute (\ref{eq:maximization}) for the corner points of the tube.
+
+In the conditional in line 9, we check whether the robustness $\delta$ is greater than the incorrect region error.
+If this is not the case, the initial value for $\delta$ was not robust to the magnitude of this error, and we need to re-design the controller with a greater $\delta$.
+Indeed in line 15, the value $\delta$ for the next iteration has to be at least the same magnitude of the current errorChoise.
+Moreover, we increase by a small scalar $\varepsilon_{SAFE}$ (in the order of 0.001) the value for $\delta$ to speed-up the convergence of the analysis.
+
+In case the conditional in line 9 succeeds, the precision tuning phase starts.
+The way we do the precision tuning is the following: we provide in input to Daisy a numerical error-bound together with an expression to quantize (e.g.
+an activation function).
+Daisy returns in output both the minimal-uniform precision, and the mixed-precision configuration, such that the quantization of the expression in the given precision configuration introduces an error that is bounded by the input error.
+
+In line 10 we compute the error bound for approximate control output error.
+This is going to be the maximal error we tolerate for activation functions.
+The precision tuning at line 11 receives in input the approximation control error together with the coefficients F and G.
+In Line 12 we give to Daisy the error $\varepsilon$ for borders, together with the hyperplanes coefficients H and K.
 

### 2019-04-11 emsoft-2019/intro.tex

@@
 We have implemented our algorithm on top of Matlab's multi-parametric toolbox 
-for robust explicit MPC \cite{Matlab-MPT?}
+for robust explicit MPC~\cite{matlabMPT}
 and the Daisy tool for multi-precision tuning and fixed-point error analysis \cite{Daisy}.

### 2019-04-11 emsoft-2019/experiments.tex
edits to experimental section

@@
 
-We evaluate our complete pipeline on two benchmarks: the inverted pendulum
-described in~\autoref{sec:example} and a well-known 4D example for aircraft
-controller design.
-%\eva{Describe aircraft example, add citation}
+We evaluate our complete pipeline on two benchmarks. 
+The first one is the inverted pendulum problem depicted in Section \ref{sec:example}, where we set
+$m=0.344$ kg, $b=0.48$ N s/m, $L=1.703$ m and $T_s=0.1$ s. The gain $K$ is
+selected such the $\bar A$ has poles at $-0.1$ and $-0.5$. Moreover, we select
+$N=2$, $R=1$ and $Q=Q_F=100\mathbf{\it I}$, where $\mathbf{ \it I}$ denotes the
+identity matrix of proper size.
 
-%\Mahmoud{
-For the inverted pendulum problem depicted in Section \ref{sec:example}, we set  $m=.344$ kg, $b=0.48$ N s/m, $L=1.703$ m and $T_s=0.1$ s.
-The gain $K$ is selected such the $\bar A$ has poles at $-0.1$ and $-0.5$.
-Moreover, we select $N=2$, $R=1$ and $Q=Q_F=100\mathbf{\it I}$, where $\mathbf{ \it I}$ denotes the identity matrix of proper size.
-The aircraft 4-D model is borrowed from \cite{Kapasouris:1998}.
-The control inputs are the elevator and flaperon angles, and the attack and pitch angles are the output states that need to be regulated.
-The open-loop system is unstable as it has a pole with positive real part.
-Both control inputs are constrained between $-/+25$ degrees.
-Both the outputs are only constrained during the first prediction horizon.
-You also specify scale factors for outputs.
-Using the gain $K$, the poles of $\bar A$ are placed at $-5$, $-3$, $-1$ and $-2$.
-The robust MPC problem is solved for $N=2$, $R=\mathbf{\it I}$ and $Q=Q_F=5\mathbf{\it I}$.
-Note that for both of the examples, matrices $R$, $Q$ and $Q_F$ are selected such that convergrnce to the origin is given more weight comparing to the control effort as long as constraints are satisfied.
-\\
-We use MATLAB and MPT toolbox software (\cite{matlabMPT})  to compute the explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}).
-For the set of $\varepsilon$ and $\delta$ listed in the Table \ref{tab:ipd}, the off-line computed controller consists of $14$ regions with $58$ 2-D hyperplanes in total.
-Similarly, for the aircraft model MATLAB computed a robust EMPC with $27$ regions and $217$ 4-D hyperplanes.
-The only exception is when $\delta=0.30$ and $\varepsilon$=0.001 for which, we got $26$ regions having $208$ hyperplanes.
-In general, we expect that increasing $\delta$ results in shrinking of feasible set size.%}
+Our second benchmark is a well-known 4D example for aircraft
+controller design~\cite{Kapasouris:1998}.
+The control inputs for the aircraft 4-D model are the elevator and flaperon angles,
+and the attack and pitch angles are the output states that need to be regulated.
+The open-loop system is unstable as it has a pole with positive real part. Both
+control inputs are constrained between $\pm25$ degrees. The outputs are
+only constrained during the first prediction horizon. You also specify scale
+factors for outputs. Using the gain $K$, the poles of $\bar A$ are placed at
+$-5$, $-3$, $-1$ and $-2$. The robust MPC problem is solved for $N=2$,
+$R=\mathbf{\it I}$ and $Q=Q_F=5\mathbf{\it I}$. Note that for both of the
+examples, matrices $R$, $Q$ and $Q_F$ are selected such that convergence to the
+origin is given more weight compared to the control effort as long as
+constraints are satisfied.
 
@@
 
-\eva{Explain why we choose 32 bits uniform as baseline}
-\eva{Explain why we don't compare against other tools (resp. the one)}
+We do not compare against the existing technique of~\citet{imperialrmpc} which aims to reduce memory
+usage in explicit MPC control, as it requires the user to provide a (uniform)
+fixed-precision up front. Instead, we let Daisy find the minimum uniform
+precision needed. Additionally, we compare against a uniform 32-bit precision
+baseline, which in the absence of special user insight would be a reasonable safe choice.
+
 \autoref{tab:ipd} shows the total number of bits required to implement each
 controller using different precision options: uniform 32 bit precision
-(`Uni32'), uniform but custom precision (`Uni', chosen precision in parentheses)
+(`Uni32'), minimal uniform precision (`Uni', chosen precision in parentheses)
 and mixed precision (`Mix'). We split the memory requirement into the bits
 required for storing F and G and H and K. We show the results for each benchmark
-for ten different combinations of $\delta$ and $\varepsilon$, varying one while
+for ten different combinations of $\Delta$ and $\varepsilon_Q$, varying one while
 keeping the other fixed.
 For the pendulum, the execution time of the whole analysis is 10 minutes no matter the
-initial values for $\delta$ and $\varepsilon$, while for the aircraft it is 36
-minutes. \rocco{maybe table for execution times}
+initial values for $\Delta$ and $\varepsilon_Q$, while for the aircraft it is 36
+minutes.
 
+%\rocco{maybe table for execution times}
 % In \autoref{tab:ipd} we report the evaluation of our approach on both the
@@
 %\eva{Compute the actual averages for all F, G, H, K and not only approximations}
-For the inverted pendulum, minimal uniform precision saves $57.5\%$ of memory
-compared to a uniform 32 bit baseline (column `\%32vU' in~\autoref{tab:ipd}) on
-average overall (for F, G, H and K together). Mixed-precision further reduces the memory
-requirement by $10.4\%$ on average with respect to the minimal uniform baseline
-(column `\%UvM' in~\autoref{tab:ipd}). 
-\autoref{tab:ipd} shows a more detailed breakdown of the memory requirement
-between F and G and H and K. The memory requirements for the storage of
-hyperplanes H and K depends only on the size of the tubes $\varepsilon$ so that
-memory requirements remain constant for fixed $\varepsilon$.
+For the inverted pendulum, minimal uniform precision saves on average $57.5\%$ of memory
+compared to a uniform 32 bit baseline overall, i.e. for F, G, H and K together. 
+Mixed-precision further reduces the memory
+requirement by $10.4\%$ on average with respect to the minimal uniform baseline. 
+\autoref{tab:ipd} shows a more detailed breakdown of the memory requirements and savings
+between F and G and H and K.
+The memory requirements for the storage of hyperplanes H and K depends only on
+the size of the tubes $\varepsilon_Q$ so that memory requirements remain constant
+for fixed $\varepsilon_Q$.
 
@@
 additional $17.6\%$ w.r.t. minimal uniform precision. We observe higher relative
-memory savings by mixed-precision for storing H and K.
+memory savings by mixed-precision for storing H and K than for the inverted pendulum example.
 
@@
 
+% We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the
+% explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}).
+%We evaluate our algorithm with different choices of $\varepsilon_Q$ and $\Delta$.
+For the inverted pendulum Matlab's MPT toolbox~\cite{matlabMPT} computes a controller
+consisting of $14$ regions with $58$ 2D hyperplanes in total for all choices of $\varepsilon_Q$ and $\Delta$. 
+For the aircraft model, Matlab computes a robust EMPC with
+$27$ regions and $217$ 4D hyperplanes for most values of $\varepsilon_Q$ and $\Delta$. 
+The only exception is when $\Delta=0.30$
+and $\varepsilon_Q=0.001$ for which we get $26$ regions having $208$ hyperplanes.
+In general, we expect that increasing $\Delta$ results in shrinking of feasible
+set size.
+
 %We noticed the following common behavior in the two benchmarks: 
-As expected, when $\delta$ decreases, the activation functions (F, G) need to be
-more precise and require more memory, because the space for approximation error
-is reduced. Similarly, when the value of $\varepsilon$ increases, the memory
+As expected, when $\Delta$ decreases, the control actions (F, G) need to be implemented
+more precisely and require more memory, because the space for approximation error
+is reduced. Similarly, when the value of $\varepsilon_Q$ increases, the memory
 requirements for H, K can be relaxed.
 
-We note two differences among these two benchmarks.
-In the aircraft,
+%We note two differences among these two benchmarks.
+We note that for the aircraft example,
 the precision for F and G is almost double with respect to the pendulum. This is
 because the magnitude of F and G is on the order of $10^{3}$ while for the
-pendulum it is on the order of several units (note that for F and G the memory gain
-from Uni to Mix (\%UvM) is only slightly less than the one for the pendulum).
+pendulum it is on the order of several units. Note, however, that for F and G the memory gain
+from minimal uniform to mixed precision (\%UvM) is only slightly less than the one for the pendulum.
 
-\eva{The below explanation only mentions aircraft. What is the difference to pendulum?}
-The second difference consists in the last two lines in Table\ref{tab:ipd}.
-In the aircraft, when $\varepsilon$=0.0030, the \maxUij exceeds $\delta=0.1$ and we
-need to design again the controller (it corresponds to the else branch in
-Listing\ref{fig:overview}). The loop converges after 5 iterations (\texttt{then}
-branch of the conditional) with $\delta=0.112$. After each iteration, the new value
-for $\delta$ is the last \maxUij\space plus a constant value in the order of
-$10^{-3}$. Thanks to this $\varepsilon_{SAFE}$ we sensibly reduce memory demand
+%The second difference consists in the last two lines in Table\ref{tab:ipd}.
+For the aircraft example, when $\varepsilon_Q=0.0030$, the error due to selecting the wrong region (\maxUij) 
+exceeds the given value of $\Delta=0.1$ and our algorithm
+needs to design a new controller (corresponding to the \texttt{else} branch in~\autoref{fig:overview}). 
+The loop converges after 5 iterations (\texttt{then}
+branch of the conditional) with $\Delta=0.112$. In each iteration, the value
+for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.
+Thus, the algorithm reduces memory demand
 at the expense of slightly more disturbance for the controller. When
-$\varepsilon$=0.0050 the analysis converges after 4 iterations and the same
-discussion holds.
+$\varepsilon_Q=0.0050$ the analysis converges after 4 iterations.
+\eva{Does this mean that for the other settings, the loop in~\autoref{fig:overview}
+is executed only once?}
 
-\eva{It is still not clear to me whether we need this discussion or the columns `max' and `$err(u_i)$'
-in the table. These are internal computations and it seems that they do not really show anything
-surprising/different than the number of bits show?}
-The first halves of both pendulum and aircraft sections in \autoref{tab:ipd}, show how $\delta$ does not affect the maximal error among regions \maxUij.
-We verify that a variation for $\delta$ (typically in the order of $\pm$ 0.1) results in a minimal alteration to the domain of regions X (in the order of $\pm 10^{-10}$), not enough to produce a sensitive variation to \maxUij.
-Then, when \maxUij\space is constant the error bound for computations $err(u_{i})$ decreases together with $\delta$.
-The memory required for the storage of F and G depends on $err(u_{i})$: the smaller the value for $err(u_{i})$, the more precise has to be the arithmetic for activation functions.
+% \eva{It is still not clear to me whether we need this discussion or the columns `max' and `$err(u_i)$'
+% in the table. These are internal computations and it seems that they do not really show anything
+% surprising/different than the number of bits show?}
+% The first halves of both pendulum and aircraft sections in \autoref{tab:ipd},
+% show how $\Delta$ does not affect the maximal error among regions \maxUij. We
+% verify that a variation for $\Delta$ (typically in the order of $\pm$ 0.1)
+% results in a minimal alteration to the domain of regions X (in the order of $\pm
+% 10^{-10}$), not enough to produce a sensitive variation to \maxUij. Then, when
+% \maxUij\space is constant the error bound for computations $err(u_{i})$
+% decreases together with $\Delta$. The memory required for the storage of F and G
+% depends on $err(u_{i})$: the smaller the value for $err(u_{i})$, the more
+% precise has to be the arithmetic for activation functions.
 
-In the second halves in \autoref{tab:ipd}, we fix the value for $\delta$ and we try different $\varepsilon$.
-When we increase the safe space between two regions by $\varepsilon$, the value for \maxUij is computed for new corner points.
-It happens because of the continuity of PWA activation functions: when \statevarmath is on the border between two generic regions $i$, $j$ the value for \maxUij is close to zero.
-The more $\varepsilon$ moves \statevarmath far from the border, the more \maxUij increases.
-When \maxUij is almost equal to $\delta$, the space for $err(u_{i})$ is minimized, and the controller requires high precision for computations (see last lines for pendulum and aircraft in Table\ref{tab:ipd}).
-On the other hand, when $\varepsilon$ increases, the analysis can reduce the memory requirements for the storage of borders (see columns Uni and Mix in the second halves of both benchmarks).
+% In the second halves in \autoref{tab:ipd}, we fix the value for $\Delta$ and we
+% try different $\varepsilon_Q$. When we increase the safe space between two regions
+% by $\varepsilon_Q$, the value for \maxUij is computed for new corner points. It
+% happens because of the continuity of PWA activation functions: when
+% \statevarmath is on the border between two generic regions $i$, $j$ the value
+% for \maxUij is close to zero. The more $\varepsilon_Q$ moves \statevarmath far
+% from the border, the more \maxUij increases. When \maxUij is almost equal to
+% $\Delta$, the space for $err(u_{i})$ is minimized, and the controller requires
+% high precision for computations (see last lines for pendulum and aircraft in
+% Table\ref{tab:ipd}). On the other hand, when $\varepsilon_Q$ increases, the
+% analysis can reduce the memory requirements for the storage of borders (see
+% columns Uni and Mix in the second halves of both benchmarks).
 
@@
 %\Mahmoud{
-The goal of experiments in this section is to show that our algorithm works well even for the case that the controller consists of thousands of PWA functions and regions. 
+The goal of the experiment in this section is to show that our algorithm works
+well even for the case that the controller consists of thousands of regions.
 %Using the algorithm described in Section \ref{???}, the minimum number of bits for storing the controller is computed such that $\delta$ and $\varepsilon$ are respected. 
-This experiment is different from the end-to-end case in the sense that designing robust EMPC for the error bound $\delta$ is replaced with designing EMPC that might not count for $\delta$.
-Given an EMPC, one can perform robustness analysis to come up with an input error bound $\delta$ under which the performance specifications are satisfied.
-From the implementation point of view, this helps us to scale up-to controllers with thousands of regions, skiping the restrictions for designing robust EMPC with longer time horizons.
-At this point, our algorithm takes $\delta$ (along with a properly selected $\varepsilon$) and produces the optimum mixed precision that results in significant memory save.\\
+This experiment is different from the end-to-end case in the sense that
+designing robust EMPC for the error bound $\Delta$ is replaced with designing
+EMPC that might not account for $\Delta$. Given an EMPC, one can perform
+robustness analysis to come up with an input error bound $\Delta$ under which
+the performance specifications are satisfied. From the implementation point of
+view, this helps us to generate controllers with thousands of regions,
+skiping the restrictions for designing robust EMPC with longer time horizons. 
+% At this point, our algorithm takes $\Delta$ (along with a properly selected
+% $\varepsilon_Q$) and produces the optimum mixed precision that results in
+% significant memory save.
+
 The benchmark in this experiment is the double integrator, a canonical example
-of a second order control system. Following gives the state space descreption for the discrete time version of double integrator
+of a second order control system \todo{cite something?}. The state space description
+for the discrete time version of the double integrator is given by:
 \begin{equation}
@@
 	5\\5
-	\end{bmatrix}\\
-	-1\leq& u_k \leq 1
+	\end{bmatrix}, \quad
+	-1\leq u_k \leq 1
 \end{align*}%}
@@
 
-%\Mahmoud{
-For this example, $\delta$ and $\varepsilon$ are fixed into $0.1$ and $0.001$, respectively.
-However, by changing the time horizon $N$ we evaluate scalability of our approach for controllers with very large number of regions.
-Generally, increasing $N$ results in higher number of regions for the output controller.
-To compute the explicit model predictive controllers for different time horizons, we use MATLAB MPC toolbox.%}
+For this example, $\Delta$ and $\varepsilon_Q$ are fixed to $0.1$ and $0.001$,
+respectively. By changing the time horizon $N$, we evaluate the scalability
+of our approach for controllers with very large number of regions, as 
+increasing $N$ generally results in a higher number of regions for the output controller. To
+compute the explicit model predictive controllers for different time horizons,
+we use Matlab's MPC toolbox. \todo{is this the same as before? If so, add a 'again'}
 
@@
 
-The design of the controller in MATLAB takes few minutes, then controllers and
-hyperplanes are encoded in Daisy for memory optimization. On average, the
-analysis of a controller or an hyperplane in Daisy, requires less than two
-minutes and less than 500MB of memory. The cluster used for the evaluation has
-48 cores, and the memory consumption on the cluster is always bounded by
-15GB. Memory optimization is trivially parallelizable, because any controller or
-hyperplane can be analyzed independently.
+The design of the controller in Matlab takes a few minutes, then controllers and
+hyperplanes are encoded in Daisy for finite-precision assignment. On average, the
+analysis of a single controller or hyperplane in Daisy requires less than two
+minutes and less than 500MB of memory. The finite-precision assignment is trivially parallelizable, 
+because any controller or hyperplane can be analyzed independently.
+We thus run this analysis on a cluster with 48 cores, and note that the 
+memory consumption remains below 15GB. 
 %\eva{There should be an explanation why this is not providing end-to-end robustness}
 
-\autoref{tab:di} shows the details of this experiment.
-We observe that our analysis scales up to 1200 controllers and 25000 hyperplanes in few
-hours.  The computed minimal uniform precision saves $49.8\%$ of memory
-compared to a uniform $32$ bit baseline (column `\%32vU' in~\autoref{tab:di}) on
-average overall (for F, G, H and K together). Moreover, mixed-precision reduces the memory
-requirement by $9.6\%$ on average with respect to the minimal uniform baseline
-(column `\%UvM' in~\autoref{tab:di}). 
-%\eva{Compute and say something about the overall savings for F, G, H, K, and proper average (at least for UvM)}
+\autoref{tab:di} shows the results of this experiment.
+We observe that our analysis scales up to 1200 controllers and 25000 hyperplanes \todo{these are not in the table!}
+in a few hours.  The computed minimal uniform precision saves on average $49.8\%$ of memory
+compared to a uniform $32$ bit baseline overall (for F, G, H and K together). 
+Moreover, mixed-precision reduces the memory requirement by an additional
+$9.6\%$ on average with respect to the minimal uniform baseline.
 We further observe that relative savings remain largely constant for different 

### 2019-04-11 emsoft-2019/Motiv.tex
sec. 2 is modified

@@
 %\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
-(ii) to minimize the total number of bits that are required for storing the explicit controller 
-while ensuring the implementation error $e\leq \Delta$ is satisfied by the implementation.
+(ii) to minimize the total number of bits that are required for storing the explicit controller.
 
@@
  \Sadegh{
-For our example, we choose $\Delta_0=0$ and $\mathcal W = \{0\}$. 
+For our example, we choose $\Delta_0=0.01$ and $\mathcal W = \{0\}$. 
 We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$.
-Next, we ask Daisy
+Over the computed controller, we compute the error due to incorrect region selection $e$ and in case that $e<\Delta$, we ask Daisy
 to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
@@
 \Sadegh{
-Unfortunately, $\Delta_0=0$ is not realizable, as the implementation error is always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
+Unfortunately, $\Delta_0=0$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
+%always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
 %\eva{Is this the error due to mixed-precision or due to wrong regions?}
-Therefore, we define $\Delta_1 := \Delta_0 + \delta$ with $\delta$ being a fixed threshold (we chose $\delta = 0.05$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
+Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.
 Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
 shown in Figure~\ref{fig:inverted_pendulum}(b).
-The controller has \RM{XX} regions.
+The controller has $14$ regions.
 \RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps} 
 }
+%\begin{equation}
+%\kappa(x_k)=
+%\begin{cases}
+%.05x_k-9.67 & \text{if $x_k\in \mathcal{R}_1$}\\
+%F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
+%\vdots\\
+%F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
+%\end{cases} 
+%\end{equation}
 
@@
 for the corresponding robust explicit MPC.
-Daisy also computes a static error bound of \RM{what?}
+Daisy also computes a static error bound of $0.03$.
 Since this error bound is less than our robustness margin $\Delta_1 = 0.05$, we terminate the loop
@@
 to the smallest uniform precision implementation that respects $\Delta_1$,
-and about $XXX\%$ \RM{what} less memory than an implementation that uniformly uses
+and about $57\%$ less memory than an implementation that uniformly uses
 32 bits.
@@
 \tikzstyle{block} = [draw, rectangle, 
-	minimum height=3em, minimum width=6em]
+minimum height=4em, minimum width=6em]
+\tikzstyle{block2} = [draw, rectangle, 
+minimum height=1em, minimum width=4em]
 \tikzstyle{sum} = [draw,  circle, node distance=1cm]
@@
 \tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
-	\begin{figure*}[t]
+\begin{figure}[t]
 	\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
 	\centering
-			\node [block,scale=1,,text width=3.5cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
-			node distance=1cm] (RMPC) {Robust explicit MPC design (computed by MATLAB)};
+	\node [block,scale=1,,text width=5cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
+	node distance=1cm] (RMPC) {Robust explicit MPC design};
 	%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
-			\node [block, scale=1,right=2.5cm of RMPC,
-			node distance=5cm,text width=4cm] (mixed) {Finite precision implementation (computed by Daisy)};
+	\node [block, scale=1,below=2.5cm of RMPC,
+	node distance=5cm,text width=5cm] (Uij) {Point location error computation};
 	\node [draw, diamond, 
-			minimum height=3em, minimum width=3em, right =1cm of mixed,
-			node distance=5cm] (decide) {$e\leq \bar \Delta$};
-			\node [block, right of=decide,
-			node distance=3cm] (done) {Done};
-			\node [block, below of= decide,
-			node distance=3cm] (delta) {increase $\Delta$};
-			\node [scale=1] at (3,-.25)  {
-				$u(x)=Kx+v$
-			};
+	minimum height=3em, minimum width=3em, below =1cm of Uij,
+	node distance=5cm] (decide) {$e\leq  \Delta$};
+	\node [block, below=1cm of decide,node distance=3cm] (done) {Mixed-precision implementation};
+	\node [block2, right=2cm of decide,
+	node distance=3cm] (delta) {Increase $\Delta$};
+	\node [block,below of= done] (output) {Low-precision controller};
+	%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
 	\node at (9,-.25) {$e$};
 
-			\draw [draw,->] (RMPC) -- node [pos=-.1] {}(mixed);
-			\draw [->] (mixed) -- node [name=aaa] {}(decide);
-			\draw [->] (decide) -- node [above,pos=.3] {Yes} (done);
+	\draw [draw,->] (RMPC) -- node [left] {high-precision controller}(Uij);
+	\draw [->] (Uij) -- node [left] {$e$}(decide);
+	\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
 	\draw [->] (decide) -- node[pos=0.99] {} 
 	node [] {No} (delta);
-			\draw [->] (delta) -| node [above] {} (RMPC);
+	\draw [->] (delta) |- node [above] {} (RMPC);
+	\draw [->] (done) -- node [above] {} (output);
 
+	\node [block2, scale=1] at (1.885,-.42) {MATLAB} ;
+	\node [block2, scale=1] at (1.97,-4.18) {Daisy} ;
+	\node [block2, scale=1] at (1.58,-8.84) {Daisy} ;
 	\end{tikzpicture}
-	\caption{high-level description of the proposed memory-efficient robust MPC design
-\RM{what is $\bar{\Delta}$}
-\RM{try to draw a better picture spanning only one column. the information in this pic is sparse}
-\RM{why is $u$ a single affine map?}
-\RM{why is Daisy only giving $e$? Shouldn't it also return the best mixed precision impl?}
-}
+	\caption{high-level description of the proposed memory-efficient robust MPC design}
 	\label{fig:overview}
-\end{figure*}
+\end{figure}
+
+%	\tikzstyle{block} = [draw, rectangle, 
+%	minimum height=3em, minimum width=6em]
+%	\tikzstyle{sum} = [draw,  circle, node distance=1cm]
+%	\tikzstyle{input} = [coordinate]
+%	\tikzstyle{output} = [coordinate]
+%	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
+%	\begin{figure*}[t]
+%		\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
+%			\centering
+%			\node [block,scale=1,,text width=3.5cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
+%			node distance=1cm] (RMPC) {Robust explicit MPC design (computed by MATLAB)};
+%			%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
+%			\node [block, scale=1,right=2.5cm of RMPC,
+%			node distance=5cm,text width=4cm] (mixed) {Finite precision implementation (computed by Daisy)};
+%			\node [draw, diamond, 
+%			minimum height=3em, minimum width=3em, right =1cm of mixed,
+%			node distance=5cm] (decide) {$e\leq \bar \Delta$};
+%			\node [block, right of=decide,
+%			node distance=3cm] (done) {Done};
+%			\node [block, below of= decide,
+%			node distance=3cm] (delta) {increase $\Delta$};
+%			\node [scale=1] at (3,-.25)  {
+%				$u(x)=Kx+v$
+%			};
+%		\node at (9,-.25) {$e$};
+%			
+%			
+%			\draw [draw,->] (RMPC) -- node [pos=-.1] {}(mixed);
+%			\draw [->] (mixed) -- node [name=aaa] {}(decide);
+%			\draw [->] (decide) -- node [above,pos=.3] {Yes} (done);
+%			\draw [->] (decide) -- node[pos=0.99] {} 
+%			node [] {No} (delta);
+%			\draw [->] (delta) -| node [above] {} (RMPC);
+%	
+%	\end{tikzpicture}
+%	\caption{high-level description of the proposed memory-efficient robust MPC design
+%\RM{what is $\bar{\Delta}$}
+%\RM{try to draw a better picture spanning only one column. the information in this pic is sparse}
+%\RM{why is $u$ a single affine map?}
+%\RM{why is Daisy only giving $e$? Shouldn't it also return the best mixed precision impl?}
+%}
+%	\label{fig:overview}
+%\end{figure*}

### 2019-04-11 emsoft-2019/Cont_Syn.tex
fixes for algorithm

@@
 \begin{figure}
-\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},basicstyle=\small\ttfamily]
- (*$\delta$*) = input()
- (*$\varepsilon_{Q}$*) = input()
- assert ((*$\delta$*) >= 0 and (*$\varepsilon_{Q}$*) > 0)
- (*$\varepsilon$*) = (*$\varepsilon_{A/D}$*) + (*$\varepsilon_{Q}$*)
+\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily]
+ $\Delta$ = input()
+ $\varepsilon_{Q}$ = input()
+ assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
+ $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$
 
- while True:
-   F,G,H,K = design_robust_MPC((*$\delta$*))
-   errorChoise = incorrect_region_error(F,G,H,K,(*$\varepsilon$*))
-   if (*$\delta$*) > errorChoise:
-     errorAct = (*$\delta$*) - errorChoise
-     precision_tuning(F, G, errorAct)
-     precision_tuning(H, K, (*$\varepsilon$*))
-     break
+ while true:
+   F, G, H, K = design_robust_MPC($\Delta$)
+   errorRegion = incorrect_region_error(F, G, H, K, $\varepsilon$)
+   if $\Delta$ > errorRegion:
+     errorAct = $\Delta$ - errorRegion
+     $\hat{\text{F}}$, $\hat{\text{G}}$ = precision_tuning(F, G, errorAct)
+     $\hat{\text{H}}$, $\hat{\text{K}}$ = precision_tuning(H, K, $\varepsilon$)
+     return $\hat{\text{F}}$, $\hat{\text{G}}$, $\hat{\text{H}}$, $\hat{\text{K}}$
    else:
-     (*$\delta$*)=errorChoise+(*$\varepsilon_{SAFE}$*)
+     $\Delta$ = errorRegion + $\varepsilon_{SAFE}$
 \end{lstlisting}
-\caption{design of robust MPC with precision tuning}
+\caption{Algorithm for designing memory-efficient robust EMPC controller}
 \label{lst:alg}
@@
 In the previous section, we assumed a given precision $p$. In this section we
-present our algorithm for deriving a suitable value of $p$ fully automatically.
+present our algorithm for deriving suitable values of $p$ fully automatically.
+Further, while~\autoref{sec:Error_Analysis} assumed a uniform fixed-point precision,
+our tuning algorithm derives possibly different precisions for different control
+values.
 
@@
 algorithm, not only the equations from the previous section}
-\autoref{lst:alg} reports the optimization algorithm we implemented to build robust MPC controllers with guaranteed error bounds.
+\autoref{lst:alg} shows a high-level view of our optimization algorithm for
+implementing robust MPC controllers with guaranteed error bounds.
 
+\eva{\autoref{lst:alg} needs another input: state-space model which goes into the MPC designer}
+\eva{Add here the explanation why $\varepsilon_Q$ is an input}
 From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$.

### 2019-04-11 emsoft-2019/Cont_Syn.tex
Controller Syn.

--- 2019-04-11 emsoft-2019/Cont_Syn.tex
@@
      precision_tuning(F, G, errorAct)
-     precision_tuning(H, K, (*$\varepsilon$*))
+     precision_tuning(H, K, (*$\varepsilon_{Q}$*))
      break
@@
 From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$.
-$\delta$ is the maximal disturbance coefficient the controller has to be designed for.
+$\delta$ is the disturbance .
 It is a problem dependent parameter, and thus can be any positive number.
@@
 
-Once input parameters are verified, in line 7 we design the controller in MATLAB MPC Toolbox.
+Once input parameters are verified, in line 7 we design the controller in MATLAB multi-parametric toolbox.
 The suite receives in input the coefficient $\delta$, and the state space model for the plant (e.g.
@@
 
-\eva{The precision tuning, which is the main contribution of the paper is not explained.}
+%\eva{The precision tuning, which is the main contribution of the paper is not explained.}
 
@@
 \eva{Some notes about how this is implemented}
+We wrote a script Python to interface the design of the controller in MATLAB Toolbox with the precision tuning phase in Daisy.
+The script divides in two main components: (i) a parser to process the output from MATLAB suite and (ii) a procedure to encode the vectors F,G and H,K in expressions formatted for Daisy.
 

### 2019-04-11 emsoft-2019/RMPC_Daisy.tex
sadegh

@@
 \section{Explicit MPC and Finite Precision}
-In this section, we provide relevant background on robust explicit MPC and
+In this section, we provide relevant background on robust explicit MPC,
 fixed-point arithmetic and error analysis.
@@
 In this paper, we focus on the robust formulation of MPC which at each time step
-minimizes the worst-case value of the objective function\todo{which objective function? first mention here without explanation} with respect to the
-disturbances over the control inputs. We consider the objective function to
-be quadratic with respect to the states and inputs. To reduce the 
-conservativeness of the optimization and enlarge the set of feasible input
-trajectories, we assume the pair $(A,B)$ is stabilizable and
-$u_k=Kx_k+v_k$, where $K$ is selected such that some desired property such as stability is satisfied, and synthesize $v_k$ for the system.
-\eva{I don't understand the above sentence. Maybe split into several sentences? Where does $u_k$ come from (the sentence right now says you assume $u_k$)?}
+minimizes the worst-case value of an objective function with respect to the
+disturbances over the control inputs. We assume the objective function is
+quadratic with respect to the states and inputs.
+We assume a linear translation on the input with the form
+$$u_k=Kx_k+v_k$$
+and synthesize $v_k$ instead of $u_k$. This choice reduces the 
+conservativeness of the optimization and enlarges the set of feasible input
+trajectories. The matrix $K$ is selected such that some desired property is satisfied under suitable assumption on the system, e.g., stability property if the pair $(A,B)$ is stabilizable.
+
+%\eva{I don't understand the above sentence. Maybe split into several sentences? Where does $u_k$ come from (the sentence right now says you assume $u_k$)?}
 %The modifed state evolution of the system will be $x_{k+1}=\bar Ax_k+Bv_k+Ew_k$ with $\bar A := A +BK$.
@@
 \quad &u_i=Kx_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
-&u_i\in\mathcal{U},\quad \forall w_i\in\mathcal{W}, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
-&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
+&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\,\,\forall i\in\{0,1,\cdots,N\},
+%&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
 \end{align}
@@
 %
-where $\mathcal U$ and $\mathcal X$ are polyhedral sets as\todo{of?} feasible
-sets of inputs and states. Matrices $Q\in\reals^{n\times n}$ and
-$Q_F\in\reals^{n\times n}$ are positive definite, $R\in\reals^{m\times m}$ is
-positive semidefinite and $N$ denotes the length of the prediction horizon.
-\eva{What are $Q, Q_F, R$ and where do they come from?}
+where $\mathcal U$ and $\mathcal X$ are polyhedral sets denoting the feasible
+sets of inputs and states. Positive definite matrices $Q\in\reals^{n\times n}$ and
+$Q_F\in\reals^{n\times n}$ indicate weights on the states. $R\in\reals^{m\times m}$ is
+positive semidefinite and indicates a weight on the input in the objective function. $N$ denotes the length of the prediction horizon.
+%\eva{What are $Q, Q_F, R$ and where do they come from?}
 
@@
 \end{equation}
-where $\mathcal{R}_i$ is a ploytope\todo{polytope?} determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
+where $\mathcal{R}_i$ is a ployhedron determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
 \end{theorem}

### 2019-04-11 emsoft-2019/Motiv.tex

@@
 Our overall goal is to 
-(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of \Sadegh{an additional bounded
-disturbance $\Delta$ modeling the implementation error (both errors due to choosing a wrong region and the finite-precision computation of the control action);}
+(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of an additional bounded
+disturbance $\Delta$ modeling the implementation error (both errors due to choosing a wrong region and the finite-precision computation of the control action);
 and at the same time
@@
 Figure \ref{fig:overview} gives a high-level overview of our proposed setup.
-\Sadegh{
 We start by selecting an initial bound $\Delta_0$ on the implementation error and enlarge $\mathcal W$ with $\Delta_0$ as $\mathcal W_{\Delta_0}$, where
@@
 \end{equation}
- }
 
- \Sadegh{
 For our example, we choose $\Delta_0=0.01$ and $\mathcal W = \{0\}$. 
 We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$.
-Over the computed controller, we compute the error due to incorrect region selection $e$ and in case that $e<\Delta$, we ask Daisy
+Over the computed controller, we compute the error due to an incorrect region selection $e$ and in case that $e<\Delta_0$, we ask Daisy
 to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
@@
 and its mixed-precision implementation is at most $\Delta_0$.
-}
 
-\Sadegh{
-Unfortunately, $\Delta_0=0$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
+Unfortunately, $\Delta_0=0.01$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
 %always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
@@
 \RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps}
-}
+
 %\begin{equation}

### 2019-04-11 emsoft-2019/Error_Analysis.tex

@@
 
-We used two software for implementing the analysis: MATLAB MPC Toolbox and Daisy. The two communicate through a Python interface.
+The two main quantities we need to compute are: the incorrect region error and the memory demand, because the values for $\delta$ and $\varepsilon_{Q}$ are given in input to the analysis.
 
-The region selection error is computed in MATLAB.
-Since the function $u_{i}-u_{j}$ is linear, and we defined the tube as a convex region, we need to evaluate the function only at the corner points of the tube, and keep the result with the maximal magnitude.
+\rocco{@Mahmoud below}
+The incorrect region error is computed in MATLAB multi-parametric toolbox.
+Due to the linearity of function $u_{i}-u_{j}$, and because we defined the tube as a convex region, we need to evaluate the function only at the corner points of the tube, and keep the result with the maximal magnitude.
 
-The approximation error, and the precision required for borders are both computed in Daisy. 
-We provide in input to Daisy the expression we want to quantize together with the error bound we can tolerate.
-Daisy checks whether the input expression, quantized in unary uniform precision (1bit), introduces an error bounded by the input error.
-If this is not the case, Daisy increases the precision format by 1 bit and iterates again.
-The procedure terminates when the first valid format is matched.
-This minimal word-length is going to be the baseline for the mixed-precision tuning phase.
-The mixed-precision phase starts from the uniform precision detected in previous step (baseline).
+The approximation error and the precision tuning for both borders and active functions are computed in Daisy.
+$\varepsilon_{Q}$ is given in input to the analysis.
+After we compute the incorrect region in MATLAB we obtain the value for max error $err(u_{i})$ from (8).
+Then we give the errors and the vectors F,G and H,K in input to Daisy.
+We used Daisy as a verification tool: we provide in input the expression we want to quantize (e.g.
+$\mathcal{R}_{i}$) together with the error bound we can tolerate (e.g.
+$\varepsilon_{Q}$), and Daisy returns a precision configuration (uniform or mixed) such that the input error is satisfied.
+The way it finds the right configuration for uniform precision is the following: it starts by checking whether the input expression, quantized in unary uniform precision (1bit), introduces an error bounded by the input error.
+If this is not the case, Daisy increases the precision format by 1 bit and check whether the error now is satisfied.
+This unary increment runs inside a loop that terminates when the first valid format is matched.
+This uniform word-length is going to be the baseline for the mixed-precision tuning phase.
+The mixed-precision algorithm keeps a list of variables to quantize, and collects different candidate configurations that satisfy the input error.
+It returns the best configuration based on the evaluation of a quality function.
 

### 2019-04-11 emsoft-2019/Cont_Syn.tex
section 5

--- 2019-04-11 emsoft-2019/Cont_Syn.tex
@@
 \begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily]
+ model = input() 
  $\Delta$ = input()
@@
  while true:
-   F, G, H, K = design_robust_MPC($\Delta$)
+   F, G, H, K = design_robust_MPC(model, $\Delta$)
    errorRegion = incorrect_region_error(F, G, H, K, $\varepsilon$)
@@
      $\hat{\text{F}}$, $\hat{\text{G}}$ = precision_tuning(F, G, errorAct)
-     $\hat{\text{H}}$, $\hat{\text{K}}$ = precision_tuning(H, K, $\varepsilon$)
+     $\hat{\text{H}}$, $\hat{\text{K}}$ = precision_tuning(H, K, $\varepsilon_Q$)
      return $\hat{\text{F}}$, $\hat{\text{G}}$, $\hat{\text{H}}$, $\hat{\text{K}}$
@@
 present our algorithm for deriving suitable values of $p$ fully automatically.
-Further, while~\autoref{sec:Error_Analysis} assumed a uniform fixed-point precision,
+Further, while~\autoref{sec:Error_Analysis} assumed a uniform finite precision,
 our tuning algorithm derives possibly different precisions for different control
@@
 
-\subsection{Algorithm}
-\eva{This section needs to structure the explanation in the order in which it
-appears in the algorithm (i.e. starting from the input and explaining why for
-instance $\varepsilon_Q$ is an input), and should reference the lines in the
-algorithm, not only the equations from the previous section}
+%\subsection{Algorithm}
 \autoref{lst:alg} shows a high-level view of our optimization algorithm for
@@
 
-\eva{\autoref{lst:alg} needs another input: state-space model which goes into the MPC designer}
-\eva{Add here the explanation why $\varepsilon_Q$ is an input}
-From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$.
-$\delta$ is the maximal disturbance coefficient the controller has to be designed for.
+Given a state-space model of a plant (line 1), our algorithm returns four matrices
+$\hat{\text{F}}$, $\hat{\text{G}}$, $\hat{\text{H}}$, and $\hat{\text{K}}$,
+which soundly implement a robust explicit MPC controller in mixed-precision
+fixed-point arithmetic.
+Our algorithm takes two additional inputs, $\Delta$ and $\varepsilon_Q$ (line 2, 3). 
+The disturbance $\Delta$ provided by the user represents a starting point for 
+the search for a robust controller. In principle, the user can set $\Delta = 0$,
+however note that the finite-precision implementation of the controller will always
+incur at least some small error. In practice we thus start the search with a slightly
+larger value, e.g. $\Delta = 0.1$. Our algorithm will perform a linear search and
+increase $\Delta$ if needed.
+
+The third input parameter is $\varepsilon_Q$. In~\autoref{sec:Error_Analysis} we
+showed that if the user provides a precision $p$, then we can automatically
+compute $\varepsilon_Q$.
+Now, we want to \emph{derive} a suitable precision $p$, however, and face an
+issue. In order to derive $p$ for some expression, Daisy and any other precision
+tuning tool requires an error bound which should be satisfied. I.e. either a
+precision $p$ is given, and we can compute an error bound, or the error bound is
+given and we can derive a precision $p$. We cannot do both at the same time; the
+problem would be underconstrained. We solve this chicken-and-egg issue by
+requiring the user to provide $\varepsilon_Q$ as the input.
+
+We need to distribute the available `disturbance budget' among the two error
+sources: error due to selecting the wrong region, which is given by the
+quantization of $\hat{\text{H}}$ and $\hat{\text{K}}$, and the error due to
+quantization of the control action, given by $\hat{\text{F}}$, $\hat{\text{G}}$.
+The quantization of $\hat{\text{H}}$ and $\hat{\text{K}}$ is determined by
+$\varepsilon_Q$, thus by providing this input value, the user effectively
+chooses how much precision to allow for $\hat{\text{H}}$ and $\hat{\text{K}}$.
+Note that this precision comes at the expense of the precision of
+$\hat{\text{F}}$ and $\hat{\text{G}}$, i.e. the more accurately $\hat{\text{H}}$
+and $\hat{\text{K}}$ are represented, the more approximate $\hat{\text{F}}$ and
+$\hat{\text{G}}$ need to be and vice versa.
+We note that one could straight-forwardly extend our algorithm to include an
+outer loop which would explore different values for $\varepsilon_Q$. For our
+experiments in~\autoref{sec:experiments}, we vary this value manually.
+
+% From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$.
+$\delta$ is the disturbance .
 It is a problem dependent parameter, and thus can be any positive number.
 Typically, it is in the order of 0.1.
-$\varepsilon_{Q}$ is the imprecision error-bound for the quantization of borders. 
-The latter has to be strictly greater than zero, otherwise we could rely on infinite precision for storage of borders. Usually, the value for $\varepsilon_{Q}$ is in the order of 0.001.
+% $\varepsilon_{Q}$ is the imprecision error-bound for the quantization of borders. 
+% The latter has to be strictly greater than zero, otherwise we could rely on infinite precision for storage of borders. Usually, the value for $\varepsilon_{Q}$ is in the order of 0.001.
 
-In line 4, we compute the error $\varepsilon$ as described in (11), where $\varepsilon_{A/D}$ is a constant parameter dependent on the specific of the converter.
+Unlike the initial $\Delta$, $\varepsilon_Q$ needs to be strictly positive (line 4)
+for mixed-precision tuning tools to work correctly.
+Line 5 computes the width of the tubes $\varepsilon$ as shown in~\autoref{eq:epsilontot},
+which will be used to bound the error due to selecting the wrong region
+($\varepsilon_{A/D}$ is a constant parameter dependent on the specifics of the
+converter).
 
-Once input parameters are verified, in line 7 we design the controller in MATLAB MPC Toolbox.
-The suite receives in input the coefficient $\delta$, and the state space model for the plant (e.g.
-inverted pendulum or aircraft) we need to control.
-The suite returns a piecewise affine function (F and G) together with a polytopes region partitioning (H and K).
+The algorithm then calls Matlab's multi-parametric toolbox to design an explicit
+MPC controller for the given state-space model which is robust to the initial
+disturbance $\Delta$ (line 8). The result is a controller represented by four matrices
+\texttt{F, G, H, K} given in high precision.
 
-In line 8, we compute the incorrect region error: we build the tube regions around the borders (\ref{eq:tube})  using $\varepsilon$ and we compute (\ref{eq:maximization}) for the corner points of the tube.
+\emph{Assuming} that we can implement the polytope region partitioning (given by
+matrices \texttt{H, K}) with an implementation error of at most $\varepsilon_Q$,
+our algorithm proceeds to compute the error due to selecting the wrong region (line 9).
+This computation works as explained in~\autoref{sec:Error_Analysis}, \autoref{eq:maximization}.
 
-In the conditional in line 9, we check whether the robustness $\delta$ is greater than the incorrect region error.
+% Once input parameters are verified, in line 7 we design the controller in MATLAB
+% multi-parametric toolbox. The suite receives in input the coefficient $\delta$,
+% and the state space model for the plant (e.g. inverted pendulum or aircraft) we
+% need to control. The suite returns a piecewise affine function (F and G)
+% together with a polytopes region partitioning (H and K).
+
+% In line 8, we compute the incorrect region error: we build the tube regions around the borders (\ref{eq:tube})  using $\varepsilon$ and we compute (\ref{eq:maximization}) for the corner points of the tube.
+
+The algorithm then checks whether the region error remains below the disturbance
+bound used for the synthesis of the controller (line 10). 
+If the error already exceeds $\Delta$, we do not attempt to compute a finite-precision
+assignment, as the controller design is already infeasible.
+In this case, we increase $\Delta$ by a fixed (small) amount $\varepsilon_{SAFE}$ (line 16) and 
+design a new controller.
+
+% In the conditional in line 9, we check whether the robustness $\delta$ is greater than the incorrect region error.
 If this is not the case, the initial value for $\delta$ was not robust to the magnitude of this error, and we need to re-design the controller with a greater $\delta$.
-Indeed in line 15, the value $\delta$ for the next iteration has to be at least the same magnitude of the current errorChoise.
+% Indeed in line 15, the value $\delta$ for the next iteration has to be at least the same magnitude of the current errorChoise.
 Moreover, we increase by a small scalar $\varepsilon_{SAFE}$ (in the order of 0.001) the value for $\delta$ to speed-up the convergence of the analysis.
 
-In case the conditional in line 9 succeeds, the precision tuning phase starts.
+If the region error is smaller than $\Delta$, we still have an error budget \texttt{errorAct} left
+over to implement the control actions in finite precision (line 11).
+For the precision assignment, we first call Daisy with the expressions for the
+control actions given by \texttt{F} and \texttt{G}, and the remaining error
+budget as the error bound (line 12).
+Then we call Daisy with the expressions of the region bounds given by \texttt{H}
+and \texttt{K}, now with the error bound $\varepsilon_Q$ (line 13).
+In both cases, Daisy determines a quantization of the input matrices (Daisy also
+determines the fixed-point formats of the arithmetic operations, which we ignore here).
+Daisy either computes a minimal uniform fixed-point precision (word length),
+i.e. it searches for the smallest uniform precision which still satisfies the
+error bound, or it returns a mixed-precision assignment, where each value and
+intermediate operation can potentially have different word length.
+In our experiments in~\autoref{sec:experiments}, we compare the two modes and show
+that mixed-precision leads to smaller memory footprints.
+
+Note that Daisy always returns a quantization (at least for our linear
+expressions). If the error bound given is very small (but larger than zero),
+Daisy will return a fixed-point precision with a large number bits, but will not
+fail.
+
+% In case the conditional in line 9 succeeds, the precision tuning phase starts.
 The way we do the precision tuning is the following: we provide in input to Daisy a numerical error-bound together with an expression to quantize (e.g.
@@
 
-In line 10 we compute the error bound for approximate control output error.
+% In line 10 we compute the error bound for approximate control output error.
 This is going to be the maximal error we tolerate for activation functions.
@@
 
-\eva{The precision tuning, which is the main contribution of the paper is not explained.}
+%\eva{The precision tuning, which is the main contribution of the paper is not explained.}
 
-\subsection{Implementation}
-\eva{Some notes about how this is implemented}
+\paragraph{Implementation}
 
-\eva{Below is the previous text:}
-%In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.
-We need to solve the two inequalities in (\ref{eq:delta}) (\ref{eq:quantizationlines}) in order to build a controller with guarantees of robustness.
-%The equation for $\varepsilon$ in (\ref{eq:epsilontot}),  contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is the error generated from the quantization of hyperplanes $\mathcal{R}$ in a finite number of bits.
-%This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
-%The rule for $\varepsilon_{Q}$ is the following:
-%\begin{equation}\label{eq:quantizationlines}
-%\varepsilon_{Q} > (H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})
-%\end{equation}
-%This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$.
-We use Daisy to solve inequality (\ref{eq:quantizationlines}) with respect to p: we assign an arbitrary value to $\varepsilon_{Q}$ and find the minimal-precision p such that the inequality holds.
-The main advantage of using this approach (compared to fixing the precision p a priori), is that the value for $\varepsilon_{Q}$ can be regulated based on micro-controller specifications (e.g.
-memory availability).
-%To solve (\ref{eq:quantizationlines}) we used Daisy: a static analyzer for finite precision expressions, ables to provide a sound upper-bound to the maximal approximation error of a formula with respect to its real (infinite precision) counterpart.
-Since the magnitude of the round-off error depends on the range of input variables, any variable encoded in Daisy has to be bounded.
-In a similar way, we solve the inequality in (\ref{eq:delta}) with respect to p:
-\begin{flalign}
-\label{eq:deltaminusmax}
-&delta - \Big(\max_{\forall i,j\;|\;neighbour(i,j)}|u_{i}-u_{j}|\Big)>=\\
-& \max_{\forall\;\regionimath{i}\;in\;\statespace} err(u_{i})_{p}\nonumber
-\end{flalign}
+We implemented our algorithm in a Python script which interfaces between Matlab
+and Daisy and which implements the high-level structure from~\autoref{lst:alg}.
+The interface parses the output from Matlab and encodes the matrices \texttt{F,
+G, H, K} and the error bounds in Daisy's input format.
+\eva{Can we say something about parallelization?}
 
-Be aware that the left side of (\ref{eq:deltaminusmax}) is not parametrized in p (it is a plain number).
-Only the right size of (\ref{eq:deltaminusmax}) actually depends on the precision p.
-We compute the left side of the inequality using large enough precision p (e.g.
-64 bits) such that we can safely ignore the error resulting from the computation.
-Then, we encode (\ref{eq:deltaminusmax}) in Daisy to detect precision p. Note that p used to solve (\ref{eq:quantizationlines}) can be different from $p'$ used to solve (\ref{eq:deltaminusmax}).
-
-In Listing \ref{lst:alg} we describe the procedure used to design a robust MPC controller such that (\ref{eq:deltaminusmax}) is satisfied.
-
-First, the designer of the controller provides the initial values for delta and $\varepsilon_{Q}$.
-Even if it possible to assign value zero to delta~\cite{imperialrmpc}, we do not encourage such initialization value: it is going to fail the analysis (at least) for the first iteration, because the error in (\ref{eq:maxfperror}) is going to be greater than zero.
-A better initialization would be to set delta to an arbitrary small value, slightly greater than zero.
-
-On the other hand, the value for $\varepsilon_{Q}$ has to be strictly greater than zero, otherwise we could rely on infinite precision for p in (\ref{eq:quantizationlines}).
-
-Once input parameters are verified, we design the controller in MATLAB.
-
-We compute (\ref{eq:maximization}) and we compare the result with delta.
-Again, in the conditional inside the loop, delta has to be strictly greater than \maxUij\space otherwise we do not have space for computing the precision for (\ref{eq:deltaminusmax}).
-In case the conditional is true,
-the precision tuning phase starts.
-For the precision tuning of activation functions, we allow an error that is bounded by the left side of inequality (\autoref{eq:deltaminusmax}).
-While for the quantization of hyperplanes the error bound is $\varepsilon_{Q}$.
-
-In case the conditional fails and \maxUij is greater than or equal to delta, the controller needs to be re-designed with a robustness value that is at least equal to the current value of \maxUij.
-The same suggestion for input parameters holds also here: the constant $\varepsilon_{SAFE}$ is used to relax the value for delta, to a value slightly greater than \maxUij.
-In this way, we relax the constraint used in the next iteration of precision tuning.
-Otherwise, in case $\varepsilon_{SAFE}$ is equal to zero, the next iteration of the loop is going to predict unnecessarily wide precision value for p, usually greater than 32 bits.
+% We wrote a script Python to interface the design of the controller in MATLAB Toolbox with the precision tuning phase in Daisy.
+The script divides in two main components: (i) a parser to process the output from MATLAB suite and (ii) a procedure to encode the vectors F,G and H,K in expressions formatted for Daisy.

### 2019-04-11 emsoft-2019/experiments.tex
section 5
fix

@@
 %!TEX root = main.tex
-\section{Experimental Results}
+\section{Experimental Results}\label{sec:experiments}
 \input{table_pendulum_aircraft}
@@
 exceeds the given value of $\Delta=0.1$ and our algorithm
-needs to design a new controller (corresponding to the \texttt{else} branch in~\autoref{fig:overview}). 
-The loop converges after 5 iterations (\texttt{then}
-branch of the conditional) with $\Delta=0.112$. In each iteration, the value
+needs to design a new controller (corresponding to the \texttt{No} branch in~\autoref{fig:overview}). 
+The loop converges after 5 iterations (\texttt{Yes}
+branch of the diagram) with $\Delta=0.112$. In each iteration, the value
 for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.
@@
 \autoref{tab:di} shows the results of this experiment.
-We observe that our analysis scales up to 1200 controllers and 25000 hyperplanes \todo{these are not in the table!}
-in a few hours.  The computed minimal uniform precision saves on average $49.8\%$ of memory
+We observe that our analysis scales up to 1829 controllers and 14632 hyperplanes in a few hours.  The computed minimal uniform precision saves on average $49.8\%$ of memory
 compared to a uniform $32$ bit baseline overall (for F, G, H and K together). 

### 2019-04-12 emsoft-2019/experiments.tex
fix for experiments

@@
 exceeds the given value of $\Delta=0.1$ and our algorithm
-needs to design a new controller (corresponding to the \texttt{No} branch in~\autoref{fig:overview}). 
-The loop converges after 5 iterations (\texttt{Yes}
-branch of the diagram) with $\Delta=0.112$. In each iteration, the value
+needs to design a new controller (corresponding to the \texttt{else} branch in~\autoref{lst:alg}). 
+The loop converges after 5 iterations (\texttt{then}
+branch in our algorithm) with $\Delta=0.112$. In each iteration, the value
 for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.

### 2019-04-12 emsoft-2019/related.tex
Small change to intro (list of contributions) and added a paper in related work

@@
 platforms. Large-size manufacturers use industrial digital computers called
-\emph{programmable logic controller (PLC)} for such implementations. A PLC is
+\emph{programmable logic controllers (PLC)} for such implementations. A PLC is
 able to perform the computations required by a digital controller using
@@
 implementation down.
+We target implementations for low-end microcontrollers.
 
@@
 
+\citet{SahaM12} consider memory optimization for event-driven controllers
+using a scratchpad to selectively load control parameters based on the current state.
+Our work, in contrast, is a static mapping of controller parameters.
+
 %\Sadegh{adding a few references on explicit MPC.}

### 2019-04-12 emsoft-2019/Cont_Syn.tex
section 4

@@
 and \texttt{K}, now with the error bound $\varepsilon_Q$ (line 13).
+
 In both cases, Daisy determines a quantization of the input matrices (Daisy also
 determines the fixed-point formats of the arithmetic operations, which we ignore here).
-Daisy either computes a minimal uniform fixed-point precision (word length),
-i.e. it searches for the smallest uniform precision which still satisfies the
-error bound, or it returns a mixed-precision assignment, where each value and
-intermediate operation can potentially have different word length.
+Daisy either computes a minimal uniform fixed-point precision (i.e. word length),
+or it returns a mixed-precision assignment, where each value and
+intermediate operation can potentially have a different word length.
+To determine the minimal uniform precision, Daisy performs a linear search.
+It starts from the smallest precision (1 bit) and checks whether it satisfies the
+error bound. If not, the precision is increased by 1 bit and the first precision
+that satisfies the error bound is returned.
+Minimal uniform precision is used as a starting point for mixed-precision tuning,
+which attempts to assign a lower precision to some variables. 
 In our experiments in~\autoref{sec:experiments}, we compare the two modes and show
-that mixed-precision leads to smaller memory footprints.
+that mixed precision leads to smaller memory footprints.
 
@@
 
-\paragraph{Implementation}
+\subsection{Implementation}
 

### 2019-04-12 emsoft-2019/Error_Analysis.tex
fix
section 4

--- 2019-04-10 emsoft-2019/Error_Analysis.tex
@@
 lengths fully automatically in~\autoref{sec:Controller_Synthesis}.
-\eva{The `p' below is the fixed/uniform word length? If so, please explain here}
-\eva{Should we mention here the paper which does the LP-based analysis, i.e.
-contrast our approach?}
+While we do not employ the error analysis independently of controller and
+precision synthesis, we note that it is an alternative way of bounding errors to
+existing methods~\cite{imperialrmpc}.
 
-In the same way described in \cite{imperialrmpc}, the output of the controller can be affected by two main sources errors which an error
-analysis has to capture: 
+For simplicity of notation, we assume a uniform word length $p$ in this section,
+though our algorithm (and implementation) support mixed-precision as well.
+
+The output of an explicit MPC controller can be affected by two main sources
+errors, which an error analysis has to capture\cite{imperialrmpc}:
 \begin{itemize}
-  \item[(i)] \emph{incorrect region selection}: an incorrect control action can be chosen
+  \item[(i)] \emph{incorrect region selection}: 
     due to analog-digital conversion and quantization of $H_i$ and $K_i$,
+    the controller can choose an incorrect control action $u_j$ instead of $u_i$
 
@@
 
-We thus have to ensure that these errors remain below the error bound $\delta$
+We have to ensure that these errors remain below the error bound $\Delta$
 used to design the robust MPC controller:
 \begin{align}\label{eq:delta}
-  \max_{\forall i,j. \mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i.\mathcal{R}_{i}\in\mathcal{R}} err(u_{i})_{p} \le \delta
+  \max_{\forall i,j. \mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i.\mathcal{R}_{i}\in\mathcal{R}} err(u_{i})_{p} \le \Delta
 \end{align}
-where $i,j$ are the indexes of two generic regions $\mathcal{R}_{i}$ and
-$\mathcal{R}_{j}$, \\ $\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})$ states that
-two regions share at least a point, $u_{i}$ is the
-control action for controller $i$, and $err(u_{i})_{p}$ is
-the approximation error for computing the activation function $u_{i}$ in fixed precision using p bits format.
-\paragraph{Incorrect Region Selection}
+where $i,j$ are the indexes of two distinct regions $\mathcal{R}_{i}$ and
+$\mathcal{R}_{j}$, \\ $\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})$
+states that two regions share at least a point, $u_{i}$ is the control action
+for controller $i$, and $err(u_{i})_{p}$ captures the approximation error for
+computing the control action $u_{i}$ in fixed precision $p$.
+
+\subsection{Incorrect Region Selection}
 
 The first part of the error in~\autoref{eq:delta} captures the error due to
-selection of the wrong control action, i.e. with infinite-precision arithmetic
+selecting of the wrong control action. That is, with infinite-precision arithmetic
 and in the absence of any uncertainty from hardware measurements we would choose
@@
 \begin{align} \label{eq:maximization}
-  &\max_{\forall i,j.\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|= \\
-  &\max_{\forall i,j.\mathit{neighbour}(\mathcal{R}_{i},\mathcal{R}_{j})}|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
+  \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|&= \\
+  \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
 \end{align}
@@
 This would lead to a gross over-approximation, however, since the controller
-will choose a wrong region only in a relative narrow neighbourhood, or
+will choose a wrong region only in a relative narrow neighborhood, or
 \emph{tube}, around the boundary between two regions $R_i$ and $R_j$.
-In~\autoref{eq:maximization}, we thus constrain $x_k$ to be within an appropriate tube:
+
+The border between two regions $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$ is defined by 
+their corresponding boundaries:
+\begin{equation}
+\mathit{border}_{i,j} :=(H_i \statevar - K_i ) - (H_j \statevar - K_j)
+\end{equation}
+for appropriate matching borders $H_i, K_i$ and $H_j, K_j$.
+
+In~\autoref{eq:maximization}, we thus constrain $\statevar$ to be within an appropriate tube:
 \begin{equation}\label{eq:tube}
-(\mathit{border}_{i,j} \ge -\varepsilon) \land (\mathit{border}_{i,j} \le \varepsilon)
+|\mathit{border}_{i,j}| \le \varepsilon
 \end{equation}
-where $\mathit{border}_{i,j}$ constrains $x_k$ to be on the border between two regions
-$R_i$ and $R_j$ and $\varepsilon$ captures the uncertainty in computing the
-correct region.
-
-\eva{The below, I believe, is somehow defining $border_{i,j}$, but I don't understand
-how. Please explicitly define $border_{i,j}$.}
-In formula $\exists\; m,n \;$such that:
-\begin{equation}
-\mathit{border}_{i,j}=(H_{i}\statevar-K_{j})_{m} = (H_{j}\statevar-K_{j})_{n}
-\end{equation}
-where $m$ and $n$ are the indexes of the matching border respectively in $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$.
-
-The width of the tube $\varepsilon$, i.e. the uncertainty in computing $x_k$ and
-thus the correct region, is due to two sources of errors: analog-to-digital
-conversion $\varepsilon_{A/D}$ and the quantization of region bounds
-$\mathcal{R}$ in memory $\varepsilon_{Q}$:
+where $\varepsilon$ captures the uncertainty in computing the
+correct region and thus the width of the tube.
+%
+The width of the tube $\varepsilon$ is due to two sources of errors:
+analog-to-digital conversion $\varepsilon_{A/D}$ and the quantization of region
+bounds in memory $\varepsilon_{Q}$:
 \begin{equation}\label{eq:epsilontot}
@@
 \end{equation*}
-where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), p is the number of bits available to quantize the analog signal, and $2^{p}$ is the resolution of the converter.
-
-\eva{which bits, who determines these?}
+where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $p$
+is the number of bits available to quantize the analog signal, and $2^{p}$ is
+the resolution of the converter.
 
 While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
-$\varepsilon_{Q}$ depends on the precision used to store the boundaries, and it is user defined at compile time. This
-second error can be tuned based on a trade-off between accuracy of the storage and
-memory storage required~\cite{memoryMPC}.
-%
-$\varepsilon_{Q}$ is given by:
+$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
 \begin{equation}\label{eq:quantizationlines}
-  \varepsilon_{Q} > |(H-\hat{H}_{p})\qstatevar+(K-\hat{K}_{p})|
+  \varepsilon_{Q} = |(H_i - \hat{H}_i) \qstatevar + (K_i - \hat{K}_i)|
 \end{equation}
-\eva{Shouldn't this equation have some absolute values in it?}
-\eva{The equation above does not give any hint for how to compute it.
-I would prefer to add the inequality to \autoref{eq:epsilontot} and give an equality here that explicitly shows how to compute this.
-Then also rephrase the below}
+\eva{For which index is this evaluated, $i$, $j$ or both?}
+That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
+precision (H and K), and its counter-part quantized in $p$ bits precision
+($\hat{H}_{p}$ and $\hat{K}_{p}$).
+This second error can be tuned providing a trade-off between accuracy and
+memory storage required.
 
-The inequality guarantees that the distance between any hyperplane in infinite precision (H and K), and its counter-part quantized in p bits precision ($\hat{H}_{p}$ and $\hat{K}_{p}$) is bounded by $\varepsilon_{Q}$.
+\subsection{Approximate Control Output}
 
-\paragraph{Approximate Control Output}
+Once a control action $u_i$ is chosen, computing $u_{i}$ itself introduces
+imprecision because $u_i$ needs to be evaluated in finite-precision arithmetic:
+\begin{equation}\label{eq:fperror}
+  err(u_{i})_{p} = | (F_i - \hat{F}_{i}) \statevar + ( G_i - \hat{G}_{i} ) |
+\end{equation}
+where $\hat{F}$ and $\hat{G}$ represent the quantized values (in $p$ bits) for
+the infinite precision values $F$ and $G$.
 
-Computing $u_{i}$ itself introduces imprecision because $u_i$ needs to be evaluated 
-in finite precision arithmetic:
-\begin{equation}\label{eq:fperror}
-  err(u_{i})_{p}=|(\hat{F}_{p}-F)\statevar+(\hat{G}_{p}-G)|
-\end{equation}
-where $\hat{F}$ and $\hat{G}$ represent the rounded values (in p bits) for the infinite precision values $F$ and $G$.
+\autoref{eq:fperror} is evaluated for all \statevarmath that are inside the
+region $\mathcal{R}_i$, together with all the values in the tube surrounding
+region $\mathcal{R}_i$.
+In this way we compute the error also for those points that belong to a neighbor
+of $\mathcal{R}_i$, but because of finite-precision errors they are erroneously
+mapped to control action $u_i$.
 
-In (\ref{eq:fperror}) the domain for \statevarmath are all the points in region $i$, together with all the values in the tube surrounding region $i$. 
-In this way we compute the error also for those points, that belong to a neighbor of $i$, but because of $\varepsilon$ they are erroneously located inside region $i$.
+\subsection{Implementation}
 
-\eva{This section so far says nothing about how we actually compute these errors (incl. with which tools). 
-This should come here}
-\paragraph{Implementation}
+The incorrect region error (\autoref{eq:maximization}) is computed using
+Matlab's multi-parametric toolbox. Due to the linearity of function
+$u_{i}-u_{j}$, and because we defined the tube as a convex region, it suffices
+to evaluate the function only at the corner points of the tube, and keep the
+result with the maximal magnitude.
+\eva{This needs more details. Which function(s) and algorithm from Matlab are used?}
+\eva{How do you determine which regions are neighbors? resp. which borders are matching?}
 
-The designer of the controller fixes the value for $epsilon$ at compile time before starting the analysis.
-$\varepsilon_{Q}$ is also a user dependent parameter fixed at compile time.
-The value for $\varepsilon_{Q}$ depends on the total amount of memory we can dedicate to the storage of H and K on the target controller.
+$\varepsilon_Q$ and $err(u_{i})_{p}$ are computed by Daisy. For this we encode
+the expressions in~\autoref{eq:quantizationlines} and \autoref{eq:fperror}
+respectively as straight-line arithmetic expressions and specify the constraints
+on the domain of $\statevar$ in the precondition.
+Daisy performs a dataflow analysis to determine the finite-precision roundoff
+errors. This error computation differs from the one employed by
+\citet{imperialrmpc} which phrases the roundoff error computation as a (relaxed)
+mixed integer programming problem.
 
-The first part of equation (7) is solved in MATLAB.
-Since the function $u_{i}-u_{j}$ is linear, and we define the tube as a convex region, we need to evaluate the function only at the corner points of the tube and keep the value with the maximal magnitude.
+While our actual synthesis algorithm (\autoref{sec:Controller_Synthesis}) does
+not compute the errors $\varepsilon_Q$ and $err(u_{i})_{p}$ explicitly, the
+error verification is used internally by Daisy to determine a suitable precision
+$p$ and can also be called explicitly without the precision optimization.
 
-The second part of equation (7), and the precision required for hyperplanes storage are both computed in Daisy. 
-The way we use the analyzer is the following: we give an error bound in input to Daisy together with the coefficients we want to quantize (H, K or F, G).
-Daisy iteratively tries different uniform precisions for the quantization of the coefficients, and stops when it finds the minimal word-length such that the error in input is satisfied.
-Daisy starts the search from unary word-length (1bit), and increases the precision with a one by one step at each iteration.
-It stops when the current (uniform) configuration introduces an approximation error that is bounded by the input error.
-This minimal word-length is going to be the baseline for the mixed-precision tuning phase.
-
-Our analysis returns the total memory (in bits) required by the configuration detected in Daisy.
-The designer can then tune the epsilon value based on the memory consumption of the current configuration.
+% The approximation error and the precision tuning for both borders and active
+% functions are computed in Daisy. $\varepsilon_{Q}$ is given in input to the
+% analysis. After we compute the incorrect region in MATLAB we obtain the value
+% for max error $err(u_{i})$ from (8). Then we give the errors and the vectors F,G
+% and H,K in input to Daisy. We used Daisy as a verification tool: we provide in
+% input the expression we want to quantize (e.g. $\mathcal{R}_{i}$) together with
+% the error bound we can tolerate (e.g. $\varepsilon_{Q}$), and Daisy returns a
+% precision configuration (uniform or mixed) such that the input error is
+% satisfied. The way it finds the right configuration for uniform precision is the
+% following: it starts by checking whether the input expression, quantized in
+% unary uniform precision (1bit), introduces an error bounded by the input error.
+% If this is not the case, Daisy increases the precision format by 1 bit and check
+% whether the error now is satisfied. This unary increment runs inside a loop that
+% terminates when the first valid format is matched. This uniform word-length is
+% going to be the baseline for the mixed-precision tuning phase. The
+% mixed-precision algorithm keeps a list of variables to quantize, and collects
+% different candidate configurations that satisfy the input error. It returns the
+% best configuration based on the evaluation of a quality function.

### 2019-04-12 emsoft-2019/intro.tex

@@
 We have applied our technique on a number of standard benchmark examples.
-Our implementation finds that our mixed-precision implementation can save up to 20\% memory (on average, XXX\%) in controller
-implementations over a uniform-precision implementation (and a saving of XXX\% over a uniform 32-bit implementation), while
+Our implementation finds that our mixed-precision implementation can save up to 20\% memory (on average, \RM{XXX}\%) in controller
+implementations over a uniform-precision implementation (and a saving of \RM{XXX}\% over a uniform 32-bit implementation), while
 maintaining the correctness of the controller.
-In absolute terms, the saving corresponds to YYY KB over a uniform precision implementation on our largest benchmark.
+In absolute terms, the saving corresponds to \RM{YYY} KB over a uniform precision implementation on our largest benchmark.
 In each case, the analysis takes only a few minutes of computation.
@@
 we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes\todo{Hours?}.
+
+We summarize our contributions.
+\begin{itemize}
+\item We provide an end-to-end tuning algorithm for robust explicit MPC;
+\item We design a static and scalable error analysis algorithm for piecewise affine functions;
+\item Through a set of standard control benchmarks, we demonstrate that our tuning algorithm
+can achieve up to 20\% savings in memory while maintaining robustness.
+\end{itemize}

### 2019-04-12 emsoft-2019/main.tex
main
related
First draft of intro. Please read comments in Sec 1, 2 and fix them
section 5
experimental section, making tables use space properly

@@
 \usepackage{xparse}
-\setlength{\tabcolsep}{0.5em} % for the horizontal padding
-{\renewcommand{\arraystretch}{1.1}% for the vertical padding
-%\usepackage[dvipsnames]{xcolor}
+%\usepackage{showframe}
+
+\renewcommand{\dblfloatpagefraction}{0.5} % allow float page
+\def\sectionautorefname{Section}
+\def\subsectionautorefname{Section}
+
 \usepackage[backgroundcolor=Apricot, textsize=footnotesize]{todonotes}
@@
 \newcommand{\Sadegh}{\textcolor{blue}}
+\newcommand{\Mahmoud}{\textcolor{magenta}}
+\newcommand{\RM}[1]{{\textcolor{red}{$\clubsuit$ #1 $\clubsuit$}}}
 
@@
 %
-% These commands are for a PROCEEDINGS abstract or paper.
-% \copyrightyear{2018}
-% \acmYear{2018}
-% \setcopyright{acmlicensed}
-% \acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-% \acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
-% \acmPrice{15.00}
-% \acmDOI{10.1145/1122445.1122456}
+%These commands are for a PROCEEDINGS abstract or paper.
+%\copyrightyear{2018}
+%\acmYear{2018}
+%\setcopyright{acmlicensed}
+%\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
+%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
+%\acmPrice{15.00}
+%\acmDOI{10.1145/1122445.1122456}
 % \acmISBN{978-1-4503-9999-9/18/06}
@@
 % The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
-\title{Memory-Efficient Mixed-Precision Implementations for\\Robust Explicit MPC}
+\title{Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control}
 

### 2019-04-12 emsoft-2019/experiments.tex
experimental section, making tables use space properly
info about different used toolboxes is added

@@
 %We evaluate our algorithm with different choices of $\varepsilon_Q$ and $\Delta$.
-For the inverted pendulum Matlab's MPT toolbox~\cite{matlabMPT} computes a controller
+We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}).
+For the inverted pendulum MPT toolbox~\cite{matlabMPT} computes a controller
 consisting of $14$ regions with $58$ 2D hyperplanes in total for all choices of $\varepsilon_Q$ and $\Delta$. 
@@
 $\varepsilon_Q=0.0050$ the analysis converges after 4 iterations.
-\eva{Does this mean that for the other settings, the loop in~\autoref{fig:overview}
-is executed only once?}
+For the other values of $\Delta$ and $\varepsilon$ and for the pendulum example,
+the loop in~\autoref{lst:alg} is executed only once.
 
@@
 compute the explicit model predictive controllers for different time horizons,
-we use Matlab's MPC toolbox. \todo{is this the same as before? If so, add a 'again'}
+we use Matlab's MPC toolbox. %\todo{is this the same as before? If so, add a 'again'}
 

### 2019-04-12 emsoft-2019/experiments.tex
adding a comment

@@
 We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}). 
+\eva{What are the 'underlying computations'? Isn't this supposed to go into the
+implementation section of Section 5?}
 For the inverted pendulum MPT toolbox~\cite{matlabMPT} computes a controller

### 2019-04-12 emsoft-2019/Cont_Syn.tex
polytope

@@
 
-\emph{Assuming} that we can implement the polytope region partitioning (given by
+\emph{Assuming} that we can implement the polyhedral region partitioning (given by
 matrices \texttt{H, K}) with an implementation error of at most $\varepsilon_Q$,

### 2019-04-12 emsoft-2019/Motiv.tex
polytope

@@
 and the input torque at time $kT_s$ with $T_s$ being an appropriate sample time.
-The disturbance $w_k\in\mathbb R^2$, \Sadegh{bounded with a polyhedral set $w_k\in \mathcal W$, captures the modeling error due to 
-linearization and discretization}. 
+The disturbance $w_k\in\mathbb R^2$, bounded with a polyhedral set $w_k\in \mathcal W$, captures the modeling error due to 
+linearization and discretization. 
 The parameter $g=9.81 [m/s^2]$ is the gravitational acceleration, $m$ is the ball mass, $b$ is the rotational fraction coefficient, 

### 2019-04-12 emsoft-2019/RMPC_Daisy.tex
polytope

@@
 \end{equation}
-where $\mathcal{R}_i$ is a ployhedron determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
+where $\mathcal{R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
 \end{theorem}
@@
 The actual implementation of the controller requires storing the matrices $F_i,G_i,H_i,K_i$ for all $i\in\{1,2,\ldots,P\}$.
-At each time step $k$, the current state $x_k$ is used to detect the right polytope $i$ such that $H_i x_k\le K_i$.
+At each time step $k$, the current state $x_k$ is used to detect the right polyhedral region $i$ such that $H_i x_k\le K_i$.
 Then the control action $v_k = F_i x_k + G_i$ is computed and applied to the system.
@@
 %Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong.
-Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polytope $i$ to which the state $x_k$ belong.
-The most straightforward technique is a linear search over all polytopes in \statespace\space using a switch/case conditional statement as shown in~\autoref{lst:caseof}.
+Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong.
+The most straightforward technique is a linear search over all polyhedral region in \statespace\space using a switch/case conditional statement as shown in~\autoref{lst:caseof}.
 %\Sadegh{Perhaps we can mention another approach here? add references.}

### 2019-04-12 emsoft-2019/Error_Analysis.tex
updating sec. 4

@@
 \begin{equation*}
-\varepsilon_{A/D}=\frac{V_{cc}}{2^{p}-1}
+\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
 \end{equation*}
-where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $p$
-is the number of bits available to quantize the analog signal, and $2^{p}$ is
+where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
+is the number of bits available to quantize the analog signal, and $2^{r}$ is
 the resolution of the converter.
@@
 Once a control action $u_i$ is chosen, computing $u_{i}$ itself introduces
-imprecision because $u_i$ needs to be evaluated in finite-precision arithmetic:
+imprecision, because, $u_i$ needs to be evaluated in finite-precision arithmetic:
 \begin{equation}\label{eq:fperror}
@@
 
-The incorrect region error (\autoref{eq:maximization}) is computed using
-Matlab's multi-parametric toolbox. Due to the linearity of function
-$u_{i}-u_{j}$, and because we defined the tube as a convex region, it suffices
+%The incorrect region error (\autoref{eq:maximization}) is computed using Matlab's multi-parametric toolbox. 
+Due to the affinity of function
+$u_{i}-u_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
 to evaluate the function only at the corner points of the tube, and keep the
 result with the maximal magnitude.
+To evaluate the point location error across the corner points, we need to first locate the corner points as well as all the regions which share those corner points.
+We start by computing the vertices for each region $R_i$ by converting the convex set of constraint inequalities for that region into the set of vertices at the intersections of those inequalities using existing tools such as $\mathit{lcon2vert}$ written for MATLAB (\cite{????}).
+The computed vertex $v_i$ will be associated with a $n-D$ hypercube with the edge length of $2 \varepsilon$.
+Each of the $2^n$ vertices of this hypercube is counted as a corner point.
+In order to find out which regions have the same vertex $v_i$, one approach is to compute and save the set of vertices for all the regions and then to find out the neighboring regions via exhaustive search with the saved set of vertices.
+Alternatively, for the vertex $v_i$, all the regions $R_j$s having $v_i$ as their vertex can be identified if at least $n$ of their hyperplanes cross $v_i$.
+We used both approaches; however, the later scales up better when we have millions of vertices.
+In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|u_{j1}-u_{j2}|$ is computed; (v) finally, we pick the greatest corner error point.
+
 \eva{This needs more details. Which function(s) and algorithm from Matlab are used?}

### 2019-04-12 emsoft-2019/Error_Analysis.tex
updating sec. 4

@@
 We used both approaches; however, the later scales up better when we have millions of vertices.
-In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|u_{j1}-u_{j2}|$ is computed; (v) finally, we pick the greatest corner error point.
+In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|u_{j1}-u_{j2}|$ is computed; (v) finally, we pick the greatest corner error.
 

### 2019-04-12 emsoft-2019/Motiv.tex

@@
 
-\tikzstyle{block} = [draw, rectangle, 
-minimum height=4em, minimum width=6em]
-\tikzstyle{block2} = [draw, rectangle, 
-minimum height=1em, minimum width=4em]
+\begin{figure}
+\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
+\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
+\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
+\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
 \tikzstyle{sum} = [draw,  circle, node distance=1cm]
@@
 \tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
-\begin{figure}[t]
-	\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
+
 \centering
-	\node [block,scale=1,,text width=5cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
-	node distance=1cm] (RMPC) {Robust explicit MPC design};
+	\begin{tikzpicture}[auto,node distance=2cm,>=latex',scale=1]
+	\node [block,scale=1,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
+	node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
 	%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
-	\node [block, scale=1,below=2.5cm of RMPC,
-	node distance=5cm,text width=5cm] (Uij) {Point location error computation};
-	\node [draw, diamond, 
-	minimum height=3em, minimum width=3em, below =1cm of Uij,
-	node distance=5cm] (decide) {$e\leq  \Delta$};
-	\node [block, below=1cm of decide,node distance=3cm] (done) {Mixed-precision implementation};
-	\node [block2, right=2cm of decide,
+	\node [block3, scale=1,below=1.3cm of RMPC,
+	node distance=3.8cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (Uij) {Point location error computation};
+	\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=5cm] (decide) {$e\leq  \Delta$};
+	\node [block3, below=0.8cm of decide,node distance=3cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
+	\node [block2, right=1.3cm of decide,
 	node distance=3cm] (delta) {Increase $\Delta$};
-	\node [block,below of= done] (output) {Low-precision controller};
+	\node [block1,below = 0.8cm of done] (output) {Low-precision controller};
 	%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
@@
 
-	\draw [draw,->] (RMPC) -- node [left] {high-precision controller}(Uij);
+	\draw [draw,->, align=center] (RMPC) -- node [left] {high-precision\\ controller}(Uij);
 	\draw [->] (Uij) -- node [left] {$e$}(decide);
@@
 
-	\node [block2, scale=1] at (1.885,-.42) {MATLAB} ;
-	\node [block2, scale=1] at (1.97,-4.18) {Daisy} ;
-	\node [block2, scale=1] at (1.58,-8.84) {Daisy} ;
+	%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
+	%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
+	%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
 	\end{tikzpicture}
-	\caption{high-level description of the proposed memory-efficient robust MPC design}
+	%\end{adjustbox}
+	\caption{High-level description of the proposed memory-efficient robust MPC design.}
 	\label{fig:overview}

### 2019-04-12 emsoft-2019/abstract.tex
adding missing numbers to introduction

@@
 a robust controller and a low-bitwidth approximation 
-that is statically guaranteed to always be within the robustness margin to the original controller.
-We have implemented our algorithm and show, on a set of benchmarks, that our optimization
-can reduce space requirements by up to 20\% (and about 10\% on average), compared to a uniform precision
-implementation of the original controller.
+that is statically guaranteed to always be within the robustness margin of the original controller.
+We have implemented our algorithm and show on a set of benchmarks that our optimization
+can reduce space requirements by up to 20.9\% and on average by 12.6\% 
+compared to a minimal uniform precision implementation of the original controller.

### 2019-04-12 emsoft-2019/intro.tex
adding missing numbers to introduction

@@
 \section{Introduction}
-\eva{General comment: it feels a bit long until the intro discusses the actual problem,
-but it reads nicely and motivates the problem well, so it's probably fine}
 \eva{General comment: should we add some more references to related work (and not only to MPC)?}
@@
 ability to systematically handle processes with many state and input variables as well as constraints on them. 
+\todo{any citations?}
 
@@
 First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
-problem can involve many (often hundreds) of regions.
+problem can involve many (often hundreds) of regions. \todo{citation for such example, e.g. the double integrator}
 Since the memory consumption grows linearly with the number of regions, 
-this can be a limited factor in using explicit MPC on resource-constrained micro-controllers.
+this can be a limiting factor in using explicit MPC on resource-constrained micro-controllers.
 Second, many low-end micro-controllers only support fixed-point arithmetic.
-Errors in the controller implementation are inversely proportional to the number of bits used for representing each variable. 
+Errors in the controller implementation are inversely proportional to the number of bits used for representing each variable~\cite{Anta10}. 
 An implementation of explicit MPC has to be \emph{robust} to 
-implementation errors to be able to enforce hard constraints on the states at run time.
+implementation errors to be able to enforce hard constraints on the states at run time~\cite{imperialrmpc}.
 
@@
 in a \emph{memory-efficient} and \emph{robust} way.
-We propose an automatic controller and mixed-precision implementation co-design technique that computes a minimal set \todo{What is meant by minimal?} of mixed
-precision assignments for all variables while ensuring the resulting implementation error remains within the robustness margin.
+We propose an automatic controller and mixed-precision implementation co-design
+technique that computes mixed-precision assignments which minimize bitwidths for all
+variables while ensuring the resulting implementation error remains within the
+robustness margin.
 
-Our proposed method iteratively solves a robust version of the MPC which explicitly considers fixed-point implementation errors
+Our proposed method iteratively solves a robust version of MPC which explicitly considers finite-precision implementation errors
 in the model; see~\autoref{fig:overview}.
@@
 
+To the best of our knowledge, our algorithm is the first to automatically and soundly
+synthesize a suitable fixed-point precision for explicit robust MPC controllers,
+and the first to consider mixed-precision in this context.
+
 We have implemented our algorithm on top of Matlab's multi-parametric toolbox 
 for robust explicit MPC~\cite{matlabMPT}
-and the Daisy tool for multi-precision tuning and fixed-point error analysis \cite{Daisy}.
+and the Daisy tool for multi-precision tuning and fixed-point error analysis~\cite{Daisy}.
 We have applied our technique on a number of standard benchmark examples.
-Our implementation finds that our mixed-precision implementation can save up to 20\% memory (on average, \RM{XXX}\%) in controller
-implementations over a uniform-precision implementation (and a saving of \RM{XXX}\% over a uniform 32-bit implementation), while
-maintaining the correctness of the controller.
-In absolute terms, the saving corresponds to \RM{YYY} KB over a uniform precision implementation on our largest benchmark.
-In each case, the analysis takes only a few minutes of computation.
+
+Our algorithm finds mixed-precision implementations which save up to 20.9\%
+memory (on average, 12.6\%) in controller implementations over a minimal
+uniform-precision implementation (and an average saving of 46.8\% over a uniform
+32-bit implementation), while maintaining the correctness of the controller.
+
+For smaller examples, the analysis takes only a few minutes of computation.
 We also demonstrate the scalability of our mixed-precision tuning and error bounds analysis:
-we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes\todo{Hours?}.
+we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few hours.
+In absolute terms, the memory saving corresponds to 21KB over a uniform
+precision implementation on our largest benchmark.
 
-We summarize our contributions.
+In summary, our contributions are:
 \begin{itemize}
+\item We design a static and scalable error analysis algorithm for piecewise affine functions;
 \item We provide an end-to-end tuning algorithm for robust explicit MPC;
-\item We design a static and scalable error analysis algorithm for piecewise affine functions;
 \item Through a set of standard control benchmarks, we demonstrate that our tuning algorithm

### 2019-04-12 emsoft-2019/intro.tex
small fix for intro

@@
 \section{Introduction}
-\eva{General comment: should we add some more references to related work (and not only to MPC)?}
+%\eva{General comment: should we add some more references to related work (and not only to MPC)?}
 Model predictive control (MPC) is a technique to design control actions by solving finite-horizon open-loop
@@
 and the Daisy tool for multi-precision tuning and fixed-point error analysis~\cite{Daisy}.
+
 We have applied our technique on a number of standard benchmark examples.
-
 Our algorithm finds mixed-precision implementations which save up to 20.9\%

### 2019-04-12 emsoft-2019/experiments.tex
fixing improvement values in experimental section text

@@
 %\eva{Compute the actual averages for all F, G, H, K and not only approximations}
-For the inverted pendulum, minimal uniform precision saves on average $57.5\%$ of memory
+For the inverted pendulum, minimal uniform precision saves on average $52.6\%$ of memory
 compared to a uniform 32 bit baseline overall, i.e. for F, G, H and K together. 
 Mixed-precision further reduces the memory
-requirement by $10.4\%$ on average with respect to the minimal uniform baseline. 
+requirement by $10.5\%$ on average with respect to the minimal uniform baseline (and 57.5\% w.r.t to 
+uniform 32 bit baseline). 
 \autoref{tab:ipd} shows a more detailed breakdown of the memory requirements and savings
@@
 %\eva{Compute actual and overall averages here too}
-For the aircraft example, minimal uniform precision saves on average $33.5\%$
+For the aircraft example, minimal uniform precision saves on average $19.3\%$
 overall w.r.t. a uniform 32 bit baseline, and mixed-precision saves an
-additional $17.6\%$ w.r.t. minimal uniform precision. We observe higher relative
+additional $17.7\%$ w.r.t. minimal uniform precision (33.6\% w.r.t to uniform 32 bit). We observe higher relative
 memory savings by mixed-precision for storing H and K than for the inverted pendulum example.
@@
 \autoref{tab:di} shows the results of this experiment.
-We observe that our analysis scales up to 1829 controllers and 14632 hyperplanes in a few hours.  The computed minimal uniform precision saves on average $49.8\%$ of memory
+We observe that our analysis scales up to 1829 controllers and 14632 hyperplanes in a few hours.  The computed minimal uniform precision saves on average $44.5\%$ of memory
 compared to a uniform $32$ bit baseline overall (for F, G, H and K together). 
 Moreover, mixed-precision reduces the memory requirement by an additional
-$9.6\%$ on average with respect to the minimal uniform baseline.
+$9.3\%$ on average with respect to the minimal uniform baseline (49.6\% w.r.t. uniform 32 bit).
 We further observe that relative savings remain largely constant for different 

### 2019-04-12 emsoft-2019/Cont_Syn.tex
fix

@@
 G, H, K} and the error bounds in Daisy's input format.
-\eva{Can we say something about parallelization?}
+The precision tuning for activation functions (line 12) and hyperplanes (line 13) can be efficiently done in parallel, because the analysis of a single region is completely independent from the others.
+Same holds for hyperplanes.
+A relatively simple improvement to the current parallelization could be to run precision tuning for hyperplanes and active functions together, without waiting for the latter to terminate.
+Nevertheless, we suspect a minimal impact on performance, because usually the number of hyperplanes is an order of magnitude greater than regions.
+Thus, this is the main bottleneck of the algorithm.
+%\eva{Can we say something about parallelization?}
 

### 2019-04-12 emsoft-2019/Motiv.tex
updating sec. 2

@@
 \label{sec:example}
+\begin{figure}
+	\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
+	\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
+	\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
+	\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
+	\tikzstyle{input} = [coordinate]
+	\tikzstyle{output} = [coordinate]
+	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
+	{\centering
+
+		%\begin{center}
+		%\hspace*{\fill} 
+		\begin{tikzpicture}[auto,node distance=1cm,>=latex']
+		\node [block,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
+		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
+		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
+		\node [block3,below=1.3cm of RMPC,
+		node distance=1cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (Uij) {Incorrect region selection error};
+		\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=1cm] (decide) {$e\leq  \Delta$};
+		\node [block3, below=0.8cm of decide,node distance=1cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
+		\node [block2, right=1.3cm of decide,
+		node distance=1cm] (delta) {Increase $\Delta$};
+		\node [block1,below = 0.8cm of done] (output) {Low-precision controller};
+		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
+		\node at (9,-.25) {$e$};
+
+		\draw [draw,->, align=center] (RMPC) -- node [left] {high-precision\\ controller}(Uij);
+		\draw [->] (Uij) -- node [left] {$e$}(decide);
+		\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
+		\draw [->] (decide) -- node[pos=0.99] {} 
+		node [] {No} (delta);
+		\draw [->] (delta) |- node [above] {} (RMPC);
+		\draw [->] (done) -- node [above] {} (output);
+		%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
+		%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
+		%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
+		\end{tikzpicture}\par}
+	%	\hspace{\fill} 
+	%\end{center}
+	%\end{adjustbox}
+	\caption{High-level description of the proposed memory-efficient robust MPC design.}
+	\label{fig:overview}
+\end{figure}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
 	\begin{tabular}{cc}
@@
 shown in Figure~\ref{fig:inverted_pendulum}(b).
-The controller has $14$ regions.
-\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps}
+The controller has $14$ regions. Following demostrates one sample mapping, including the activation condition and its corresponding affine function
+\begin{equation*}
+\resizebox{.9\hsize}{!}{$
+\begin{bmatrix}
+-0.005  &0.999\\
+-0.998  &-0.049\\
+0.005  &-0.999\\
+0.998   &0.049
+\end{bmatrix}x_k\leq 
+\begin{bmatrix}
+0.416\\
+3.157\\
+0.617\\
+-0.0124
+\end{bmatrix}
+\Rightarrow
+u(x_k)=\begin{bmatrix}
+0.05&-9.67
+\end{bmatrix}x_k+4.02$}
+\end{equation*}
+where, output of robust EMPC at state $x_k$ is denoted by $u(x_k)$. Notice that all the rest of mappings have similar format.
+%\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps}
 
@@
 32 bits.
-
-\begin{figure}
-\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
-\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
-\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
-\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
-\tikzstyle{sum} = [draw,  circle, node distance=1cm]
-\tikzstyle{input} = [coordinate]
-\tikzstyle{output} = [coordinate]
-\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
-
-\centering
-	\begin{tikzpicture}[auto,node distance=2cm,>=latex',scale=1]
-	\node [block,scale=1,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
-	node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
-	%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
-	\node [block3, scale=1,below=1.3cm of RMPC,
-	node distance=3.8cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (Uij) {Point location error computation};
-	\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=5cm] (decide) {$e\leq  \Delta$};
-	\node [block3, below=0.8cm of decide,node distance=3cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
-	\node [block2, right=1.3cm of decide,
-	node distance=3cm] (delta) {Increase $\Delta$};
-	\node [block1,below = 0.8cm of done] (output) {Low-precision controller};
-	%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
-	\node at (9,-.25) {$e$};
-
-	\draw [draw,->, align=center] (RMPC) -- node [left] {high-precision\\ controller}(Uij);
-	\draw [->] (Uij) -- node [left] {$e$}(decide);
-	\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
-	\draw [->] (decide) -- node[pos=0.99] {} 
-	node [] {No} (delta);
-	\draw [->] (delta) |- node [above] {} (RMPC);
-	\draw [->] (done) -- node [above] {} (output);
-
-	%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
-	%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
-	%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
-	\end{tikzpicture}
-	%\end{adjustbox}
-	\caption{High-level description of the proposed memory-efficient robust MPC design.}
-	\label{fig:overview}
-\end{figure}
 

### 2019-04-12 emsoft-2019/Cont_Syn.tex
new inverted pendulum

--- 2019-04-12 emsoft-2019/Cont_Syn.tex
@@
 G, H, K} and the error bounds in Daisy's input format.
-\eva{Can we say something about parallelization?}
+
+We run the precision tuning for control actions (line 12) and hyperplanes (line 13) in
+parallel, because the analysis of a single region or hyperplane is completely independent from
+the others. 
+We currently first perform precision tuning for control actions and then for
+hyperplanes. These two steps could be run concurrently as well, though the
+impact is likely going to be minimal because the number of hyperplanes is
+usually an order of magnitude greater than the number of regions.
+
+% A relatively simple improvement to the current parallelization could be to run precision tuning for hyperplanes and active functions together, without waiting for the latter to terminate.
+Nevertheless, we suspect a minimal impact on performance, because usually the number of hyperplanes is an order of magnitude greater than regions.
+Thus, this is the main bottleneck of the algorithm.
+%\eva{Can we say something about parallelization?}
 

### 2019-04-12 emsoft-2019/experiments.tex
small fixes

@@
 %We evaluate our algorithm with different choices of $\varepsilon_Q$ and $\Delta$.
-We use Matlab's MPT toolbox~\cite{matlabMPT} to compute the explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}). 
-\eva{What are the 'underlying computations'? Isn't this supposed to go into the
-implementation section of Section 5?}
+
 For the inverted pendulum MPT toolbox~\cite{matlabMPT} computes a controller
@@
 The benchmark in this experiment is the double integrator, a canonical example
-of a second order control system \todo{cite something?}. The state space description
+of a second order control system. The state space description
 for the discrete time version of the double integrator is given by:

### 2019-04-12 emsoft-2019/intro.tex
small fixes

@@
 First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
-problem can involve many (often hundreds) of regions. \todo{citation for such example, e.g. the double integrator}
+problem can involve many (often hundreds) of regions~\cite{memoryMPC}.
 Since the memory consumption grows linearly with the number of regions, 

### 2019-04-12 emsoft-2019/Motiv.tex
new inverted pendulum
Comments in Motiv

@@
 	\begin{tabular}{cc}
-	\includegraphics[width=2cm,height=3cm]{Figs/inv_pend.png}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
+	\includegraphics[width=2cm,height=3cm]{Figs/inverted_pendulum.pdf}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
 	(a)&(b)
@@
 %\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
-(ii) to minimize the total number of bits that are required for storing the explicit controller.
+(ii) to minimize the total number of bits that are required to represent an explicit controller.
 
@@
 We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. 
+\RM{the following setence is not understandable. This is the first time we introduce incorrect region selection.
+Who is Daisy?}
+\RM{A better version is to informally define incorrect region selection. Say that we run an algorithm for incorrect region
+selection to bound the possible error. 
+Break the sentence into two. Introduce Daisy as a mixed-precision tuning tool.}
 Over the computed controller, we compute the error due to an incorrect region selection $e$ and in case that $e<\Delta_0$, we ask Daisy
@@
 
-Unfortunately, $\Delta_0=0.01$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
+Unfortunately, $\Delta_0=0.01$ is not realizable, as the region selection error is $0.019$ and hence $e>\Delta_0$. 
 %always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.

### 2019-04-12 emsoft-2019/intro.tex
Comments in Motiv

@@
 %\eva{General comment: should we add some more references to related work (and not only to MPC)?}
+
 Model predictive control (MPC) is a technique to design control actions by solving finite-horizon open-loop
-optimal control problems at each sampling instant.
+optimal control problems at each sampling instant \cite{RMD17}.
 The result of each optimization gives a sequence of optimal control actions, only the first of which is applied
@@
 optimizes a performance index. 
-MPC has shown to be successful in a wide variety of industrial applications, due to its 
+MPC has shown to be successful in a wide variety of industrial applications \cite{QinBadgwell03}, due to its 
 ability to systematically handle processes with many state and input variables as well as constraints on them.
-\todo{any citations?}
 
@@
 First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
-problem can involve many (often hundreds) of regions~\cite{memoryMPC}.
+problem can involve many (often hundreds) of regions.
 Since the memory consumption grows linearly with the number of regions, 
@@
 
-Our proposed method iteratively solves a robust version of MPC which explicitly considers finite-precision implementation errors
-in the model; see~\autoref{fig:overview}.
+Our proposed method iteratively solves a robust version of MPC 
+which explicitly considers finite-precision implementation errors as disturbances
+in the dynamics \cite{RamirezC06}; see~\autoref{fig:overview}.
 Initially, we estimate a bound $\Delta = \Delta_0$ on the implementation error and solve a
-min-max quadratic program for explicit robust MPC \cite{delaPea:2005}, where the system
+min-max quadratic program for explicit robust MPC \cite{delaPea:2005,RamirezC06}, where the system
 model has an explicit disturbance bounded by $\Delta$.
 The solution is represented as a piecewise affine map.
+\RM{need to add the step on incorrect region selection.}
 We use an automated mixed-precision tuning tool to find an approximate implementation of the piecewise affine

### 2019-04-12 emsoft-2019/intro.tex

@@
 First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
-problem can involve many (often hundreds) of regions.
+problem can involve many (often hundreds) of regions~\cite{memoryMPC}.
 Since the memory consumption grows linearly with the number of regions, 

### 2019-04-12 emsoft-2019/Motiv.tex
centering figure 1

@@
 \begin{figure}
+\centering
 	\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
@@
 	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
-	{\centering
+	{
 
@@
 
-		\draw [draw,->, align=center] (RMPC) -- node [left] {high-precision\\ controller}(Uij);
+		\draw [draw,->, align=center] (RMPC) -- node [left] {High-precision controller}(Uij);
 		\draw [->] (Uij) -- node [left] {$e$}(decide);
@@
 	%\end{adjustbox}
-	\caption{High-level description of the proposed memory-efficient robust MPC design.}
+	\caption{Overview of the proposed memory-efficient robust MPC control design.}
 	\label{fig:overview}

### 2019-04-12 emsoft-2019/RMPC_Daisy.tex
renaming section to background
Added conclusion. Fixed Fig 3.

@@
 % !TEX root = main.tex
-\section{Explicit MPC and Finite Precision}
+\section{Background}
 In this section, we provide relevant background on robust explicit MPC,
@@
 \end{align}
-where, $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables and $Y$, $H$, $G_m$, $G_c$,$S_m$, $S_c$, $W_m$, $W_c$, $g_m$ are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).
+where $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables, and $Y$, $H$, $G_m$, $G_c$, $S_m$, $S_c$, $W_m$, $W_c$, and $g_m$ 
+are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).
 
@@
 Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong. 
-The most straightforward technique is a linear search over all polyhedral region in \statespace\space using a switch/case conditional statement as shown in~\autoref{lst:caseof}.
-%\Sadegh{Perhaps we can mention another approach here? add references.}
+The most straightforward technique is a linear search over all polyhedral regions (Fig.~\ref{lst:caseof}).
 
 \begin{figure}[t]
-\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={switch, case, then}]
-switch($\statevar$):
-  case ($H_{1}\statevar<=K_{1}$) then ($v_{k}=F_1x_k+G_1$)
-  case ($H_{2}\statevar<=K_{2}$) then ($v_{k}=F_2x_k+G_2$)
-  case ($H_{3}\statevar<=K_{3}$) then ($v_{k}=F_3x_k+G_3$)
+\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
+if ($H_{1}\statevar \leq K_{1}$) then $v_{k}=F_1x_k+G_1$
+elseif ($H_{2}\statevar \leq K_{2}$) then $v_{k}=F_2x_k+G_2$
+elseif ($H_{3}\statevar \leq K_{3}$) then $v_{k}=F_3x_k+G_3$
 ...
-  case ($ H_{P}\statevar<=K_{P}$) then ($v_{k}=F_Px_k+G_P$)
+elseif ($ H_{P}\statevar\leq K_{P}$) then $v_{k}=F_Px_k+G_P$
+return $v_k$
 \end{lstlisting}

### 2019-04-12 emsoft-2019/conclusion.tex
Added conclusion. Fixed Fig 3.

\section{Conclusion}

We have described an automatic technique to tune an explicit MPC
controller that implements the controller in mixed-precision fixed-point arithmetic
while ensuring that the resulting loss of precision does not invalidate the
constraints of the original control problem.
Our technique models potential fixed-point imprecision explicitly as a disturbance
term, and uses robust explicit MPC to design a controller.
A static error analysis and a mixed-precision tuning tool is then 
used to find an efficient implementation of the controller function.
The implementation maintains the numerical error to within
the disturbance bounds used by the robust controller.
In experiments, we show that our technique can yield significant savings in memory,
ranging up to 20\%. 
In addition, the static analysis scales to controllers with hundreds of regions.

### 2019-04-12 emsoft-2019/RMPC_Daisy.tex
Typo fixes.

@@
 \begin{equation}
-\mathcal X_s = \bigcup_{i}(H_{i}\statevar<=K_{i}).
+\mathcal X_s = \bigcup_{i}(H_{i}\statevar\leq K_{i}).
 \end{equation}
 
-The actual implementation of the controller requires storing the matrices $F_i,G_i,H_i,K_i$ for all $i\in\{1,2,\ldots,P\}$.
-At each time step $k$, the current state $x_k$ is used to detect the right polyhedral region $i$ such that $H_i x_k\le K_i$.
-Then the control action $v_k = F_i x_k + G_i$ is computed and applied to the system.
-
-%Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong.
+The implementation of the controller stores the matrices $F_i,G_i,H_i,K_i$ for all $i\in\{1,2,\ldots,P\}$. 
+At each time step $k$, the current state $x_k$ is used to detect the polyhedral region 
+such that $H_i x_k\le K_i$. Then the control action $u_k = F_i x_k + G_i$ is computed and applied to the system.
 Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong. 
@@
 \begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
-if ($H_{1}\statevar \leq K_{1}$) then $v_{k}=F_1x_k+G_1$
-elseif ($H_{2}\statevar \leq K_{2}$) then $v_{k}=F_2x_k+G_2$
-elseif ($H_{3}\statevar \leq K_{3}$) then $v_{k}=F_3x_k+G_3$
+if ($H_{1}\statevar \leq K_{1}$) then $u_{k}=F_1x_k+G_1$
+elseif ($H_{2}\statevar \leq K_{2}$) then $u_{k}=F_2x_k+G_2$
+elseif ($H_{3}\statevar \leq K_{3}$) then $u_{k}=F_3x_k+G_3$
 ...
-elseif ($ H_{P}\statevar\leq K_{P}$) then $v_{k}=F_Px_k+G_P$
-return $v_k$
+elseif ($ H_{P}\statevar\leq K_{P}$) then $u_{k}=F_Px_k+G_P$
+return $u_k$
 \end{lstlisting}

### 2019-04-12 emsoft-2019/RMPC_Daisy.tex
typo fixes

@@
 where $x\in \reals^{n\times 1}$ is the state, $u\in \reals^{m\times 1}$ is the control input and $w\in \reals^{d\times 1}$ is the disturbance.
-Matrices $A\in \reals^{n\times n}$, $B\in \reals^{n\times m}$ and $E\in \reals^{n\times d}$ are capturing respectively the effects of current state, input and disturbance on the next state.
+Matrices $A\in \reals^{n\times n}$, $B\in \reals^{n\times m}$ and $E\in \reals^{n\times d}$  capture respectively the effects of current state, input and disturbance on the next state.
 We assume the disturbance $w$ belongs to a set $\mathcal{W}$ where $\mathcal{W}$ is a polyhedral set.
@@
 conservativeness of the optimization and enlarges the set of feasible input
-trajectories. The matrix $K$ is selected such that some desired property is satisfied under suitable assumption on the system, e.g., stability property if the pair $(A,B)$ is stabilizable.
+trajectories. The matrix $K$ is selected such that some desired property is satisfied under suitable assumptions on the system, e.g., stability if the pair $(A,B)$ is stabilizable.
 
@@
 The optimization \eqref{eq:multi_param_prog} can be solved using multi-parametric techniques to compute the explicit form of $\kappa(\cdot)$.
-An efficient implementation of such computations is available in the multi-parametric toolbox of MATLAB~\cite{matlabMPT, matlabYALMIP}.
+An efficient implementation of such computations is available in the multi-parametric toolbox of Matlab~\cite{matlabMPT, matlabYALMIP}.
 Let us denote the set of states $x_0$ for which the optimization  \eqref{eq:multi_param_prog} is feasible by $\mathcal X_s$.
@@
 
-To keep the cost of implementation down, low-end microcontrollers usually have
-limited memory and computational power. Therefore, implementation of the above
+To keep the implementation cost down, low-end microcontrollers usually have
+limited memory and computational power. Therefore, the implementation of the above
 explicit MPC on microcontrollers will bring some issues since all regions'

### 2019-04-12 emsoft-2019/Motiv.tex
updating sec 2

@@
 Break the sentence into two. Introduce Daisy as a mixed-precision tuning tool.}
-Over the computed controller, we compute the error due to an incorrect region selection $e$ and in case that $e<\Delta_0$, we ask Daisy
-to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
+
+The output of robust  EMPC given by Matlab decomposes the control domain into a finite number of polyhedra together with an affine map for each domain.
+At each time step, the state vector $x_k$ is read (or estimated) and based on the domain that it belongs to, the output of controller is determined.
+However, due to error by fixed-point implementation, it is possible that the domain is selected incorrectly.
+This causes an error term which we refer to it as incorrect region selection error.
+Over the high-precision controller, we compute the error due to an incorrect region selection $e$.
+In case that $e<\Delta_0$, we would like to find the smallest number of bits required for implementing the controller such that we are still within the safe bound $\Delta_0$.
+To do so, we ask Daisy, which is a mixed-precision tuning tool, to provide us with a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
 at all points in the control domain, the difference between the infinite-precision controller function

### 2019-04-12 emsoft-2019/RMPC_Daisy.tex
section 4

--- 2019-04-12 emsoft-2019/RMPC_Daisy.tex
@@
 % !TEX root = main.tex
-\section{Background}
+\section{Explicit MPC and Finite Precision}
 In this section, we provide relevant background on robust explicit MPC,
@@
 \begin{theorem}[\cite{delaPea:2005}]
+\label{thm:EMPC}
 The optimization \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution.
@@
 \end{align}
-where $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables, and $Y$, $H$, $G_m$, $G_c$, $S_m$, $S_c$, $W_m$, $W_c$, and $g_m$ 
-are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).
+where, $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables and $Y$, $H$, $G_m$, $G_c$,$S_m$, $S_c$, $W_m$, $W_c$, $g_m$ are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).
 
@@
 Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong.
-The most straightforward technique is a linear search over all polyhedral regions (Fig.~\ref{lst:caseof}).
+The most straightforward technique is a linear search over all polyhedral region in \statespace\space using a switch/case conditional statement as shown in~\autoref{lst:caseof}.
+%\Sadegh{Perhaps we can mention another approach here? add references.}
 
 \begin{figure}[t]
-\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
-if ($H_{1}\statevar \leq K_{1}$) then $v_{k}=F_1x_k+G_1$
-elseif ($H_{2}\statevar \leq K_{2}$) then $v_{k}=F_2x_k+G_2$
-elseif ($H_{3}\statevar \leq K_{3}$) then $v_{k}=F_3x_k+G_3$
+\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={switch, case, then}]
+switch($\statevar$):
+  case ($H_{1}\statevar<=K_{1}$) then ($v_{k}=F_1x_k+G_1$)
+  case ($H_{2}\statevar<=K_{2}$) then ($v_{k}=F_2x_k+G_2$)
+  case ($H_{3}\statevar<=K_{3}$) then ($v_{k}=F_3x_k+G_3$)
     ...
-elseif ($ H_{P}\statevar\leq K_{P}$) then $v_{k}=F_Px_k+G_P$
-return $v_k$
+  case ($ H_{P}\statevar<=K_{P}$) then ($v_{k}=F_Px_k+G_P$)
 \end{lstlisting}

### 2019-04-12 emsoft-2019/Error_Analysis.tex

@@
 
-We first present our error analysis assuming given fixed-point word lengths,
-before explaining our optimization algorithm which determines suitable word
-lengths fully automatically in~\autoref{sec:Controller_Synthesis}.
-While we do not employ the error analysis independently of controller and
+In this section, we present our error analysis assuming that a fixed-point word lengths is given.
+Then in the next section, we explain our optimization algorithm which determines suitable word
+lengths fully automatically.% in~\autoref{sec:Controller_Synthesis}.
+While we do not employ the error analysis independently of the controller and
 precision synthesis, we note that it is an alternative way of bounding errors to
 existing methods~\cite{imperialrmpc}.
+\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}
 
-For simplicity of notation, we assume a uniform word length $p$ in this section,
-though our algorithm (and implementation) support mixed-precision as well.
+For simplicity of notation, we assume in this section a uniform word length $p$,
+but our algorithm (and implementation) is applied to mixed-precision to reduce the memory usage.
 
-The output of an explicit MPC controller can be affected by two main sources
-errors, which an error analysis has to capture\cite{imperialrmpc}:
+Consider the controller obtained from explicit MPC according to Theorem~\ref{thm:EMPC}.
+Define the affine control functions associated with each polyhedral region $\mathcal R_i$, $i\in\{1,2,\ldots, P\}$, as
+$$\inputm{i}:\mathcal R_i\rightarrow \mathcal U \quad \text{ with } \quad \inputm{i}(x) := Kx + F_i x + G_i.$$
+Implementation of the controller can be affected by two main sources of
+error:
+%which an error analysis has to capture \cite{imperialrmpc}:
 \begin{itemize}
   \item[(i)] \emph{incorrect region selection}:
-    due to analog-digital conversion and quantization of $H_i$ and $K_i$,
-    the controller can choose an incorrect control action $u_j$ instead of $u_i$
+   instead of a correct affine function $\inputm{i}$, the implementation may choose an incorrect affine function $\inputm{j}$. This can happen either
+    due to an analog-to-digital conversion in the measured states or due to the quantization in matrices $H_i$ and $K_i$ of the region $\mathcal R_i$; and
 
-  \item[(ii)] \emph{approximate control output}: the control output is computed
-    using quantized $F_i$ and $G_i$, accumulating errors.
+  \item[(ii)] \emph{approximation in the computation of the affine function}: for any selected region $\mathcal R_i$, the affine function $\inputm{i}$ is evaluated using the quantized versions of $K$, $F_i$ and $G_i$.
 \end{itemize}
 
-We have to ensure that these errors remain below the error bound $\Delta$
-used to design the robust MPC controller:
-\begin{align}\label{eq:delta}
-  \max_{\forall i,j. \mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}| + \max_{\forall i.\mathcal{R}_{i}\in\mathcal{R}} err(u_{i})_{p} \le \Delta
+We have to ensure that the sum of these two errors remain below the bound $\Delta$
+used in the design of the robust explicit MPC:
+\begin{align}
+  \max\{\|\inputm{i}-\inputm{j}\|,\,&\forall i,j,\,\, i\neq j, \mathcal{R}_{i}\cap\mathcal{R}_{j}\neq\emptyset\} \nonumber\\
+  &+  \max\{err(\inputm{i})_{p},\, i=1,2,\ldots,P\} \le \Delta.
+  \label{eq:delta}
 \end{align}
-where $i,j$ are the indexes of two distinct regions $\mathcal{R}_{i}$ and
-$\mathcal{R}_{j}$, \\ $\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})$
-states that two regions share at least a point, $u_{i}$ is the control action
-for controller $i$, and $err(u_{i})_{p}$ captures the approximation error for
-computing the control action $u_{i}$ in fixed precision $p$.
+%where $i,j$ are the indexes of two distinct regions $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$, 
+The first term is the error of incorrect region selection.
+The maximum is taken over all neighboring regions $\mathcal R_i,\mathcal R_j$ recognisable by having non-empty intersection.
+The function norm $\|\inputm{i}-\inputm{j}\|$ is taken by maximizing over all possible values of the state $x_k$.
+$err(\inputm{i})_{p}$ in
+the second term captures the approximation error in the computation of the affine function $\inputm{i}$ when a fixed precision $p$ is used.
+%$\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})$
+%states that two regions share at least a point, $\inputm{i}$ is the control action
+%for controller $i$, and $err(\inputm{i})_{p}$ captures the approximation error for
+%computing the control action $\inputm{i}$ in fixed precision $p$.
 
@@
 The first part of the error in~\autoref{eq:delta} captures the error due to
-selecting of the wrong control action. That is, with infinite-precision arithmetic
-and in the absence of any uncertainty from hardware measurements we would choose
-control action $u_i$, but due to uncertainties we actually choose control action $u_j$:
-\begin{align} \label{eq:maximization}
-  \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}|u_{i}-u_{j}|&= \\
-  \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
-\end{align}
+selecting of the incorrect region.
+This would happen since the matrices $H_i,K_i$ are stored in the hardware with fixed-point formats. In order to quantify the error, we define the expanded regions
+\begin{equation*}
+\bar{\mathcal R}_i := \bigcup_{\hat H_i,\hat K_i} \left\{x\in\mathbb R^n\,|\,\hat H_i x\le \hat K_i, \|H_i-\hat H_i\|\le \epsilon_f,\|K_i-\hat K_i\|\le \epsilon_f\right\}
+\end{equation*}
+for $i\in\{1,2,\ldots, P\}$, where $\epsilon_f$ is the maximum error of using fixed-point format instead of the precise values.
+The norm is also applied element-wise to the entries of the matrices.
+Note that $\mathcal R_i\subset \bar{\mathcal R}_i$.
+In other words, $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$.
+Note that $\bar{\mathcal R}_i\cap \bar{\mathcal R}_j$ gives us the states where one of the two regions $\mathcal R_i, \mathcal R_i$ might be selected instead of the other one because of the fixed-precision implementation of the regions.
+% $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$ that include all states in $\mathcal R_i$this definition expands the regions $\mathcal $
+ %That is, with infinite-precision arithmetic
+ Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over this intersection:
+ \begin{equation}
+ \label{eq:maximization}
+ \max\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal R}_{i}\cap\bar{\mathcal R}_{j},\,\, i\neq j\}
+% \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
+ \end{equation}
 
-%Because of the linearity of the function $u_{i}-u_{j}$, and because of the
+%and in the absence of any uncertainty from hardware measurements we would choose
+%control action $\inputm{i}$, but due to uncertainties we actually choose control action $\inputm{j}$:
+%\begin{align} \label{eq:maximization}
+ % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}|\inputm{i}-\inputm{j}|&= \\
+ % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
+%\end{align}
+
+%Because of the linearity of the function $\inputm{i}-\inputm{j}$, and because of the
 %convexity of the regions $i$ and $j$, it is enough to evaluate function
@@
 
-A naive computation of this error would consider all possible values of $x_k$.
-This would lead to a gross over-approximation, however, since the controller
-will choose a wrong region only in a relative narrow neighborhood, or
-\emph{tube}, around the boundary between two regions $R_i$ and $R_j$.
+%A naive computation of this error would consider all possible values of $x_k$.
+%This would lead to a gross over-approximation, however, since the controller
+%will choose a wrong region only in a relative narrow neighborhood, or
+%\emph{tube}, around the boundary between two regions $R_i$ and $R_j$.
 
-The border between two regions $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$ is defined by 
-their corresponding boundaries:
-\begin{equation}
-\mathit{border}_{i,j} :=(H_i \statevar - K_i ) - (H_j \statevar - K_j)
-\end{equation}
-for appropriate matching borders $H_i, K_i$ and $H_j, K_j$.
+%The border between two regions $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$ is defined by 
+%their corresponding boundaries:
+%\begin{equation}
+%\mathit{border}_{i,j} :=(H_i \statevar - K_i ) - (H_j \statevar - K_j)
+%\end{equation}
+%for appropriate matching borders $H_i, K_i$ and $H_j, K_j$.
 
-In~\autoref{eq:maximization}, we thus constrain $\statevar$ to be within an appropriate tube:
-\begin{equation}\label{eq:tube}
-|\mathit{border}_{i,j}| \le \varepsilon
-\end{equation}
-where $\varepsilon$ captures the uncertainty in computing the
-correct region and thus the width of the tube.
+%In~\autoref{eq:maximization}, we thus constrain $\statevar$ to be within an appropriate tube:
+%\begin{equation}\label{eq:tube}
+%|\mathit{border}_{i,j}| \le \varepsilon
+%\end{equation}
+%where $\varepsilon$ captures the uncertainty in computing the
+%correct region and thus the width of the tube.
 %
+
+\begin{comment}
+We should also include the error in 
 The width of the tube $\varepsilon$ is due to two sources of errors:
@@
 memory storage required.
+\end{comment}
 
@@
 
-Once a control action $u_i$ is chosen, computing $u_{i}$ itself introduces
-imprecision, because, $u_i$ needs to be evaluated in finite-precision arithmetic:
+We should also include the error due to
+analog-to-digital conversion $\varepsilon_{A/D}$.
+Analog to digital conversion happens just before the controller receives the measured state from sensor
+and is given by:
+\begin{equation*}
+\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
+\end{equation*}
+where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
+is the number of bits available to quantize the analog signal, and $2^{r}$ is
+the resolution of the converter. The associated error in the output of the controller is $\varepsilon_{A/D}\max_i\{\|K+F_i\|\}$.
+
+Once a quantized state $\hat x$ is given and a region $\mathcal R_i$ is chosen, computing $\inputm{i}$ itself introduces
+imprecision, because, $\inputm{i}$ needs to be evaluated in finite-precision arithmetic:
 \begin{equation}\label{eq:fperror}
-  err(u_{i})_{p} = | (F_i - \hat{F}_{i}) \statevar + ( G_i - \hat{G}_{i} ) |
+  err(\inputm{i})_{p} = | (F_i - \hat{F}_{i}) \statevar + ( G_i - \hat{G}_{i} ) |
 \end{equation}
@@
 of $\mathcal{R}_i$, but because of finite-precision errors they are erroneously
-mapped to control action $u_i$.
+mapped to control action $\inputm{i}$.
 
@@
 Due to the affinity of function
-$u_{i}-u_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
+$\inputm{i}-\inputm{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
 to evaluate the function only at the corner points of the tube, and keep the
@@
 We used both approaches; however, the later scales up better when we have millions of vertices.
-In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|u_{j1}-u_{j2}|$ is computed; (v) finally, we pick the greatest corner error.
+In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|\inputm{j1}-\inputm{j2}|$ is computed; (v) finally, we pick the greatest corner error.
 
@@
 
-$\varepsilon_Q$ and $err(u_{i})_{p}$ are computed by Daisy. For this we encode
+$\varepsilon_Q$ and $err(\inputm{i})_{p}$ are computed by Daisy. For this we encode
 the expressions in~\autoref{eq:quantizationlines} and \autoref{eq:fperror}
@@
 While our actual synthesis algorithm (\autoref{sec:Controller_Synthesis}) does
-not compute the errors $\varepsilon_Q$ and $err(u_{i})_{p}$ explicitly, the
+not compute the errors $\varepsilon_Q$ and $err(\inputm{i})_{p}$ explicitly, the
 error verification is used internally by Daisy to determine a suitable precision
@@
 % analysis. After we compute the incorrect region in MATLAB we obtain the value
-% for max error $err(u_{i})$ from (8). Then we give the errors and the vectors F,G
+% for max error $err(\inputm{i})$ from (8). Then we give the errors and the vectors F,G
 % and H,K in input to Daisy. We used Daisy as a verification tool: we provide in

### 2019-04-12 emsoft-2019/Motiv.tex
fixed example description

--- 2019-04-12 emsoft-2019/Motiv.tex
@@
 where $\theta_k$, $\omega_k$, and $u_k$ denote respectively the angular position, angular speed, 
-and the input torque at time $kT_s$ with $T_s$ being an appropriate sample time.
+and the input torque at time $kT_s$ with $T_s$ being an appropriate sampling time.
 The disturbance $w_k\in\mathbb R^2$, bounded with a polyhedral set $w_k\in \mathcal W$, captures the modeling error due to 
@@
 For our example, we choose $\Delta_0=0.01$ and $\mathcal W = \{0\}$. 
-We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. 
-\RM{the following setence is not understandable. This is the first time we introduce incorrect region selection.
-Who is Daisy?}
-\RM{A better version is to informally define incorrect region selection. Say that we run an algorithm for incorrect region
-selection to bound the possible error. 
-Break the sentence into two. Introduce Daisy as a mixed-precision tuning tool.}
-Over the computed controller, we compute the error due to an incorrect region selection $e$ and in case that $e<\Delta_0$, we ask Daisy
-to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
-at all points in the control domain, the difference between the infinite-precision controller function
-and its mixed-precision implementation is at most $\Delta_0$.
+We use Matlab to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. 
+% \RM{the following setence is not understandable. This is the first time we introduce incorrect region selection.
+% Who is Daisy?}
+% \RM{A better version is to informally define incorrect region selection. Say that we run an algorithm for incorrect region
+% selection to bound the possible error. 
+% Break the sentence into two. Introduce Daisy as a mixed-precision tuning tool.}
 
-Unfortunately, $\Delta_0=0.01$ is not realizable, as the region selection error is $0.019$ and hence $e>\Delta_0$. 
+The output of robust EMPC given by Matlab decomposes the control domain into a
+finite number of polyhedral domains together with an affine map for each domain. At each
+time step, the state vector $x_k$ is read (or estimated) and based on the domain
+that it belongs to, the corresponding control output is computed. 
+However, the polyhedral regions are implemented in finite precision so that
+it is possible that due to quantization errors the domain is selected incorrectly.
+We refer to the resulting error as incorrect region selection error.
+% However, due to error by fixed-point implementation, it is possible that the domain is selected
+% incorrectly. This causes an error term which we refer to it as incorrect region
+% selection error.
+
+In our example, we compute an incorrect region selection error $e = 0.019$, which is larger
+than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount to
+$\Delta_1 = 0.05$ and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
+%
+% Over the high-precision controller, we compute the error due to an incorrect region selection $e$.
+In case that $e<\Delta_0$, we would like to find the smallest number of bits required for implementing the controller such that we are still within the safe bound $\Delta_0$.
+To do so, we ask Daisy, which is a mixed-precision tuning tool, to provide us with a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
+% at all points in the control domain, the difference between the infinite-precision controller function
+% and its mixed-precision implementation is at most $\Delta_0$.
+%
+%Unfortunately, $\Delta_0=0.01$ is not realizable, as the region selection error is $0.019$ and hence $e>\Delta_0$. 
 %always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
 %\eva{Is this the error due to mixed-precision or due to wrong regions?}
-Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.
-Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
-shown in Figure~\ref{fig:inverted_pendulum}(b).
-The controller has $14$ regions. Following demostrates one sample mapping, including the activation condition and its corresponding affine function
+% Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.
+Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller
+with 14 regions, shown in~\autoref{fig:inverted_pendulum}(b).
+A sample region with the corresponding affine map is shown below:
+%Following demostrates one sample mapping, including the activation condition and its corresponding affine function
 \begin{equation*}
@@
 \end{equation*}
-where, output of robust EMPC at state $x_k$ is denoted by $u(x_k)$. Notice that all the rest of mappings have similar format.
-%\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps}
+where the output of robust EMPC at state $x_k$ is denoted by $u(x_k)$. 
+The remaining mappings have a similar structure.
+For this new controller, the incorrect region selection error is still
+approximately $e = 0.019$, which is now below the disturbance bound $\Delta_1$,
+so that we can continue with the precision assignment.
 
@@
 
-Next, we ask Daisy to provide us with mixed-precision implementation for all the parameters and to compute a static bound on the
-implementation error. 
-The mixed-precision scheme given by Daisy results in an implementation with $6084$ bits in total 
+Next, we use the precision tuning tool Daisy to provide us with a mixed-precision 
+implementation for all the parameters which satisfies the error bound $0.031$,
+which is given by the remaining error budget $\Delta_1 - e = 0.05 - 0.019$.  
+The mixed-precision implementation returned by Daisy requires $6084$ bits in total 
 for the corresponding robust explicit MPC.
-Daisy also computes a static error bound of $0.03$.
-Since this error bound is less than our robustness margin $\Delta_1 = 0.05$, we terminate the loop
-and return this implementation.
+% Since this error bound is less than our robustness margin $\Delta_1 = 0.05$, we terminate the loop
+% and return this implementation.
 The mixed-precision implementation takes about $10\%$ less memory compared 

### 2019-04-12 emsoft-2019/Error_Analysis.tex
fixing section 4

@@
 Define the affine control functions associated with each polyhedral region $\mathcal R_i$, $i\in\{1,2,\ldots, P\}$, as
-$$\inputm{i}:\mathcal R_i\rightarrow \mathcal U \quad \text{ with } \quad \inputm{i}(x) := Kx + F_i x + G_i.$$
+$$v_{i}:\mathcal R_i\rightarrow \mathcal U \quad \text{ with } \quad v_{i}(x) := F_i x + G_i.$$
 Implementation of the controller can be affected by two main sources of
@@
   \item[(i)] \emph{incorrect region selection}:
-   instead of a correct affine function $\inputm{i}$, the implementation may choose an incorrect affine function $\inputm{j}$. This can happen either
+   instead of a correct affine function $v_{i}$, the implementation may choose an incorrect affine function $v_{j}$. This can happen either
     due to an analog-to-digital conversion in the measured states or due to the quantization in matrices $H_i$ and $K_i$ of the region $\mathcal R_i$; and
 
-  \item[(ii)] \emph{approximation in the computation of the affine function}: for any selected region $\mathcal R_i$, the affine function $\inputm{i}$ is evaluated using the quantized versions of $K$, $F_i$ and $G_i$.
+  \item[(ii)] \emph{approximation in the computation of the affine function}: for any selected region $\mathcal R_i$, the affine function $v_{i}$ is evaluated using the quantized versions of $F_i$ and $G_i$.
 \end{itemize}
@@
 \begin{align}
-  \max\{\|\inputm{i}-\inputm{j}\|,\,&\forall i,j,\,\, i\neq j, \mathcal{R}_{i}\cap\mathcal{R}_{j}\neq\emptyset\} \nonumber\\
-  &+  \max\{err(\inputm{i})_{p},\, i=1,2,\ldots,P\} \le \Delta.
+  \max\{\|v_{i}-v_{j}\|,\,&\forall i,j,\,\, i\neq j, \mathcal{R}_{i}\cap\mathcal{R}_{j}\neq\emptyset\} \nonumber\\
+  &+  \max\{err(v_{i})_{p},\, i=1,2,\ldots,P\} \le \Delta.
   \label{eq:delta}
@@
 The maximum is taken over all neighboring regions $\mathcal R_i,\mathcal R_j$ recognisable by having non-empty intersection.
-The function norm $\|\inputm{i}-\inputm{j}\|$ is taken by maximizing over all possible values of the state $x_k$.
-$err(\inputm{i})_{p}$ in
-the second term captures the approximation error in the computation of the affine function $\inputm{i}$ when a fixed precision $p$ is used.
+The function norm $\|v_{i}-v_{j}\|$ is taken by maximizing over all possible values of the state $x_k$.
+$err(v_{i})_{p}$ in
+the second term captures the approximation error in the computation of the affine function $v_{i}$ when a fixed precision $p$ is used.
 %$\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})$
-%states that two regions share at least a point, $\inputm{i}$ is the control action
-%for controller $i$, and $err(\inputm{i})_{p}$ captures the approximation error for
-%computing the control action $\inputm{i}$ in fixed precision $p$.
+%states that two regions share at least a point, $v_{i}$ is the control action
+%for controller $i$, and $err(v_{i})_{p}$ captures the approximation error for
+%computing the control action $v_{i}$ in fixed precision $p$.
 
@@
 selecting of the incorrect region.
-This would happen since the matrices $H_i,K_i$ are stored in the hardware with fixed-point formats. In order to quantify the error, we define the expanded regions
+This would happen since the matrices $H_i,K_i$ are stored in the hardware with fixed-point formats.
+In order to quantify the error, we define the expanded border $\bar{\mathcal B}_{ij}$ as the tube around the border between the regions $\mathcal{R}_i$ and $\mathcal{R}_j$:
+% \begin{equation*}
+% \bar{\mathcal R}_i := \bigcup_{\hat H_i,\hat K_i} \left\{x\in\mathbb R^n\,|\,\hat H_i x\le \hat K_i, \|H_i-\hat H_i\|\le \epsilon_f,\|K_i-\hat K_i\|\le \epsilon_f\right\}
+% \end{equation*}
+% for $i\in\{1,2,\ldots, P\}$, where $\epsilon_f$ is the maximum error of using fixed-point format instead of the precise values. The norm is also applied element-wise to the entries of the matrices.
+
 \begin{equation*}
-\bar{\mathcal R}_i := \bigcup_{\hat H_i,\hat K_i} \left\{x\in\mathbb R^n\,|\,\hat H_i x\le \hat K_i, \|H_i-\hat H_i\|\le \epsilon_f,\|K_i-\hat K_i\|\le \epsilon_f\right\}
+\hat{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon \right\}
 \end{equation*}
-for $i\in\{1,2,\ldots, P\}$, where $\epsilon_f$ is the maximum error of using fixed-point format instead of the precise values.
-The norm is also applied element-wise to the entries of the matrices.
-Note that $\mathcal R_i\subset \bar{\mathcal R}_i$.
-In other words, $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$.
-Note that $\bar{\mathcal R}_i\cap \bar{\mathcal R}_j$ gives us the states where one of the two regions $\mathcal R_i, \mathcal R_i$ might be selected instead of the other one because of the fixed-precision implementation of the regions.
+where $\varepsilon$ captures the uncertainty in computing the correct region.
+%
+The width of the tube $\varepsilon$ is due to two sources of errors:
+analog-to-digital conversion $\varepsilon_{A/D}$ and the quantization of region
+bounds in memory $\varepsilon_{Q}$:
+\begin{equation}\label{eq:epsilontot}
+  \varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
+\end{equation}
+
+Analog conversion happens just before the controller receives the sensor input from the plant
+and is given by:
+\begin{equation*}
+\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
+\end{equation*}
+where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
+is the number of bits available to quantize the analog signal, and $2^{r}$ is
+the resolution of the converter.
+
+While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
+$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
+\begin{equation}\label{eq:quantizationlines}
+  \varepsilon_{Q} = \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|
+\end{equation}
+where $\hat{x}$ is the finite-precision value of $x$.
+%\eva{For which index is this evaluated, $i$, $j$ or both?}
+That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
+precision (H and K), and its counter-part quantized in $p$ bits precision
+($\hat{H}_{p}$ and $\hat{K}_{p}$).
+This second error can be tuned providing a trade-off between accuracy and
+memory storage required.
+
+% Note that $\mathcal R_i\subset \bar{\mathcal R}_i$. In other words, $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$.
+% Note that $\bar{\mathcal R}_i\cap \bar{\mathcal R}_j$ gives us the states where one of the two regions $\mathcal R_i, \mathcal R_i$ might be selected instead of the other one because of the fixed-precision implementation of the regions.
 % $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$ that include all states in $\mathcal R_i$this definition expands the regions $\mathcal $
  %That is, with infinite-precision arithmetic
- Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over this intersection:
+ Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
+ the expanded borders:
  \begin{equation}
  \label{eq:maximization}
- \max\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal R}_{i}\cap\bar{\mathcal R}_{j},\,\, i\neq j\}
+ \max\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}
 % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
@@
 %and in the absence of any uncertainty from hardware measurements we would choose
-%control action $\inputm{i}$, but due to uncertainties we actually choose control action $\inputm{j}$:
+%control action $v_{i}$, but due to uncertainties we actually choose control action $v_{j}$:
 %\begin{align} \label{eq:maximization}
- % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}|\inputm{i}-\inputm{j}|&= \\
+ % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}|v_{i}-v_{j}|&= \\
  % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|\nonumber
@@
 
-%Because of the linearity of the function $\inputm{i}-\inputm{j}$, and because of the
+%Because of the linearity of the function $v_{i}-v_{j}$, and because of the
 %convexity of the regions $i$ and $j$, it is enough to evaluate function
@@
 
-We should also include the error due to
-analog-to-digital conversion $\varepsilon_{A/D}$.
-Analog to digital conversion happens just before the controller receives the measured state from sensor
-and is given by:
-\begin{equation*}
-\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
-\end{equation*}
-where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
-is the number of bits available to quantize the analog signal, and $2^{r}$ is
-the resolution of the converter. The associated error in the output of the controller is $\varepsilon_{A/D}\max_i\{\|K+F_i\|\}$.
+% We should also include the error due to
+% analog-to-digital conversion $\varepsilon_{A/D}$.
+% Analog to digital conversion happens just before the controller receives the measured state from sensor
+% and is given by:
+% \begin{equation*}
+% \varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
+% \end{equation*}
+% where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
+% is the number of bits available to quantize the analog signal, and $2^{r}$ is
+% the resolution of the converter. The associated error in the output of the controller is $\varepsilon_{A/D}\max_i\{\|K+F_i\|\}$.
 
-Once a quantized state $\hat x$ is given and a region $\mathcal R_i$ is chosen, computing $\inputm{i}$ itself introduces
-imprecision, because, $\inputm{i}$ needs to be evaluated in finite-precision arithmetic:
+Once a quantized state $\hat x$ is given and a region $\mathcal R_i$ is chosen, computing $v_{i}$ itself introduces
+imprecision, because, $v_{i}$ needs to be evaluated in finite-precision arithmetic:
 \begin{equation}\label{eq:fperror}
-  err(\inputm{i})_{p} = | (F_i - \hat{F}_{i}) \statevar + ( G_i - \hat{G}_{i} ) |
+  err(v_{i})_{p} = | (F_i - \hat{F}_{i}) \statevar + ( G_i - \hat{G}_{i} ) |
 \end{equation}
@@
 of $\mathcal{R}_i$, but because of finite-precision errors they are erroneously
-mapped to control action $\inputm{i}$.
+mapped to control action $v_{i}$.
 
@@
 Due to the affinity of function
-$\inputm{i}-\inputm{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
+$v_{i}-v_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
 to evaluate the function only at the corner points of the tube, and keep the
@@
 We used both approaches; however, the later scales up better when we have millions of vertices.
-In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|\inputm{j1}-\inputm{j2}|$ is computed; (v) finally, we pick the greatest corner error.
+In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|v_{j1}-v_{j2}|$ is computed; (v) finally, we pick the greatest corner error.
 
@@
 
-$\varepsilon_Q$ and $err(\inputm{i})_{p}$ are computed by Daisy. For this we encode
+$\varepsilon_Q$ and $err(v_{i})_{p}$ are computed by Daisy. For this we encode
 the expressions in~\autoref{eq:quantizationlines} and \autoref{eq:fperror}
@@
 While our actual synthesis algorithm (\autoref{sec:Controller_Synthesis}) does
-not compute the errors $\varepsilon_Q$ and $err(\inputm{i})_{p}$ explicitly, the
+not compute the errors $\varepsilon_Q$ and $err(v_{i})_{p}$ explicitly, the
 error verification is used internally by Daisy to determine a suitable precision
@@
 % analysis. After we compute the incorrect region in MATLAB we obtain the value
-% for max error $err(\inputm{i})$ from (8). Then we give the errors and the vectors F,G
+% for max error $err(v_{i})$ from (8). Then we give the errors and the vectors F,G
 % and H,K in input to Daisy. We used Daisy as a verification tool: we provide in

### 2019-04-12 emsoft-2019/Error_Analysis.tex
fixing section 4.3

@@
 precision synthesis, we note that it is an alternative way of bounding errors to
-existing methods~\cite{imperialrmpc}.
-\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}
+existing methods~\cite{imperialrmpc}, which phrase the roundoff error computation as a (relaxed)
+mixed integer programming problem.
+%\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}
 
@@
 
-%The incorrect region error (\autoref{eq:maximization}) is computed using Matlab's multi-parametric toolbox. 
+The incorrect region error (\autoref{eq:maximization}) is computed with Matlab.
+
 Due to the affinity of function
@@
 result with the maximal magnitude. 
-To evaluate the point location error across the corner points, we need to first locate the corner points as well as all the regions which share those corner points.
-We start by computing the vertices for each region $R_i$ by converting the convex set of constraint inequalities for that region into the set of vertices at the intersections of those inequalities using existing tools such as $\mathit{lcon2vert}$ written for MATLAB (\cite{????}).
-The computed vertex $v_i$ will be associated with a $n-D$ hypercube with the edge length of $2 \varepsilon$.
-Each of the $2^n$ vertices of this hypercube is counted as a corner point.
-In order to find out which regions have the same vertex $v_i$, one approach is to compute and save the set of vertices for all the regions and then to find out the neighboring regions via exhaustive search with the saved set of vertices.
-Alternatively, for the vertex $v_i$, all the regions $R_j$s having $v_i$ as their vertex can be identified if at least $n$ of their hyperplanes cross $v_i$.
-We used both approaches; however, the later scales up better when we have millions of vertices.
-In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|v_{j1}-v_{j2}|$ is computed; (v) finally, we pick the greatest corner error.
+To evaluate the incorrect region selection error across
+the corner points, we need to first locate the corner points as well as all the
+regions which share those corner points. 
+Each region $R_i$ is represented by a set of contraints. We first extract the
+set of vertices of $R_i$ using the open source Matlab library
+$\mathit{lcon2vert}$~\cite{??}.
+For each computed vertex $v_i$, we compute a $n-D$
+hypercube with the edge length of $2 \varepsilon$. 
+Each of the $2^n$ vertices of this hypercube is counted as a corner point, on which
+we evaluate $\|u_i - u_j\|$.
 
-\eva{This needs more details. Which function(s) and algorithm from Matlab are used?}
-\eva{How do you determine which regions are neighbors? resp. which borders are matching?}
+In order to find out which regions share a vertex $v_i$, we implemented two approaches.
+The first approach determines the set of neighboring regions via an exhaustive
+search over the set of vertices. However, we observed that this algorithm only
+scales to small numbers of regions.
+Our second approach works on the observation that all the regions $R_j$s 
+having $v_i$ as their vertex can be identified if at least $n$ of their hyperplanes cross $v_i$.
+
+% In brief, we go
+% through these steps: (i) for each region, the set of vertices are computed; (ii)
+% for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as
+% their own vertex are found; (iii) for the vertex $v_i$, the set of corner points
+% $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every
+% corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal
+% R_{ij_2})$, the corresponding corner error $|v_{j1}-v_{j2}|$ is computed; (v)
+% finally, we pick the greatest corner error.
+
+% \eva{This needs more details. Which function(s) and algorithm from Matlab are used?}
+% \eva{How do you determine which regions are neighbors? resp. which borders are matching?}
 
@@
 Daisy performs a dataflow analysis to determine the finite-precision roundoff
-errors. This error computation differs from the one employed by
-\citet{imperialrmpc} which phrases the roundoff error computation as a (relaxed)
-mixed integer programming problem.
+errors. 
+% This error computation differs from the one employed by
+% \citet{imperialrmpc} which phrases the roundoff error computation as a (relaxed)
+% mixed integer programming problem.
 

### 2019-04-12 emsoft-2019/RMPC_Daisy.tex

@@
 We assume a linear translation on the input with the form
-$$u_k=Kx_k+v_k$$
+$$u_k=\mu x_k+v_k$$
 and synthesize $v_k$ instead of $u_k$. This choice reduces the 
 conservativeness of the optimization and enlarges the set of feasible input
-trajectories. The matrix $K$ is selected such that some desired property is satisfied under suitable assumptions on the system, e.g., stability if the pair $(A,B)$ is stabilizable.
+trajectories. The matrix $\mu$ is selected such that some desired property is satisfied under suitable assumptions on the system, e.g., stability if the pair $(A,B)$ is stabilizable.
 
@@
 \text{s.t.} \quad &x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
-\quad &u_i=Kx_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+\quad &u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
 &u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\,\,\forall i\in\{0,1,\cdots,N\},
@@
 The optimization \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution.
-Furthermore, for the case that $R>0$, the controller is $u_k = K x_k + \kappa(x_k)$ with $\kappa(\cdot)$ being a continuous piecewise affine (PWA) function over polyhedral regions:
+Furthermore, for the case that $R>0$, the controller is $u_k = \mu x_k + \kappa(x_k)$ with $\kappa(\cdot)$ being a continuous piecewise affine (PWA) function over polyhedral regions:
 \begin{equation}
@@
 \begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
-if ($H_{1}\statevar \leq K_{1}$) then $u_{k}=F_1x_k+G_1$
-elseif ($H_{2}\statevar \leq K_{2}$) then $u_{k}=F_2x_k+G_2$
-elseif ($H_{3}\statevar \leq K_{3}$) then $u_{k}=F_3x_k+G_3$
+if ($H_{1}\statevar \leq K_{1}$) then $v_{k}=F_1x_k+G_1$
+elseif ($H_{2}\statevar \leq K_{2}$) then $v_{k}=F_2x_k+G_2$
+elseif ($H_{3}\statevar \leq K_{3}$) then $v_{k}=F_3x_k+G_3$
 ...
-elseif ($ H_{P}\statevar\leq K_{P}$) then $u_{k}=F_Px_k+G_P$
-return $u_k$
+elseif ($ H_{P}\statevar\leq K_{P}$) then $v_{k}=F_Px_k+G_P$
+return $v_k$
 \end{lstlisting}

### 2019-04-12 emsoft-2019/experiments.tex

@@
 The first one is the inverted pendulum problem depicted in Section \ref{sec:example}, where we set
-$m=0.344$ kg, $b=0.48$ N s/m, $L=1.703$ m and $T_s=0.1$ s. The gain $K$ is
+$m=0.344$ kg, $b=0.48$ N s/m, $L=1.703$ m and $T_s=0.1$ s. The gain $\mu$ is
 selected such the $\bar A$ has poles at $-0.1$ and $-0.5$. Moreover, we select
@@
 only constrained during the first prediction horizon. You also specify scale
-factors for outputs. Using the gain $K$, the poles of $\bar A$ are placed at
+factors for outputs. Using the gain $\mu$, the poles of $\bar A$ are placed at
 $-5$, $-3$, $-1$ and $-2$. The robust MPC problem is solved for $N=2$,

### 2019-04-12 emsoft-2019/Error_Analysis.tex
comment on section 4

@@
 Then in the next section, we explain our optimization algorithm which determines suitable word
-lengths fully automatically.% in~\autoref{sec:Controller_Synthesis}.
+lengths fully automatically.
+% in~\autoref{sec:Controller_Synthesis}.
 While we do not employ the error analysis independently of the controller and
@@
 set of vertices of $R_i$ using the open source Matlab library
-$\mathit{lcon2vert}$~\cite{??}.
+$\mathit{lcon2vert}$~\cite{lcon2vertMatlab}.
 For each computed vertex $v_i$, we compute a $n-D$
@@
 
+\textcolor{red}{Sadegh: This is long comment on the content of this section.
+I cannot figure out how this line of reasoning is mapped to the implementation.
+We can discard my comment given that we are close to the deadline.}
+
+\Sadegh{
+I don't agree that we should add $\varepsilon_{A/D}$ and $\varepsilon_Q$ together.
+I understand that the implementation is done according to this, but I think we need to multiply $\varepsilon_{A/D}$ by the maximum norm of the coefficients $F_i$ in the controller.
+There are three approximations:
+\begin{itemize}
+\item using the quantized measured state $\hat x$ instead of the actual state $x$. We assume $\|x - \hat x\|\le \varepsilon_{A/D}$.
+\item using $\hat H_i,\hat K_i$ which are the quantized versions of $H_i,K_i$ with $p$ bits precision. This is related to the boundaries of the regions.
+\item using $\hat F_i,\hat G_i$ which are the quantized versions of $F_i,G_i$ with $p$ bits precision. This is related to the affine functions.
+\end{itemize}
+Let me define the sets $\mathcal H := \{H_i,K_i,i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i,i=1,2,\ldots, P\}$. Similarly, we define $\hat{\mathcal H}$ and $\hat{\mathcal F}$.
+The controller (which is a piecewise affine function) can be written as the parametric function $\kappa(\mathcal H,\mathcal F,x)$. Our main goal is to make sure that
+$$\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)\|\le \Delta,\quad \forall x\in\mathcal X_{\mathsf s}.$$
+We use tirangle these inequality:
+\begin{align*}
+\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)
+\|\le&\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
++&\|\kappa(\hat{\mathcal H},\mathcal F,\hat x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)\|.
+\end{align*}
+The second term is exactly what we have in section 4.2 (error in the evaluation of the affine function).
+The first term can be further decomposed as
+\begin{align*}
+\|\kappa(\mathcal H,&\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
+&\le \|\kappa(\mathcal H,\mathcal F,x)-\kappa(\mathcal H,\mathcal F,\hat x)\|+
+ \|\kappa(\mathcal H,\mathcal F,\hat x) - \kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
+&\le \max_i\{\|F_i\|_2\}\|x-\hat x\| + \varepsilon_Q\\
+& \le \max_i\{\|F_i\|_2\}\varepsilon_{A/D}+ \varepsilon_Q.
+\end{align*}
+The error $\varepsilon_{A/D}$ shows itself in the output of the controller by being amplified with the Lipschitz constant of the function which is $\max_i\{\|F_i\|_2\}$. 
+As far as I can tell, $\varepsilon_{A/D}$ doesn't have anything to do with $\varepsilon_Q$.
+The computation of $\varepsilon_Q$ should be only with respect to the use of $\hat{\mathcal H}$ instead of $\mathcal H$ in the evaluation of constraints for the same value $\hat x$.
+}
 % The approximation error and the precision tuning for both borders and active

### 2019-04-12 emsoft-2019/Error_Analysis.tex
Various changes throughout.

--- 2019-04-12 emsoft-2019/Error_Analysis.tex
@@
 
-In this section, we present our error analysis assuming that a fixed-point word lengths is given.
+In this section, we present our error analysis assuming that a fixed word length $p$ is given.
 Then in the next section, we explain our optimization algorithm which determines suitable word
-lengths fully automatically.% in~\autoref{sec:Controller_Synthesis}.
-While we do not employ the error analysis independently of the controller and
-precision synthesis, we note that it is an alternative way of bounding errors to
-existing methods~\cite{imperialrmpc}, which phrase the roundoff error computation as a (relaxed)
-mixed integer programming problem.
-%\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}
-
-For simplicity of notation, we assume in this section a uniform word length $p$,
-but our algorithm (and implementation) is applied to mixed-precision to reduce the memory usage.
+lengths for different variables fully automatically. % in~\autoref{sec:Controller_Synthesis}.
+%
+% For simplicity of notation, we assume in this section a uniform word length $p$,
+% but our algorithm (and implementation) is applied to mixed-precision to reduce the memory usage.
 
@@
 %where $i,j$ are the indexes of two distinct regions $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$, 
-The first term is the error of incorrect region selection.
-The maximum is taken over all neighboring regions $\mathcal R_i,\mathcal R_j$ recognisable by having non-empty intersection.
+The first term is the error of incorrect region selection. The maximum is taken over all neighboring regions 
+$\mathcal R_i,\mathcal R_j$ (two regions are neighboring if their intersection is non-empty).
 The function norm $\|v_{i}-v_{j}\|$ is taken by maximizing over all possible values of the state $x_k$. 
@@
 That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
-precision (H and K), and its counter-part quantized in $p$ bits precision
+precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
 ($\hat{H}_{p}$ and $\hat{K}_{p}$).
@@
 
-Due to the affinity of function
-$v_{i}-v_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
+Since $v_{i}-v_{j}$ is also affine, and because we defined the tube as a convex region 
+surrounding the corresponding hyperplane, it suffices
 to evaluate the function only at the corner points of the tube, and keep the
@@
 set of vertices of $R_i$ using the open source Matlab library
-$\mathit{lcon2vert}$~\cite{??}.
-For each computed vertex $v_i$, we compute a $n-D$
+$\mathit{lcon2vert}$~\cite{lcon2vertMatlab}.
+For each computed vertex $v_i$, we compute a $n$-dimensional
 hypercube with the edge length of $2 \varepsilon$. 
@@
 
-$\varepsilon_Q$ and $err(v_{i})_{p}$ are computed by Daisy. For this we encode
+The error terms $\varepsilon_Q$ and $err(v_{i})_{p}$ are computed by Daisy. For this we encode
 the expressions in~\autoref{eq:quantizationlines} and \autoref{eq:fperror}

### 2019-04-12 emsoft-2019/Motiv.tex
Various changes throughout.

@@
 % !TEX root = main.tex
-\section{Overview}
-\label{sec:example}
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 
-% Model Predictive Control (MPC) refers to the class of control strategies that design control actions by solving a finite horizon optimal control problem at each sampling instant.
-While each optimization gives a sequence of optimal control actions, only the first action is applied to the process.
-The same procedure is applied in the next time instance after receiving the updated value of the process state.
-MPC has shown to be successful in industrial applications since it is able to handle large number of states and control actions and automatically considers constraints in the optimization.
-% 
-% The optimization of each time instance uses a dynamic model of the process to predict the future states and find the optimal sequence of actions that satisfies all the constraints.
-The objective function of the optimization is usually linear or quadratic.
-The resulting optimization problem can be cast as a linear program (LP) or quadratic program (QP), respectively, if the dynamic model is linear.
-For hybrid models with linear dynamics in each mode, the optimization problem can be cast as a mixed integer linear or quadratic program (MILP/MIQP).
+\section{Overview}
+\label{sec:example}
 
-\begin{figure}[h]
+\begin{figure}[t]
 	\begin{tabular}{cc}
@@
 We use Matlab to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. 
-% \RM{the following setence is not understandable. This is the first time we introduce incorrect region selection.
-% Who is Daisy?}
-% \RM{A better version is to informally define incorrect region selection. Say that we run an algorithm for incorrect region
-% selection to bound the possible error. 
-% Break the sentence into two. Introduce Daisy as a mixed-precision tuning tool.}
-
+%
 The output of robust EMPC given by Matlab decomposes the control domain into a
-finite number of polyhedral domains together with an affine map for each domain. At each
-time step, the state vector $x_k$ is read (or estimated) and based on the domain
+finite number of polyhedral domains together with an affine map for each domain. 
+At each time step, the state vector $x_k$ is read (or estimated) and based on the domain
 that it belongs to, the corresponding control output is computed. 
 However, the polyhedral regions are implemented in finite precision so that
-it is possible that due to quantization errors the domain is selected incorrectly.
-We refer to the resulting error as incorrect region selection error.
+it is possible that due to quantization errors the domain is selected incorrectly, and therefore
+a different affine map is computed for the control.
+We refer to the resulting error as \emph{incorrect region selection} error.
 % However, due to error by fixed-point implementation, it is possible that the domain is selected
@@
 % selection error.
-
 In our example, we compute an incorrect region selection error $e = 0.019$, which is larger
@@
 $\Delta_1 = 0.05$ and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.
+
 %
-% Over the high-precision controller, we compute the error due to an incorrect region selection $e$.
-In case that $e<\Delta_0$, we would like to find the smallest number of bits required for implementing the controller such that we are still within the safe bound $\Delta_0$.
-To do so, we ask Daisy, which is a mixed-precision tuning tool, to provide us with a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
-% at all points in the control domain, the difference between the infinite-precision controller function
-% and its mixed-precision implementation is at most $\Delta_0$.
-%
-%Unfortunately, $\Delta_0=0.01$ is not realizable, as the region selection error is $0.019$ and hence $e>\Delta_0$. 
-%always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
-%\eva{Is this the error due to mixed-precision or due to wrong regions?}
-% Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.
 Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller
@@
 A sample region with the corresponding affine map is shown below:
-%Following demostrates one sample mapping, including the activation condition and its corresponding affine function
 \begin{equation*}
@@
 The remaining mappings have a similar structure.
-For this new controller, the incorrect region selection error is still
+For this new controller, the incorrect region selection error is 
 approximately $e = 0.019$, which is now below the disturbance bound $\Delta_1$,
@@
 
-Next, we use the precision tuning tool Daisy to provide us with a mixed-precision 
-implementation for all the parameters which satisfies the error bound $0.031$,
-which is given by the remaining error budget $\Delta_1 - e = 0.05 - 0.019$.  
-The mixed-precision implementation returned by Daisy requires $6084$ bits in total 
-for the corresponding robust explicit MPC.
-% Since this error bound is less than our robustness margin $\Delta_1 = 0.05$, we terminate the loop
-% and return this implementation.
-The mixed-precision implementation takes about $10\%$ less memory compared 
+Next, we use the precision tuning tool Daisy \cite{Daisy} to provide a mixed-precision 
+implementation for all the parameters which satisfies the error bound $\Delta_1  - e = 0.05 - 0.019 = 0.031$.
+The mixed-precision implementation returned by Daisy requires $6084$ bits.
+Thus, the mixed-precision implementation takes about $10\%$ less memory compared 
 to the smallest uniform precision implementation that respects $\Delta_1$,

### 2019-04-12 emsoft-2019/intro.tex
Various changes throughout.

--- 2019-04-12 emsoft-2019/intro.tex
@@
 
-One way to tackle these problems is through \emph{explicit MPC} \cite{Bemporad:2002,Alessio2009}, which formulates the optimization
+One way to tackle these problems is through \emph{explicit MPC} (EMPC) \cite{Bemporad:2002,Alessio2009}, which formulates the optimization
 problem but computes offline a symbolic representation of the solution as a function of the state.
@@
 For example, for linear time invariant models with linear constraints and quadratic costs, the optimization
-problem for MPC can be modeled as a quadratic program, and explicit MPC techniques solve the optimization problem
+problem for MPC can be modeled as a quadratic program, and EMPC techniques solve the optimization problem
 using multi-parametric programming techniques.
@@
 and an affine map for each region.
-The implementation of explicit MPC stores a lookup table of the affine maps and performs a number of affine computations
+The implementation of EMPC stores a lookup table of the affine maps and performs a number of affine computations
 online to find the appropriate region for the current state and to evaluate the control.  
@@
 
-However, there are still bottlenecks in implementing explicit MPC on resource-constrained embedded micro-controllers.
-First, implementations of explicit MPCs can suffer from large memory usage, because the solution of the optimization
-problem can involve many (often hundreds) of regions.
+However, there are still bottlenecks in implementing EMPC on resource-constrained embedded micro-controllers.
+First, implementations of EMPCs can suffer from large memory usage, because the solution of the optimization
+problem can involve many (often hundreds) of regions~\cite{memoryMPC}.
 Since the memory consumption grows linearly with the number of regions, 
-this can be a limiting factor in using explicit MPC on resource-constrained micro-controllers.
+this can be a limiting factor in using EMPC on resource-constrained micro-controllers.
 Second, many low-end micro-controllers only support fixed-point arithmetic.
 Errors in the controller implementation are inversely proportional to the number of bits used for representing each variable~\cite{Anta10}. 
-An implementation of explicit MPC has to be \emph{robust} to 
+An implementation of EMPC has to be \emph{robust} to 
 implementation errors to be able to enforce hard constraints on the states at run time~\cite{imperialrmpc}.
 
-In this paper, we consider the problem of implementing explicit MPC on low-end microcontrollers with fixed-point arithmetic
+In this paper, we consider the problem of implementing EMPC on low-end microcontrollers with fixed-point arithmetic
 in a \emph{memory-efficient} and \emph{robust} way.
@@
 Our proposed method iteratively solves a robust version of MPC 
-which explicitly considers finite-precision implementation errors as disturbances
+which considers finite-precision implementation errors as disturbances
 in the dynamics \cite{RamirezC06}; see~\autoref{fig:overview}.
@@
 model has an explicit disturbance bounded by $\Delta$.
-The solution is represented as a piecewise affine map.
-\RM{need to add the step on incorrect region selection.}
-We use an automated mixed-precision tuning tool to find an approximate implementation of the piecewise affine
-map. 
-We statically compute the error of the implementation, taking into account errors
-in evaluating the affine maps as well as choosing the wrong affine map due to quantization.
-If the error is at most $\Delta$, we are done: the implementation satisfies the robustness margin in the model.
+The solution is represented as a set of polyhedral regions, and an affine map for each region.
+
+Next, we consider the error in the control input arising out of a fixed-point implementation of the solution.
+The error has two sources.
+First, the fixed point implementation may pick a different polyhedral region (due to imprecision
+in checking membership in a polyhedron).
+Second, the fixed-precision implementation of the affine function will have a numerical error due to quantization.
+We bound both sources of error statically and automatically,  by finding the maximum possible error due to incorrect region selection
+as well as a static bound on the error in computing the affine map.
+If the error is at most $\Delta$, we know that the implementation satisfies the robustness margin in the model and
+we use an automated mixed-precision tuning tool to find an optimal bitwidth allocation that keeps the implementation below the error bound.
 If not, we increase the error bound $\Delta$ and run the loop again to find a new robust controller and find its best mixed-precision
@@
 \begin{itemize}
-\item We design a static and scalable error analysis algorithm for piecewise affine functions;
-\item We provide an end-to-end tuning algorithm for robust explicit MPC;
+\item We provide an end-to-end automatic tuning algorithm for robust explicit MPC that ensures
+hard constraints on the state are met despite numerical errors;
+\item We design a static and scalable error analysis algorithm for piecewise affine functions to bound
+errors in controller implementations; and
 \item Through a set of standard control benchmarks, we demonstrate that our tuning algorithm

### 2019-04-12 emsoft-2019/related.tex
Various changes throughout.

@@
 error analysis techniques and perform mixed-precision optimization~\cite{Lee2006,Pang2011},
-similar to the approach implemented in the tool Daisy which we use.
+similar to the approach implemented in the tool Daisy used in this paper.
+An alternate way to bound errors in fixed point implementations of EMPC 
+through mixed integer programming is given by~\citet{imperialrmpc}.

### 2019-04-12 emsoft-2019/Error_Analysis.tex

--- 2019-04-12 emsoft-2019/Error_Analysis.tex
@@
 
-In this section, we present our error analysis assuming that a fixed-point word lengths is given.
+In this section, we present our error analysis assuming that a fixed word length $p$ is given.
 Then in the next section, we explain our optimization algorithm which determines suitable word
-lengths fully automatically.
-% in~\autoref{sec:Controller_Synthesis}.
-While we do not employ the error analysis independently of the controller and
-precision synthesis, we note that it is an alternative way of bounding errors to
-existing methods~\cite{imperialrmpc}, which phrase the roundoff error computation as a (relaxed)
-mixed integer programming problem.
-%\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}
-
-For simplicity of notation, we assume in this section a uniform word length $p$,
-but our algorithm (and implementation) is applied to mixed-precision to reduce the memory usage.
+lengths for different variables fully automatically. % in~\autoref{sec:Controller_Synthesis}.
+%
+% For simplicity of notation, we assume in this section a uniform word length $p$,
+% but our algorithm (and implementation) is applied to mixed-precision to reduce the memory usage.
 
@@
 $\mathit{lcon2vert}$~\cite{lcon2vertMatlab}.
-For each computed vertex $v_i$, we compute a $n-D$
+For each computed vertex $v_i$, we compute a $n$-dimensional
 hypercube with the edge length of $2 \varepsilon$. 

### 2019-04-13 emsoft-2019/related.tex
updates

@@
 expensive optimization problems. In contrast, the explicit MPC used in our work performs controller synthesis at the design time.
+Synthesizing digital controllers with formal guarantees while having finite-precision implementation is studied in \cite{SSPBLSZ19} for stochastic systems.
 
@@
 similar to the approach implemented in the tool Daisy used in this paper.
-An alternate way to bound errors in fixed point implementations of EMPC 
+An alternative way of bounding errors in fixed-point implementations of EMPC 
 through mixed integer programming is given by~\citet{imperialrmpc}.

### 2019-04-13 emsoft-2019/Motiv.tex
Fig 2 with subfigure

@@
 	%\end{adjustbox}
-	\caption{Overview of the proposed memory-efficient robust MPC control design.}
+	\caption{Overview of the proposed memory-efficient robust EMPC control design.}
 	\label{fig:overview}
@@
 \label{sec:example}
-
-\begin{figure}[t]
-	\begin{tabular}{cc}
-	\includegraphics[width=2cm,height=3cm]{Figs/inverted_pendulum.pdf}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
-	(a)&(b)
-	\end{tabular}
-	\caption{(a) Inverted pendulum; (b) 2-D plot of polyhedral partitions for an explicit MPC applied to the inverted pendulum.}
-	\label{fig:inverted_pendulum}
-\end{figure}
 
@@
 Additionally, we require the state constraints $\theta_k\in[-\pi,\pi]$ and $\omega_k\in[-\pi/8,\pi/8]$ to hold at all time instances.
+
+\begin{figure}[t]
+	\centering
+  \begin{subfigure}[b]{0.33\columnwidth}
+      \includegraphics[width=\textwidth]{Figs/inverted_pendulum.pdf}
+      \vspace{0.05cm}
+      \caption{}
+  \end{subfigure}
+  %~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+  \begin{subfigure}[b]{0.66\columnwidth}
+      \includegraphics[width=\textwidth]{Figs/regs.jpg}
+      \caption{}
+  \end{subfigure}
+	\caption{(a) Inverted pendulum; (b) 2D plot of polyhedral partitions for an EMPC applied to the inverted pendulum.}
+	\label{fig:inverted_pendulum}
+\end{figure}
 

### 2019-04-15 emsoft-2019/Cont_Syn.tex
small fixes
notation

@@
  while true:
-   F, G, H, K = design_robust_MPC(model, $\Delta$)
-   errorRegion = incorrect_region_error(F, G, H, K, $\varepsilon$)
+   $F$, $G$, $H$, $K$ = design_robust_MPC(model, $\Delta$)
+   errorRegion = incorrect_region_error($F$, $G$, $H$, $K$, $\varepsilon$)
    if $\Delta$ > errorRegion:
      errorAct = $\Delta$ - errorRegion
-     $\hat{\text{F}}$, $\hat{\text{G}}$ = precision_tuning(F, G, errorAct)
-     $\hat{\text{H}}$, $\hat{\text{K}}$ = precision_tuning(H, K, $\varepsilon_Q$)
-     return $\hat{\text{F}}$, $\hat{\text{G}}$, $\hat{\text{H}}$, $\hat{\text{K}}$
+     $\hat{F}$, $\hat{G}$ = precision_tuning($F$, $G$, errorAct)
+     $\hat{H}$, $\hat{K}$ = precision_tuning($H$, $K$, $\varepsilon_Q$)
+     return $\hat{F}$, $\hat{G}$, $\hat{H}$, $\hat{K}$
    else:
@@
 Given a state-space model of a plant (line 1), our algorithm returns four matrices
-$\hat{\text{F}}$, $\hat{\text{G}}$, $\hat{\text{H}}$, and $\hat{\text{K}}$,
+$\hat{F}$, $\hat{G}$, $\hat{H}$, and $\hat{K}$,
 which soundly implement a robust explicit MPC controller in mixed-precision
@@
 sources: error due to selecting the wrong region, which is given by the
-quantization of $\hat{\text{H}}$ and $\hat{\text{K}}$, and the error due to
-quantization of the control action, given by $\hat{\text{F}}$, $\hat{\text{G}}$.
-The quantization of $\hat{\text{H}}$ and $\hat{\text{K}}$ is determined by
+quantization of $\hat{H}$ and $\hat{K}$, and the error due to
+quantization of the control action, given by $\hat{F}$, $\hat{G}$.
+The quantization of $\hat{H}$ and $\hat{K}$ is determined by
 $\varepsilon_Q$, thus by providing this input value, the user effectively
-chooses how much precision to allow for $\hat{\text{H}}$ and $\hat{\text{K}}$.
+chooses how much precision to allow for $\hat{H}$ and $\hat{K}$.
 Note that this precision comes at the expense of the precision of
-$\hat{\text{F}}$ and $\hat{\text{G}}$, i.e. the more accurately $\hat{\text{H}}$
-and $\hat{\text{K}}$ are represented, the more approximate $\hat{\text{F}}$ and
-$\hat{\text{G}}$ need to be and vice versa.
+$\hat{F}$ and $\hat{G}$, i.e. the more accurately $\hat{H}$
+and $\hat{K}$ are represented, the more approximate $\hat{F}$ and
+$\hat{G}$ need to be and vice versa.
 We note that one could straight-forwardly extend our algorithm to include an
@@
 disturbance $\Delta$ (line 8). The result is a controller represented by four matrices
-\texttt{F, G, H, K} given in high precision.
+$F$, $G$, $H$, $K$ given in high precision.
 
 \emph{Assuming} that we can implement the polyhedral region partitioning (given by
-matrices \texttt{H, K}) with an implementation error of at most $\varepsilon_Q$,
+matrices $H$, $K$) with an implementation error of at most $\varepsilon_Q$,
 our algorithm proceeds to compute the error due to selecting the wrong region (line 9).
@@
 For the precision assignment, we first call Daisy with the expressions for the
-control actions given by \texttt{F} and \texttt{G}, and the remaining error
+control actions given by $F$ and $G$, and the remaining error
 budget as the error bound (line 12).
-Then we call Daisy with the expressions of the region bounds given by \texttt{H}
-and \texttt{K}, now with the error bound $\varepsilon_Q$ (line 13).
+Then we call Daisy with the expressions of the region bounds given by $H$
+and $K$, now with the error bound $\varepsilon_Q$ (line 13).
 
@@
 and Daisy and which implements the high-level structure from~\autoref{lst:alg}.
-The interface parses the output from Matlab and encodes the matrices \texttt{F,
-G, H, K} and the error bounds in Daisy's input format.
+The interface parses the output from Matlab and encodes the matrices $F$,
+$G$, $H$, $K$ and the error bounds in Daisy's input format.
+
+We set up the problem with YALMIP~\cite{matlabYALMIP}, and use 
+Matlab's MPT toolbox~\cite{matlabMPT} to compute the robust explicit MPC.
 

### 2019-04-15 emsoft-2019/Methodology.tex
notation

@@
 The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called region.
-A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar<=K_{i}$.
+A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar\le K_{i}$.
 
@@
 \begin{equation}
-\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
+\statespace = \bigcup_{i}(H_{i}\statevar\le K_{i})
 \end{equation}
@@
 
-A drawback in the design of explicit MPC is that both regions boundaries (H and K) and activation functions (F and G), have to be stored on the micro-controller.
+A drawback in the design of explicit MPC is that both regions boundaries ($H$ and $K$) and activation functions ($F$ and $G$), have to be stored on the micro-controller.
 Usually these devices have limited memory, in the order of KBs.
@@
 \subsection{Precision Tuning}
-In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is generated by the quantization of hyperplanes $H\statevar<=K$ in a finite number of bits.
+In formula (\ref{eq:epsilontot}), the equation for $\varepsilon$ contains: $\varepsilon_{A/D}$ that is the error introduced by the analog-digital conversion, and $\varepsilon_{Q}$ that is generated by the quantization of hyperplanes $H\statevar\le K$ in a finite number of bits.
 This $\varepsilon_{Q}$ can be tuned based on memory availability in the micro-controller.
@@
 \end{equation}
-This inequality assures that the distance between any hyperplane represented in infinite precision (H and K), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$.
+This inequality assures that the distance between any hyperplane represented in infinite precision ($H$ and $K$), and its counter-part quantized in p bits ($(\hat{H})_{p}$ and $(\hat{K})_{p}$), is bounded by $\varepsilon_{Q}$.
 
@@
 
-Since the state variable \statevarmath is bounded by \statespace, and F,G,H, and K are vectors of constants, we can rely on Daisy for this verification step.
+Since the state variable \statevarmath is bounded by \statespace, and $F,G,H$ and $K$ are vectors of constants, we can rely on Daisy for this verification step.
 
@@
 max_err=delta-maxUij
-UNI_MIX_precision(F,G,max_err)
-UNI_MIX_precision(H,K,(*$\varepsilon_{Q}$*))
+UNI_MIX_precision($F$,$G$,max_err)
+UNI_MIX_precision($H$,$K$,(*$\varepsilon_{Q}$*))
 break

### 2019-04-15 emsoft-2019/experiments.tex
notation

@@
 and mixed precision (`Mix'). We split the memory requirement into the bits
-required for storing F and G and H and K. We show the results for each benchmark
+required for storing $F$, $G$, $H$ and $K$. We show the results for each benchmark
 for ten different combinations of $\Delta$ and $\varepsilon_Q$, varying one while
@@
 For the inverted pendulum, minimal uniform precision saves on average $52.6\%$ of memory
-compared to a uniform 32 bit baseline overall, i.e. for F, G, H and K together. 
+compared to a uniform 32 bit baseline overall, i.e. for $F$, $G$, $H$ and $K$ together. 
 Mixed-precision further reduces the memory
@@
 \autoref{tab:ipd} shows a more detailed breakdown of the memory requirements and savings
-between F and G and H and K.
-The memory requirements for the storage of hyperplanes H and K depends only on
+between $F$, $G$, $H$ and $K$.
+The memory requirements for the storage of hyperplanes $H$ and $K$ depends only on
 the size of the tubes $\varepsilon_Q$ so that memory requirements remain constant
@@
 additional $17.7\%$ w.r.t. minimal uniform precision (33.6\% w.r.t to uniform 32 bit). We observe higher relative
-memory savings by mixed-precision for storing H and K than for the inverted pendulum example.
+memory savings by mixed-precision for storing $H$ and $K$ than for the inverted pendulum example.
 
@@
 %We noticed the following common behavior in the two benchmarks: 
-As expected, when $\Delta$ decreases, the control actions (F, G) need to be implemented
+As expected, when $\Delta$ decreases, the control actions ($F$, $G$) need to be implemented
 more precisely and require more memory, because the space for approximation error
 is reduced. Similarly, when the value of $\varepsilon_Q$ increases, the memory
-requirements for H, K can be relaxed.
+requirements for $H$ and $K$ can be relaxed.
 
@@
 We note that for the aircraft example,
-the precision for F and G is almost double with respect to the pendulum. This is
-because the magnitude of F and G is on the order of $10^{3}$ while for the
-pendulum it is on the order of several units. Note, however, that for F and G the memory gain
+the precision for $F$ and $G$ is almost double with respect to the pendulum. This is
+because the magnitude of $F$ and $G$ is on the order of $10^{3}$ while for the
+pendulum it is on the order of several units. Note, however, that for $F$ and $G$ the memory gain
 from minimal uniform to mixed precision (\%UvM) is only slightly less than the one for the pendulum.
@@
 We observe that our analysis scales up to 1829 controllers and 14632 hyperplanes in a few hours.  The computed minimal uniform precision saves on average $44.5\%$ of memory
-compared to a uniform $32$ bit baseline overall (for F, G, H and K together). 
+compared to a uniform $32$ bit baseline overall (for $F$, $G$, $H$ and $K$ together). 
 Moreover, mixed-precision reduces the memory requirement by an additional

### 2019-06-11 emsoft-2019/V2/response.tex
V2 folder is added+Rev 4 is answered

\Mahmoud{\section{Response}	
We thank the reviewers for the detailed and useful feedback on our submission! We plan to improve our paper while taking into account the minor comments. Our response to your specific questions are summarized as follows.\\	
\textbf{Execution time for EMPCs(REVIEWER 4)}\\
The total time to evaluate the PWA function for a given $x_k$ in \autoref{eq:affine_map} consists of two steps:
\begin{itemize}
\item Selecting the region $\mathcal R_i$ such that $x_k\in \mathcal R_i$.
\item To evaluate the corresponding affine map $F_i x_k +G_i$. 
\end{itemize}
Evaluating the affine map is straightforward and requires less computations compared to the region selection step. Direct implementation of region selection (\autoref{lst:caseof}) is simple, but inefficient. More efficiency can be achieved by leveraging binary search tree structures (e.g. \cite{Mnnigmann:2011}). In general, explicit MPC is well-known for its high-speed implementation over embedded systems with low computational power. \cite{Johansen:2007} shows that explicit MPCs with hundreds of regions can be implemented on application specific integrated circuit (ASIC) with about $20000$ gates, leading to computation times in the order of $1\mu s$. In \cite{Bemporad:2006}, it is shown that for typical problems evaluating the explicit MPC takes significantly shorter time in comparison to solving on-line QP. \\
\textbf{Termination of algorithm for robust EMPC design (\autoref{lst:alg}) (REVIEWER 4)}\\
From theoretical point of view, the numerical error does not necessarily converge as each new designed controller may differ from the previous ones. Therefore, it is not easy to give an upper bound over the number of times that the robust MPC design needs to be repeated. However, one can use results on continuity of $argmin$ function in 
\begin{align*}
\label{eq:argmin}
&u_0(x_0,\Delta),\cdots,u_{N-1}(x_0,\Delta)=\\
&argmin \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
&\text{s.t.} \quad x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
%\quad &u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}_{\Delta},\,\,\forall i\in\{0,1,\cdots,N\},
\end{align*}
 assuming its unique solution to every $\Delta$ and compute the Lipschitz constant for it over variations of $\Delta$. The computed Lipschitz constant will be only dependent on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used to evaluate the maximum error over incorrect region selection. From experimental point of view, using a reasonable $\varepsilon_{SAFE}$, our observations show that numerical error always has converged after only a few iterations.
}

### 2019-06-11 emsoft-2019/V2/Error_Analysis.tex
V2 folder is added+Rev 4 is answered

--- 2019-04-12 emsoft-2019/Error_Analysis.tex
@@
 \begin{equation*}
-\hat{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon \right\}
+\hat{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
 \end{equation*}
@@
 \begin{equation}\label{eq:quantizationlines}
-  \varepsilon_{Q} = \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|
+  \varepsilon_{Q} \ge  \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|, \quad \forall \hat{x},\forall i,
 \end{equation}
@@
  \label{eq:maximization}
- \max\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}
+ \max_{x,i,j}\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}.
 % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
@@
 \begin{equation}\label{eq:quantizationlines}
-  \varepsilon_{Q} = |(H_i - \hat{H}_i) \qstatevar + (K_i - \hat{K}_i)|
+  \varepsilon_{Q} \ge  |(H_i - \hat{H}_i) \qstatevar + (K_i - \hat{K}_i)|, \forall  \qstatevar
 \end{equation}
@@
 \begin{equation}\label{eq:fperror}
-  err(v_{i})_{p} = | (F_i - \hat{F}_{i}) \statevar + ( G_i - \hat{G}_{i} ) |
+  err(v_{i})_{p} \ge  | (F_i - \hat{F}_{i}) \statevar + ( G_i - \hat{G}_{i} ) |,\quad \forall \statevar\in \mathcal{R}_i\cup\bar{\mathcal B}_{ij},\,\,\forall j,
 \end{equation}
@@
 region $\mathcal{R}_i$, together with all the values in the tube surrounding
-region $\mathcal{R}_i$.
+region $\mathcal{R}_i$ (union of $\bar{\mathcal B}_{ij}$ for all $j$).
 In this way we compute the error also for those points that belong to a neighbor
@@
 
+\begin{comment}
 \textcolor{red}{Sadegh: This is long comment on the content of this section.
@@
 }
+\end{comment}
 % The approximation error and the precision tuning for both borders and active

### 2019-06-11 emsoft-2019/V2/finite_precision.tex
V2 folder is added+Rev 4 is answered

--- 2019-04-11 emsoft-2019/finite_precision.tex
@@
 In this work, we use the tool Daisy which implements roundoff error
-analysis and mixed-precision tuning~\cite{DaisyTuning} for fixed-point arithmetic, and is
+analysis~\cite{Daisy} and mixed-precision tuning~\cite{DaisyTuning} for fixed-point arithmetic, and is
 available as open-source. Fixed-point arithmetic implementations can choose different

### 2019-06-11 emsoft-2019/V2/response.tex
updating the response

@@
 We plan to improve our paper while taking into account the minor comments.
-Our response to your specific questions are summarized as follows.\\
-\textbf{Execution time for EMPCs(REVIEWER 4)}\\
+Our response to your specific questions are summarized as follows.
+These points will be added later into the main body of the final version of our paper.\\
+\textbf{Execution time for EMPCs (Reviewer 4)}\\
 The total time to evaluate the PWA function for a given $x_k$ in \autoref{eq:affine_map} consists of two steps:
@@
 \end{itemize}
-Evaluating the affine map is straightforward and requires less computations compared to the region selection step.
+Evaluating the affine map is straightforward and requires less computational effort compared to the region selection step.
 Direct implementation of region selection (\autoref{lst:caseof}) is simple, but inefficient.
@@
 \\
-\textbf{Termination of algorithm for robust EMPC design (\autoref{lst:alg}) (REVIEWER 4)}\\
+\textbf{Termination of the algorithm for robust EMPC design (Reviewer 4)}\\
 From theoretical point of view, the numerical error does not necessarily converge as each new designed controller may differ from the previous ones.
@@
 The computed Lipschitz constant will be only dependent on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used to evaluate the maximum error over incorrect region selection.
-From experimental point of view, using a reasonable $\varepsilon_{SAFE}$, our observations show that numerical error always has converged after only a few iterations.
+This Lipschitz constant can be quite large, leading into a very conservative bound on maximum number of iterations before convergence.
+However, from experimental point of view, using a reasonable $\varepsilon_{SAFE}$, our observations show that convergence always happened after only a few iterations.
 }

### 2019-06-11 emsoft-2019/V2/Cont_Syn.tex
minor comments are addressed

--- 2019-04-15 emsoft-2019/Cont_Syn.tex
@@
 \begin{figure}
-\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily]
+\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily,escapeinside={<@}{@>}]
  model = input() 
@@
  assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
- $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$
+ $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@\Mahmoud{//the width of the uncertain area}@>
 
@@
 requiring the user to provide $\varepsilon_Q$ as the input.
+\Mahmoud{Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up-to $10^{-2}$.
+Increasing the $\varepsilon_Q$ leads into more memore save over $H$ and $K$, requiring more precision for $F$ and $G$ (\autoref{tab:di}).
+Of course, too large values for $\varepsilon_Q$ can result in failure of RMPC design.
+However, this is usually not the case over reasonable choices for $\varepsilon_Q$.}
 

### 2019-06-11 emsoft-2019/V2/Motiv.tex
V2 folder is added+Rev 4 is answered
update
minor comments are addressed

--- 2019-04-13 emsoft-2019/Motiv.tex
@@
 		\node [block,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
-		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
+		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set \Mahmoud{$\mathcal W_{\Delta}$}};
+		\Mahmoud{\node [block1,below = 0.8cm of RMPC] (highprec) {High-precision controller (\autoref{eq:affine_map})};}
 		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
-		\node [block3,below=1.3cm of RMPC,
+		\node [block3,below=.8cm of highprec,
 		node distance=1cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (Uij) {Incorrect region selection error};
@@
 		\node [block2, right=1.3cm of decide,
-		node distance=1cm] (delta) {Increase $\Delta$};
-		\node [block1,below = 0.8cm of done] (output) {Low-precision controller};
+		node distance=1cm] (delta) {\Mahmoud{ $\Delta=e+\varepsilon_{SAFE}$}};
+		\node [block1,below = 0.8cm of done] (output) {Low-precision controller \Mahmoud{(\autoref{eq:affine_map})}};
 		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
@@
 
-		\draw [draw,->, align=center] (RMPC) -- node [left] {High-precision controller}(Uij);
+		\draw [draw,->, align=center] (RMPC) -- node [left] {}(highprec);
+		\draw [draw,->, align=center] (highprec) -- node [left] {}(Uij);
+		%\draw [draw,->, align=center] (RMPC) -- node [left] {High-precision controller}(Uij);
 		\draw [->] (Uij) -- node [left] {$e$}(decide);
@@
 We start by selecting an initial bound $\Delta_0$ on the implementation error and enlarge $\mathcal W$ with $\Delta_0$ as $\mathcal W_{\Delta_0}$, where
-\begin{equation}
+\begin{equation}\label{eq:W_delta}
 \mathcal W_{\Delta} := \{w_1+w_2 \,|\, w_1\in \mathcal W, \|w_2\|\le \Delta\}
@@
 In our example, we compute an incorrect region selection error $e = 0.019$, which is larger
-than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount to
+than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount \Mahmoud{$\varepsilon_{SAFAE}=0.031$} to
 $\Delta_1 = 0.05$ and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.

### 2019-06-11 emsoft-2019/V2/RMPC_Daisy.tex
V2 folder is added+Rev 4 is answered
minor comments are addressed

--- 2019-04-12 emsoft-2019/RMPC_Daisy.tex
@@
 Matrices $A\in \reals^{n\times n}$, $B\in \reals^{n\times m}$ and $E\in \reals^{n\times d}$  capture respectively the effects of current state, input and disturbance on the next state.
-We assume the disturbance $w$ belongs to a set $\mathcal{W}$ where $\mathcal{W}$ is a polyhedral set.
+We assume the disturbance $w$ belongs to a set $\Mahmoud{\mathcal{W}_{\Delta}}$ where $\Mahmoud{\mathcal{W}_{\Delta}}$ is a polyhedral set \Mahmoud{defined by \autoref{eq:W_delta}}.
 In this paper, we focus on the robust formulation of MPC which at each time step
@@
 \quad &u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
-&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\,\,\forall i\in\{0,1,\cdots,N\},
+&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\Mahmoud{\mathcal{W}_{\Delta}},\,\,\forall i\in\{0,1,\cdots,N\},
 %&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
@@
 \begin{equation}
+\label{eq:affine_map}
 \kappa(x_k)=
@@
 At each time step $k$, the current state $x_k$ is used to detect the polyhedral region 
-such that $H_i x_k\le K_i$. Then the control action $u_k = F_i x_k + G_i$ is computed and applied to the system.
+such that $H_i x_k\le K_i$. Then the control action $v_k = F_i x_k + G_i$ is computed and applied to the system.
 Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong. 

### 2019-06-11 emsoft-2019/V2/intro.tex
minor comments are addressed

--- 2019-04-12 emsoft-2019/intro.tex
@@
 and an affine map for each region. 
-The implementation of EMPC stores a lookup table of the affine maps and performs a number of affine computations
-online to find the appropriate region for the current state and to evaluate the control.  
-Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to compute fast online
+\Mahmoud{Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.}
+Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{online computations}
 or to certify a complex optimization routine.
@@
 Our proposed method iteratively solves a robust version of MPC 
-which considers finite-precision implementation errors as disturbances
+\Mahmoud{that} considers finite-precision implementation errors as disturbances
 in the dynamics \cite{RamirezC06}; see~\autoref{fig:overview}.
@@
 We have applied our technique on a number of standard benchmark examples.
-Our algorithm finds mixed-precision implementations which save up to 20.9\%
+Our algorithm finds mixed-precision implementations \Mahmoud{that} save up to 20.9\%
 memory (on average, 12.6\%) in controller implementations over a minimal

### 2019-06-11 emsoft-2019/V2/response.tex
updates

@@
-\Mahmoud{\section{Response}	
-We thank the reviewers for the detailed and useful feedback on our submission!
-We plan to improve our paper while taking into account the minor comments.
-Our response to your specific questions are summarized as follows.
-These points will be added later into the main body of the final version of our paper.\\
+\Mahmoud{\section{Revision Letter}	
+We thank the reviewers for the detailed and useful feedback on our submission. First, we will detail the main changes we made. Afterwards, we provide responses to your specific questions. 
+\subsection{Changes}
+We have improved our paper while taking into account all the minor comments.
+Particularly, \autoref{fig:overview} has been updated and the Remark \ref{rem:eps_Q} is added.
+Other changes are minor and are highlighted within the text.
+\subsection{Responses}
+Here, we provide answer to the main inquiries posed by reviewers. These points will be added later into the main body of the final version of our paper.\\
 \textbf{Execution time for EMPCs (Reviewer 4)}\\

### 2019-06-11 emsoft-2019/V2/Cont_Syn.tex
updates

@@
 requiring the user to provide $\varepsilon_Q$ as the input. 
-\Mahmoud{Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up-to $10^{-2}$.
-Increasing the $\varepsilon_Q$ leads into more memore save over $H$ and $K$, requiring more precision for $F$ and $G$ (\autoref{tab:di}).
+\Mahmoud{
+	\begin{remark}\label{rem:eps_Q}
+		Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up-to $10^{-2}$.
+Increasing the $\varepsilon_Q$ leads into more memory save over $H$ and $K$, while requiring more precision for $F$ and $G$ (\autoref{tab:di}).
 Of course, too large values for $\varepsilon_Q$ can result in failure of RMPC design.
-However, this is usually not the case over reasonable choices for $\varepsilon_Q$.}
+However, this is usually not the case over reasonable choices for $\varepsilon_Q$.
+	\end{remark}}
 

### 2019-06-11 emsoft-2019/V2/Motiv.tex
updates

@@
 The mixed-precision implementation returned by Daisy requires $6084$ bits.
-Thus, the mixed-precision implementation takes about $10\%$ less memory compared 
+Thus, \Mahmoud{for this introductory example,} the mixed-precision implementation takes about $10\%$ less memory compared 
 to the smallest uniform precision implementation that respects $\Delta_1$,

### 2019-06-11 emsoft-2019/V2/finite_precision.tex
updates

@@
 To reduce memory usage and increase efficiency, we want to choose as short word
-lengths as possible. Mixed-precision tuning tools automatically determine possibly different
+lengths as possible, \Mahmoud{as this way memory footprint is minimized and run-time is not influenced.} Mixed-precision tuning tools automatically determine possibly different
 word lengths for different values~\cite{DaisyTuning,Lee2006}. Compared to uniform precision (or word length),

### 2019-06-11 emsoft-2019/V2/conclusion.tex
updates

--- 2019-04-12 emsoft-2019/conclusion.tex
@@
 In addition, the static analysis scales to controllers with hundreds of regions.
+\Mahmoud{All in all, using our proposed method, model predictive control under input and state constraints can be achieved while the memory footprint is minimized.
+By leveraging our method, memory requirement for implementation of explicit MPCs over the industrial embedded systems reduces.
+One exciting direction for future work would be to investigate effect of stochastic noises on the proposed design methodology.}

### 2019-06-11 emsoft-2019/V2/intro.tex
updates

@@
 and obtaining the optimal action for the next time instance. 
-Moreover, the optimization solver needs to be certified when using MPC in safety critical applications.
+Moreover, the optimization solver needs to be certified when using MPC in safety critical applications \Mahmoud{\cite{Alessio2009}}.
 
@@
 Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{online computations}
-or to certify a complex optimization routine.
+or to certify a complex optimization routine \Mahmoud{\cite{memoryMPC}}.
 
 However, there are still bottlenecks in implementing EMPC on resource-constrained embedded micro-controllers.
-First, implementations of EMPCs can suffer from large memory usage, because the solution of the optimization
+First, implementations of EMPCs \Mahmoud{over industrial micro-controllers with limited memory} can suffer from large memory usage, because the solution of the optimization
 problem can involve many (often hundreds) of regions~\cite{memoryMPC}.
@@
 If not, we increase the error bound $\Delta$ and run the loop again to find a new robust controller and find its best mixed-precision
-implementation.
+implementation. \Mahmoud{While our formulation is general enough to take the effect of measurement/process noise into account, this is not subject of study of the current paper.}
 
@@
 precision implementation on our largest benchmark.
+\Mahmoud{It should be noticed that these savings are not affecting the run-time.
+Synthesis of the controller and the corresponding precisions are all performed offline.}
 

### 2019-06-13 emsoft-2019/V2/response.tex
Revision letter is updated

@@
 \subsection{Changes}
-We have improved our paper while taking into account all the minor comments.
+We have improved our paper while considering all the minor comments.
 Particularly, \autoref{fig:overview} has been updated and the Remark \ref{rem:eps_Q} is added.
 Other changes are minor and are highlighted within the text.
+We also plan to distribute our tool once the double blinded review phase is passed.
 \subsection{Responses}
-Here, we provide answer to the main inquiries posed by reviewers. These points will be added later into the main body of the final version of our paper.\\
-\textbf{Execution time for EMPCs (Reviewer 4)}\\
+Here, we provide answer to the main inquiries posed by the reviewers. These points will be added later into the main body of the final version of our paper.\\
+\textbf{Significance of memory savings reported in the paper} (Reviewer 1)\\
+Explicit MPC is a class of controllers which is mainly appropriate for implementation over processors with limited computational power as it omits the need for massive online optimizations.
+This speed up in execution comes however with relatively high memory demand due to high number of PWA mappings that must be saved over the memory.
+Typical memory of these processors is in the order of tens of kilobytes (e.g.
+$32$ KB) and hence $21$ KB is considered as a significant save.\\
+\textbf{Do memory savings in our approach come with a run-time cost?} (Reviewer 1)
+\\
+No. It should be noticed that savings are not affecting the run-time as synthesizing of the controller and the corresponding mixed precision computations are all performed offline.\\
+\textbf{Do achieved savings correspond also to actual implementation?} (Reviewers 1 $\&$ 4)\\
+MATLAB and Daisy are solely used for offline computations.
+The output of our algorithm contains (almost) all the information required for implementation of the verified controller over embedded systems.
+Therefore, the same savings can be expected when the controller is implemented on an actual embedded system.\\
+\textbf{Taking uncertainties other than quantization into account} (Reviewer 1)\\
+Our formulation is general enough to take the effect of measurement/process noise into account.
+More specifically, $\Delta$ in $\mathcal{W}_{\Delta}$ can in general give upper-bound over the sum of uncertainties with different sources.
+However, this is not subject of study of the current paper.\\
+\textbf{Complexity of the proposed approach} (Reviewer 2)\\
+In \cite{Alessio2009} it is shown that the upper bound over the number of regions $P$ is $2^q$, where $q$ denotes the total number of constraints in \autoref{eq:RMPC_prob}.
+In theory one cannot find an upper bound for the maximum number of hyperplanes enclosing a region.
+To compute the incorrect region selection error, assuming that each partition at most has $\bar n_f$ faces, in the worst case $i\times\bar n_f\times 2^q$ affine computations would be enough, where $i$ denotes the number of times that RMPC design is repeated for updated $\Delta$s.
+In our experiments, computation of incorrect region selection takes only a few minutes for our largest tested benchmarks.
+\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}\\
+\textbf{Extension of the proposed method into the nonlinear dynamical systems} (Reviwer 2)\\
+It should be noticed that EMPC is a class of controllers specifically proposed for linear time invariant (LTI) systems.
+To cover nonlinear systems, one approach is to linearize them around an appropriately selected equilibrium point of the system and to model the differences as a bounded disturbance as in \autoref{eq:RMPC_prob}.
+Taking the upper bound over nonlinearities into account will result in enlarging $\Delta$ which characterizes $\mathcal{W}_{\Delta}$.
+For reasonable values of $\Delta$, in principle RMPC design should work successfully.
+Further, it should be noticed that the rest of analysis (over MATLAB and Daisy) do not rely on the LTI property of the under study system and could be adjusted for other families of controllers.
+However, such analysis are beyond the scope of this paper as (perturbed) LTI systems are considered as an important class of dynamical systems.\\
+\textbf{Releasing the developed package} (Reviewers 3 $\&$ 4)\\
+We definitely plan to distribute our package once the double blinded review phase is passed.\\ 
+\textbf{Reason for the special format of solution to \autoref{eq:RMPC_prob} as polyhedral decomposition} (Reviewer 3)\\
+We use results in \cite{delaPea:2005}; since this is not among this paper's contributions, we do not go beyond giving a general outline of this result.
+\\
+\textbf{Execution time for EMPCs} (Reviewer 4)\\
 The total time to evaluate the PWA function for a given $x_k$ in \autoref{eq:affine_map} consists of two steps:

### 2019-06-13 emsoft-2019/V2/intro.tex
updates
Revision letter is updated

@@
 If not, we increase the error bound $\Delta$ and run the loop again to find a new robust controller and find its best mixed-precision
-implementation. \Mahmoud{While our formulation is general enough to take the effect of measurement/process noise into account, this is not subject of study of the current paper.}
+implementation. %\Mahmoud{While our formulation is general enough to take the effect of measurement/process noise into account, this is not subject of study of the current paper.}
 
@@
 and the Daisy tool for multi-precision tuning and fixed-point error analysis~\cite{Daisy}.
+%\Mahmoud{It should be noticed that MATLAB and Daisy are solely used for offline computations.
+The output of our algorithm contains the information required for implementation of the verified controller over embedded systems.}
 
-We have applied our technique on a number of standard benchmark examples.
-Our algorithm finds mixed-precision implementations \Mahmoud{that} save up to 20.9\%
+We have applied our technique on a number of standard benchmark examples. \Mahmoud{Taking all these benchmarks into account,}
+our algorithm finds mixed-precision implementations \Mahmoud{that} save up to 20.9\%
 memory (on average, 12.6\%) in controller implementations over a minimal
@@
 precision implementation on our largest benchmark.
-\Mahmoud{It should be noticed that these savings are not affecting the run-time.
+%\Mahmoud{It should be noticed that these savings are not affecting the run-time.
 Synthesis of the controller and the corresponding precisions are all performed offline.}
@@
 \begin{itemize}
-\item We provide an end-to-end automatic tuning algorithm for robust explicit MPC that ensures
+\item We provide an end-to-end automatic tuning algorithm for robust explicit MPC that ensures \Mahmoud{that}
 hard constraints on the state are met despite numerical errors;

### 2019-06-13 emsoft-2019/V2/response.tex
updates

@@
 We have improved our paper while considering all the minor comments.
-Particularly, \autoref{fig:overview} has been updated and the Remark \ref{rem:eps_Q} is added.
-Other changes are minor and are highlighted within the text.
+Particularly, \autoref{fig:overview} is updated and the Remark \ref{rem:eps_Q} is added.
+Other changes are minor and are highlighted within the body of the paper.
 We also plan to distribute our tool once the double blinded review phase is passed.
@@
 In our experiments, computation of incorrect region selection takes only a few minutes for our largest tested benchmarks.
-\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}\\
+\underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}}\\
 \textbf{Extension of the proposed method into the nonlinear dynamical systems} (Reviwer 2)\\
@@
 \textbf{Reason for the special format of solution to \autoref{eq:RMPC_prob} as polyhedral decomposition} (Reviewer 3)\\
-We use results in \cite{delaPea:2005}; since this is not among this paper's contributions, we do not go beyond giving a general outline of this result.
+We use the results in \cite{delaPea:2005}; since this is not among this paper's contributions, we do not go beyond giving a general outline of these results.
 \\

### 2019-06-13 emsoft-2019/V2/intro.tex
updates

@@
 \Mahmoud{Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.}
-Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{online computations}
+Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{massive online computations}
 or to certify a complex optimization routine \Mahmoud{\cite{memoryMPC}}.

### 2019-06-13 emsoft-2019/V2/finite_precision.tex
explicitly say what Daisy does

@@
 error of the result by tracking worst-case errors at every operation. Given a
-word length for each value, several tools automatically determine the number of
+word length for each value, several tools\Eva{, including the tool Daisy which we use,} automatically determine the number of
 integer bits needed and compute roundoff errors using a dataflow analysis~\cite{Daisy,Gappa}.
@@
 fixed-point arithmetic and the error analysis, is challenging to do manually.  
-Automated mixed-precision tuning tools usually perform a search: they repeatedly
+Automated mixed-precision tuning tools\Eva{, including Daisy,} usually perform a search: they repeatedly
 select a candidate mixed-precision assignment (i.e. different word lengths for

### 2019-06-13 emsoft-2019/V2/response.tex
Rocco minor comments

@@
 $32$ KB) and hence $21$ KB is considered as a significant save.\\
-\textbf{Do memory savings in our approach come with a run-time cost?} (Reviewer 1)
-\\
-No. It should be noticed that savings are not affecting the run-time as synthesizing of the controller and the corresponding mixed precision computations are all performed offline.\\
+\textbf{Do memory savings in our approach come with a run-time cost?} (Reviewer 1)\\
+No.
+It should be noticed that savings are not affecting the run-time as synthesizing of the controller and the corresponding mixed precision computations are all performed offline.\Rocco{On the other hand, mixed-precision naturally requires casting operators, which may potentially affect the running time.}\\
 \textbf{Do achieved savings correspond also to actual implementation?} (Reviewers 1 $\&$ 4)\\
@@
 In our experiments, computation of incorrect region selection takes only a few minutes for our largest tested benchmarks.
-\underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}}\\
+%\underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}}
+\\
+\Rocco{The complexity of precision tuning is linear with respect to the number of regions and hyperplanes.
+So, $P+\bar n_f\times P$ is an upper bound for the number of problems we need to encode in Daisy.
+In each encoding, the uniform-precision detection takes linear steps before convergence.
+It starts from 1-bit and increases the precision one by one until the first valid configuration.
+The complexity of mixed-precision tuning, with delta-debugging, is $n\times log(n)$ in average, and bounded by $n^2$ in the worst case, with n number of variables.}\\
 \textbf{Extension of the proposed method into the nonlinear dynamical systems} (Reviwer 2)\\

### 2019-06-14 emsoft-2019/V2/intro.tex
updates

--- 2019-06-13 emsoft-2019/V2/intro.tex
@@
 \Mahmoud{Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.}
-Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{online computations}
+Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{perform massive online computations}
 or to certify a complex optimization routine \Mahmoud{\cite{memoryMPC}}.

### 2019-07-12 emsoft-2019/camera_ready/response.tex
camera_ready folder is added

--- 2019-06-13 emsoft-2019/V2/response.tex
@@
 \Mahmoud{\section{Revision Letter}	
-We thank the reviewers for the detailed and useful feedback on our submission. First, we will detail the main changes we made. Afterwards, we provide responses to your specific questions. 
+We thank the reviewers for the detailed and useful feedback on our submission. First, we will detail the main changes we made. Below, we provide responses to your specific questions. 
 \subsection{Changes}
@@
 Typical memory of these processors is in the order of tens of kilobytes (e.g.
-$32$ KB) and hence $21$ KB is considered as a significant save.\\
+$32$ KB) and hence $21$ KB is considered as a significant saving.\\
 \textbf{Do memory savings in our approach come with a run-time cost?} (Reviewer 1)\\
 No.
-It should be noticed that savings are not affecting the run-time as synthesizing of the controller and the corresponding mixed precision computations are all performed offline.\Rocco{On the other hand, mixed-precision naturally requires casting operators, which may potentially affect the running time.}\\
+It should be noticed that savings are not affecting the run-time as synthesizing of the controller and the corresponding mixed precision computations are all performed offline.
+The output of our analysis is an implementation in mixed precision arithmetic that checks which polyhedral region the current state belongs to and computes the corresponding affine mapping.
+This computation is fast.
+See below for further discussion.\\
 \textbf{Do achieved savings correspond also to actual implementation?} (Reviewers 1 $\&$ 4)\\
@@
 \\
-\Rocco{The complexity of precision tuning is linear with respect to the number of regions and hyperplanes.
-So, $P+\bar n_f\times P$ is an upper bound for the number of problems we need to encode in Daisy.
-In each encoding, the uniform-precision detection takes linear steps before convergence.
+The complexity of precision tuning is linear with respect to the number of regions and hyperplanes. So, $P+\bar n_f\times P$ is an upper bound for the number of problems we need to encode in Daisy.
+In each encoding, the uniform-precision detection takes linear number of steps before convergence.
 It starts from 1-bit and increases the precision one by one until the first valid configuration.
-The complexity of mixed-precision tuning, with delta-debugging, is $n\times log(n)$ in average, and bounded by $n^2$ in the worst case, with n number of variables.}\\
+The complexity of mixed-precision tuning, with delta-debugging, is $n\times log(n)$ in average, and bounded by $n^2$ in the worst case, with n number of variables.\\
 \textbf{Extension of the proposed method into the nonlinear dynamical systems} (Reviwer 2)\\
@@
 We use the results in \cite{delaPea:2005}; since this is not among this paper's contributions, we do not go beyond giving a general outline of these results.
+In particular, we omitted the proof from \cite{delaPea:2005}.
 \\
@@
 \textbf{Termination of the algorithm for robust EMPC design (Reviewer 4)}\\
-From theoretical point of view, the numerical error does not necessarily converge as each new designed controller may differ from the previous ones.
+From a theoretical point of view, the numerical error does not necessarily converge as each new designed controller may differ from the previous ones.
 Therefore, it is not easy to give an upper bound over the number of times that the robust MPC design needs to be repeated.
@@
 This Lipschitz constant can be quite large, leading into a very conservative bound on maximum number of iterations before convergence.
-However, from experimental point of view, using a reasonable $\varepsilon_{SAFE}$, our observations show that convergence always happened after only a few iterations.
+However, from an experimental point of view, using a reasonable $\varepsilon_{SAFE}$, our observations show that convergence always happened after only a few iterations.
 }

### 2019-07-12 emsoft-2019/camera_ready/Cont_Syn.tex
camera_ready folder is added

--- 2019-06-11 emsoft-2019/V2/Cont_Syn.tex
@@
  assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
- $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@\Mahmoud{//the width of the uncertain area}@>
+ $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@\Mahmoud{//width of the tube}@>
 

### 2019-07-12 emsoft-2019/camera_ready/finite_precision.tex
camera_ready folder is added

--- 2019-06-11 emsoft-2019/V2/finite_precision.tex
@@
 error of the result by tracking worst-case errors at every operation. Given a
-word length for each value, several tools automatically determine the number of
+word length for each value, several tools\Mahmoud{, including the tool Daisy which we use,} automatically determine the number of
 integer bits needed and compute roundoff errors using a dataflow analysis~\cite{Daisy,Gappa}.
@@
 fixed-point arithmetic and the error analysis, is challenging to do manually.  
-Automated mixed-precision tuning tools usually perform a search: they repeatedly
+Automated mixed-precision tuning tools\Mahmoud{, including Daisy,} usually perform a search: they repeatedly
 select a candidate mixed-precision assignment (i.e. different word lengths for

### 2019-07-17 emsoft-2019/camera_ready/Cont_Syn.tex
inserting responses into the text

@@
 requiring the user to provide $\varepsilon_Q$ as the input. 
-\Mahmoud{
-	\begin{remark}\label{rem:eps_Q}
-		Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up-to $10^{-2}$.
+%\Mahmoud{
+%	\begin{remark}\label{rem:eps_Q}
+%		Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up-to $10^{-2}$.
 Increasing the $\varepsilon_Q$ leads into more memory save over $H$ and $K$, while requiring more precision for $F$ and $G$ (\autoref{tab:di}).
@@
 However, this is usually not the case over reasonable choices for $\varepsilon_Q$.
-	\end{remark}}
+%	\end{remark}}
 
@@
 for mixed-precision tuning tools to work correctly.
+\Mahmoud{Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up-to $10^{-2}$.
+Increasing the $\varepsilon_Q$ leads into more memory save over $H$ and $K$, while requiring more precision for $F$ and $G$.
+Of course, too large values for $\varepsilon_Q$ can result in failure of RMPC design.
+However, this is usually not the case over reasonable choices for $\varepsilon_Q$.}
 Line 5 computes the width of the tubes $\varepsilon$ as shown in~\autoref{eq:epsilontot},
@@
 Then we call Daisy with the expressions of the region bounds given by $H$
-and $K$, now with the error bound $\varepsilon_Q$ (line 13).
-
+and $K$, now with the error bound $\varepsilon_Q$ (line 13).\Mahmoud{
+\begin{remark}
+From a theoretical point of view, the error due to wrong region selection does not necessarily converge as each new designed controller may differ from the previous ones.
+Therefore, it is not easy to give an upper bound over the number of times that the robust MPC design needs to be repeated.
+However, by rewriting \autoref{eq:RMPC_prob}, we have
+\begin{align*}
+\label{eq:argmin}
+&u_0(x_0,\Delta),\cdots,u_{N-1}(x_0,\Delta)=\\
+&argmin \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
+&\text{s.t.} \quad x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+%\quad &u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}_{\Delta},\,\,\forall i\in\{0,1,\cdots,N\},
+\end{align*}
+one can use results on continuity of $argmin$ function, assuming its unique solution to every $\Delta$, to  compute the Lipschitz constant for it over variations of $\Delta$.
+The computed Lipschitz constant will be only dependent on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used to evaluate the maximum error over incorrect region selection.
+This Lipschitz constant can be quite large, leading into a very conservative bound on maximum number of iterations before convergence.
+However, from an experimental point of view, using a reasonable $\varepsilon_{SAFE}$, our observations show that convergence always happened after only a few iterations.
+\end{remark}}
 In both cases, Daisy determines a quantization of the input matrices (Daisy also
@@
 Daisy will return a fixed-point precision with a large number bits, but will not
-fail.
+fail.\\
+\Mahmoud{In \cite{Alessio2009} it is shown that the upper bound over the number of regions $P$ is $2^q$, where $q$ denotes the total number of constraints in \autoref{eq:RMPC_prob}.
+In theory one cannot find an upper bound for the maximum number of hyperplanes enclosing a region.
+To compute the incorrect region selection error, assuming that each partition at most has $\bar n_f$ faces, in the worst case $i\times\bar n_f\times 2^q$ affine computations would be enough, where $i$ denotes the number of times that RMPC design is repeated for updated $\Delta$s.
+In our experiments, computation of incorrect region selection takes only a few minutes for our largest tested benchmarks.
+%\underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}}
+\\
+The complexity of precision tuning is linear with respect to the number of regions and hyperplanes. So, $P+\bar n_f\times P$ is an upper bound for the number of problems we need to encode in Daisy.
+In each encoding, the uniform-precision detection takes linear number of steps before convergence.
+It starts from 1-bit and increases the precision one by one until the first valid configuration.
+The complexity of mixed-precision tuning, with delta-debugging, is $n\times log(n)$ in average, and bounded by $n^2$ in the worst case, with n number of variables.}
 

### 2019-07-17 emsoft-2019/camera_ready/Error_Analysis.tex
camera_ready folder is added
inserting responses into the text

--- 2019-06-11 emsoft-2019/V2/Error_Analysis.tex
@@
 \begin{equation*}
-\hat{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
+\Mahmoud{\bar{\mathcal B}_{ij}} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
 \end{equation*}
@@
 % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
- \end{equation}
+ \end{equation}\Mahmoud{ 
+ \begin{remark}
+ 	Our formulation is general enough to take the effect of measurement/process noise into account.
+More specifically, $\Delta$ in $\mathcal{W}_{\Delta}$ can in general give upper-bound over the sum of uncertainties with different sources.
+However, this is not subject of study of the current paper.
+Moreover, to cover nonlinear systems, one approach is to linearize them around an appropriately selected equilibrium point of the system and to model the differences as a bounded disturbance as in \autoref{eq:RMPC_prob}.
+Taking the upper bound over nonlinearities into account will result in enlarging $\Delta$ which characterizes $\mathcal{W}_{\Delta}$.
+For reasonable values of $\Delta$, in principle RMPC design should work successfully.
+Further, it should be noticed that the rest of analysis (over MATLAB and Daisy) do not rely on the LTI property of the under study system and could be adjusted for other families of controllers.
+However, such analysis are beyond the scope of this paper as (perturbed) LTI systems are considered as an important class of dynamical systems.
+ 	\end{remark}}
 
@@
 $p$ and can also be called explicitly without the precision optimization.
-
+\Mahmoud{\begin{remark}
+	MATLAB and Daisy are solely used for offline computations.
+The output of our algorithm contains (almost) all the information required for implementation of the verified controller over embedded systems.
+Therefore, the same savings can be expected when the controller is implemented on an actual embedded system.
+\end{remark}}
 \begin{comment}

### 2019-07-17 emsoft-2019/camera_ready/Motiv.tex
inserting responses into the text

--- 2019-06-11 emsoft-2019/V2/Motiv.tex
@@
 
-\begin{figure}[t]
-	\centering
-  \begin{subfigure}[b]{0.33\columnwidth}
-      \includegraphics[width=\textwidth]{Figs/inverted_pendulum.pdf}
-      \vspace{0.05cm}
-      \caption{}
-  \end{subfigure}
-  %~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-  \begin{subfigure}[b]{0.66\columnwidth}
-      \includegraphics[width=\textwidth]{Figs/regs.jpg}
-      \caption{}
-  \end{subfigure}
-	\caption{(a) Inverted pendulum; (b) 2D plot of polyhedral partitions for an EMPC applied to the inverted pendulum.}
-	\label{fig:inverted_pendulum}
-\end{figure}
+%\begin{figure}[t]
+%	\centering
+%  \begin{subfigure}[b]{0.33\columnwidth}
+%      \includegraphics[width=\textwidth]{Figs/inverted_pendulum.pdf}
+%      \vspace{0.05cm}
+%      \caption{}
+%  \end{subfigure}
+%  %~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+%  \begin{subfigure}[b]{0.66\columnwidth}
+%      \includegraphics[width=\textwidth]{Figs/regs.jpg}
+%      \caption{}
+%  \end{subfigure}
+%	\caption{(a) Inverted pendulum; (b) 2D plot of polyhedral partitions for an EMPC applied to the inverted pendulum.}
+%	\label{fig:inverted_pendulum}
+%\end{figure}
 
@@
 In our example, we compute an incorrect region selection error $e = 0.019$, which is larger
-than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount \Mahmoud{$\varepsilon_{SAFAE}=0.031$} to
+than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount \Mahmoud{$\varepsilon_{SAFE}=0.031$} to
 $\Delta_1 = 0.05$ and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.

### 2019-07-17 emsoft-2019/camera_ready/RMPC_Daisy.tex
inserting responses into the text

--- 2019-06-11 emsoft-2019/V2/RMPC_Daisy.tex
@@
 The most straightforward technique is a linear search over all polyhedral regions (Fig.~\ref{lst:caseof}).
-
+\Mahmoud{
+\begin{remark}
+	The total time to evaluate the PWA function for a given $x_k$ in \autoref{eq:affine_map} consists of two steps:
+	\begin{itemize}
+		\item Selecting the region $\mathcal R_i$ such that $x_k\in \mathcal R_i$.
+		\item To evaluate the corresponding affine map $F_i x_k +G_i$. 
+	\end{itemize}
+	Evaluating the affine map is straightforward and requires less computational effort compared to the region selection step.
+Direct implementation of region selection (\autoref{lst:caseof}) is simple, but inefficient.
+More efficiency can be achieved by leveraging binary search tree structures (e.g.
+\cite{Mnnigmann:2011}).
+In general, explicit MPC is well-known for its high-speed implementation over embedded systems with low computational power.
+\cite{Johansen:2007} shows that explicit MPCs with hundreds of regions can be implemented on application specific integrated circuit (ASIC) with about $20000$ gates, leading to computation times in the order of $1\mu s$.
+In \cite{Bemporad:2006}, it is shown that for typical problems evaluating the explicit MPC takes significantly shorter time in comparison to solving on-line QP.
+\end{remark}
+}
 \begin{figure}[t]

### 2019-07-17 emsoft-2019/camera_ready/intro.tex
inserting responses into the text

--- 2019-06-14 emsoft-2019/V2/intro.tex
@@
 Synthesis of the controller and the corresponding precisions are all performed offline.}
-
+\Mahmoud{It should be noticed that EMPC is a class of controllers which is mainly appropriate for implementation over processors with limited computational power and memory.
+Typical memory of these processors is in the order of tens of kilobytes (e.g.
+$32$ KB) and hence $21$ KB is considered as a significant saving.
+Also, memory savings are not affecting the run-time as synthesizing of the controller and the corresponding mixed precision computations are all performed offline.}\\
 In summary, our contributions are:

### 2019-07-17 emsoft-2019/camera_ready/Cont_Syn.tex
colors-->blue

@@
 for mixed-precision tuning tools to work correctly.
-\Mahmoud{Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up-to $10^{-2}$.
+\Mahmoudd{Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up-to $10^{-2}$.
 Increasing the $\varepsilon_Q$ leads into more memory save over $H$ and $K$, while requiring more precision for $F$ and $G$.
@@
 Then we call Daisy with the expressions of the region bounds given by $H$
-and $K$, now with the error bound $\varepsilon_Q$ (line 13).\Mahmoud{
+and $K$, now with the error bound $\varepsilon_Q$ (line 13).\Mahmoudd{
 \begin{remark}
@@
 fail.\\
-\Mahmoud{In \cite{Alessio2009} it is shown that the upper bound over the number of regions $P$ is $2^q$, where $q$ denotes the total number of constraints in \autoref{eq:RMPC_prob}.
+\Mahmoudd{In \cite{Alessio2009} it is shown that the upper bound over the number of regions $P$ is $2^q$, where $q$ denotes the total number of constraints in \autoref{eq:RMPC_prob}.
 In theory one cannot find an upper bound for the maximum number of hyperplanes enclosing a region.

### 2019-07-17 emsoft-2019/camera_ready/Error_Analysis.tex
colors-->blue

@@
 % \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
- \end{equation}\Mahmoud{ 
+ \end{equation}\Mahmoudd{ 
  \begin{remark}
@@
 $p$ and can also be called explicitly without the precision optimization.
-\Mahmoud{\begin{remark}
+\Mahmoudd{To encourage reproducible research, our implementation is made available.
+\footnote{Please insert the link to our package here!!!}}
+\Mahmoudd{\begin{remark}
 	MATLAB and Daisy are solely used for offline computations.

### 2019-07-17 emsoft-2019/camera_ready/intro.tex
colors-->blue

@@
 Synthesis of the controller and the corresponding precisions are all performed offline.}
-\Mahmoud{It should be noticed that EMPC is a class of controllers which is mainly appropriate for implementation over processors with limited computational power and memory.
+\Mahmoudd{It should be noticed that EMPC is a class of controllers which is mainly appropriate for implementation over processors with limited computational power and memory.
 Typical memory of these processors is in the order of tens of kilobytes (e.g.

### 2019-07-25 emsoft-2019/camera_ready/Cont_Syn.tex
polishing the text

--- 2019-07-12 emsoft-2019/camera_ready/Cont_Syn.tex
@@
  assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
- $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@\Mahmoud{//width of the tube}@>
+ $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@$\quad$//\,\,width of the tube@>
 
@@
 for mixed-precision tuning tools to work correctly.
+\Mahmoudd{Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up to $10^{-2}$.
+Increasing $\varepsilon_Q$ leads into more memory save over $H$ and $K$ while requiring more precision for $F$ and $G$.
+Of course, too large values for $\varepsilon_Q$ can result in failure of the RMPC design.
+However, this is usually not the case over reasonable choices for $\varepsilon_Q$.}
 Line 5 computes the width of the tubes $\varepsilon$ as shown in~\autoref{eq:epsilontot},
@@
 
+\smallskip
+\noindent
+\Mahmoudd{
+\textbf{Termination of the algorithm.}
+From a theoretical point of view, the error due to a wrong region selection does not necessarily converge since each new designed controller may differ from the previous ones.
+Therefore, it is not easy to give an upper bound over the number of times that the robust MPC design needs to be repeated.
+However, by rewriting \autoref{eq:RMPC_prob}, we have
+\begin{align*}
+\nu_0(x_0, \Delta),\ldots&,\nu_{N-1}(x_0,\Delta)=\\
+argmin & \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
+\quad  \text{s.t.} \quad & x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+\quad \quad & u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
+\quad \quad & u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}_{\Delta},\,\,\forall i\in\{0,1,\cdots,N\}.
+%&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
+\end{align*}
+Assuming the optimization has a unique solution for every $\Delta$, 
+one may use the results on continuity of the $argmin$ function to compute an upper bound on the Lipschitz constant of the optimal input $\nu = \kappa(x)$ in Equation~\eqref{eq:affine_map} that holds for all $\Delta$.
+The computed bound will only depend on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used to evaluate the maximum error over incorrect region selection.
+This bound can be quite large, leading to a very conservative bound on the maximum number of iterations before convergence.
+From an experimental point of view, our observations show that using a reasonable $\varepsilon_{SAFE}$, convergence always reached after only a few iterations.}
+
+\smallskip
+\noindent
+\Mahmoudd{
+\textbf{Computational complexity.} It is shown in \cite{Alessio2009} that the number of regions $P$ in Equation~\eqref{eq:affine_map} is upper bounded by $2^q$, where $q$ is the total number of constraints in \autoref{eq:RMPC_prob}.
+%In theory, one cannot find an upper bound for the maximum number of hyperplanes enclosing a region.
+Assuming that each region has at most $\bar n_f$ hyperplanes, computation of the incorrect region selection error requires at most $i\times\bar n_f\times 2^q$ affine computations, where $i$ denotes the number of times the RMPC design updates $\Delta$ before convergence.
+In our experiments, the computation of the incorrect region selection error takes only a few minutes for our largest tested benchmarks.
+%\underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}}
+\\
+The complexity of the precision tuning is linear with respect to the number of regions and hyperplanes.
+So, $(P+\bar n_f\times P)$ is an upper bound for the number of problems we need to encode in Daisy.
+In each encoding, the uniform-precision detection takes linear number of steps before convergence.
+It starts from 1-bit and increases the precision one by one until the first valid configuration.
+The complexity of mixed-precision tuning with delta-debugging is $n\times log(n)$ in average, and bounded by $n^2$ in the worst case, with $n$ being the number of variables.}
+
 % In case the conditional in line 9 succeeds, the precision tuning phase starts.

### 2019-07-25 emsoft-2019/camera_ready/Error_Analysis.tex
polishing the text

--- 2019-06-11 emsoft-2019/V2/Error_Analysis.tex
@@
 \begin{equation*}
-\hat{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
+\bar{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
 \end{equation*}
@@
  \end{equation}
+
+ %\Mahmoudd{ 
+ %\begin{remark}
+ %	Our formulation is general enough to take the effect of measurement/process noise into account.
+More specifically, $\Delta$ in $\mathcal{W}_{\Delta}$ can in general give upper-bound over the sum of uncertainties with different sources.
+However, this is not subject of study of the current paper.
+Moreover, to cover nonlinear systems, one approach is to linearize them around an appropriately selected equilibrium point of the system and to model the differences as a bounded disturbance as in \autoref{eq:RMPC_prob}.
+Taking the upper bound over nonlinearities into account will result in enlarging $\Delta$ which characterizes $\mathcal{W}_{\Delta}$.
+For reasonable values of $\Delta$, in principle RMPC design should work successfully.
+Further, it should be noticed that the rest of analysis (over MATLAB and Daisy) do not rely on the LTI property of the under study system and could be adjusted for other families of controllers.
+However, such analysis are beyond the scope of this paper as (perturbed) LTI systems are considered as an important class of dynamical systems.
+ %	\end{remark}}
 
@@
 $p$ and can also be called explicitly without the precision optimization.
-
+\Mahmoudd{To encourage reproducible research, our implementation is made available online.\footnote{\url{https://github.com/rospoly/rmpc-daisy}}}
+\Mahmoudd{\begin{remark}
+	Note that we use MATLAB and Daisy solely for offline computations.
+The output of our algorithm contains (almost) all the information required for implementation of the verified controller over embedded systems.
+Therefore, the same savings can be expected when the controller is implemented on an actual embedded system.
+\end{remark}}
 \begin{comment}

### 2019-07-25 emsoft-2019/camera_ready/Motiv.tex
polishing the text

@@
 		\node [block,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
-		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set \Mahmoud{$\mathcal W_{\Delta}$}};
-		\Mahmoud{\node [block1,below = 0.8cm of RMPC] (highprec) {High-precision controller (\autoref{eq:affine_map})};}
+		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
+		\node [block1,below = 0.8cm of RMPC] (highprec) {\Mahmoud{High-precision controller (\autoref{eq:affine_map})}};
 		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
@@
 		\node [block2, right=1.3cm of decide,
-		node distance=1cm] (delta) {\Mahmoud{ $\Delta=e+\varepsilon_{SAFE}$}};
+		node distance=1cm] (delta) {$\Delta=e+\varepsilon_{SAFE}$};
 		\node [block1,below = 0.8cm of done] (output) {Low-precision controller \Mahmoud{(\autoref{eq:affine_map})}};
@@
 In our example, we compute an incorrect region selection error $e = 0.019$, which is larger
-than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount \Mahmoud{$\varepsilon_{SAFE}=0.031$} to
+than $\Delta_0=0.01$. We therefore increase the disturbance bound by a fixed amount $\varepsilon_{SAFE}=0.031$ to
 $\Delta_1 = 0.05$ and enlarge the disturbance set as $\mathcal W_{\Delta_1}$.
@@
 The mixed-precision implementation returned by Daisy requires $6084$ bits.
-Thus, \Mahmoud{for this introductory example,} the mixed-precision implementation takes about $10\%$ less memory compared 
+Thus, for this introductory example, the mixed-precision implementation takes about $10\%$ less memory compared 
 to the smallest uniform precision implementation that respects $\Delta_1$,

### 2019-07-25 emsoft-2019/camera_ready/RMPC_Daisy.tex
colors-->blue
polishing the text

--- 2019-06-11 emsoft-2019/V2/RMPC_Daisy.tex
@@
 Matrices $A\in \reals^{n\times n}$, $B\in \reals^{n\times m}$ and $E\in \reals^{n\times d}$  capture respectively the effects of current state, input and disturbance on the next state.
-We assume the disturbance $w$ belongs to a set $\Mahmoud{\mathcal{W}_{\Delta}}$ where $\Mahmoud{\mathcal{W}_{\Delta}}$ is a polyhedral set \Mahmoud{defined by \autoref{eq:W_delta}}.
+We assume the disturbance $w$ belongs to a set $\mathcal{W}_{\Delta}$ where $\mathcal{W}_{\Delta}$ is a polyhedral set defined in \autoref{eq:W_delta}.
 In this paper, we focus on the robust formulation of MPC which at each time step
@@
 \quad &u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
-&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\Mahmoud{\mathcal{W}_{\Delta}},\,\,\forall i\in\{0,1,\cdots,N\},
+&u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}_{\Delta},\,\,\forall i\in\{0,1,\cdots,N\},
 %&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
@@
 \end{theorem}
-The essential idea behind this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and transform the optimization \eqref{eq:RMPC_prob} into the following quadratic program:
+
+The proof of this theorem can be found in \cite{delaPea:2005}.
+The essential idea behind the theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and transform the optimization \eqref{eq:RMPC_prob} into the following quadratic program:
 %\begin{align}
@@
 
-The implementation of the controller stores the matrices $F_i,G_i,H_i,K_i$ for all $i\in\{1,2,\ldots,P\}$. 
+The implementation of the controller stores matrices $F_i,G_i,H_i,K_i$ for all $i\in\{1,2,\ldots,P\}$. 
 At each time step $k$, the current state $x_k$ is used to detect the polyhedral region 
@@
 The most straightforward technique is a linear search over all polyhedral regions (Fig.~\ref{lst:caseof}).
+\Mahmoudd{
+\begin{remark}
+	The total time to evaluate the PWA function in \autoref{eq:affine_map} for a given $x_k$ consists of two steps: (a) selecting the region $\mathcal R_i$ such that $x_k\in \mathcal R_i$ and (b) evaluating the corresponding affine map $F_i x_k +G_i$.
+	Evaluating the affine map is straightforward and requires less computational effort compared to the region selection step.
+Direct implementation of region selection (\autoref{lst:caseof}) is simple, but inefficient.
+More efficiency can be achieved by leveraging binary search tree structures (e.g.
+\cite{Mnnigmann:2011}).\\
+	In general, explicit MPC is well-known for its high-speed implementation over embedded systems with low computational power.
+The authors in \cite{Johansen:2007} show that explicit MPCs with hundreds of regions can be implemented on application specific integrated circuits (ASIC) with about $20000$ gates, leading to computation times in the order of $1\mu s$.
+It is shown in \cite{Bemporad:2006} that for typical problems evaluating the explicit MPC takes significantly shorter time in comparison to solving on-line quadratic programs.
+\end{remark}}
+
+\Mahmoudd{ 
+ \begin{remark}
+ It should be noticed that EMPC is a class of controllers specifically proposed for linear time invariant (LTI) systems.
+To cover nonlinear systems, one approach is to linearize them around an appropriately selected equilibrium point of the system and to model the differences as a bounded disturbance as in \autoref{eq:RMPC_prob}.
+Taking the upper bound over nonlinearities into account will result in enlarging $\Delta$ which characterizes $\mathcal{W}_{\Delta}$.
+For reasonable values of $\Delta$, in principle RMPC design should work successfully.
+Further, it should be noticed that the rest of analysis in the sequel (over MATLAB and Daisy) do not rely on the LTI property of the system under study and could be adjusted for other families of controllers.
+ %However, such analysis are beyond the scope of this paper as (perturbed) LTI systems are considered as an important class of dynamical systems.
+\end{remark}}
 

### 2019-07-25 emsoft-2019/camera_ready/conclusion.tex
camera_ready folder is added
polishing the text

--- 2019-04-12 emsoft-2019/conclusion.tex
@@
+% !TEX root = main.tex
 \section{Conclusion}
@@
 ranging up to 20\%. 
-In addition, the static analysis scales to controllers with hundreds of regions.
+In addition, the static analysis scales to controllers with hundreds of regions.\\
+One exciting direction for future work would be to investigate the effect of stochastic disturbances on the proposed methodology and find a scheme to reduce statistically the memory footprint of the controller implementation.
+
+%\Mahmoud{All in all, using our proposed method, model predictive control under input and state constraints can be achieved while the memory footprint is minimized.
+By using our method, memory requirement for implementation of explicit MPCs over the industrial embedded systems reduces.
+One exciting direction for future work would be to investigate effect of stochastic noises on the proposed design methodology.}

### 2019-07-25 emsoft-2019/camera_ready/finite_precision.tex
polishing the text

--- 2019-06-11 emsoft-2019/V2/finite_precision.tex
@@
 error of the result by tracking worst-case errors at every operation. Given a
-word length for each value, several tools automatically determine the number of
+word length for each value, several tools, including the tool Daisy which we use, automatically determine the number of
 integer bits needed and compute roundoff errors using a dataflow analysis~\cite{Daisy,Gappa}.
@@
 To reduce memory usage and increase efficiency, we want to choose as short word
-lengths as possible, \Mahmoud{as this way memory footprint is minimized and run-time is not influenced.} Mixed-precision tuning tools automatically determine possibly different
+lengths as possible. This will minimize the memory footprint without influencing the run-time. Mixed-precision tuning tools automatically determine possibly different
 word lengths for different values~\cite{DaisyTuning,Lee2006}. Compared to uniform precision (or word length),
@@
 fixed-point arithmetic and the error analysis, is challenging to do manually.  
-Automated mixed-precision tuning tools usually perform a search: they repeatedly
+Automated mixed-precision tuning tools, including Daisy, usually perform a search: they repeatedly
 select a candidate mixed-precision assignment (i.e. different word lengths for

### 2019-07-25 emsoft-2019/camera_ready/intro.tex
polishing the text

--- 2019-06-14 emsoft-2019/V2/intro.tex
@@
 and obtaining the optimal action for the next time instance. 
-Moreover, the optimization solver needs to be certified when using MPC in safety critical applications \Mahmoud{\cite{Alessio2009}}.
+Moreover, the optimization solver needs to be certified when using MPC in safety critical applications~\cite{Alessio2009}.
 
@@
 problem for MPC can be modeled as a quadratic program, and EMPC techniques solve the optimization problem
-using multi-parametric programming techniques.
+using multi-parametric programming.
 The explicit solution is representable as a partition of the controller domain into a number of polyhedral regions,
 and an affine map for each region. 
-\Mahmoud{Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.}
-Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to \Mahmoud{perform massive online computations}
-or to certify a complex optimization routine \Mahmoud{\cite{memoryMPC}}.
+Given the current state, EMPC draws the corresponding affine mapping out of a stored lookup table and evaluates the control.
+Explicit MPC thus expands the class of systems being controlled by MPC strategies, by taking out the need to perform massive online computations
+or to certify a complex optimization routine \cite{memoryMPC}.
 
 However, there are still bottlenecks in implementing EMPC on resource-constrained embedded micro-controllers.
-First, implementations of EMPCs \Mahmoud{over industrial micro-controllers with limited memory} can suffer from large memory usage, because the solution of the optimization
+First, implementations of EMPCs on industrial micro-controllers with limited memory can suffer from large memory usage, because the solution of the optimization
 problem can involve many (often hundreds) of regions~\cite{memoryMPC}.
@@
 Our proposed method iteratively solves a robust version of MPC 
-\Mahmoud{that} considers finite-precision implementation errors as disturbances
+that considers finite-precision implementation errors as disturbances
 in the dynamics \cite{RamirezC06}; see~\autoref{fig:overview}.
@@
 
-We have applied our technique on a number of standard benchmark examples. \Mahmoud{Taking all these benchmarks into account,}
-our algorithm finds mixed-precision implementations \Mahmoud{that} save up to 20.9\%
+We have applied our technique on a number of standard benchmark examples. Taking all these benchmarks into account,
+our algorithm finds mixed-precision implementations that save up to 20.9\%
 memory (on average, 12.6\%) in controller implementations over a minimal
@@
 Synthesis of the controller and the corresponding precisions are all performed offline.}
-
+\Mahmoudd{We note that EMPC is a class of controllers that is mainly appropriate for implementation over processors with limited computational power and memory.
+Typical memory of these processors is in the order of tens of kilobytes (e.g.
+$32$ KB) and hence $21$ KB is considered as a significant saving.
+Also, the memory savings do not affect the run-time since  the controller synthesis and the corresponding mixed precision computations are all performed offline.}\\
 In summary, our contributions are:
 \begin{itemize}
-\item We provide an end-to-end automatic tuning algorithm for robust explicit MPC that ensures \Mahmoud{that}
-hard constraints on the state are met despite numerical errors;
+\item We provide an end-to-end automatic tuning algorithm for robust explicit MPC that ensures satisfaction of
+hard constraints on the state despite numerical errors;
 \item We design a static and scalable error analysis algorithm for piecewise affine functions to bound

### 2019-07-26 emsoft-2019/camera_ready/Motiv.tex
class is updated into acmsmall

@@
 \begin{figure}[t]
-\centering
+%\centering
 	\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
@@
 	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
+	%\begin{center}
 	{
 
-		%\begin{center}
+		%\centering
 		%\hspace*{\fill} 
@@
 		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
-		\node [block1,below = 0.8cm of RMPC] (highprec) {\Mahmoud{High-precision controller (\autoref{eq:affine_map})}};
+		\node [block1,below = 0.8cm of RMPC] (highprec) {High-precision controller (\autoref{eq:affine_map})};
 		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
@@
 		node distance=1cm] (delta) {$\Delta=e+\varepsilon_{SAFE}$};
-		\node [block1,below = 0.8cm of done] (output) {Low-precision controller \Mahmoud{(\autoref{eq:affine_map})}};
+		\node [block1,below = 0.8cm of done] (output) {Low-precision controller (\autoref{eq:affine_map})};
 		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
-		\node at (9,-.25) {$e$};
+		%\node at (9,-.25) {$e$};
 
@@
 \begin{equation*}
-\resizebox{.9\hsize}{!}{$
+%\resizebox{.9\hsize}{!}{$
 \begin{bmatrix}
@@
 0.05&-9.67
-\end{bmatrix}x_k+4.02$}
+\end{bmatrix}x_k+4.02%$}
 \end{equation*}

### 2019-07-26 emsoft-2019/camera_ready/RMPC_Daisy.tex
class is updated into acmsmall

@@
 \begin{figure}[t]
-\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
+%\begin{center}
+%\begin{tabular}{c}
+\begin{lstlisting}[mathescape=true,frame=lines,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
 if ($H_{1}\statevar \leq K_{1}$) then $v_{k}=F_1x_k+G_1$
@@
 \end{lstlisting}
+%\end{tabular}
+%\end{center}
 \caption{Structure of an explicit MPC controller}

### 2019-07-29 emsoft-2019/camera_ready/Cont_Syn.tex
My pass on the final version.

@@
 issue. In order to derive $p$ for some expression, Daisy and any other precision
-tuning tool requires an error bound which should be satisfied. I.e. either a
+tuning tool requires an error bound which should be satisfied. That is, either a
 precision $p$ is given, and we can compute an error bound, or the error bound is
 given and we can derive a precision $p$. We cannot do both at the same time; the
-problem would be underconstrained. We solve this chicken-and-egg issue by
-requiring the user to provide $\varepsilon_Q$ as the input. 
+problem would be underconstrained. We solve this chicken-and-egg problem by
+requiring the user to provide $\varepsilon_Q$ as part of the input.
 %\Mahmoud{
@@
 
-We need to distribute the available `disturbance budget' among the two error
+We need to distribute the available ``disturbance budget'' among the two error
 sources: error due to selecting the wrong region, which is given by the
@@
 and $\hat{K}$ are represented, the more approximate $\hat{F}$ and
-$\hat{G}$ need to be and vice versa.
+$\hat{G}$ need to be to fit into the disturbance budget, and vice versa.
 We note that one could straight-forwardly extend our algorithm to include an
@@
 
-Unlike the initial $\Delta$, $\varepsilon_Q$ needs to be strictly positive (line 4)
+Unlike the initial $\Delta$, the parameter $\varepsilon_Q$ needs to be strictly positive (line 4)
 for mixed-precision tuning tools to work correctly. 
-\Mahmoudd{Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up to $10^{-2}$.
-Increasing $\varepsilon_Q$ leads into more memory save over $H$ and $K$ while requiring more precision for $F$ and $G$.
-Of course, too large values for $\varepsilon_Q$ can result in failure of the RMPC design.
-However, this is usually not the case over reasonable choices for $\varepsilon_Q$.}
+Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up to $10^{-2}$. 
+\RM{repetition:}
+Increasing $\varepsilon_Q$ leads to more memory savings over $H$ and $K$ while requiring more precision for $F$ and $G$. 
+\RM{end}
+Of course, a large value for $\varepsilon_Q$ can result in failure of the RMPC design. 
+\RM{imprecise:}However, this is usually not the case over reasonable choices for $\varepsilon_Q$.
+\RM{omit?}
 Line 5 computes the width of the tubes $\varepsilon$ as shown in~\autoref{eq:epsilontot},
@@
 \noindent
-\Mahmoudd{
 \textbf{Termination of the algorithm.}
@@
 \nu_0(x_0, \Delta),\ldots&,\nu_{N-1}(x_0,\Delta)=\\
-argmin & \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
+\mathrm{argmin} & \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
 \quad  \text{s.t.} \quad & x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
@@
 Assuming the optimization has a unique solution for every $\Delta$, 
-one may use the results on continuity of the $argmin$ function to compute an upper bound on the Lipschitz constant of the optimal input $\nu = \kappa(x)$ in Equation~\eqref{eq:affine_map} that holds for all $\Delta$.
-The computed bound will only depend on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used to evaluate the maximum error over incorrect region selection.
+one may use the results on continuity of the $\mathrm{argmin}$ function to compute an upper bound on the 
+Lipschitz constant of the optimal input $\nu = \kappa(x)$ in Equation~\eqref{eq:affine_map} that holds for all $\Delta$. 
+The computed bound will only depend on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used 
+to evaluate the maximum error over incorrect region selection. 
 This bound can be quite large, leading to a very conservative bound on the maximum number of iterations before convergence. 
-From an experimental point of view, our observations show that using a reasonable $\varepsilon_{SAFE}$, convergence always reached after only a few iterations.}
+From an experimental point of view, our observations show that for our range of parameters $\varepsilon_{\mathit{SAFE}}$, convergence was
+always reached after only a few iterations.
 
@@
 \noindent
-\Mahmoudd{
-\textbf{Computational complexity.} It is shown in \cite{Alessio2009} that the number of regions $P$ in Equation~\eqref{eq:affine_map} is upper bounded by $2^q$, where $q$ is the total number of constraints in \autoref{eq:RMPC_prob}.
-%In theory, one cannot find an upper bound for the maximum number of hyperplanes enclosing a region.
-Assuming that each region has at most $\bar n_f$ hyperplanes, computation of the incorrect region selection error requires at most $i\times\bar n_f\times 2^q$ affine computations, where $i$ denotes the number of times the RMPC design updates $\Delta$ before convergence.
+\textbf{Computational complexity.} 
+It is shown in \cite{Alessio2009} that the number of regions $P$ 
+in Equation~\eqref{eq:affine_map} is upper bounded by $2^q$, where $q$ is the total number of constraints in \autoref{eq:RMPC_prob}.
+Assuming that each region has at most $N$ hyperplanes, computation of the incorrect region selection error requires at 
+most $i\times N\times 2^q$ affine computations, where $i$ denotes the number of times the RMPC design updates $\Delta$ before convergence. 
 In our experiments, the computation of the incorrect region selection error takes only a few minutes for our largest tested benchmarks. 
-%\underline{\textbf{Rocco: What about complexity of Daisy's computations in terms of number of regions $P$ and $n$?}}
-\\
 The complexity of the precision tuning is linear with respect to the number of regions and hyperplanes. 
-So, $(P+\bar n_f\times P)$ is an upper bound for the number of problems we need to encode in Daisy.
-In each encoding, the uniform-precision detection takes linear number of steps before convergence.
+So, $(P+ N\times P)$ is an upper bound for the number of problems we need to encode in Daisy.
+In each encoding, the uniform-precision detection takes linear number of steps \RM{in what parameter?} before convergence. 
 It starts from 1-bit and increases the precision one by one until the first valid configuration. 
-The complexity of mixed-precision tuning with delta-debugging is $n\times log(n)$ in average, and bounded by $n^2$ in the worst case, with $n$ being the number of variables.}
+The complexity of mixed-precision tuning with delta-debugging is $n\times log(n)$ in average, 
+and bounded by $n^2$ in the worst case, where $n$ is the number of variables. \RM{how is $n$ related to the other parameters?}
 

### 2019-07-29 emsoft-2019/camera_ready/Error_Analysis.tex
class is updated into acmsmall
My pass on the final version.

@@
 used in the design of the robust explicit MPC:
-\begin{align}
-  \max\{\|v_{i}-v_{j}\|,\,&\forall i,j,\,\, i\neq j, \mathcal{R}_{i}\cap\mathcal{R}_{j}\neq\emptyset\} \nonumber\\
-  &+  \max\{err(v_{i})_{p},\, i=1,2,\ldots,P\} \le \Delta.
+\begin{equation}
+  \max\{\|v_{i}-v_{j}\|,\,\forall i,j,\,\, i\neq j, \mathcal{R}_{i}\cap\mathcal{R}_{j}\neq\emptyset\} +  \max\{\mathit{err}(v_{i})_{p},\, i=1,2,\ldots,P\} \le \Delta.
   \label{eq:delta}
-\end{align}
+\end{equation}
 %where $i,j$ are the indexes of two distinct regions $\mathcal{R}_{i}$ and $\mathcal{R}_{j}$, 
@@
 $\mathcal R_i,\mathcal R_j$ (two regions are neighboring if their intersection is non-empty).
-The function norm $\|v_{i}-v_{j}\|$ is taken by maximizing over all possible values of the state $x_k$. 
-$err(v_{i})_{p}$ in
-the second term captures the approximation error in the computation of the affine function $v_{i}$ when a fixed precision $p$ is used.
+The function norm $\|v_{i}-v_{j}\|$ is taken by maximizing over all possible values of the state $x_k$ \RM{in $\mathcal{R}_i \cap \mathcal{R}_j$? Or all states?}. 
+The term $\mathit{err}(v_{i})_{p}$ in
+the second part captures the approximation error in the computation of the affine function $v_{i}$ when a fixed precision $p$ is used.
 %$\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})$
@@
 $p$ and can also be called explicitly without the precision optimization.
-\Mahmoudd{To encourage reproducible research, our implementation is made available online.\footnote{\url{https://github.com/rospoly/rmpc-daisy}}}
-\Mahmoudd{\begin{remark}
-	Note that we use MATLAB and Daisy solely for offline computations.
-The output of our algorithm contains (almost) all the information required for implementation of the verified controller over embedded systems.
-Therefore, the same savings can be expected when the controller is implemented on an actual embedded system.
-\end{remark}}
+
+Note that we use MATLAB and Daisy solely for offline computations during the compilation of the controller.
+At runtime, there is no additional cost.
+% The output of our algorithm contains (almost) all the information required for implementation of the verified controller over embedded systems. 
+% Therefore, the same savings can be expected when the controller is implemented on an actual embedded system.
+
+\RM{what about the following commented-out comment of Sadegh?}
 \begin{comment}

### 2019-07-29 emsoft-2019/camera_ready/Motiv.tex
My pass on the final version.

@@
 
-As a smaller example, consider the standard problem of designing a controller for an inverted pendulum depicted in~\autoref{fig:inverted_pendulum}~{(a)}.
+As a simple example, consider the standard problem of designing a controller for an inverted pendulum depicted in~\autoref{fig:inverted_pendulum}~{(a)}.
 The goal of the controller is to keep the pendulum at the vertical position while satisfying hard constraints on the state variables and control inputs.
@@
 linearization and discretization. 
-The parameter $g=9.81 [m/s^2]$ is the gravitational acceleration, $m$ is the ball mass, $b$ is the rotational fraction coefficient, 
+The parameter $g=9.81 [m/s^2]$ is the gravitational acceleration, $m$ is the ball mass, $b$ is the rotational friction coefficient, 
 and $L$ is the length of the bar. 
@@
   \end{subfigure}
-	\caption{(a) Inverted pendulum; (b) 2D plot of polyhedral partitions for an EMPC applied to the inverted pendulum.}
+	\caption{(a) Inverted pendulum; (b) 2D plot of polyhedral partitions for an EMPC for the inverted pendulum.}
 	\label{fig:inverted_pendulum}
@@
 We start by selecting an initial bound $\Delta_0$ on the implementation error and enlarge $\mathcal W$ with $\Delta_0$ as $\mathcal W_{\Delta_0}$, where
+we define
 \begin{equation}\label{eq:W_delta}
@@
 finite number of polyhedral domains together with an affine map for each domain. 
-At each time step, the state vector $x_k$ is read (or estimated) and based on the domain
-that it belongs to, the corresponding control output is computed. 
-However, the polyhedral regions are implemented in finite precision so that
-it is possible that due to quantization errors the domain is selected incorrectly, and therefore
+At each time step, the state vector $(\theta_k, \omega_k)$ is read (or estimated), and based on the polyhedral domain
+that it belongs to, the corresponding affine map is computed as the control output.
+
+Since the polyhedral regions are implemented in finite precision, 
+it is possible that due to quantization errors, the polyhedral domain is selected incorrectly, and therefore
 a different affine map is computed for the control.
 We refer to the resulting error as \emph{incorrect region selection} error.
-% However, due to error by fixed-point implementation, it is possible that the domain is selected
-% incorrectly. This causes an error term which we refer to it as incorrect region
-% selection error.
 In our example, we compute an incorrect region selection error $e = 0.019$, which is larger
@@
 0.998   &0.049
-\end{bmatrix}x_k\leq 
+\end{bmatrix}
+\begin{bmatrix}
+\theta_k\\
+\omega_k
+\end{bmatrix}
+%
+\leq 
 \begin{bmatrix}
@@
 \Rightarrow
-u(x_k)=\begin{bmatrix}
+u(\begin{bmatrix} \theta_k\\ \omega_k \end{bmatrix})=\begin{bmatrix}
 0.05&-9.67
-\end{bmatrix}x_k+4.02%$}
+\end{bmatrix}\begin{bmatrix}\theta_k\\ \omega_k\end{bmatrix} +4.02%$}
 \end{equation*}
-where the output of robust EMPC at state $x_k$ is denoted by $u(x_k)$. 
+where the output of robust EMPC at state $(\theta_k, \omega_k)$ is denoted by $u(\theta_k, \omega_k)$. 
 The remaining mappings have a similar structure.
@@
 
-Next, we use the precision tuning tool Daisy \cite{Daisy} to provide a mixed-precision 
+We can implement the controller using uniform $32$ bit integers, or by selecting a uniform bitwidth.
+These take, respectively, $XX$ and $YY$ bits.
+\RM{how many bits do we need for the uniform prec impl? how many bits for 32 bits?} 
+But we can do better.
+We use the precision tuning tool Daisy \cite{Daisy} to provide a mixed-precision 
 implementation for all the parameters which satisfies the error bound $\Delta_1  - e = 0.05 - 0.019 = 0.031$.
 The mixed-precision implementation returned by Daisy requires $6084$ bits.
-Thus, for this introductory example, the mixed-precision implementation takes about $10\%$ less memory compared 
+Thus, for this example, the mixed-precision implementation takes about $10\%$ less memory compared 
 to the smallest uniform precision implementation that respects $\Delta_1$,
-and about $57\%$ less memory than an implementation that uniformly uses
-32 bits.
+and about $57\%$ less memory than an implementation that uniformly uses 32 bits.
 

### 2019-07-29 emsoft-2019/camera_ready/RMPC_Daisy.tex
My pass on the final version.

@@
 The most straightforward technique is a linear search over all polyhedral regions (Fig.~\ref{lst:caseof}).
-\Mahmoudd{
-\begin{remark}
-	The total time to evaluate the PWA function in \autoref{eq:affine_map} for a given $x_k$ consists of two steps: (a) selecting the region $\mathcal R_i$ such that $x_k\in \mathcal R_i$ and (b) evaluating the corresponding affine map $F_i x_k +G_i$.
-	Evaluating the affine map is straightforward and requires less computational effort compared to the region selection step.
-Direct implementation of region selection (\autoref{lst:caseof}) is simple, but inefficient.
-More efficiency can be achieved by leveraging binary search tree structures (e.g.
-\cite{Mnnigmann:2011}).\\
-	In general, explicit MPC is well-known for its high-speed implementation over embedded systems with low computational power.
-The authors in \cite{Johansen:2007} show that explicit MPCs with hundreds of regions can be implemented on application specific integrated circuits (ASIC) with about $20000$ gates, leading to computation times in the order of $1\mu s$.
-It is shown in \cite{Bemporad:2006} that for typical problems evaluating the explicit MPC takes significantly shorter time in comparison to solving on-line quadratic programs.
-\end{remark}}
+More efficiency can be achieved by using binary search tree structures (e.g., \cite{Mnnigmann:2011}).
 
-\Mahmoudd{ 
- \begin{remark}
- It should be noticed that EMPC is a class of controllers specifically proposed for linear time invariant (LTI) systems.
-To cover nonlinear systems, one approach is to linearize them around an appropriately selected equilibrium point of the system and to model the differences as a bounded disturbance as in \autoref{eq:RMPC_prob}.
-Taking the upper bound over nonlinearities into account will result in enlarging $\Delta$ which characterizes $\mathcal{W}_{\Delta}$.
-For reasonable values of $\Delta$, in principle RMPC design should work successfully.
-Further, it should be noticed that the rest of analysis in the sequel (over MATLAB and Daisy) do not rely on the LTI property of the system under study and could be adjusted for other families of controllers.
- %However, such analysis are beyond the scope of this paper as (perturbed) LTI systems are considered as an important class of dynamical systems.
-\end{remark}}
+% The total time to evaluate the PWA function in \autoref{eq:affine_map} for a given $x_k$ consists of two steps: 
+% (a) selecting the region $\mathcal R_i$ such that $x_k\in \mathcal R_i$ and 
+% (b) evaluating the corresponding affine map $F_i x_k +G_i$.
+% Evaluating the affine map is straightforward and requires less computational effort compared to the region selection step. 
+% Direct implementation of region selection (\autoref{lst:caseof}) is simple, but inefficient.
+
+To keep the implementation cost down, low-end microcontrollers usually have limited computational power and memory. 
+In general, explicit MPC is well-known for its high-speed implementation in embedded systems with low computational power. 
+Johansen et al.~\cite{Johansen:2007} show that explicit MPCs with hundreds of regions can be implemented on application specific integrated circuits (ASIC) 
+with about $20000$ gates, leading to computation times in the order of $1\mu s$. 
+It is shown in \cite{Bemporad:2006} that for typical problems evaluating the explicit MPC takes significantly less
+time in comparison to solving on-line quadratic programs.
+In this paper, we present an approach for minimizing the memory usage of the implementation while satisfying
+the hard constraints on the states, thus ensuring the controllers can be implemented in low-memory microcontrollers.
+
+While we focus on linear time invariant systems, EMPC is also applicable to nonlinear systems by linearization
+around an appropriately selected equilibrium point and modeling the error in the linearization as a disturbance.
+% 
+% It should be noticed that EMPC is a class of controllers specifically proposed for linear time invariant (LTI) systems. 
+% To cover nonlinear systems, one approach is to linearize them around an appropriately selected equilibrium point of the system and 
+% to model the differences as a bounded disturbance as in \autoref{eq:RMPC_prob}. 
+% This results in enlarging $\Delta$ which characterizes $\mathcal{W}_{\Delta}$. 
+% For reasonable values of $\Delta$, in principle RMPC design should work successfully. 
+Note that the rest of our analysis in the sequel (over MATLAB and Daisy) do not 
+rely on the LTI property of the system under study and could be adjusted for other families of controllers
+as long as they are presented as piecewise affine functions.
 
@@
 %Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.
-
-To keep the implementation cost down, low-end microcontrollers usually have
-limited memory and computational power. Therefore, the implementation of the above
-explicit MPC on microcontrollers will bring some issues since all regions'
-matrices ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s) have
-to be stored on the microcontroller. Our paper presents an
-approach for minimizing the memory usage of the implementation while satisfying
-the hard constraints on the states.
-%\section{Finite Precision Implementation}
-%\Sadegh{To be included by Rocco}

### 2019-07-29 emsoft-2019/camera_ready/conclusion.tex
My pass on the final version.

@@
 We have described an automatic technique to tune an explicit MPC
-controller that implements the controller in mixed-precision fixed-point arithmetic
+controller.
+Our technique implements the controller in mixed-precision fixed-point arithmetic
 while ensuring that the resulting loss of precision does not invalidate the
 constraints of the original control problem.
-Our technique models potential fixed-point imprecision explicitly as a disturbance
+We model potential fixed-point imprecision explicitly as a disturbance
 term, and uses robust explicit MPC to design a controller.
@@
 In experiments, we show that our technique can yield significant savings in memory,
-ranging up to 20\%. 
-In addition, the static analysis scales to controllers with hundreds of regions.\\
-One exciting direction for future work would be to investigate the effect of stochastic disturbances on the proposed methodology and find a scheme to reduce statistically the memory footprint of the controller implementation.
+ranging up to 20\% in our experiments. 
+In addition, the static analysis scales to controllers with hundreds of regions.
+One direction for future work would be to investigate the effect of stochastic disturbances on the proposed methodology and find a 
+scheme to statistically reduce the memory footprint of the controller implementation.
 

### 2019-07-29 emsoft-2019/camera_ready/experiments.tex
My pass on the final version.

--- 2019-04-15 emsoft-2019/experiments.tex
@@
 We evaluate a prototype implementation of the algorithm in~\autoref{lst:alg}
-on three examples. For the first two, we apply the complete pipeline (design and memory optimization)
+on three examples.\footnote{
+ Our implementation is available online at \url{https://github.com/rospoly/rmpc-daisy}.
+}
+For the first two, we apply the complete pipeline (design and memory optimization)
 which returns an end-to-end robust controller. With the third example, we evaluate

### 2019-07-29 emsoft-2019/camera_ready/finite_precision.tex
My pass on the final version.

@@
 
-The controller has to be stored and evaluated on a microcontroller in
-finite precision, since infinite-precision real values cannot be stored on
-today's digital computers.
+We now discuss finite-precision issues in the implementation of a controller.
+% The controller has to be stored and evaluated on a microcontroller in finite precision.
+%  since infinite-precision real values cannot be stored on today's digital computers.
 The standard choice for low-power platforms is fixed-point arithmetic. Unlike
@@
 however, more compilation effort to determine certain operations statically at
-compile time (that the floating-point hardware unit performs dynamically).
+compile time that the floating-point hardware unit performs dynamically.
 
@@
 % introduces roundoff errors, these can be tracked with a dataflow analysis
-Finite precision unavoidably introduces roundoff errors, which can accumulate
+Finite precision introduces roundoff errors, which can accumulate
 during the course of a computation.
@@
 error bounds, both the ranges and errors are computed using interval~\cite{intervals} or
-affine arithmetic~\cite{affineArithmetic} which compute sound enclosures. 
+affine arithmetic~\cite{affineArithmetic}, which compute sound enclosures. 
 Affine arithmetic tracks linear correlations between variables, so for linear expressions
@@
 
-In this work, we use the tool Daisy which implements roundoff error
-analysis~\cite{Daisy} and mixed-precision tuning~\cite{DaisyTuning} for fixed-point arithmetic, and is
-available as open-source. Fixed-point arithmetic implementations can choose different
-rounding modes; here we consider truncation, which is more efficient than
-rounding.
+In this work, we use the open-source tool Daisy which implements roundoff error
+analysis~\cite{Daisy} and mixed-precision tuning~\cite{DaisyTuning} for fixed-point arithmetic.
+% and is available as open-source. 
+Fixed-point arithmetic implementations can choose different
+rounding modes; here we consider truncation, which is more efficient than rounding.

### 2019-07-29 emsoft-2019/camera_ready/intro.tex
My pass on the final version.

@@
 
-To the best of our knowledge, our algorithm is the first to automatically and soundly
-synthesize a suitable fixed-point precision for explicit robust MPC controllers,
-and the first to consider mixed-precision in this context.
+In summary, our algorithm automatically and soundly synthesizes a suitable fixed-point mixed-precision implementation
+for explicit robust MPC controllers.
 
@@
 precision implementation on our largest benchmark. 
-%\Mahmoud{It should be noticed that these savings are not affecting the run-time.
-Synthesis of the controller and the corresponding precisions are all performed offline.}
-\Mahmoudd{We note that EMPC is a class of controllers that is mainly appropriate for implementation over processors with limited computational power and memory.
-Typical memory of these processors is in the order of tens of kilobytes (e.g.
-$32$ KB) and hence $21$ KB is considered as a significant saving.
-Also, the memory savings do not affect the run-time since  the controller synthesis and the corresponding mixed precision computations are all performed offline.}\\
+%\Mahmoud{It should be noticed that these savings are not affecting the run-time. Synthesis of the controller and the corresponding precisions are all performed offline.}
+A large class of EMPC applications implement the controller in processors with limited computational power and memory;
+typically,  these processors have memory in the order of tens of kilobytes (e.g., $32$ KB).
+Thus, $21$ KB is a significant saving. 
+Also, the memory savings do not affect the run-time performance 
+since our controller synthesis and the corresponding mixed precision computations are all performed offline.
+
 In summary, our contributions are:

### 2019-07-31 emsoft-2019/camera_ready/Cont_Syn.tex
updates

@@
 Typical values for $\varepsilon_Q$ can range from $10^{-4}$ up to $10^{-2}$. 
-\RM{repetition:}
-Increasing $\varepsilon_Q$ leads to more memory savings over $H$ and $K$ while requiring more precision for $F$ and $G$. 
-\RM{end}
-Of course, a large value for $\varepsilon_Q$ can result in failure of the RMPC design. 
-\RM{imprecise:}However, this is usually not the case over reasonable choices for $\varepsilon_Q$.
-\RM{omit?}
+%\RM{repetition:}
+%Increasing $\varepsilon_Q$ leads to more memory savings over $H$ and $K$ while requiring more precision for $F$ and $G$. 
+%\RM{end}
+%Of course, a large value for $\varepsilon_Q$ can result in failure of the RMPC design. 
+%\RM{imprecise:}However, this is usually not the case over reasonable choices for $\varepsilon_Q$.
+%\RM{omit?}
 Line 5 computes the width of the tubes $\varepsilon$ as shown in~\autoref{eq:epsilontot},
@@
 So, $(P+ N\times P)$ is an upper bound for the number of problems we need to encode in Daisy.
-In each encoding, the uniform-precision detection takes linear number of steps \RM{in what parameter?} before convergence. 
-It starts from 1-bit and increases the precision one by one until the first valid configuration. 
+In each encoding, the uniform-precision detection %takes linear number of steps \RM{in what parameter?} before convergence. 
+%It 
+starts from 1-bit and increases the precision one by one until the first valid configuration. 
 The complexity of mixed-precision tuning with delta-debugging is $n\times log(n)$ in average, 

### 2019-08-01 emsoft-2019/camera_ready/Cont_Syn.tex
Took out the paragraph on compkexity.
updates

@@
  assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
- $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@$\quad$//\,\,width of the tube@>
+ <@\textcolor{blue}{$\varepsilon$ = $\max_i \{||F_i||_2\}\varepsilon_{A/D}+\varepsilon_{Q}$}@>$\quad$//width of the tube
 

### 2019-08-01 emsoft-2019/camera_ready/Error_Analysis.tex
updates

@@
 $\mathcal R_i,\mathcal R_j$ (two regions are neighboring if their intersection is non-empty).
-The function norm $\|v_{i}-v_{j}\|$ is taken by maximizing over all possible values of the state $x_k$ \RM{in $\mathcal{R}_i \cap \mathcal{R}_j$? Or all states?}. 
+The function norm $\|v_{i}-v_{j}\|$ is taken by maximizing over all possible values of the state $x$ %\RM{
+in $\mathcal{R}_i \cap \mathcal{R}_j$. %}
 The term $\mathit{err}(v_{i})_{p}$ in
@@
  %That is, with infinite-precision arithmetic
+ Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
+ the expanded borders:
+ \begin{equation}
+ \label{eq:maximization}
+ \max_{x,i,j}\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}.
+% \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
+ \end{equation}
+ %%%%%%%%%%%%%%
+ \subsection{Incorrect Region Selection}
+ 	The first part of the error in~\autoref{eq:delta} captures the error due to
+ 	selecting of the incorrect region.
+ 	This would happen since the matrices $H_i,K_i$ are stored in the hardware with fixed-point formats.
+In order to quantify the error, we define the expanded border $\bar{\mathcal B}_{ij}$ as the tube around the border between the regions $\mathcal{R}_i$ and $\mathcal{R}_j$:
+ 	\begin{equation*}
+ 	\bar{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
+ 	\end{equation*}
+ 	where $\varepsilon$ captures the uncertainty in computing the correct region.
+ 	%
+ 	The width of the tube $\varepsilon$ is due to two sources of errors:
+ 	\Mahmoud{\begin{itemize}
+ 		\item analog-to-digital conversion $\varepsilon_{A/D}$: using the quantized output of the analog-to-digital converter $\hat x$ instead of the actual state $x$.
+We assume $\|x - \hat x\|\le \varepsilon_{A/D}$.
+ 		\item quantization of region
+ 		bounds in memory $\varepsilon_{Q}$: using $\hat H_i,\hat K_i$ which are the quantized versions of $H_i,K_i$ with $p$ bits precision. This is related to the boundaries of the regions.
+ 		%\item using $\hat F_i,\hat G_i$ which are the quantized versions of $F_i,G_i$ with $p$ bits precision. This is related to the affine functions.
+ 	\end{itemize}
+ 	Note that the error resulted from using the quantized versions of $F_i,G_i$ is discussed in \autoref{subsec:app_cont_err}.
+ 	 %We denote to controllers $\kappa(\mathcal H,x)$ and $\kappa(\mathcal{\hat H},\hat)$ to distinguish between the case that fixed point representation is used or not.
+ 	We define the fixed point realization of the controller in \autoref{eq:affine_map} as:
+ 	 	\begin{equation}
+ 	 	\label{eq:affine_map_hat}
+ 	 	\hat\kappa(\hat x_k)=
+ 	 	\begin{cases}
+ 	 	\hat F_1\hat x_k+\hat G_1 & \text{if $\hat x_k\in \mathcal{\hat R}_1$}\\
+ 	 	\hat F_2\hat x_k+\hat G_2 & \text{if $\hat x_k\in \mathcal{\hat R}_2$}\\
+ 	 	\vdots\\
+ 	 	\hat F_P x_k+\hat G_P & \text{if $ \hat x_k\in \mathcal{\hat R}_P$}
+ 	 	\end{cases} 
+ 	 	\end{equation}
+ 	 	where $\mathcal{\hat R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal{\hat R}_i= \{ \hat x\in\mathcal X\,|\, \hat H_i\hat x\leq \hat K_i\}$.
+Let us also define the sets $\mathcal H := \{H_i,K_i,i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i,i=1,2,\ldots, P\}$.
+Similarly, we define $\hat{\mathcal H}:= \{\hat H_i,\hat K_i,i=1,2,\ldots, P\}$ and $\hat{\mathcal F}:=\{\hat F_i,\hat G_i,i=1,2,\ldots, P\}$.
+Using the triangle inequality we have:
+ 	 	\begin{align*}
+ 	 	\|\kappa(x)-\hat \kappa(\hat x)
+ 	 	\|\le&\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
+ 	 	+&\|\kappa(\hat{\mathcal H},\mathcal F,\hat x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)\|.
+ 	 	\end{align*}
+ 	 	where $\kappa(\mathcal H^*,\mathcal F^*,x^*)$ denotes the controller defined over the sets $\mathcal F^*$, $\mathcal H^*$ and the state $x^*$.
+The second term corresponds to the control approximation error and will be discussed in \autoref{subsec:app_cont_err}.
+ 	 	The first term can be further decomposed as
+ 	 	\begin{align*}
+ 	 	\|\kappa(\mathcal H,&\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
+ 	 	&\le \|\kappa(\mathcal H,\mathcal F,x)-\kappa(\mathcal H,\mathcal F,\hat x)\|+
+ 	 	\|\kappa(\mathcal H,\mathcal F,\hat x) - \kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
+ 	 	&\le \max_i\{\|F_i\|_2\}\|x-\hat x\| + \varepsilon_Q\\
+ 	 	& \le \max_i\{\|F_i\|_2\}\varepsilon_{A/D}+ \varepsilon_Q.
+ 	 	\end{align*}
+ 	 	Therefore, we can compute the tube width $\varepsilon$ as:
+ 	 	\begin{equation}\label{eq:epsilontot}
+ 	 	\varepsilon=\max_i \{||F_i||_2\}\varepsilon_{A/D}+\varepsilon_{Q}
+ 	 	\end{equation}
+ 	}
+% 	\Mahmoud{We define the fixed point realization of the controller in \autoref{eq:affine_map} as:
+% 	\begin{equation}
+% 	\label{eq:affine_map_hat}
+% 	\hat\kappa(\hat x_k)=
+% 	\begin{cases}
+% 	\hat F_1\hat x_k+\hat G_1 & \text{if $\hat x_k\in \mathcal{\hat R}_1$}\\
+% 	\hat F_2\hat x_k+\hat G_2 & \text{if $\hat x_k\in \mathcal{\hat R}_2$}\\
+% 	\vdots\\
+% 	\hat F_P x_k+\hat G_P & \text{if $ \hat x_k\in \mathcal{\hat R}_P$}
+% 	\end{cases} 
+% 	\end{equation}
+% 	where $\hat x_k$ denotes the output of the analog-to-digital converter corresponding to the input $x_k$.
+Further, $\hat F_i, \hat G_i$ denote the fixed point representations corresponding to $F_i, G_i$ and $\mathcal{\hat R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal{\hat R}_i= \{ \hat x\in\mathcal X\,|\, \hat H_i\hat x\leq \hat K_i\}$.}
+%
+%	\Mahmoud{Let us define the sets $\mathcal H := \{H_i,K_i,i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i,i=1,2,\ldots, P\}$.
+Similarly, we define $\hat{\mathcal H}:= \{\hat H_i,\hat K_i,i=1,2,\ldots, P\}$ and $\hat{\mathcal F}:=\{\hat F_i,\hat G_i,i=1,2,\ldots, P\}$, where $\hat F_i$, $\hat G_i$, $\hat H_i$ and $\hat K_i$ denote the fixed point representations corresponding to $F_i$, $G_i$, $H_i$ and $K_i$, respectively.
+}
+%
+% 	\begin{equation}\label{eq:epsilontot1}
+% 	\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
+% 	\end{equation}
+ 	%
+ 	%
+ 	Analog conversion happens just before the controller receives the sensor input from the plant
+ 	and is given by:
+ 	\begin{equation*}
+ 	\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
+ 	\end{equation*}
+ 	where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
+ 	is the number of bits available to quantize the analog signal, and $2^{r}$ is
+ 	the resolution of the converter.\\
+ 	While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
+ 	$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
+ 	\begin{equation}\label{eq:quantizationlines}
+ 	\varepsilon_{Q} \ge  \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|, \quad \forall \hat{x},\forall i,
+ 	\end{equation}
+ 	where $\hat{x}$ is the finite-precision value of $x$.
+ 	%\eva{For which index is this evaluated, $i$, $j$ or both?}
+ 	That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
+ 	precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
+ 	($\hat{H}_{p}$ and $\hat{K}_{p}$).
+ 	This second error can be tuned providing a trade-off between accuracy and
+ 	memory storage required.
  	Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
@@
 \subsection{Approximate Control Output}
+\label{subsec:app_cont_err}
 

### 2019-08-01 emsoft-2019/camera_ready/Motiv.tex
updates

@@
 		node distance=1cm] (delta) {$\Delta=e+\varepsilon_{SAFE}$};
-		\node [block1,below = 0.8cm of done] (output) {Low-precision controller (\autoref{eq:affine_map})};
+		\node [block1,below = 0.8cm of done] (output) {Low-precision controller (\Mahmoud{\autoref{eq:affine_map_hat}})};
 		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
@@
 We can implement the controller using uniform $32$ bit integers, or by selecting a uniform bitwidth.
-These take, respectively, $XX$ and $YY$ bits.
-\RM{how many bits do we need for the uniform prec impl? how many bits for 32 bits?} 
+These take, respectively, $13824$ and $6744$ bits.
+%\RM{how many bits do we need for the uniform prec impl? how many bits for 32 bits?} 
 But we can do better.

### 2019-08-01 emsoft-2019/camera_ready/Error_Analysis.tex
Small modifications.

@@
  	\Mahmoud{\begin{itemize}
- 		\item analog-to-digital conversion $\varepsilon_{A/D}$: using the quantized output of the analog-to-digital converter $\hat x$ instead of the actual state $x$.
+ 		\item analog-to-digital conversion $\varepsilon_{A/D}$: 
+		the error introduced by using the quantized output of the analog-to-digital converter $\hat x$ instead of the actual state $x$. 
 		We assume $\|x - \hat x\|\le \varepsilon_{A/D}$.
- 		\item quantization of region
- 		bounds in memory $\varepsilon_{Q}$: using $\hat H_i,\hat K_i$ which are the quantized versions of $H_i,K_i$ with $p$ bits precision. This is related to the boundaries of the regions.
+ 		\item quantization of region bounds in memory $\varepsilon_{Q}$: the error introduced by 
+		using the quantized versions $\hat H_i$, $\hat K_i$ of $H_i$, $K_i$ with $p$ bits of precision. 
+		This is related to the boundaries of the regions.
  		%\item using $\hat F_i,\hat G_i$ which are the quantized versions of $F_i,G_i$ with $p$ bits precision. This is related to the affine functions.
  	\end{itemize}
- 	Note that the error resulted from using the quantized versions of $F_i,G_i$ is discussed in \autoref{subsec:app_cont_err}.
- 	 %We denote to controllers $\kappa(\mathcal H,x)$ and $\kappa(\mathcal{\hat H},\hat)$ to distinguish between the case that fixed point representation is used or not.
+ 	Note that the error resulting from using the quantized versions of $F_i,G_i$ will be discussed in \autoref{subsec:app_cont_err}.
  	We define the fixed point realization of the controller in \autoref{eq:affine_map} as:
@@
  	 	\end{equation}
- 	 	where $\mathcal{\hat R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal{\hat R}_i= \{ \hat x\in\mathcal X\,|\, \hat H_i\hat x\leq \hat K_i\}$.
-Let us also define the sets $\mathcal H := \{H_i,K_i,i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i,i=1,2,\ldots, P\}$.
-Similarly, we define $\hat{\mathcal H}:= \{\hat H_i,\hat K_i,i=1,2,\ldots, P\}$ and $\hat{\mathcal F}:=\{\hat F_i,\hat G_i,i=1,2,\ldots, P\}$.
+ 	 	where $\mathcal{\hat R}_i$ is a polyhedral region determined by a set of linear inequalities 
+$\mathcal{\hat R}_i= \{ \hat x\in\mathcal X\mid \hat H_i\hat x\leq \hat K_i\}$. 
+Let us define the sets $\mathcal H := \{H_i,K_i\mid i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i \mid i=1,2,\ldots, P\}$. 
+Similarly, we define $\hat{\mathcal H}:= \{\hat H_i,\hat K_i\mid i=1,2,\ldots, P\}$ and $\hat{\mathcal F}:=\{\hat F_i,\hat G_i\mid i=1,2,\ldots, P\}$. 
 Using the triangle inequality we have:
@@
  	 	\|\kappa(x)-\hat \kappa(\hat x)
- 	 	\|\le&\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
- 	 	+&\|\kappa(\hat{\mathcal H},\mathcal F,\hat x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)\|.
+ 	 	\|\le&\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\| +\|\kappa(\hat{\mathcal H},\mathcal F,\hat x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)\|.
  	 	\end{align*}
  	 	where $\kappa(\mathcal H^*,\mathcal F^*,x^*)$ denotes the controller defined over the sets $\mathcal F^*$, $\mathcal H^*$ and the state $x^*$. 
-The second term corresponds to the control approximation error and will be discussed in \autoref{subsec:app_cont_err}.
+	The second term on the right corresponds to the control approximation error and will be discussed in \autoref{subsec:app_cont_err}.
  	 	The first term can be further decomposed as

### 2019-08-01 emsoft-2019/camera_ready/Cont_Syn.tex
last updates

--- 2019-07-31 emsoft-2019/camera_ready/Cont_Syn.tex
@@
  assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
- $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@$\quad$//\,\,width of the tube@>
+$\varepsilon$ = $\max_i \{||F_i||_2\}\varepsilon_{A/D}+\varepsilon_{Q}$$\quad$//width of the tube
 
@@
 implementing robust MPC controllers with guaranteed error bounds.
-
 Given a state-space model of a plant (line 1), our algorithm returns four matrices
@@
 This bound can be quite large, leading to a very conservative bound on the maximum number of iterations before convergence. 
-From an experimental point of view, our observations show that for our range of parameters $\varepsilon_{\mathit{SAFE}}$, convergence was
+From an experimental point of view, our observations show that for reasonable range of parameters, convergence was
 always reached after only a few iterations.
 
+\begin{comment}
+\RM{I took out the following section because it was too hacky. The complexity should be given in terms of the original
+problem input, but we keep inventing new parameters. Also, $n$ below in the complexity of mixed precision tuning doesn't make
+sense. In case we bring this back, it should be fixed.}
 \smallskip
@@
 
-% In case the conditional in line 9 succeeds, the precision tuning phase starts.
-The way we do the precision tuning is the following: we provide in input to Daisy a numerical error-bound together with an expression to quantize (e.g.
-an activation function).
-Daisy returns in output both the minimal-uniform precision, and the mixed-precision configuration, such that the quantization of the expression in the given precision configuration introduces an error that is bounded by the input error.
-
-% In line 10 we compute the error bound for approximate control output error.
-This is going to be the maximal error we tolerate for activation functions.
-The precision tuning at line 11 receives in input the approximation control error together with the coefficients F and G.
-In Line 12 we give to Daisy the error $\varepsilon$ for borders, together with the hyperplanes coefficients H and K.
-
-%\eva{The precision tuning, which is the main contribution of the paper is not explained.}
+\end{comment}
 

### 2019-08-01 emsoft-2019/camera_ready/Error_Analysis.tex
last updates

@@
 
-\subsection{Incorrect Region Selection}
-
-The first part of the error in~\autoref{eq:delta} captures the error due to
-selecting of the incorrect region.
-This would happen since the matrices $H_i,K_i$ are stored in the hardware with fixed-point formats.
+%\subsection{Incorrect Region Selection}
+%
+%The first part of the error in~\autoref{eq:delta} captures the error due to
+%selecting of the incorrect region.
+%This would happen since the matrices $H_i,K_i$ are stored in the hardware with fixed-point formats.
 In order to quantify the error, we define the expanded border $\bar{\mathcal B}_{ij}$ as the tube around the border between the regions $\mathcal{R}_i$ and $\mathcal{R}_j$:
-% \begin{equation*}
-% \bar{\mathcal R}_i := \bigcup_{\hat H_i,\hat K_i} \left\{x\in\mathbb R^n\,|\,\hat H_i x\le \hat K_i, \|H_i-\hat H_i\|\le \epsilon_f,\|K_i-\hat K_i\|\le \epsilon_f\right\}
-% \end{equation*}
-% for $i\in\{1,2,\ldots, P\}$, where $\epsilon_f$ is the maximum error of using fixed-point format instead of the precise values. The norm is also applied element-wise to the entries of the matrices.
-
-\begin{equation*}
-\bar{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
-\end{equation*}
-where $\varepsilon$ captures the uncertainty in computing the correct region.
+%% \begin{equation*}
+%% \bar{\mathcal R}_i := \bigcup_{\hat H_i,\hat K_i} \left\{x\in\mathbb R^n\,|\,\hat H_i x\le \hat K_i, \|H_i-\hat H_i\|\le \epsilon_f,\|K_i-\hat K_i\|\le \epsilon_f\right\}
+%% \end{equation*}
+%% for $i\in\{1,2,\ldots, P\}$, where $\epsilon_f$ is the maximum error of using fixed-point format instead of the precise values.
+The norm is also applied element-wise to the entries of the matrices.
 %
-The width of the tube $\varepsilon$ is due to two sources of errors:
-analog-to-digital conversion $\varepsilon_{A/D}$ and the quantization of region
-bounds in memory $\varepsilon_{Q}$:
-\begin{equation}\label{eq:epsilontot}
-  \varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
-\end{equation}
-
-Analog conversion happens just before the controller receives the sensor input from the plant
-and is given by:
-\begin{equation*}
-\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
-\end{equation*}
-where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
-is the number of bits available to quantize the analog signal, and $2^{r}$ is
-the resolution of the converter.
-
-While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
-$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
-\begin{equation}\label{eq:quantizationlines}
-  \varepsilon_{Q} \ge  \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|, \quad \forall \hat{x},\forall i,
-\end{equation}
-where $\hat{x}$ is the finite-precision value of $x$.
-%\eva{For which index is this evaluated, $i$, $j$ or both?}
-That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
-precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
-($\hat{H}_{p}$ and $\hat{K}_{p}$).
-This second error can be tuned providing a trade-off between accuracy and
-memory storage required.
-
-% Note that $\mathcal R_i\subset \bar{\mathcal R}_i$. In other words, $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$.
-% Note that $\bar{\mathcal R}_i\cap \bar{\mathcal R}_j$ gives us the states where one of the two regions $\mathcal R_i, \mathcal R_i$ might be selected instead of the other one because of the fixed-precision implementation of the regions.
-% $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$ that include all states in $\mathcal R_i$this definition expands the regions $\mathcal $
- %That is, with infinite-precision arithmetic
- Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
- the expanded borders:
- \begin{equation}
- \label{eq:maximization}
- \max_{x,i,j}\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}.
-% \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
- \end{equation}
+%\begin{equation*}
+%\bar{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
+%\end{equation*}
+%where $\varepsilon$ captures the uncertainty in computing the correct region.
+%%
+%The width of the tube $\varepsilon$ is due to two sources of errors:
+%analog-to-digital conversion $\varepsilon_{A/D}$ and the quantization of region
+%bounds in memory $\varepsilon_{Q}$:
+%\begin{equation}\label{eq:epsilontot}
+%  \varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
+%\end{equation}
+%
+%Analog conversion happens just before the controller receives the sensor input from the plant
+%and is given by:
+%\begin{equation*}
+%\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
+%\end{equation*}
+%where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
+%is the number of bits available to quantize the analog signal, and $2^{r}$ is
+%the resolution of the converter.
+%
+%While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
+%$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
+%\begin{equation}\label{eq:quantizationlines}
+%  \varepsilon_{Q} \ge  \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|, \quad \forall \hat{x},\forall i,
+%\end{equation}
+%where $\hat{x}$ is the finite-precision value of $x$.
+%%\eva{For which index is this evaluated, $i$, $j$ or both?}
+%That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
+%precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
+%($\hat{H}_{p}$ and $\hat{K}_{p}$).
+%This second error can be tuned providing a trade-off between accuracy and
+%memory storage required.
+%
+%% Note that $\mathcal R_i\subset \bar{\mathcal R}_i$. In other words, $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$.
+%% Note that $\bar{\mathcal R}_i\cap \bar{\mathcal R}_j$ gives us the states where one of the two regions $\mathcal R_i, \mathcal R_i$ might be selected instead of the other one because of the fixed-precision implementation of the regions.
+%% $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$ that include all states in $\mathcal R_i$this definition expands the regions $\mathcal $
+% %That is, with infinite-precision arithmetic
+% Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
+% the expanded borders:
+% \begin{equation}
+% \label{eq:maximization}
+% \max_{x,i,j}\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}.
+%% \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
+% \end{equation}
  %%%%%%%%%%%%%%
@@
  	The width of the tube $\varepsilon$ is due to two sources of errors:
- 	\Mahmoud{\begin{itemize}
+ 	\begin{itemize}
  		\item analog-to-digital conversion $\varepsilon_{A/D}$: 
@@
  	Note that the error resulting from using the quantized versions of $F_i,G_i$ will be discussed in \autoref{subsec:app_cont_err}.
- 	We define the fixed point realization of the controller in \autoref{eq:affine_map} as:
+ 	We define the fixed point realization of the controller in \autoref{eq:affine_map} as
  	 	\begin{equation}
@@
  	 	\vdots\\
- 	 	\hat F_P x_k+\hat G_P & \text{if $ \hat x_k\in \mathcal{\hat R}_P$}
+ 	 	\hat F_P x_k+\hat G_P & \text{if $ \hat x_k\in \mathcal{\hat R}_P$}.
  	 	\end{cases} 
@@
  	 	\begin{equation}\label{eq:epsilontot}
- 	 	\varepsilon=\max_i \{||F_i||_2\}\varepsilon_{A/D}+\varepsilon_{Q}
+ 	 	\varepsilon=\max_i \{||F_i||_2\}\varepsilon_{A/D}+\varepsilon_{Q}.
  	 	\end{equation}
- 	}
+
 % 	\Mahmoud{We define the fixed point realization of the controller in \autoref{eq:affine_map} as:
@@
  	precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
- 	($\hat{H}_{p}$ and $\hat{K}_{p}$).
+ 	($\hat{H}$ and $\hat{K}$).
  	This second error can be tuned providing a trade-off between accuracy and
@@
 
-The incorrect region error (\autoref{eq:maximization}) is computed with Matlab.
-
-Since $v_{i}-v_{j}$ is also affine, and because we defined the tube as a convex region 
+The incorrect region error (\autoref{eq:maximization}) is computed with Matlab. Since $v_{i}-v_{j}$ is also affine, and because we defined the tube as a convex region 
 surrounding the corresponding hyperplane, it suffices
@@
 regions which share those corner points. 
-Each region $R_i$ is represented by a set of contraints. We first extract the
+Each region $R_i$ is represented by a set of constraints. We first extract the
 set of vertices of $R_i$ using the open source Matlab library
@@
 
-\RM{what about the following commented-out comment of Sadegh?}
+%\RM{what about the following commented-out comment of Sadegh?}
 \begin{comment}
